### 2015-01-29 article.tex
rename proof.tex to article.tex, add pdf

\documentclass[12pt, a4paper]{article}

\usepackage{amsfonts}
\usepackage{amsmath}

\usepackage[all]{xy}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% le set avoid 231,213
\newcommand{\C}[1]{A_{#1}(231,213)}

% le set de toutes les permitaton
\newcommand{\Perm}[1]{\mathcal{S}_{#1}}

% permutation text
\newcommand{\ptext}{\pi}

% permutation motif
\newcommand{\pmotif}{\sigma}

\newcommand{\x}{X}
\newcommand{\y}{Y}
\newcommand{\bmotif}{(\sigma,\x,\y)}

% compteur pour les proposition, definition etc...
\newcounter{num}
\setcounter{num}{0}
\newcommand{\num}{\stepcounter{num} }
\newcommand{\numl}[1]{\refstepcounter{num}\label{#1}}

%downstep
\newcommand{\dstep}{d}

%upstep
\newcommand{\ustep}{u}

\title{Pattern matching for (231,231) avoiding permutations}
\author{Both Emerite NEOU, Romeo RIZZI}
\date{}

\begin{document}
	\maketitle 
	\tableofcontents

	\abstract{
	  	Given two permutations, 
	  	a text $\ptext$ 
	  	and a motif $\pmotif$,
	  	the \textbf{permutation pattern problem}
	  	asks if there exists a normalized subsequence of $\ptext$
	  	which equals $\pmotif$.
	  	We study this problem for the permutation 
	  	avoiding (231,231).

	}

	\section{Introduction}

%	The permutation pattern problem asks if there exists a normalized subsequence of a text $\ptext$ which equals to a motif $\pmotif$.
%	If so we write $\pmotif \preceq \ptext$.
%	If not we say that $\ptext$ \textbf{avoid} $\pmotif$.
%	This was first introduced by Knuth \cite{Knuth:1997:ACP:260999}
%	who proves that permutation sortable by stacks
%	avoid the motif $231$. 
%	The problem is NP-hard in general,
%	but for some classes of permutation,
%	polynomial time solution exists.
%	For instance the separable permutation \cite{Bose93patternmatching}.
%	We contribute studying this problem 
%	and related one for the class of permutation avoiding (231,213). 
%	This is interesting because this class is in linear bijection between the classes of (123,132),(132,213) and (132,213)
%	avoiding permutation, and all the classes obtainable by reversal or/and
%	complementation (see \cite{Simion1985383}).\\
%	 
%
%	
%	This paper is organized as follows.
%	Section 2 presents the needed definition.
%	Section 3 solves the permutation pattern problem with
%	(213,231) avoiding permutations.
%	Section 4 focus on the problem the
%	related problem of computing a longest permutation avoiding (213,231).
%	Finally, section 5 summarizes 
%	results for related problems.

	\section{Definition}

		This section presents the decomposition used and some notation.\\

		We denote by $A_{n}(m_1,m_2)$ the class
		of permutation of size $n$ which avoid 
		the motif $m_1$ and $m_2$. 
		$\Perm{n}$ the permutation of size $n$.
		$[n]$ the set $\{1,2,...,n\}.$
		For a permutation p, let $p[i:j]$, 
		be the permutation from element $i$ to $j$,
		$p[:j]$ be the prefix ending at index $j$
		and $p[i:]$ be the suffix starting at index $i$.\\

		Given two permutations
		$\pmotif$ and $\ptext$
		we say that $\pmotif$
		is a motif/match of
		$\ptext$,
		if and only if
		there exists 
		and increasing function 
		$\sigma:[|\pmotif|]->[|\pmotif|]$
		such that : $\forall i$ and 
		$\forall j$ $i,j \in |\pmotif| $
		if $\pmotif(i)<\pmotif(j)$
		then $\ptext(\sigma(i))<\ptext(\sigma(j))$.\\

		%\subsection{Stripe}

		A \textbf{Stripe} of a permutation
		 is a mapping into \textbf{up step} (noted $\ustep$) 
		or a \textbf{down step} (noted $\dstep$).
		An element $i$ of a permutation $p$ is an up step if and only if $i$ is not the last element and $p(i)<p(i+1)$.
		An element $i$ of a permutation $p$ is a down step if and only if $i$ is not the last element and $p(i)>p(i+1)$.	
		By convention the last element is mapped as the second to last element.\\ 	
		Formally a Stripe is a function $\mathcal{S} : \Perm{n},[n] \to \{\dstep,\ustep\}$ define as :\\
		$ \mathcal{S}(p,i) = \left\{ 
		  \begin{array}{l l}
		    \ustep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)>0$ }\\
		    \dstep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)<0$ }\\
		     \mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
		  \end{array} \right. $\\

		By extension we define  $\mathcal{S} : \Perm{n} \to \{\dstep,\ustep\}^{n}$ such as :
		$\mathcal{S}(p)=\mathcal{S}(p,1)\mathcal{S}(p,2)...\mathcal{S}(p,n)$.
		We call $\mathcal{S}(p)$ the stripe of $p$.
		For example the stripe of the permutation $(12,11,10,1,2,3,4,9,8,5,6,7)$, 
		is $\dstep,\dstep,\dstep,\ustep,\ustep,\ustep,\ustep,\dstep,\dstep,\ustep,\ustep,\ustep$.\\

%		\textbf{Corollary \num} The stripe function
%		for $\C{n}$ are in bijection with with $\{\ustep,\dstep\}^{n-1}$.\\

%		\textbf{Proposition \numl{updown}} Let $p \in \C{n}$,
%		$\forall x,y \in [n]$, 
%		$\mathcal{S}(p,x)=\ustep$
%		and $\\mathcal{S}(p,y)=\dstep$
%		then $p(x)<p(y)$.\\

		Formally we say that the stripe of $\pmotif \in \Perm{m}$ is a motif
		of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
		such that : \\
		$\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
		If a stripe $R_2$ is a motif of a stripe $R_1$,
		it means that there exists
		a subsequence of $R_1$ such as
		this sequence is equal to $R_2$.
%		We say that a set is a match 
%		if and only if there exists a function such as define above
%		and the set is the set of image of this function.\\
		For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1,\ustep_2)$ is a motif of  the stripe \\
		$(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$ ,
		because we can match \\
		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4)$ and $(\ustep_1,\ustep_2)$ to 
		$(\ustep_5,\ustep_6)$.
		\begin{figure}[h!]
			\begin{displaymath}
				\xymatrix@=0.3cm{
					\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]& \ustep_2 \ar[ddrrrrr]  \\
					\\
					\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 & \ustep_7 & \\
				}
			\end{displaymath}     
		\end{figure}		
		But the stripe $(\dstep,\ustep,\dstep,\dstep,\dstep)$ is not a motif of the stripe\\ $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$.\\

		A \textbf{bivincular motif} generalize
		a motif. 
		A bivincular motif allows 
		to force element to be adjacent in position
		or/and in value.
		A bivincular motif
		is a motif with two set $\bmotif$,
		the first set contains the first index 
		of two consecutive index
		and the second set contains the first index
		of the two consecutive elements.
		Formally, Let $\bmotif$ 
		be a bivincular motif 
		and $\ptext$ a permutation.
		if $i \in \x$,
		and $i$ is matched with $j$ in $\ptext$
		then $i+1$ must be matched with $j+1$,
		with the special case of $0$ and $|\pmotif|$ :
		$0 \in \x$ then the first element of $\pmotif$
		must be matched with the first element of $\ptext$,
		and $|\pmotif| \in \x$ then the last element of $\pmotif$
		must be matched with the last element of $\ptext$.
		if $i \in \y$,
		and $i$ is matched with $j$ in $\ptext$
		then $i+1$ must be matched with $l$
		such as $\ptext(l)=\ptext(j)+1$,
		with the special case of $0$ and $|\pmotif|$ :
		$0 \in \y$ then the minimal element of $\pmotif$
		must be matched with the minimal element of $\ptext$,
		and $|\pmotif| \in \y$ then the maximal element of $\pmotif$
		must be matched with the maximal element of $\ptext$.

	\section{Pattern Matching Problem With Text and Motif Avoiding (231,213)}

		In this section we focus 
		on the problem of pattern matching if
		both the motif and the text
		avoid (231,213).
		We first exhibit some properties of a stripe 
		of a permutation avoiding (231,213).\\

		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\C{n}$ 
		then the first element is either
		the minimal or the maximal element.\\

		\textbf{Proof} Suppose that we have
		$p \in \mathcal{S}_{n}$, and
		$p(1) \neq 1 $ and $p(1) \neq n$ then we have either
		$p(1) ... n ... 1$ or $p(1) ... 1 ... n $, either the motif 231 or 213, which is not possible by hypothesis. $\Box$\\

		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\C{n}$ if and only if for $1 \leq i \leq n$ 
		$p[i:]$ start either with the maximal element
		or the minimal element of $p[i:]$.\\

		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \C{n}$ its stripe can be define such as, \\
		$\mathcal{S}(p,i) = \left\{ 
  		\begin{array}{l l}
   			\ustep & \quad \text{if $p(i)$ is the minimal element of $p[i:]$}\\    
   			\dstep & \quad \text{if $p(i)$ is the maximal element of $p[i:]$}\\
  		 	\mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
	 	\end{array} \right. 
	 	$\\

		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \C{n}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		$\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)<p(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
		if $i$ is a up step and
		if $j$ is a down step
		then $p(i)<p(j)$.\\

		\textbf{Proof} By induction on the size of the permutation :
		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
		Suppose the proposition true for $\C{n}$.
		Let $p \in \C{n+1}$, 
		we show that the proposition holds for $p$.
		Let $p'$ be the permutation $p[2:]$.
		$p' \in \C{n}$, so
		every element of $p'$ verify our lemma (by induction).
		We still need to compare the first element with the rest.
		Except that the first element
		is the maximal (minimal) element of all the permutation 
		(by Lemma \ref{firstelement}).
		Moreover if the first element is the maximal (minimal)
		it will mapped to an down step (up step).
		So the proposition is also true
		for the first element.
		$\Box$\\

		\textbf{Lemma \numl{upup} \thenum} Let $p \in \C{n}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		$\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\ustep$
		then $p(i)<p(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
		if $i$ is a up step 
		and $j$ is a up step
		and $ i<j$
		then $p(i)<p(j)$.\\

		%\textbf{Proof} Same as before.\\

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an down step (up step).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \C{n}$,
		$\forall i,j \in [n]$,
		$i<j$,
		$\mathcal{S}(p,i)=\dstep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)>p(j)$.\\

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
		if $i$ is a down step
		and $j$ is a down step
		and $ i<j$
		then $p(i)>p(j)$.\\

		%\textbf{Proof} Same as before.\\

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an down step (up step).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \C{n}$.
		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.\\

		\textbf{Proof} \\
		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
		by subsequence $s$.
		By definition $s$ normalized is equal to
		$\pmotif$ so they have the same stripe.\\ 
		$\Leftarrow$ 
		Let $\ptext \in \Perm{n}$, 
		$R_1$ be is stripe, 
		$\pmotif \in \Perm{m}$
		and $R_2$ is stripe.
		Let $\phi$ be the function
		that match $R_2$ to $R_1$.
		We define $\varphi$ as, 
		$\forall x \in [m]$,
		$\varphi(x) = \phi(x)$.
		Suppose\\ $\exists x,y \in [|\pmotif|], \text{ $\pmotif(x)<\pmotif(y)$ 
		and $\ptext(\varphi(x))>\ptext(\varphi(y))$ }$,
		without lost of generality we can suppose that $x<y$
		But :
		\begin{itemize}

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			(if x and y are increasing in $\pmotif$),
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			(the match are also increasing).
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{upup}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{downdown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			which contradict our hypothesis,
			so this case is not possible.$\Box$

		\end{itemize}
		So this is not possible. $\Box$\\

		\textbf{Proposition  \num \thenum} Let $\pmotif$ and $\ptext$
		be two permutations avoiding (231,213), 
		we can decide in linear time if $\pmotif$ 
		appear in $\ptext$.\\

		\textbf{Proof}	
		To solve the permutation pattern for a permutation in $\C{n}$, 
		we find a match in the stripe of the permutation and the pattern.
		This can be done linearly by a greedy algorithm, 
		by matching a step whenever it is possible.
		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{stripe}},
		we do not have to compute the stripe advance.
		Therefore we have an (online) algorithm.$\Box$\\

%		\subsection{With Motif Avoiding (231,213)}	
%		
%			\textbf{Proposition \num} Let $\pmotif$, $\ptext$ 
%			be two permutation,
%			with  $\pmotif$ a permutation avoiding (231,213), 
%			we can decide in $O(|\pmotif|*|\ptext|^3)$ time
%			and $O(|\ptext|^3) space$
%			if $\pmotif$ 
%			appear in $\ptext$.\\	
%
%			\textbf{Proof}
%			We consider the following problem :\\
%			
%			Given a motif $\pmotif$ avoiding $(231,213)$,
%			a text $\ptext$, $i$,$j$ , $i<j$.\\
%			
%			$\mathbb{P}_{\pmotif,\ptext,min,max}(i,j)= \left\{ 
%				\begin{array}{l l}
%					true & \text{If the sufixe of $\pmotif$ starting at $i$}\\
%						& \text{is a pattern of the suffix of $\ptext$} \\
%						& \text{with every element in $[min,max]$}\\
%		
%					false & otherwise\\
%				\end{array} \right.$\\
%		
%			$\mathbb{P}_{\pmotif,\ptext,min,max}$ is closed under induction. 
%			it can be
%			solved by means of the following relations:\\
%			
%			
%			\textbf{BASE :} \\
%			$\mathbb{P}_{\pmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
%					\begin{array}{l l}
%						true & \text{if $min < \ptext(j) < max$
%						}\\
%						false & otherwise\\
%					\end{array} \right. $\\	
%		
%			\textbf{STEP :} \\
%			$\mathbb{P}_{\pmotif,\ptext,min,max}(i,j)= \left\{ 
%					\begin{array}{l l}
%						False & \text{if $\ptext(j)<min$ or $max<\ptext(j)$}\\
%						\bigcup_{j<k}\mathbb{P}_{\pmotif,\ptext,t(j),max}(i+1,k) 
%							& \text{if $\\mathcal{S}(\pmotif,i)=\ustep$
%							}\\
%						\bigcup_{j<k}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(i+1,k) 
%							& \text{if $\\mathcal{S}(\pmotif,i)=\dstep$
%							}\\
%					\end{array} \right. $\\
%			At each step, 
%			we are match the current element of $\pmotif$ ($\pmotif(i)$)
%			with the current element of $\ptext$ ($\ptext(j)$), if possible.
%			then we are match the rest of $\pmotif$ with 
%			every suffixes $\ptext$ starting after $j$.
%			Clearly there is a match if and only if 	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(0,k)$
%			is true.   
%			This implies a $O(|\pmotif|*|\ptext|^3)$ time
%			and $O(|\ptext|^3) space$ algorithm.\\

		\section{Pattern Matching With Motif Avoiding (231,213)}

			\textbf{Proposition  \num \thenum} Let $\pmotif$, $\ptext$ 
			be two permutation,
			with  $\pmotif$ a permutation avoiding (231,213), 
			we can decide in $O(|\pmotif|*|\ptext|^2)$ time
			and $O(|\pmotif|*|\ptext|^2)$ space
			if $\pmotif$ 
			is a motif of $\ptext$.\\

%			\textbf{Proof}
%			The main point is that
%			if we match a up step (down step) element $i_{\pmotif}$ of the motif
%			with an element $i_{\ptext}$ of the text,
%			the optimal way of matching
%			the first previous up step (down step)
%			that appear before an down step (up step)
%			is to choose the
%			maximal (minimal) element possible.
%			Indeed if we do not take
%			the maximal (minimal) element,
%			we may prevent some element
%			in the future matching.\\

			For the algorithm we introduce a decomposition,
			we decompose the motif into
			adjacent element of same step in the stripe 
			(called such sequence segment),
			and label them form left to right
			with increasing number.
			Let's call this decomposition $S$.
			For each segment, we call important 
			the leftmost element denoted by $IMP$.
			For example, given the motif $(12,11,10,1,2,3,4,9,8,5,6,7)$,
			$S(1)=(5,6,7)$, $IMP(1)=5$, 
			$S(2)=(9,8)$, $IMP(2)=9$, 
			$S(3)=(1,2,3,4)$, $IMP(3)=1$, 
			$S(4)=(12,11,10)$ and $IMP(4)=12$.\\

			Given a up step (down step) segment $S(s)$,
			if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(e)$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[e:]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:e-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior to the minimal (maximal) element of the match of (1).
			In other word if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an up step (down step),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

			Consider the following problem :\\
			$LM(s,i)$ = the optimal match of 	
				$IMP(s-1)$ 
				if there exists a match of $\pmotif[IMP(s):]$ 
				with $\ptext[i:]$
				and $IMP(s)$ 
				is matched with element $i$.\\

			This problem can be solve by induction.\\

			\textbf{BASE :} \\
			$LM(1,i)= \left\{ 
					\begin{array}{l l}

						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
						\text{if $\mathcal{S}(\pmotif,IMP(1))=\ustep$}
						\\
						\text{ $LIS(i,i',\ptext(i')) \leq S(1)$}\}&\\

						&\\

						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
						\text{if $\mathcal{S}(\pmotif,IMP(1))=\dstep$} \\
						\text{ $LDS(i,i',\ptext(i')) \leq S(1)$}\}&\\

					\end{array} \right. $\\

			\textbf{STEP :} \\
			$LM(s,i)= \left\{ 
					\begin{array}{l l}

						MIN \{0\} \cup  I(s,i) & 
						\text{if $\mathcal{S}(\pmotif,IMP(s))=\ustep$}\\

						MAX \{0\} \cup  D(s,i) & 
						\text{if $\mathcal{S}(\pmotif,IMP(s))=\ustep$}\\

					\end{array} \right. $\\

			With $I(s,i)$ ($D(s,i)$) the set of element such that
			if  $e \in I(s,i)$ then there exists 
			a match of $\pmotif[IMP(s-1):]$ in $\ptext[e:]$ and
			there is a match of $s$ in $\ptext[i:e-1]$
			with every element inferior (superior) to the match of  
			$\pmotif[IMP(s-1):]$ in $\ptext[e:]$.
			Formally we define $I(s,i)$ and $D(s,i)$ such as:\\

			$I(s,i)=\{e|\text{$i<e$ and $LM(s-1,e)\neq 0$}$ \\
			\indent \indent \indent and  $LIS(i,e-1,IMP(s-1)) \leq S(s) \}$ \\

			$D(s,i)=\{e|\text{$i<e$ and $LM(s-1,e)\neq 0$}$ \\
			\indent \indent \indent and  $LDS(i,e-1,IMP(s-1)) \leq S(s) \}$ \\

			With LIS(i,j,k) (LDS(i,j,k)) is the longest increasing (decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
			with every element of this sequence
			inferior (superior) to $k$. 
			LIS and LDS can be computed in $O(|\ptext|^2*log(log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\

			In the base case, 
			we are looking for a match for the first segment.
			Each segment is either up step or down step.
			If the segment is an up step (down step)
			we have to find an increasing (decreasing) sequence
			in the text of same size of longest that 
			the size of the segment,
			and to find the optimal solution 
			we must assure that the last element
			of the sequence is minimal (maximal).\\
			For the induction, it is the same idea
			except that we must assure that 
			every element of the sequence is superior 
			to the maximum element of the rest of the match
			or inferior to the minimal element of the rest of the match
			which is given by $LM$ of
			the previous segment.\\

			There exists a match of $\pmotif$ in $\ptext$ if and only if
			there exists a $LM(n,i)$ for $1 \leq i \leq |\ptext|$,
			with $n$ the number of segment in $\pmotif$.
			Moreover the basic case can be computed in $O(|\ptext|^2)$
			and the induction on $O(|\pmotif|*|\ptext|^2)$ $\Box$.

		\section{Pattern Matching With Bivincular Motif Avoiding (231,213)}

			\textbf{Proposition \num \thenum } Let $\bmotif$ be a bivincular motif 
			avoiding (231,213), 
			$\ptext$ a permutation,
			we can decide in $O(|\pmotif|*|\ptext|^3)$ time
			and $O(|\ptext|^3)$ space
			if $\pmotif$ 
			appear in $\ptext$.\\

			\textbf{Proof }
			We consider the following problem :\\

			Given a bivincular motif $\bmotif$ avoiding $(231,213)$,
			a text $\ptext$, $i$,$j$ , $i<j$.\\

			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[min,max]\\

					false & otherwise\\
				\end{array} \right.$\\

			$\mathbb{P}_{\pmotif,\ptext,min,max}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

			\textbf{BASE :} \\

			if $|\pmotif| \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(j)<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(|\ptext|)<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

			if $|\pmotif| \notin  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif(|\pmotif|)$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(j)<max$
						}\\
						&\text{$\ptext(j)$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif(|\pmotif|)$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(|\ptext|)<max$
						}\\
						&\text{$\ptext(|\ptext|)$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,k) 
							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,k) 
							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $min<\ptext(j)<max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\

						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
							&\text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
							&\text{and $\ptext^{-1}(\ptext(j)+1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
							&\text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $min<\ptext(j)<max$} \\
							&\text{and $\ptext^{-1}(\ptext(j)-1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							&\text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext(j)+1=\ptext(j+1)$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1)
							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext(j)-1=\ptext(j+1)$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

%			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \\ \left\{ 
%					\begin{array}{l l}
%						False & \text{if $\ptext(j)<min$ or $max<\ptext(j)$}\\
%						&\\
%					
%						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,k) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$
%							and $i \notin \x$}\\
%							& \text{and $i \notin \y$ }\\
%						&\\
%							
%						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,k) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							& \text{and $i \notin \x$ and $i \notin \y$  
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
%							& \text{and $i \in \x$ and $i \notin \y$  
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							& \text{and $i \in \x$ and $i \notin \y$  
%							}\\							
%						&\\
%							
%						False 
%						& \text{if $\ptext^{-1}(\ptext(j)+1)<j$}\\
%						&\text{and $\mathcal{S}(\pmotif,i)=\ustep$}\\
%						&\text{and $i \in \y$}\\
%						&\\
%							
%						False 
%						& \text{if $\ptext^{-1}(\ptext(j)-1)<j$}\\
%						& \text{and $\mathcal{S}(\pmotif,i)=\dstep$}\\
%						& \text{and $i \in \y$}\\	
%						&\\
%						
%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
%							&\text{and $i \notin \x$ and $i \in \y$ 
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							&\text{and $i \notin \x$ and $i \in \y$  
%							}\\	
%						&\\
%						
%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
%							&\text{and $i \in \x$ and $i \in \y$}\\ 
%							&\text{and $\ptext(j)+1=\ptext(j+1)$ 
%							}\\
%						&\\
%							
%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1)
%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
%							&\text{and $i \in \x$ and $i \in \y$}\\ 
%							&\text{and $\ptext(j)-1=\ptext(j+1)$ 
%							}\\		
%						&\\	
%						False & Otherwise\\																		
%					\end{array} \right. $\\

			At each step (i,j),
			If $i \notin \x$ and $i \notin \y$,
			we match the current element of $\pmotif$ ($\pmotif(i)$)
			with the current element of $\ptext$ ($\ptext(j)$), if possible.
			Then we match $\pmotif[i+1:]$ with 
			every suffixes $\ptext$ starting after $j$.\\

			If $i \in \x$ and $i \notin \y$,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif(i+1)$ is matched to $\ptext(j+1)$.\\

			If $i \notin \x$, $i \in \y$ and i is a down step,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext(j)-1):]$
			with the condition that
			$\pmotif(i+1)$ is matched to the element $\ptext(j)-1$.\\

			If $i \notin \x$, $i \in \y$ and i is an up step,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext(j)+1):]$
			with the condition that
			$\pmotif(i+1)$ is matched to the element $\ptext(j)+1$.\\

			If $i \in \x$, $i \in \y$ and i is a down step,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif(i+1)$ is matched to $\ptext(j+1)$,
			and that $\ptext(j+1)=\pmotif(i)-1$.\\

			If $i \in \x$, $i \in \y$ and i is an up step,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif(i+1)$ is matched to $\ptext(j+1)$,
			and that $\ptext(j+1)=\pmotif(i)+1$.\\

			There are two cases to consider searching for a match : \\
			If $|\pmotif| \in \x$ there exists a match
			if and only if\\ $\bigcup_{0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(0,0)$ is true.\\

			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(0,k)$
			is true. $\Box$

	\section{Longest Subsequence Avoiding \\(231,213) for a Permutation}

	In this section we present an algorithm to solve the problem
	of the longest subsequence avoiding (231,213).
	To do so, we need the set of element
	that are matched to an up step and the
	set of element that are matched to a down step.
	For a permutation $p$ of size $n$, we define
	$P(p) = \{i | \mathcal{S}(p,i) = \ustep \} \cup \{n\}$ and  
	$M(p) = \{i | \mathcal{S}(p,i) = \dstep \} \cup \{n\}$.\\

	\textbf{Proposition  \numl{longestIncreasingSubsequence} \thenum}
	If $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $p$ then
	$P(p)$ is a longest increasing subsequence with last element at index $f$ and
	$M(p)$ is a longest decreasing subsequence with last element at index $f$.\\

	\textbf{Proof} Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $p$, 
	suppose that $P(p)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
	Thus $|s_m|>P(p)$, clearly the sequence $s_m \cup M(p)$
	is avoiding (213,231) and is longer than $s$ witch is not possible. 
	The case for $M(p)$ follows the same idea.$\Box$\\

	\textbf{Proposition  \num \thenum}
	Given a permutation $p$, 
	finding the longest subsequence avoiding (231,213)
	can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and in $O(n)$ space.\\

	\textbf{Proof} The proposition \ref{longestIncreasingSubsequence} lead to algorithm 
	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
	Computing the longest increasing and decreasing can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.$\Box$\\

	\section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutation}

	In this section we present an algorithm to find 
	the longest common subsequence avoiding (231,213) 
	between two permutations.\\

	\textbf{Proposition \num \thenum } Given two permutation $p_1$ and $p_2$
	The longest common subsequence
	avoiding (231,213) can be solve in $O(|p_1|^3*|p_2|^3)$.\\

	\textbf{Proof } Consider the following problem, 
	that compute the longest stripe common to $p_1$ and $p_2$.
	Given two permutation $p_1$ and $p_2$.\\

	$S_{p_1,p_2}(min_1,max_1,min_2,min_2,i_1,i_2)$
	= max$\{$ $|m|$ $|$ 
	s is a pattern occurring 
	in  $p_1[i_1:]$
	by the subsequence $s_1$ and $min(s_1)=min_1$ and $max(s_1)=max_1$
	and s is occurring
	in  $p_2[i_2:]$
	by the subsequence $s_2$ and $min(s_2)=min_2$ and $max(s_2)=max_2$	
	$\}$\\

	We show that this family of problems are closed under induction.\\

	\textbf{BASE :} \\
	$S_{p_1,p_2,min_1,max_1,min_2,max_2}(|p_1|,|p_2|) = \left\{ 
			\begin{array}{l l}
				1 & \text{if $min_1<p_1(j)<max_1$  
				}\\
				& \text{ and $min_2<p_2(j)<max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

	\textbf{STEP :} \\

	$S_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2) =$\\
	\indent $ max \left\{ 
			\begin{array}{l l}
				S_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2+1) \\
				S_{p_1,p_2,min_1,max_1,min_2,max_22}(i_1+1,i_2) \\
				S'_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2)
			\end{array} \right. $\vspace{20pt}\\

	with 
	$S'_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2)=\\ \left\{ 
				\begin{array}{l l}
					1+S_{p_1,p_2,p_1(i_1),max_1,p_2(i_2)}(max_2,i_1+1,i_2+1)  & \text{$p_1(i_1)<min_1$ } \\
					& \text{and $p_2(i_2)<min_2$} \\
					&\\
					1+S_{p_1,p_2,min_1,p_1(i_1),min_2,p_2(i_2)}(i_1+1,i_2+1)  & \text{$p_1(i_1)>max_1$ } \\	
					&\text{and $p_2(i_2)>max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\

	For every pair $i,j$ we either ignore the element of $p_1$,
	either ignore the element of $p_2$, 
	either we match as the same step (if possible).
	Those relation lead to a $O(|p_1|^3*|p_2|^3)$ time and $O(|p_1|^3*|p_2|^3)$ space algorithm.$\Box$

%	\section{Related problems}
%		
%		\textbf{Proposition 3.1} Longest Minimal Common Supersequence, Shortest Maximal Common Subsequence, and Shortest Maximal Common Non-Supersequence are MAX SNP-hard.\\
%		
%		Clearly every problem over (231,213)-Avoiding permutation
%		are equivalent to problem over binary word.
%		The proposition follow what we know about those problem over binary alphabet
%		\cite{Middendorf1995317}.\\

	\section{Conclusion}

\bibliography{bibli}{}
\bibliographystyle{plain}

\end{document}

### 2015-01-29 article.tex
corrections of typo

@@
 
-% le set avoid 231,213
-\newcommand{\C}[1]{A_{#1}(231,213)}
+% 231,213
+\newcommand{\myPattern}{231,231}
+
+% avoid set
+\DeclareMathOperator{\Avd}{Av}
+\newcommand\Av[2]{\Avd_{{#1}}({#2})}
 
@@
 
-\title{Pattern matching for (231,231) avoiding permutations}
+\title{Pattern matching for (231,213) avoiding permutations}
 \author{Both Emerite NEOU, Romeo RIZZI}
@@
 	  	avoiding (231,231).
-
 	}
@@
 
-		We denote by $A_{n}(m_1,m_2)$ the class
+		We denote by $\Av{n}{213,231}$ the class
 		of permutation of size $n$ which avoid 
-		the motif $m_1$ and $m_2$. 
+		the motif $213$ and $231$. 
 		$\Perm{n}$ the permutation of size $n$.
@@
 		Given two permutations
-		$\pmotif$ and $\ptext$
+		$\pmotif$ and $\ptext$,
 		we say that $\pmotif$
@@
 		and increasing function 
-		$\sigma:[|\pmotif|]->[|\pmotif|]$
+		$\sigma:[|\pmotif|] \rightarrow [|\pmotif|]$
 		such that : $\forall i$ and 
@@
 		By convention the last element is mapped as the second to last element.\\ 	
-		Formally a Stripe is a function $\mathcal{S} : \Perm{n},[n] \to \{\dstep,\ustep\}$ define as :\\
+		Formally a Stripe is a function $\mathcal{S} : [n] \to \{\dstep,\ustep\}$ define as :\\
 		$ \mathcal{S}(p,i) = \left\{ 
@@
 		because we can match \\
-		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4)$ and $(\ustep_1,\ustep_2)$ to 
-		$(\ustep_5,\ustep_6)$.
+		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4,(\ustep_1,\ustep_2)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
 		\begin{figure}[h!]
@@
 		the first set contains the first index 
-		of two consecutive index
-		and the second set contains the first index
+		of two consecutive indexes
+		and the second set contains the first indexes
 		of the two consecutive elements.
@@
 		with the special case of $0$ and $|\pmotif|$ :
-		$0 \in \x$ then the first element of $\pmotif$
+		if $0 \in \x$ then the first element of $\pmotif$
 		must be matched with the first element of $\ptext$,
-		and $|\pmotif| \in \x$ then the last element of $\pmotif$
+		and if $|\pmotif| \in \x$ then the last element of $\pmotif$
 		must be matched with the last element of $\ptext$.
@@
 		with the special case of $0$ and $|\pmotif|$ :
-		$0 \in \y$ then the minimal element of $\pmotif$
+		if $0 \in \y$ then the minimal element of $\pmotif$
 		must be matched with the minimal element of $\ptext$,
-		and $|\pmotif| \in \y$ then the maximal element of $\pmotif$
+		and if $|\pmotif| \in \y$ then the maximal element of $\pmotif$
 		must be matched with the maximal element of $\ptext$.
@@
 
-		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\C{n}$ 
+		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{}$ 
 		then the first element is either
@@
 
-		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\C{n}$ if and only if for $1 \leq i \leq n$ 
+		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
 		$p[i:]$ start either with the maximal element
@@
 
-		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \C{n}$ its stripe can be define such as, \\
+		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \Av{n}{213,231}$ its stripe can be define such as, \\
 		$\mathcal{S}(p,i) = \left\{ 
@@
 
-		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \C{n}$,
+		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$, 
 		$i<j$, 
-		$\mathcal{S}(p,i)=\ustep$
+		if $\mathcal{S}(p,i)=\ustep$
 		and $\mathcal{S}(p,j)=\dstep$
@@
 		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
-		Suppose the proposition true for $\C{n}$.
-		Let $p \in \C{n+1}$, 
+		Suppose the proposition true for $\Av{n}{213,231}$.
+		Let $p \in \Av{n}{213,231}$, 
 		we show that the proposition holds for $p$.
 		Let $p'$ be the permutation $p[2:]$.
-		$p' \in \C{n}$, so
+		$p' \in \Av{n}{213,231}$, so
 		every element of $p'$ verify our lemma (by induction).
 		We still need to compare the first element with the rest.
-		Except that the first element
+		But the first element
 		is the maximal (minimal) element of all the permutation 
@@
 
-		\textbf{Lemma \numl{upup} \thenum} Let $p \in \C{n}$,
+		\textbf{Lemma \numl{upup} \thenum} Let $p \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$, 
 		$i<j$, 
-		$\mathcal{S}(p,i)=\ustep$
+		if $\mathcal{S}(p,i)=\ustep$
 		and $\mathcal{S}(p,j)=\ustep$
@@
 
-		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \C{n}$,
+		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$,
 		$i<j$,
-		$\mathcal{S}(p,i)=\dstep$
+		if $\mathcal{S}(p,i)=\dstep$
 		and $\mathcal{S}(p,j)=\dstep$
@@
 
-		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \C{n}$.
+		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \Av{n}{213,231}$.
 		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.\\
@@
 		Let $\ptext \in \Perm{n}$, 
-		$R_1$ be is stripe, 
+		$R_1$ be its stripe, 
 		$\pmotif \in \Perm{m}$
-		and $R_2$ is stripe.
+		and $R_2$ its stripe.
 		Let $\phi$ be the function
@@
 		$\varphi(x) = \phi(x)$.
-		Suppose\\ $\exists x,y \in [|\pmotif|], \text{ $\pmotif(x)<\pmotif(y)$ 
-		and $\ptext(\varphi(x))>\ptext(\varphi(y))$ }$,
-		without lost of generality we can suppose that $x<y$
-		But :
+		Suppose that $\exists x,y \in [|\pmotif|]$, 
+		$\pmotif(x)<\pmotif(y)$ 
+		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
+		without lost of generality we can suppose that $x<y$,
+		Let see all the case possible that can make this 
+		hypothesis possible :
 		\begin{itemize}
@@
 			As $x<y$ and as $\varphi$ is an increasing function, 
-			so $\varphi(x) < \varphi(y)$.
+			$\varphi(x) < \varphi(y)$.
 			And thus, by \textbf{Lemma \ref{upup}},
 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-			which contradict our hypothesis,
+			Which contradict our hypothesis,
 			so this case is not possible.
@@
 			As $x<y$ and as $\varphi$ is an increasing function, 
-			so $\varphi(x) < \varphi(y)$.
+			$\varphi(x) < \varphi(y)$.
 			And thus, by \textbf{Lemma \ref{updown}},
 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-			which contradict our hypothesis,
+			Which contradict our hypothesis,
 			so this case is not possible.
@@
 			As $x<y$ and as $\varphi$ is an increasing function, 
-			so $\varphi(y) < \varphi(x)$.
+			$\varphi(y) < \varphi(x)$.
 			And thus, by \textbf{Lemma \ref{downdown}},
 			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
-			which contradict our hypothesis,
+			Which contradict our hypothesis,
 			so this case is not possible.
@@
 			As $x<y$ and as $\varphi$ is an increasing function, 
-			so $\varphi(y) < \varphi(x)$.
+			$\varphi(y) < \varphi(x)$.
 			And thus, by \textbf{Lemma \ref{updown}},
 			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
-			which contradict our hypothesis,
+			Which contradict our hypothesis,
 			so this case is not possible.$\Box$
@@
 		\end{itemize}
-		So this is not possible. $\Box$\\
+		So our hypothesis is not realisable.So our assertion is true. $\Box$\\
 
@@
 		\textbf{Proof}	
-		To solve the permutation pattern for a permutation in $\C{n}$, 
-		we find a match in the stripe of the permutation and the pattern.
+		To solve the permutation pattern for a permutation in $\Av{n}{213,231}$, 
+		we find a find a match of the stripe of the pattern in the stripe of the text.
 		This can be done linearly by a greedy algorithm, 
@@
 		we do not have to compute the stripe advance.
-		Therefore we have an (online) algorithm.$\Box$\\
+		Therefore we have an linear (online) algorithm.$\Box$\\
 
@@
 			(called such sequence segment),
-			and label them form left to right
+			and label them form right to left
 			with increasing number.
@@
 			Given a up step (down step) segment $S(s)$,
-			if we want to match 
-			$\pmotif[IMP(s):]$
-			with $\ptext[i:]$
-			and match $IMP(s)$
-			with $i$.
-			The optimal way
-			of matching
-			$\pmotif[IMP(s-1):]$
-			is to choose the
-			minimal (maximal) element $\ptext(e)$
-			such that :
-			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[e:]$
-			and $IMP(s-1)$ is matched with $e$.
-			(2) The segment $S(s)$ is matched with $\ptext[i:e-1]$
-			and $IMP(s)$ is matched with $i$.
-			(3) Every elements of the match of (2),
-			is inferior to the minimal (maximal) element of the match of (1).
-			In other word if we want to
+			if we want to
 			match the suffix $s_ns_{s-1}...s_1$
@@
 			of $s_n$.			
+			In other word if we want to match 
+			$\pmotif[IMP(s):]$
+			with $\ptext[i:]$
+			and match $IMP(s)$
+			with $i$.
+			The optimal way
+			of matching
+			$\pmotif[IMP(s-1):]$
+			is to choose the
+			minimal (maximal) element $\ptext(i')$
+			such that :
+			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
+			and $IMP(s-1)$ is matched with $e$.
+			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
+			and $IMP(s)$ is matched with $i$.
+			(3) Every elements of the match of (2),
+			is inferior (superior) to the minimal (maximal) element of the match of (1).
 			Indeed when we will 

### 2015-01-30 article.tex
correction : remove the special case of last element for stripe. correction : proof for pattern matching for two permutation avoiding the motif to adapt with the definition of stripe. correction : definition of a segment in pattern mathing with motif avoiding hte motif to adapt with the definition of stripe.

@@
 		An element $i$ of a permutation $p$ is an up step if and only if $i$ is not the last element and $p(i)<p(i+1)$.
-		An element $i$ of a permutation $p$ is a down step if and only if $i$ is not the last element and $p(i)>p(i+1)$.	
-		By convention the last element is mapped as the second to last element.\\ 	
-		Formally a Stripe is a function $\mathcal{S} : [n] \to \{\dstep,\ustep\}$ define as :\\
+		An element $i$ of a permutation $p$ is a down step if and only if $i$ is not the last element and $p(i)>p(i+1)$.\\	
+		Formally a Stripe is a function $\mathcal{S} : [n-1] \to \{\dstep,\ustep\}$ define as :\\
 		$ \mathcal{S}(p,i) = \left\{ 
@@
 		    \dstep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)<0$ }\\
-		     \mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
 		  \end{array} \right. $\\
@@
 		By extension we define  $\mathcal{S} : \Perm{n} \to \{\dstep,\ustep\}^{n}$ such as :
-		$\mathcal{S}(p)=\mathcal{S}(p,1)\mathcal{S}(p,2)...\mathcal{S}(p,n)$.
+		$\mathcal{S}(p)=\mathcal{S}(p,1)\mathcal{S}(p,2)...\mathcal{S}(p,n-1)$.
 		We call $\mathcal{S}(p)$ the stripe of $p$.
 		For example the stripe of the permutation $(12,11,10,1,2,3,4,9,8,5,6,7)$, 
-		is $\dstep,\dstep,\dstep,\ustep,\ustep,\ustep,\ustep,\dstep,\dstep,\ustep,\ustep,\ustep$.\\
+		is $\dstep,\dstep,\dstep,\ustep,\ustep,\ustep,\ustep,\dstep,\dstep,\ustep,\ustep$.\\
 
@@
 %		and the set is the set of image of this function.\\
-		For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1,\ustep_2)$ is a motif of  the stripe \\
-		$(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$ ,
+		For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ is a motif of  the stripe \\
+		$(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6)$ ,
 		because we can match \\
-		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4,(\ustep_1,\ustep_2)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
+		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
 		\begin{figure}[h!]
@@
 				\xymatrix@=0.3cm{
-					\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]& \ustep_2 \ar[ddrrrrr]  \\
+					\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]\\
 					\\
-					\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 & \ustep_7 & \\
+					\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 \\
 				}
@@
    			\dstep & \quad \text{if $p(i)$ is the maximal element of $p[i:]$}\\
-  		 	\mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
 	 	\end{array} \right. 
@@
 		$\Leftarrow$ 
-		Let $\ptext \in \Perm{n}$, 
+		Let $\ptext$ be a permutation avoiding $(213,231)$, 
 		$R_1$ be its stripe, 
-		$\pmotif \in \Perm{m}$
+		$\pmotif$  be a permutation avoiding $(213,231)$, 
 		and $R_2$ its stripe.
@@
 		We define $\varphi$ as, 
-		$\forall x \in [m]$,
-		$\varphi(x) = \phi(x)$.
+		$\forall x \in [|\pmotif|-1]$,
+		$\varphi(x) = \phi(x)$,
+		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
 		Suppose that $\exists x,y \in [|\pmotif|]$, 
@@
 		\begin{itemize}		
-
 			\item if $\pmotif(x)<\pmotif(y)$, 
@@
 			so this case is not possible.$\Box$
+
+			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
+			Clearly if $\mathcal{S}(\pmotif,x)=\ustep$,
+			then $\pmotif(y)-\pmotif(x)>0$ 
+			and because we have a match in the ribbon
+			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
+			Same idea goes if $\mathcal{S}(\pmotif,x)=\dstep$.
+			So this case is not possible.
+
+			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
+			if $\mathcal{S}(\pmotif,x)=\ustep$ ie
+			$\pmotif(x+1)-\pmotif(x)>0$. Then
+			we must have either
+			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
+			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
+			to avoid $231$ or $213$ in the motif.
+			Because we have a match in the stripe
+			and what we prove above,
+			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
+			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
+			so we have either 		
+			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
+			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
+			which both lead to a $231$ or a $213$ motif
+			in the text which is not possible.
+			The same idea goes if $\mathcal{S}(\pmotif,x)=\dstep$.
 
@@
 			(called such sequence segment),
+			add the last element to the right most segment,
 			and label them form right to left

### 2015-01-30 article.tex
LNCS format

@@
-\documentclass[12pt, a4paper]{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[a4paper]{llncs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \usepackage{amsmath}
-
 \usepackage[all]{xy}
-
 \usepackage{algorithm}
 \usepackage[noend]{algpseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{complexity}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\DeclareMathOperator{\RUN}{run}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Pattern matching for (231,213) avoiding permutations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Pattern matching for $(231,213)$-avoiding permutations}
 \author{Both Emerite NEOU, Romeo RIZZI}
@@
 
-\begin{document}
+\author{%
+	Both Emerite Neou\inst{1,3}
+  Romeo Rizzi\inst{2} \and
+  St\'ephane Vialette\inst{3}
+}% end author
+\institute{%
+  Department of Computer Science,
+  Università degli Studi di Trento, Italy \\	
+	\and
+  Department of Computer Science,
+  Università degli Studi di Verona, Italy \\
+  \email{romeo.rizzi@univr.it}
+  \and
+	Universit\'e' Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC, 
+	F-77454, Marne-la-Vallée, France\\
+  \email{vialette@univ-mY.fr}
+}% end institute
+
+\date{\today}
+
 \maketitle
+
 \tableofcontents
 
-	\abstract{
-	  	Given two permutations, 
-	  	a text $\ptext$ 
-	  	and a motif $\pmotif$,
-	  	the \textbf{permutation pattern problem}
-	  	asks if there exists a normalized subsequence of $\ptext$
-	  	which equals $\pmotif$.
-	  	We study this problem for the permutation 
-	  	avoiding (231,231).
-	}
+\begin{abstract}
+bla bla\ldots
+\end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Introduction}
+\label{section:Introduction}
+
+	A permutation $\pi$ is said to contain another permutation $\sigma$,
+	in symbols $\sigma \preceq \pi$,
+	if there exists a subsequence of entries of $\pi$ that has the same relative
+	order as $\sigma$, and in this case $\sigma$ is said to be a 
+	\emph{pattern} of $\pi$.
+	Otherwise, $\pi$ is said to avoid the permutation $\sigma$.
+	For example a permutation contains the pattern $123$ (resp. $321$) if it has
+	an increasing (resp. decreasing) subsequence of length $3$.
+	Here, note that members need not actually to be consecutive, 
+	merely increasing (resp. descreasing).
+	During the last decade, the study of the pattern containment on permutations has
+	become a very active area of research.
+
+	We consider here the so-called \emph{pattern containment} problem
+	(also sometimes referred to as the pattern involvement problem):
+	Given two permutations $\sigma$ and $\pi$, this problem is to decide whether
+	$\sigma \preceq \pi$ (the problem is ascribed to Wilf in \cite{Bose:Buss:Lubiw:1998}).
+	The permutation containment problem is \NPhard~\cite{Bose:Buss:Lubiw:1998}.
+	It is, however, polynomial time solvable by brute-force enumeration
+	if $\sigma$ has bounded size.
+	Improvements to this algorithm were presented in
+	\cite{Albert:Aldred:Atkinson:Holton:ISAAC:2001} and
+	\cite{Ahal:Rabinovich:2008},
+	the latter describing a $O(|\pi|^{0.47k+o(|\sigma| )})$ time algorithm.
+	Bruner and Lackner \cite{Bruner:Lackner:SWAT:2012}
+	gave a fixed-parameter algorithm solving the pattern containment problem with
+	an exponential worst-case runtime of $O(1.79^{\RUN(\pi)})$,
+	where $\RUN(\pi)$ denotes the number of alternating runs of $\pi$.
+	(This is an improvement upon the $O(2^{|\pi|})$ runtime required by
+	brute-force search without imposing restrictions on $\sigma$ and $\pi$.)
+
+	A few particular cases of the pattern containment problem have been attacked successfully.
+	The case of increasing patterns is solvable in
+	$O(|\pi| \log \log |\sigma|)$ time in the RAM model \cite{Crochemore:Porat:2010},
+	improving the previous 30-year bound of $O(|\pi| \log |\sigma|)$.
+	(The algorithm also improves on the previous
+	$O(|\pi| \log \log |\pi|)$ bound.)
+	Furthermore, the patterns $132$, $213$, $231$, $312$ can all be handled in linear time
+	by stack sorting algorithms.
+	Any pattern of length $4$ can be detected in $O(|\pi| \log |\pi|)$ time
+	\cite{Albert:Aldred:Atkinson:Holton:ISAAC:2001}.
+	Algorithmic issues for $321$-avoiding patterns containment has been investigated in
+	\cite{Guillemot:Vialette:ISAAC:2009}.
+
+	Of particular interest in our context,
+	the pattern containment problem is also solvable in
+	polynomial time for separable patterns.
+	Separable permutations are those permutations that contain neither
+	$2413$ nor $3142$, and they are enumerated by the Schröder numbers
+	(sequence A006318 in OEIS).
+	Separable permutations has gained a lot of interest in the pattern containment
+	context during the last years.
+	Indeed, the pattern containment problem is solvable $O(kn^4)$ time and
+	$O(kn^3)$ space for separable patterns \cite{Ibarra:1997}
+	(see also \cite{Bose:Buss:Lubiw:1998}),
+	where $k$ is the length of the pattern and $n$ is the length of the
+	target permutation.
+	Notice that there are numerous characterizations of separable permutations.
+	To mention just a few examples,
+	they are the permutations whose permutation graphs are cographs
+	(\emph{i.e.} $P_4$-free graphs);
+	equivalently, a separable permutation is a permutation that can be obtained
+	from the trivial permutation $1$ by \emph{direct sums} and \emph{skew sums}.
+	To the best of our knowledge,
+	separable permutations first arose in the work of
+	Avis and Newborn~\cite{Avis:Monroe:1981},
+	who showed that they are precisely the permutations which can be sorted by an
+	arbitrary number of pop-stacks in series,
+	where a pop-stack is a restricted form of stack in which any pop operation
+	pops all items at once.
+	(Notice that the separable permutations include as a special case the
+	stack-sortable permutations, which avoid the pattern $231$.)
+	Separable permutations
+	have been widely studied in the last decade, both from a combinatorial
+	\cite{West:1995} and an algorithmic
+	\cite{Ibarra:1997,Bose:Buss:Lubiw:1998,Rossin:Bouvel:06,Bouvel:Rossin:Vialette:CPM:2007} point
+	of view.
+
+	There exist many generalisation of patterns that are worth considering
+	in the context of algorithmic issues in pattern involvement
+	(see \cite{Kitaev:book:2011} for an up-to-date survey).
+	Vincular patterns, also called generalized patterns,
+	resemble (classical) patterns, with the constraint that some of the letters in
+	an occurrence must be consecutive.
+	Of particular importance in our context,
+	Bruner and Lackner \cite{Bruner:Lackner:SWAT:2012}
+	proved that deciding whether a vincular pattern
+	$\sigma$ of length $k$ occurs in a permutation
+	$\pi \in \mathfrak{S}_n$ is $W[1]$-complete for
+	parameter $k$.
+	bivincular patterns generalize classical patterns even further than vincular
+	patterns. Indeed, in bivincular patterns, not only positions but also values
+	of elements involved in a matching may be forced to be adjacent
 

### 2015-01-30 article.tex
correct biblio

@@
 
-\tableofcontents
-
 \begin{abstract}
@@
 	We consider here the so-called \emph{pattern containment} problem
-	(also sometimes referred to as the pattern involvement problem):
+	(also sometimes referred to as the \emph{pattern involvement problem}):
 	Given two permutations $\sigma$ and $\pi$, this problem is to decide whether
@@
 	The permutation containment problem is \NPhard~\cite{Bose:Buss:Lubiw:1998}.
-	It is, however, polynomial time solvable by brute-force enumeration
+	It is, however, polynomial-time solvable by brute-force enumeration
 	if $\sigma$ has bounded size.
@@
 	brute-force search without imposing restrictions on $\sigma$ and $\pi$.)
+	Of particular importance, it was recently proved that
+	the permutation containment problem is fiexed-parameter tractable for
+	parameter $|\sigma|$
+	\cite{Guillemot:Marx:SODA:2014}.
 
@@
 	separable permutations first arose in the work of
-	Avis and Newborn~\cite{Avis:Monroe:1981},
+	Avis and Newborn~\cite{Avis:Newborn:1981},
 	who showed that they are precisely the permutations which can be sorted by an

### 2015-01-30 article.tex
correct biblio

@@
 	\cite{Guillemot:Vialette:ISAAC:2009}.
-
-	Of particular interest in our context,
-	the pattern containment problem is also solvable in
-	polynomial time for separable patterns.
+	The pattern containment problem is also solvable in
+	polynomial-time for separable patterns \cite{Ibarra:1997}
+	(see also \cite{Bose:Buss:Lubiw:1998}).
 	Separable permutations are those permutations that contain neither
@@
 	(sequence A006318 in OEIS).
-	Separable permutations has gained a lot of interest in the pattern containment
-	context during the last years.
-	Indeed, the pattern containment problem is solvable $O(kn^4)$ time and
-	$O(kn^3)$ space for separable patterns \cite{Ibarra:1997}
-	(see also \cite{Bose:Buss:Lubiw:1998}),
-	where $k$ is the length of the pattern and $n$ is the length of the
-	target permutation.
-	Notice that there are numerous characterizations of separable permutations.
-	To mention just a few examples,
-	they are the permutations whose permutation graphs are cographs
-	(\emph{i.e.} $P_4$-free graphs);
-	equivalently, a separable permutation is a permutation that can be obtained
-	from the trivial permutation $1$ by \emph{direct sums} and \emph{skew sums}.
 	To the best of our knowledge,
@@
 	stack-sortable permutations, which avoid the pattern $231$.)
-	Separable permutations
-	have been widely studied in the last decade, both from a combinatorial
-	\cite{West:1995} and an algorithmic
-	\cite{Ibarra:1997,Bose:Buss:Lubiw:1998,Rossin:Bouvel:06,Bouvel:Rossin:Vialette:CPM:2007} point
-	of view.
 

### 2015-01-31 article.tex
introduction

@@
 \DeclareMathOperator{\RUN}{run}
+\DeclareMathOperator{\RED}{red}
+\DeclareMathOperator{\AV}{Av}
 
@@
 
-\title{Pattern matching for $(231,213)$-avoiding permutations}
+\title{Pattern matching for\\ $(231,213)$-avoiding permutations}
 \author{Both Emerite NEOU, Romeo RIZZI}
@@
 	(see \cite{Kitaev:book:2011} for an up-to-date survey).
-	Vincular patterns, also called generalized patterns,
+	\emph{Vincular patterns}, also called 
+	\emph{generalized patterns},
 	resemble (classical) patterns, with the constraint that some of the letters in
@@
 	parameter $k$.
-	bivincular patterns generalize classical patterns even further than vincular
-	patterns. Indeed, in bivincular patterns, not only positions but also values
+	\emph{Bivincular patterns} generalize classical patterns even further 
+	than vincular
+	patterns. Indeed, in bivincular patterns,
+	not only positions but also values
 	of elements involved in a matching may be forced to be adjacent
+
+	This paper is organized as follows.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Definition}
-
-		This section presents the decomposition used and some notation.\\
-
-		We denote by $\Av{n}{213,231}$ the class
-		of permutation of size $n$ which avoid 
-		the motif $213$ and $231$. 
-		$\Perm{n}$ the permutation of size $n$.
-		$[n]$ the set $\{1,2,...,n\}.$
-		For a permutation p, let $p[i:j]$, 
-		be the permutation from element $i$ to $j$,
-		$p[:j]$ be the prefix ending at index $j$
-		and $p[i:]$ be the suffix starting at index $i$.\\
-
-		Given two permutations
-		$\pmotif$ and $\ptext$,
-		we say that $\pmotif$
-		is a motif/match of
-		$\ptext$,
-		if and only if
-		there exists 
-		and increasing function 
-		$\sigma:[|\pmotif|] \rightarrow [|\pmotif|]$
-		such that : $\forall i$ and 
-		$\forall j$ $i,j \in |\pmotif| $
-		if $\pmotif(i)<\pmotif(j)$
-		then $\ptext(\sigma(i))<\ptext(\sigma(j))$.\\
-
-		%\subsection{Stripe}
+\label{section:Definitions}
+
+A \emph{permutation} of length $n$ is a one-to-one function from an
+$n$-element set to itself.
+We write permutations as words 
+$\sigma = \sigma_1\,\sigma_2\,\ldots\,\sigma_n$, whose letters are distinct
+and uasually consist of the integers $1\,2\,\ldots\,n$.
+For the sake of convenience, 
+we let 
+$\pi[i:j]$ stand for 
+$\pi_i\,\pi_{i+1}\,\ldots\,\pi_j$,
+$\pi[:j]$ stand for $\pi[1:j]$ and
+$\pi[i:]$ stand for $\pi[i:n]$.
+We let $S_n$ denote the set of all permutations of length $n$.
+
+% The \emph{reduced form} of a permutation $\sigma$ on a set
+% $\{j_1, j_2, \ldots, j_k\}$ where
+% $j_1 < j_2 < \ldots < j_n$ is the permutation $\sigma'$
+% obtained by renaming the letters of $\sigma$ so that 
+% $j_i$ is renamed $i$ for all $1 \leq i \leq k$.
+% We let $\RED(\sigma)$ denote the reduced form of $\sigma$.
+% For example $\RED(453) = 231$
+% while $\RED(3174) = 2143$.
+
+A permutation $\pi$ is said to \emph{contain} the permutation $\sigma$ 
+if there exists a subsequence of (not necessarily consecutive) 
+entries of $\pi$ that has the same relative order as $\sigma$, 
+and in this case $\sigma$ is said to be a \emph{pattern} of 
+$\pi$, written $\sigma \preceq \pi$. 
+Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$. 
+For example, the permutation $\pi = 3\,9\,1\,8\,6\,7\,4\,5\,2$ 
+contains the pattern $\sigma = 51342$, 
+as can be seen in the highlighted subsequence of 
+$\pi = 3\,\mathbf{9}\,\mathbf{1}\,8\,\mathbf{6}\,\mathbf{7}\,\mathbf{4}\,5\,2$
+(or 
+$\pi = 3\,\mathbf{9}\,\mathbf{1}\,8\,\mathbf{6}\,\mathbf{7}\,4\,\mathbf{5}\,2$
+or
+$\pi = 3\,\mathbf{9}\,\mathbf{1}\,8\,\mathbf{6}\,\mathbf{7}\,4\,5\,\mathbf{2}$
+). 
+Each subsequence $(9\,1\,6\,7\,4$, 
+$9\,1\,6\,7\,5$, 
+$9\,1\,6\,7\,2$) is called a 
+\emph{copy}, 
+\emph{instance}, or 
+\emph{occurrence} of $\sigma$. 
+Since the permutation $\pi = 3\,9\,1\,8\,6\,7\,4\,5\,2$  contains no increasing subsequence of length four, $\pi$ avoids $1\,2\,3\,4$.
+
+Suppoe $P$ is a set of permutations. We let $\AV_n(p)$ denote the
+set of all $n$-permutations avoiding each permutation in $P$.
+For the sake of convenience, we omit $P$'s braces thus having
+e.g. $\AV_3(132,4312)$ instead of
+$\AV_3(\{132,4312\})$.
+A basic example is if 
+$\pi = \pi_1\,\pi_2\,\ldots\,\pi_n$ avoids $3\,2\,1$, i.e., 
+has no decreasing subsequence of length $3$, then its reverse, 
+$\pi' = \pi_n\,\pi_{n-1}\,\ldots\,\pi_1$ avoids $1\,2\,3$, i.e., 
+has no increasing subsequence of length $3$.
+
+A \emph{bivincular pattern} (abbreviated BVP) $\sigma$
+of length $k$ is a permutation in $S_k$ written in
+two-line notation 
+(that is the top row is $1\,2\,\ldots\,k$ and the bottom row
+is a permutation $\sigma_1\,\sigma_2\,\ldots\,\sigma_k$).
+We have the following conditions on the top and bottom rows
+of $\sigma$:
+\begin{itemize}
+	\item
+	If the bottom line of $\sigma$ contains
+	$\underline{\sigma_i\,\sigma_{i+1}\,\ldots\,\sigma_j}$
+	then the letters corresponding to 
+	$\sigma_i\,\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
+	$\sigma$ in a permutaton must be adjacent, whereas there is
+	no adjacency condition for
+	non-underlined consecutive letters.
+	Moreover if the bottom row of $\sigma$ begins with
+	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$ 
+	in a permutation $\pi$ must begin with the leftmost 
+	letter of $\pi$,
+	and 
+	if the bottom row of $\sigma$ begins with
+	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$ 
+	in a permutation $\pi$ must end with the rightmost 
+	letter of $\pi$.
+	\item
+	If the top line of $\sigma$ contains
+	$\overline{i\,i+1\,\ldots\,j}$ then the letters corresponding to
+	$\sigma_i, \sigma_{i+1}, \ldots, \sigma_j$ in an
+	occurrence of $\sigma$ in a permutation must be adjacent in values,
+	whereas there is no value adjacency restriction for non-overlined 
+	letters.
+	Moreover, if the top row of $\sigma$ begins with
+	$^ulcorner{1}$ then
+	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
+	the smallest letter of $\pi$, and
+	if top row of $\sigma$ ends with $k^\urcorner$ then
+	any occurrence of $\sigma$ is a permutation $\pi$ must end with
+	the largest letter of $\pi$.
+\end{itemize}
 

### 2015-01-31 article.tex
introduction

@@
 
-Suppoe $P$ is a set of permutations. We let $\AV_n(p)$ denote the
+Suppose $P$ is a set of permutations. We let $\AV_n(p)$ denote the
 set of all $n$-permutations avoiding each permutation in $P$.
@@
 has no increasing subsequence of length $3$.
+
+An \emph{ascent} of a permutation $\pi \in S_n$ is any position 
+$1 \leq i < n$ where the following value is bigger than the current one. 
+That is, if $\pi = \pi_1\,\pi_2\,\ldots\,\pi_n$, then
+$i$ is an ascent if $\pi_i < \pi_{i+1}$.
+For example, the permutation 
+$3\,4\,5\,2\,1\,6\,$7 has ascents (at positions) $1,2,5,6$.
+Similarly, a \emph{descent} is a position 
+$1 \leq i < n$ with $\pi_i > \pi_{i+1}$, 
+so every $i$ with $1 \leq i < n$ either is an ascent or is a descent of 
+$\pi$.
+Let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
+The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
+$s_{\pi,1} s_{\pi,2} \ldots s_{\pi,n-1} \in \{\ustep,\dstep\}^{n-1}$ 
+defined by 
+$\mathcal{S}_{\pi,i} = \ustep$ if $i$ an ascent in $\pi$ and
+$\mathcal{S}_\pi(i) = \dstep$ if $i$ a descent in $\pi$.
+For example the stripe of the permutation 
+$\pi = 12\,11\,10\,1\,2\,3,4\,9\,8\,5\,6\,7$ 
+is 
+$s_\pi = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
+The stripe $s_\sigma$ is a \emph{pattern} of the strip $s_\pi$
+(or $s_\sigma$ \emph{occurs} of the strip $s_\pi$) if $s_\sigma$ occurs in
+$s_\pi$ as a subsequence.
+
+% For two permutations $\
+% The stripe $s\pi$ of $\pi \in S-n$ is a motif pmotif \in \Perm{m}$ is a motif
+% of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
+% such that : \\
+% $\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
+% If a stripe $R_2$ is a motif of a stripe $R_1$,
+% it means that there exists
+% a subsequence of $R_1$ such as
+% this sequence is equal to $R_2$.
+
+% For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ is a motif of  the stripe \\
+% $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6)$ ,
+% because we can match \\
+% $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
+% \begin{figure}[h!]
+% 	\begin{displaymath}
+% 		\xymatrix@=0.3cm{
+% 			\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]\\
+% 			\\
+% 			\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 \\
+% 		}
+% 	\end{displaymath}     
+% \end{figure}		
+% But the stripe $(\dstep,\ustep,\dstep,\dstep,\dstep)$ is not a motif of the stripe\\ $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$.\\
+
+% A \textbf{bivincular motif} generalize
+% a motif. 
+% A bivincular motif allows 
+% to force element to be adjacent in position
+% or/and in value.
+% A bivincular motif
+% is a motif with two set $\bmotif$,
+% the first set contains the first index 
+% of two consecutive indexes
+% and the second set contains the first indexes
+% of the two consecutive elements.
+% Formally, Let $\bmotif$ 
+% be a bivincular motif 
+% and $\ptext$ a permutation.
+% if $i \in \x$,
+% and $i$ is matched with $j$ in $\ptext$
+% then $i+1$ must be matched with $j+1$,
+% with the special case of $0$ and $|\pmotif|$ :
+% if $0 \in \x$ then the first element of $\pmotif$
+% must be matched with the first element of $\ptext$,
+% and if $|\pmotif| \in \x$ then the last element of $\pmotif$
+% must be matched with the last element of $\ptext$.
+% if $i \in \y$,
+% and $i$ is matched with $j$ in $\ptext$
+% then $i+1$ must be matched with $l$
+% such as $\ptext(l)=\ptext(j)+1$,
+% with the special case of $0$ and $|\pmotif|$ :
+% if $0 \in \y$ then the minimal element of $\pmotif$
+% must be matched with the minimal element of $\ptext$,
+% and if $|\pmotif| \in \y$ then the maximal element of $\pmotif$
+% must be matched with the maximal element of $\ptext$.
 
@@
 
-		A \textbf{Stripe} of a permutation
-		is a mapping into \textbf{up step} (noted $\ustep$) 
-		or a \textbf{down step} (noted $\dstep$).
-		An element $i$ of a permutation $p$ is an up step if and only if $i$ is not the last element and $p(i)<p(i+1)$.
-		An element $i$ of a permutation $p$ is a down step if and only if $i$ is not the last element and $p(i)>p(i+1)$.\\	
-		Formally a Stripe is a function $\mathcal{S} : [n-1] \to \{\dstep,\ustep\}$ define as :\\
-		$ \mathcal{S}(p,i) = \left\{ 
-		  \begin{array}{l l}
-		    \ustep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)>0$ }\\
-		    \dstep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)<0$ }\\
-		  \end{array} \right. $\\
-
-		By extension we define  $\mathcal{S} : \Perm{n} \to \{\dstep,\ustep\}^{n}$ such as :
-		$\mathcal{S}(p)=\mathcal{S}(p,1)\mathcal{S}(p,2)...\mathcal{S}(p,n-1)$.
-		We call $\mathcal{S}(p)$ the stripe of $p$.
-		For example the stripe of the permutation $(12,11,10,1,2,3,4,9,8,5,6,7)$, 
-		is $\dstep,\dstep,\dstep,\ustep,\ustep,\ustep,\ustep,\dstep,\dstep,\ustep,\ustep$.\\
-
-%		\textbf{Corollary \num} The stripe function
-%		for $\C{n}$ are in bijection with with $\{\ustep,\dstep\}^{n-1}$.\\
-
-%		\textbf{Proposition \numl{updown}} Let $p \in \C{n}$,
-%		$\forall x,y \in [n]$, 
-%		$\mathcal{S}(p,x)=\ustep$
-%		and $\\mathcal{S}(p,y)=\dstep$
-%		then $p(x)<p(y)$.\\
-
-		Formally we say that the stripe of $\pmotif \in \Perm{m}$ is a motif
-		of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
-		such that : \\
-		$\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
-		If a stripe $R_2$ is a motif of a stripe $R_1$,
-		it means that there exists
-		a subsequence of $R_1$ such as
-		this sequence is equal to $R_2$.
-%		We say that a set is a match 
-%		if and only if there exists a function such as define above
-%		and the set is the set of image of this function.\\
-		For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ is a motif of  the stripe \\
-		$(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6)$ ,
-		because we can match \\
-		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
-		\begin{figure}[h!]
-			\begin{displaymath}
-				\xymatrix@=0.3cm{
-					\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]\\
-					\\
-					\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 \\
-				}
-			\end{displaymath}     
-		\end{figure}		
-		But the stripe $(\dstep,\ustep,\dstep,\dstep,\dstep)$ is not a motif of the stripe\\ $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$.\\
-
-		A \textbf{bivincular motif} generalize
-		a motif. 
-		A bivincular motif allows 
-		to force element to be adjacent in position
-		or/and in value.
-		A bivincular motif
-		is a motif with two set $\bmotif$,
-		the first set contains the first index 
-		of two consecutive indexes
-		and the second set contains the first indexes
-		of the two consecutive elements.
-		Formally, Let $\bmotif$ 
-		be a bivincular motif 
-		and $\ptext$ a permutation.
-		if $i \in \x$,
-		and $i$ is matched with $j$ in $\ptext$
-		then $i+1$ must be matched with $j+1$,
-		with the special case of $0$ and $|\pmotif|$ :
-		if $0 \in \x$ then the first element of $\pmotif$
-		must be matched with the first element of $\ptext$,
-		and if $|\pmotif| \in \x$ then the last element of $\pmotif$
-		must be matched with the last element of $\ptext$.
-		if $i \in \y$,
-		and $i$ is matched with $j$ in $\ptext$
-		then $i+1$ must be matched with $l$
-		such as $\ptext(l)=\ptext(j)+1$,
-		with the special case of $0$ and $|\pmotif|$ :
-		if $0 \in \y$ then the minimal element of $\pmotif$
-		must be matched with the minimal element of $\ptext$,
-		and if $|\pmotif| \in \y$ then the maximal element of $\pmotif$
-		must be matched with the maximal element of $\ptext$.
-
 	\section{Pattern Matching Problem With Text and Motif Avoiding (231,213)}

### 2015-01-31 article.tex
ajout : maccro pour les stripes modif : prise en compte de l ajout de la maccro modif : \upstep = a modif : consistence d une permutation avec \pi

@@
 
+%Stripe
+\DeclareMathOperator{\stripea}{s}
+\newcommand{\stripe}[2]{\stripea_{{#1}}({#2})}
+\newcommand{\stripew}[1]{\stripea_{{#1}}}
+
 % compteur pour les proposition, definition etc...
@@
 %upstep
-\newcommand{\ustep}{u}
+\newcommand{\ustep}{a}
 
@@
 The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
-$s_{\pi,1} s_{\pi,2} \ldots s_{\pi,n-1} \in \{\ustep,\dstep\}^{n-1}$ 
+$\stripe{\pi}{1} \stripe{\pi}{2} \ldots \stripe{\pi}{n-1} \in \{\ustep,\dstep\}^{n-1}$ 
 defined by 
-$\mathcal{S}_{\pi,i} = \ustep$ if $i$ an ascent in $\pi$ and
-$\mathcal{S}_\pi(i) = \dstep$ if $i$ a descent in $\pi$.
+$ \stripe{\pi}{i}= \ustep$ if $i$ an ascent in $\pi$ and
+$\stripe{\pi}{i} = \dstep$ if $i$ a descent in $\pi$.
 For example the stripe of the permutation 
@@
 is 
-$s_\pi = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
-The stripe $s_\sigma$ is a \emph{pattern} of the strip $s_\pi$
-(or $s_\sigma$ \emph{occurs} of the strip $s_\pi$) if $s_\sigma$ occurs in
-$s_\pi$ as a subsequence.
+$\stripew{\pi} = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
+The stripe $s\stripew{\sigma}$ is a \emph{pattern} of the strip $\stripew{\pi}$
+(or $s\stripew{\sigma}$ \emph{occurs} of the strip $\stripew{\pi}$) if $\stripew{\sigma}$ occurs in
+$\stripew{\pi}$ as a subsequence.
 
@@
 % $\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
-% If a stripe $R_2$ is a motif of a stripe $R_1$,
+% If a stripe $S_2$ is a motif of a stripe $S_1$,
 % it means that there exists
-% a subsequence of $R_1$ such as
-% this sequence is equal to $R_2$.
+% a subsequence of $S_1$ such as
+% this sequence is equal to $S_2$.
 
@@
 
-		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{}$ 
+		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{213,231}$ 
 		then the first element is either
@@
 		\textbf{Proof} Suppose that we have
-		$p \in \mathcal{S}_{n}$, and
-		$p(1) \neq 1 $ and $p(1) \neq n$ then we have either
-		$p(1) ... n ... 1$ or $p(1) ... 1 ... n $, either the motif 231 or 213, which is not possible by hypothesis. $\Box$\\
-
-		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
-		$p[i:]$ start either with the maximal element
-		or the minimal element of $p[i:]$.\\
-
-		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \Av{n}{213,231}$ its stripe can be define such as, \\
-		$\mathcal{S}(p,i) = \left\{ 
+		$\pi \in \mathcal{S}_{n}$, and
+		$\pi(1) \neq 1 $ and $\pi(1) \neq n$ then we have either
+		$\pi(1) ... n ... 1$ or $\pi(1) ... 1 ... n $, either the motif 231 or 213, which is not possible by hypothesis. $\Box$\\
+
+		\textbf{Corollary  \num \thenum} A permutation $\pi \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
+		$\pi[i:]$ start either with the maximal element
+		or the minimal element of $\pi[i:]$.\\
+
+		\textbf{Corollary \numl{stripe} \thenum}  If $\pi \in \Av{n}{213,231}$ its stripe can be define such as, \\
+		$\stripe{\pi}{i} = \left\{ 
   		\begin{array}{l l}
-   			\ustep & \quad \text{if $p(i)$ is the minimal element of $p[i:]$}\\    
-   			\dstep & \quad \text{if $p(i)$ is the maximal element of $p[i:]$}\\
+   			\ustep & \quad \text{if $\pi(i)$ is the minimal element of $\pi[i:]$}\\    
+   			\dstep & \quad \text{if $\pi(i)$ is the maximal element of $\pi[i:]$}\\
 	 	\end{array} \right. 
@@
 
-		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \Av{n}{213,231}$,
+		\textbf{Lemma \numl{updown}  \thenum} Let $\pi \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$, 
 		$i<j$, 
-		if $\mathcal{S}(p,i)=\ustep$
-		and $\mathcal{S}(p,j)=\dstep$
-		then $p(i)<p(j)$.\\
-
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
-		if $i$ is a up step and
-		if $j$ is a down step
-		then $p(i)<p(j)$.\\
+		if $\stripe{\pi}{i}=\ustep$
+		and $\stripe{\pi}{j}=\dstep$
+		then $\pi(i)<\pi(j)$.\\
+
+		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
+		if $i$ is an ascent and
+		if $j$ is a descent
+		then $\pi(i)<\pi(j)$.\\
 
@@
 		Suppose the proposition true for $\Av{n}{213,231}$.
-		Let $p \in \Av{n}{213,231}$, 
-		we show that the proposition holds for $p$.
-		Let $p'$ be the permutation $p[2:]$.
-		$p' \in \Av{n}{213,231}$, so
+		Let $\pi \in \Av{n}{213,231}$, 
+		we show that the proposition holds for $\pi$.
+		Let $\pi'$ be the permutation $\pi[2:]$.
+		$\pi' \in \Av{n}{213,231}$, so
 		every element of $p'$ verify our lemma (by induction).
@@
 		Moreover if the first element is the maximal (minimal)
-		it will mapped to an down step (up step).
+		it will mapped to an descent (ascent).
 		So the proposition is also true
@@
 
-		\textbf{Lemma \numl{upup} \thenum} Let $p \in \Av{n}{213,231}$,
+		\textbf{Lemma \numl{upup} \thenum} Let $\pi \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$, 
 		$i<j$, 
-		if $\mathcal{S}(p,i)=\ustep$
-		and $\mathcal{S}(p,j)=\ustep$
-		then $p(i)<p(j)$.\\
-
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
-		if $i$ is a up step 
-		and $j$ is a up step
+		if $\stripe{\pi}{i}=\ustep$
+		and $\stripe{\pi}{j}=\ustep$
+		then $\pi(i)<\pi(j)$.\\
+
+		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
+		if $i$ is a ascent
+		and $j$ is a ascent
 		and $ i<j$
@@
 %		Moreover if the first element is the maximal (minimal)
-%		it will mapped to an down step (up step).
+%		it will mapped to an descent (\pi_2).
 %		So the proposition is also true
@@
 
-		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \Av{n}{213,231}$,
+		\textbf{Lemma \numl{downdown} \thenum}  Let $\pi \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$,
 		$i<j$,
-		if $\mathcal{S}(p,i)=\dstep$
-		and $\mathcal{S}(p,j)=\dstep$
-		then $p(i)>p(j)$.\\
-
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation p,
-		if $i$ is a down step
-		and $j$ is a down step
+		if $\stripe{\pi}{i}=\dstep$
+		and $\stripe{\pi}{j}=\dstep$
+		then $\pi(i)>\pi(j)$.\\
+
+		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
+		if $i$ is a descent
+		and $j$ is a descent
 		and $ i<j$
-		then $p(i)>p(j)$.\\
+		then $\pi(i)>\pi(j)$.\\
 
@@
 %		Moreover if the first element is the maximal (minimal)
-%		it will mapped to an down step (up step).
+%		it will mapped to an descent (ascent).
 %		So the proposition is also true
@@
 		Let $\ptext$ be a permutation avoiding $(213,231)$, 
-		$R_1$ be its stripe, 
+		$S_1$ be its stripe, 
 		$\pmotif$  be a permutation avoiding $(213,231)$, 
-		and $R_2$ its stripe.
+		and $S_2$ its stripe.
 		Let $\phi$ be the function
-		that match $R_2$ to $R_1$.
+		that match $S_2$ to $S_1$.
 		We define $\varphi$ as, 
@@
 			\item if $\pmotif(x)<\pmotif(y)$, 
-			$\mathcal{S}(\pmotif,x)=\ustep$ 
-			and $\mathcal{S}(\pmotif,y)=\ustep$
+			$\stripe{\pmotif}{x}=\ustep$ 
+			and $\stripe{\pmotif}{y}=\ustep$
 			(if x and y are increasing in $\pmotif$),
-			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
+			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
 			(the match are also increasing).
@@
 			\item if $\pmotif(x)<\pmotif(y)$, 
-			$\mathcal{S}(\pmotif,x)=\ustep$ 
-			and $\mathcal{S}(\pmotif,y)=\dstep$
-			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
+			$\stripe{\pmotif}{x}=\ustep$ 
+			and $\stripe{\pmotif}{y}=\dstep$
+			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
 			As $x<y$ and as $\varphi$ is an increasing function, 
@@
 			\item if $\pmotif(x)>\pmotif(y)$, 
-			$\mathcal{S}(\pmotif,x)=\dstep$ 
-			and $\mathcal{S}(\pmotif,y)=\dstep$
-			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
+			$\stripe{\pmotif}{x}=\dstep$ 
+			and $\stripe{\pmotif}{y}=\dstep$
+			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
 			As $x<y$ and as $\varphi$ is an increasing function, 
@@
 			\item if $\pmotif(x)>\pmotif(y)$, 
-			$\mathcal{S}(\pmotif,x)=\dstep$ 
-			and $\mathcal{S}(\pmotif,y)=\ustep$
-			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
+			$\stripe{\pmotif}{x}=\dstep$ 
+			and $\stripe{\pmotif}{y}=\ustep$
+			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
 			As $x<y$ and as $\varphi$ is an increasing function, 
@@
 			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
-			Clearly if $\mathcal{S}(\pmotif,x)=\ustep$,
+			Clearly if $\stripe{\pmotif}{x}=\ustep$,
 			then $\pmotif(y)-\pmotif(x)>0$ 
@@
 			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
-			Same idea goes if $\mathcal{S}(\pmotif,x)=\dstep$.
+			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
 			So this case is not possible.
@@
 			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
-			if $\mathcal{S}(\pmotif,x)=\ustep$ ie
+			if $\stripe{\pmotif}{x}=\ustep$ ie
 			$\pmotif(x+1)-\pmotif(x)>0$. Then
@@
 			in the text which is not possible.
-			The same idea goes if $\mathcal{S}(\pmotif,x)=\dstep$.
+			The same idea goes if $\stripe{\pmotif}{x}=\dstep$.
 
@@
 %			The main point is that
-%			if we match a up step (down step) element $i_{\pmotif}$ of the motif
+%			if we match a ascnt (descent) element $i_{\pmotif}$ of the motif
 %			with an element $i_{\ptext}$ of the text,
 %			the optimal way of matching
-%			the first previous up step (down step)
-%			that appear before an down step (up step)
+%			the first previous ascnt (descent)
+%			that appear before an descent (ascent)
 %			is to choose the
@@
 
-			Given a up step (down step) segment $S(s)$,
+			Given a ascent (descent) segment $S(s)$,
 			if we want to
 			match the suffix $s_ns_{s-1}...s_1$
-			starting with an up step (down step),
+			starting with an ascent (descent),
 			and given that we know every
@@
 						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
-						\text{if $\mathcal{S}(\pmotif,IMP(1))=\ustep$}
+						\text{if $\stripe{\pmotif}{IMP(1)}=\ustep$}
 						\\
@@
 						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
-						\text{if $\mathcal{S}(\pmotif,IMP(1))=\dstep$} \\
+						\text{if $\stripe{\pmotif}{IMP(1)}=\dstep$} \\
 						\text{ $LDS(i,i',\ptext(i')) \leq S(1)$}\}&\\
@@
 						MIN \{0\} \cup  I(s,i) & 
-						\text{if $\mathcal{S}(\pmotif,IMP(s))=\ustep$}\\
+						\text{if $\stripe{\pmotif}{IMP(s)}=\ustep$}\\
 
 						MAX \{0\} \cup  D(s,i) & 
-						\text{if $\mathcal{S}(\pmotif,IMP(s))=\ustep$}\\
+						\text{if $\stripe{\pmotif}{IMP(s)}=\ustep$}\\
 
@@
 
-			$I(s,i)=\{e|\text{$i<e$ and $LM(s-1,e)\neq 0$}$ \\
-			\indent \indent \indent and  $LIS(i,e-1,IMP(s-1)) \leq S(s) \}$ \\
-
-			$D(s,i)=\{e|\text{$i<e$ and $LM(s-1,e)\neq 0$}$ \\
-			\indent \indent \indent and  $LDS(i,e-1,IMP(s-1)) \leq S(s) \}$ \\
+			$I(s,i)=\{i'|\text{$i<i'$ and $LM(s-1,i')\neq 0$}$ \\
+			\indent \indent \indent and  $LIS(i,i'-1,IMP(s-1)) \leq S(s) \}$ \\
+
+			$D(s,i)=\{i'|\text{$i<i'$ and $LM(s-1,i')\neq 0$}$ \\
+			\indent \indent \indent and  $LDS(i,i'-1,IMP(s-1)) \leq S(s) \}$ \\
 
@@
 			we are looking for a match for the first segment.
-			Each segment is either up step or down step.
-			If the segment is an up step (down step)
+			Each segment is either ascent or descent.
+			If the segment is an ascent (descent)
 			we have to find an increasing (decreasing) sequence
@@
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,k) 
-							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,k) 
+							& \text{if $\stripe{\pmotif}{i}=\ustep$
 							and $i \notin \x$}\\
@@
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,k) 
-							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,k) 
+							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							& \text{and $i \notin \x$ and $i \notin \y$  }\\
@@
 						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
-							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
+							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							& \text{and $i \in \x$ and $i \notin \y$}\\
@@
 						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
-							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
+							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							& \text{and $i \in \x$ and $i \notin \y$ }\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
-							&\text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
+						\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
+							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							&\text{and $i \notin \x$ and $i \in \y$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
-							&\text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
+						\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
+							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							&\text{and $i \notin \x$ and $i \in \y$ }\\	
@@
 
-						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
-							&\text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
+						\mathbb{P}_{\bmotif,\ptext,\ptext(j)),max}(i+1,j+1) 
+							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							&\text{and $i \in \x$ and $i \in \y$}\\ 
@@
 
-						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1)
-							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
+						\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,j+1)
+							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							&\text{and $i \in \x$ and $i \in \y$}\\ 
@@
 
-			If $i \notin \x$, $i \in \y$ and i is a down step,
+			If $i \notin \x$, $i \in \y$ and i is a descent,
 			we match $\pmotif(i)$ to $\ptext(j)$, 
@@
 
-			If $i \notin \x$, $i \in \y$ and i is an up step,
+			If $i \notin \x$, $i \in \y$ and i is an ascent,
 			we match $\pmotif(i)$ to $\ptext(j)$, 
@@
 
-			If $i \in \x$, $i \in \y$ and i is a down step,
+			If $i \in \x$, $i \in \y$ and i is a descent,
 			we match $\pmotif(i)$ to $\ptext(j)$, 
@@
 
-			If $i \in \x$, $i \in \y$ and i is an up step,
+			If $i \in \x$, $i \in \y$ and i is an ascent,
 			we match $\pmotif(i)$ to $\ptext(j)$, 
@@
 			If $|\pmotif| \in \x$ there exists a match
-			if and only if\\ $\bigcup_{0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(0,0)$ is true.\\
-
-			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(0,k)$
+			if and only if\\ $\bigcup_{0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,0)$ is true.\\
+
+			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,k)$
 			is true. $\Box$
@@
 	To do so, we need the set of element
-	that are matched to an up step and the
-	set of element that are matched to a down step.
-	For a permutation $p$ of size $n$, we define
-	$P(p) = \{i | \mathcal{S}(p,i) = \ustep \} \cup \{n\}$ and  
-	$M(p) = \{i | \mathcal{S}(p,i) = \dstep \} \cup \{n\}$.\\
+	that are matched to an ascent and the
+	set of element that are matched to a descent.
+	For a permutation $\pi$ of size $n$, we define
+	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and  
+	$M(\pi) = \{i | \stripe{\pi}{i} = \dstep \} \cup \{n\}$.\\
 
 	\textbf{Proposition  \numl{longestIncreasingSubsequence} \thenum}
-	If $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $p$ then
-	$P(p)$ is a longest increasing subsequence with last element at index $f$ and
-	$M(p)$ is a longest decreasing subsequence with last element at index $f$.\\
-
-	\textbf{Proof} Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $p$, 
-	suppose that $P(p)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
-	Thus $|s_m|>P(p)$, clearly the sequence $s_m \cup M(p)$
+	If $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$ then
+	$P(\pi)$ is a longest increasing subsequence with last element at index $f$ and
+	$M(\pi)$ is a longest decreasing subsequence with last element at index $f$.\\
+
+	\textbf{Proof} Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
+	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
+	Thus $|s_m|>P(\pi)$, clearly the sequence $s_m \cup M(\pi)$
 	is avoiding (213,231) and is longer than $s$ witch is not possible. 
-	The case for $M(p)$ follows the same idea.$\Box$\\
+	The case for $M(\pi)$ follows the same idea.$\Box$\\
 
 	\textbf{Proposition  \num \thenum}
-	Given a permutation $p$, 
+	Given a permutation $\pi$, 
 	finding the longest subsequence avoiding (231,213)
@@
 
-	\textbf{Proposition \num \thenum } Given two permutation $p_1$ and $p_2$
+	\textbf{Proposition \num \thenum } Given two permutation $\pi_1$ and $\pi_2$
 	The longest common subsequence
-	avoiding (231,213) can be solve in $O(|p_1|^3*|p_2|^3)$.\\
+	avoiding (231,213) can be solve in $O(|\pi_1|^3*|\pi_2|^3)$.\\
 
 	\textbf{Proof } Consider the following problem, 
-	that compute the longest stripe common to $p_1$ and $p_2$.
-	Given two permutation $p_1$ and $p_2$.\\
-
-	$S_{p_1,p_2}(min_1,max_1,min_2,min_2,i_1,i_2)$
+	that compute the longest stripe common to $\pi_1$ and $\pi_2$.
+	Given two permutation $\pi_1$ and $\pi_2$.\\
+
+	$S_{\pi_1,\pi_2}(min_1,max_1,min_2,min_2,i_1,i_2)$
 	= max$\{$ $|m|$ $|$ 
 	s is a pattern occurring 
-	in  $p_1[i_1:]$
+	in  $\pi_1[i_1:]$
 	by the subsequence $s_1$ and $min(s_1)=min_1$ and $max(s_1)=max_1$
 	and s is occurring
-	in  $p_2[i_2:]$
+	in  $\pi_2[i_2:]$
 	by the subsequence $s_2$ and $min(s_2)=min_2$ and $max(s_2)=max_2$	
@@
 	\textbf{BASE :} \\
-	$S_{p_1,p_2,min_1,max_1,min_2,max_2}(|p_1|,|p_2|) = \left\{ 
+	$S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(|\pi_1|,|\pi_2|) = \left\{ 
 			\begin{array}{l l}
-				1 & \text{if $min_1<p_1(j)<max_1$  
+				1 & \text{if $min_1<\pi_1(j)<max_1$  
 				}\\
-				& \text{ and $min_2<p_2(j)<max_2$}\\
+				& \text{ and $min_2<\pi_2(j)<max_2$}\\
 				0 & otherwise\\
@@
 
-	$S_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2) =$\\
+	$S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2) =$\\
 	\indent $ max \left\{ 
 			\begin{array}{l l}
-				S_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2+1) \\
-				S_{p_1,p_2,min_1,max_1,min_2,max_22}(i_1+1,i_2) \\
-				S'_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2)
+				S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2+1) \\
+				S_{\pi_1,\pi_2,min_1,max_1,min_2,max_22}(i_1+1,i_2) \\
+				S'_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2)
 			\end{array} \right. $\vspace{20pt}\\
@@
 	with 
-	$S'_{p_1,p_2,min_1,max_1,min_2,max_2}(i_1,i_2)=\\ \left\{ 
+	$S'_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2)=\\ \left\{ 
 				\begin{array}{l l}
-					1+S_{p_1,p_2,p_1(i_1),max_1,p_2(i_2)}(max_2,i_1+1,i_2+1)  & \text{$p_1(i_1)<min_1$ } \\
-					& \text{and $p_2(i_2)<min_2$} \\
+					1+S_{\pi_1,\pi_2,\pi_1(i_1),max_1,\pi_2(i_2)}(max_2,i_1+1,i_2+1)  & \text{$\pi_1(i_1)<min_1$ } \\
+					& \text{and $\pi_2(i_2)<min_2$} \\
 					&\\
-					1+S_{p_1,p_2,min_1,p_1(i_1),min_2,p_2(i_2)}(i_1+1,i_2+1)  & \text{$p_1(i_1)>max_1$ } \\	
-					&\text{and $p_2(i_2)>max_2$}\\	
+					1+S_{\pi_1,\pi_2,min_1,\pi_1(i_1),min_2,\pi_2(i_2)}(i_1+1,i_2+1)  & \text{$\pi_1(i_1)>max_1$ } \\	
+					&\text{and $\pi_2(i_2)>max_2$}\\	
 					&\\	
@@
 
-	For every pair $i,j$ we either ignore the element of $p_1$,
-	either ignore the element of $p_2$, 
+	For every pair $i,j$ we either ignore the element of $\pi_1$,
+	either ignore the element of $\pi_2$, 
 	either we match as the same step (if possible).
-	Those relation lead to a $O(|p_1|^3*|p_2|^3)$ time and $O(|p_1|^3*|p_2|^3)$ space algorithm.$\Box$
+	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.$\Box$
 

### 2015-02-01 article.tex
introduction

@@
 
+	We focus in this paper on $(213,231)$-avoiding permutation. 
+	The number of $n$-permutations that avoid both 
+	$231$ and $213$ is 
+	$t_0 = 1$ for $n = 0$ and 
+	$t_n =2^{n−1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
+	The permutations that do not contain the permutation pattern $231$
+	are exactly the \emph{stack-sortable permutations} and they are counted by 
+	the Catalan numbers \cite{Knuth:1997:ACP:260999}.
+	A stack-sortable permutation is a permutation whose elements may be sorted by 
+	an algorithm whose internal storage is limited to a single stack data structure.
+
 	This paper is organized as follows.
@@
 We write permutations as words 
-$\sigma = \sigma_1\,\sigma_2\,\ldots\,\sigma_n$, whose letters are distinct
-and uasually consist of the integers $1\,2\,\ldots\,n$.
+$\sigma = \sigma_1\sigma_2\,\ldots\,\sigma_n$, whose letters are distinct
+and uasually consist of the integers $12\,\ldots\,n$.
 For the sake of convenience, 
@@
 $\pi[i:j]$ stand for 
-$\pi_i\,\pi_{i+1}\,\ldots\,\pi_j$,
+$\pi_i\pi_{i+1}\,\ldots\,\pi_j$,
 $\pi[:j]$ stand for $\pi[1:j]$ and
@@
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$. 
-For example, the permutation $\pi = 3\,9\,1\,8\,6\,7\,4\,5\,2$ 
+For example, the permutation $\pi = 391867452$ 
 contains the pattern $\sigma = 51342$, 
 as can be seen in the highlighted subsequence of 
-$\pi = 3\,\mathbf{9}\,\mathbf{1}\,8\,\mathbf{6}\,\mathbf{7}\,\mathbf{4}\,5\,2$
+$\pi = 3\mathbf{9}\mathbf{1}8\mathbf{6}\mathbf{7}\mathbf{4}52$
 (or 
-$\pi = 3\,\mathbf{9}\,\mathbf{1}\,8\,\mathbf{6}\,\mathbf{7}\,4\,\mathbf{5}\,2$
+$\pi = 3\mathbf{9}\mathbf{1}8\mathbf{6}\mathbf{7}4\mathbf{5}2$
 or
-$\pi = 3\,\mathbf{9}\,\mathbf{1}\,8\,\mathbf{6}\,\mathbf{7}\,4\,5\,\mathbf{2}$
+$\pi = 3\mathbf{9}\mathbf{1}8\mathbf{6}\mathbf{7}45\mathbf{2}$
 ). 
-Each subsequence $(9\,1\,6\,7\,4$, 
-$9\,1\,6\,7\,5$, 
-$9\,1\,6\,7\,2$) is called a 
+Each subsequence $(91674$, 
+$91675$, 
+$91672$) is called a 
 \emph{copy}, 
@@
 \emph{occurrence} of $\sigma$. 
-Since the permutation $\pi = 3\,9\,1\,8\,6\,7\,4\,5\,2$  contains no increasing subsequence of length four, $\pi$ avoids $1\,2\,3\,4$.
+Since the permutation $\pi = 391867452$  contains no increasing subsequence of length four, $\pi$ avoids $1234$.
 
@@
 A basic example is if 
-$\pi = \pi_1\,\pi_2\,\ldots\,\pi_n$ avoids $3\,2\,1$, i.e., 
+$\pi = \pi_1\pi_2\,\ldots\,\pi_n$ avoids $321$, i.e., 
 has no decreasing subsequence of length $3$, then its reverse, 
-$\pi' = \pi_n\,\pi_{n-1}\,\ldots\,\pi_1$ avoids $1\,2\,3$, i.e., 
+$\pi' = \pi_n\pi_{n-1}\,\ldots\,\pi_1$ avoids $123$, i.e., 
 has no increasing subsequence of length $3$.
@@
 $1 \leq i < n$ where the following value is bigger than the current one. 
-That is, if $\pi = \pi_1\,\pi_2\,\ldots\,\pi_n$, then
+That is, if $\pi = \pi_1\pi_2\,\ldots\,\pi_n$, then
 $i$ is an ascent if $\pi_i < \pi_{i+1}$.
 For example, the permutation 
-$3\,4\,5\,2\,1\,6\,$7 has ascents (at positions) $1,2,5,6$.
+$345216$7 has ascents (at positions) $1,2,5,6$.
 Similarly, a \emph{descent} is a position 
@@
 two-line notation 
-(that is the top row is $1\,2\,\ldots\,k$ and the bottom row
-is a permutation $\sigma_1\,\sigma_2\,\ldots\,\sigma_k$).
+(that is the top row is $12\,\ldots\,k$ and the bottom row
+is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$).
 We have the following conditions on the top and bottom rows
@@
 	If the bottom line of $\sigma$ contains
-	$\underline{\sigma_i\,\sigma_{i+1}\,\ldots\,\sigma_j}$
+	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
 	then the letters corresponding to 
-	$\sigma_i\,\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
+	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
 	$\sigma$ in a permutaton must be adjacent, whereas there is
@@
 
-		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{213,231}$ 
-		then the first element is either
-		the minimal or the maximal element.\\
-
-		\textbf{Proof} Suppose that we have
-		$\pi \in \mathcal{S}_{n}$, and
-		$\pi(1) \neq 1 $ and $\pi(1) \neq n$ then we have either
-		$\pi(1) ... n ... 1$ or $\pi(1) ... 1 ... n $, either the motif 231 or 213, which is not possible by hypothesis. $\Box$\\
-
-		\textbf{Corollary  \num \thenum} A permutation $\pi \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
+		\begin{lemma}[Folklore]
+		\label{lemma:first element is 1 or n}
+		The 􏰅first element of any $(213,231)$-avoiding permutation
+		must be either $1$ or $n$.
+		\end{lemma}
+
+		\begin{proof} 
+		Any other initial element would serve as a `$2$' in either a 
+		$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+		\end{proof}
+
+		The above lemma gains in interest in the form of the following corollaries.
+
+		\begin{corollary}
+		$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$, 
 		$\pi[i:]$ start either with the maximal element
-		or the minimal element of $\pi[i:]$.\\
-
-		\textbf{Corollary \numl{stripe} \thenum}  If $\pi \in \Av{n}{213,231}$ its stripe can be define such as, \\
-		$\stripe{\pi}{i} = \left\{ 
-  		\begin{array}{l l}
-   			\ustep & \quad \text{if $\pi(i)$ is the minimal element of $\pi[i:]$}\\    
-   			\dstep & \quad \text{if $\pi(i)$ is the maximal element of $\pi[i:]$}\\
-	 	\end{array} \right. 
-	 	$\\
+		or the minimal element of $\pi[i:]$.
+		\end{corollary}
+
+		\begin{corollary}
+		Let $\pi \in \AV_n(213,231)$. We have
+		$$
+		\stripe{\pi}{i} =
+		\begin{cases}
+   			\ustep & \text{if $\pi(i)$ is the minimal element of $\pi[i:]$}\\    
+   			\dstep & \text{if $\pi(i)$ is the maximal element of $\pi[i:]$}\\
+	 	\end{cases}
+	 	$$
+	 	\end{corollary}
 
@@
 		is the maximal (minimal) element of all the permutation 
-		(by Lemma \ref{firstelement}).
+		(by Lemma \ref{lemma:first element is 1 or n}).
 		Moreover if the first element is the maximal (minimal)

### 2015-02-01 article.tex
modif : utilisation des environnement lemma, proposition, coroolary

--- 2015-01-31 article.tex
@@
 
-		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{213,231}$ 
+		\begin{lemma}
+		\label{lemma:firstelement}
+		If a permutation is in $\Av{n}{213,231}$ 
 		then the first element is either
-		the minimal or the maximal element.\\
+		the minimal or the maximal element.
+		\end{lemma}
+
+		%\textbf{Lemma  \numl{firstelement} \thenum}
 
@@
 
-		\textbf{Corollary  \num \thenum} A permutation $\pi \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
+		\begin{corollary}
+		\label{corollary:stripe}
+		A permutation $\pi \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
 		$\pi[i:]$ start either with the maximal element
-		or the minimal element of $\pi[i:]$.\\
-
-		\textbf{Corollary \numl{stripe} \thenum}  If $\pi \in \Av{n}{213,231}$ its stripe can be define such as, \\
+		or the minimal element of $\pi[i:]$.
+		\end{corollary}
+
+		\begin{corollary}
+		If $\pi \in \Av{n}{213,231}$ its stripe can be define such as, \\
 		$\stripe{\pi}{i} = \left\{ 
@@
 	 	\end{array} \right. 
-	 	$\\
-
-		\textbf{Lemma \numl{updown}  \thenum} Let $\pi \in \Av{n}{213,231}$,
+	 	$
+		\end{corollary}
+
+		\begin{lemma}
+		\label{lemma:updown}
+		Let $\pi \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$, 
@@
 		and $\stripe{\pi}{j}=\dstep$
-		then $\pi(i)<\pi(j)$.\\
+		then $\pi(i)<\pi(j)$.
+		\end{lemma}
 
@@
 		is the maximal (minimal) element of all the permutation 
-		(by Lemma \ref{firstelement}).
+		(by Lemma \ref{lemma:firstelement}).
 		Moreover if the first element is the maximal (minimal)
@@
 
-		\textbf{Lemma \numl{upup} \thenum} Let $\pi \in \Av{n}{213,231}$,
+		\begin{lemma}
+		\label{lemma:upup}
+		Let $\pi \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$, 
@@
 		and $\stripe{\pi}{j}=\ustep$
-		then $\pi(i)<\pi(j)$.\\
+		then $\pi(i)<\pi(j)$.
+		\end{lemma}
 
@@
 
-		\textbf{Lemma \numl{downdown} \thenum}  Let $\pi \in \Av{n}{213,231}$,
+		\begin{lemma}
+		\label{lemma:downdown}
+ 		Let $\pi \in \Av{n}{213,231}$,
 		$\forall i,j \in [n]$,
@@
 		and $\stripe{\pi}{j}=\dstep$
-		then $\pi(i)>\pi(j)$.\\
+		then $\pi(i)>\pi(j)$.
+		\end{lemma}
 
@@
 
-		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \Av{n}{213,231}$.
-		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.\\
+		\begin{proposition}
+		\label{proposition:patternMatchingStripe}
+		Let $\ptext, \pmotif \in \Av{n}{213,231}$.
+		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+		\end{proposition}
 
@@
 			$\varphi(x) < \varphi(y)$.
-			And thus, by \textbf{Lemma \ref{upup}},
+			And thus, by \textbf{Lemma \ref{lemma:upup}},
 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
@@
 			$\varphi(x) < \varphi(y)$.
-			And thus, by \textbf{Lemma \ref{updown}},
+			And thus, by \textbf{Lemma \ref{lemma:updown}},
 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
@@
 			$\varphi(y) < \varphi(x)$.
-			And thus, by \textbf{Lemma \ref{downdown}},
+			And thus, by \textbf{Lemma \ref{lemma:downdown}},
 			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
@@
 			$\varphi(y) < \varphi(x)$.
-			And thus, by \textbf{Lemma \ref{updown}},
+			And thus, by \textbf{Lemma \ref{lemma:updown}},
 			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
@@
 		by matching a step whenever it is possible.
-		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{stripe}},
+		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:stripe}},
 		we do not have to compute the stripe advance.
@@
 
-			\textbf{Proposition  \num \thenum} Let $\pmotif$, $\ptext$ 
+			\begin{proposition}
+			Let $\pmotif$, $\ptext$ 
 			be two permutation,
@@
 			if $\pmotif$ 
-			is a motif of $\ptext$.\\
+			is a motif of $\ptext$.
+			\end{proposition}
 
@@
 
-			\textbf{Proposition \num \thenum } Let $\bmotif$ be a bivincular motif 
+			\begin{proposition}
+			Let $\bmotif$ be a bivincular motif 
 			avoiding (231,213), 
@@
 			if $\pmotif$ 
-			appear in $\ptext$.\\
+			appear in $\ptext$.
+			\end{proposition}
 
@@
 
-	\textbf{Proposition  \numl{longestIncreasingSubsequence} \thenum}
+	\begin{proposition}
+	\label{proposition:longestIncreasingSubsequence}
 	If $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$ then
 	$P(\pi)$ is a longest increasing subsequence with last element at index $f$ and
-	$M(\pi)$ is a longest decreasing subsequence with last element at index $f$.\\
+	$M(\pi)$ is a longest decreasing subsequence with last element at index $f$.	
+	\end{proposition}
 
@@
 
-	\textbf{Proposition  \num \thenum}
+	\begin{proposition}
 	Given a permutation $\pi$, 
 	finding the longest subsequence avoiding (231,213)
-	can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and in $O(n)$ space.\\
-
-	\textbf{Proof} The proposition \ref{longestIncreasingSubsequence} lead to algorithm 
+	can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and in $O(n)$ space.	
+	\end{proposition}
+
+	\textbf{Proof} The proposition \ref{proposition:longestIncreasingSubsequence} lead to algorithm 
 	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
@@
 
-	\textbf{Proposition \num \thenum } Given two permutation $\pi_1$ and $\pi_2$
+	\begin{proposition}
+	Given two permutation $\pi_1$ and $\pi_2$
 	The longest common subsequence
-	avoiding (231,213) can be solve in $O(|\pi_1|^3*|\pi_2|^3)$.\\
+	avoiding (231,213) can be solve in $O(|\pi_1|^3*|\pi_2|^3)$.	
+	\end{proposition}
 

### 2015-02-02 article.tex
Section 3

--- 2015-02-01 article.tex
@@
 
-	We focus in this paper on $(213,231)$-avoiding permutation. 
+	We focus in this paper on pattern matching issues for
+	$(213,231)$-avoiding permutations.
 	The number of $n$-permutations that avoid both 
@@
 \end{itemize}
-
-	\section{Pattern Matching Problem With Text and Motif Avoiding (231,213)}
-
-		In this section we focus 
-		on the problem of pattern matching if
-		both the motif and the text
-		avoid (231,213).
-		We first exhibit some properties of a stripe 
-		of a permutation avoiding (231,213).\\
+A bivincular pattern avoids a set of permutations $P$ if its bottom
+row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Both $\pi$ and $\sigma$ are $(231,213)$-avoiding}
+\label{section:both are (231,213)-avoiding}
+
+This section is devoted to presenting a fast algorithm for deciding
+$\sigma \leq \pi$ 
+in case both $\pi$ and $\sigma$ are $(231,213)$-avoiding.
 
@@
 $231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+\qed
 \end{proof}
@@
 
-		\textbf{Lemma \numl{updown}  \thenum} Let $\pi \in \Av{n}{213,231}$,
-		$\forall i,j \in [n]$, 
-		$i<j$, 
+We need the following lemmata.
+
+\begin{lemma}
+\label{lemma:updown}
+Let $\pi \in \AV_n(213,231)$.
+For all $1 \leq i < j \leq n$, 
 if $\stripe{\pi}{i}=\ustep$
 and $\stripe{\pi}{j}=\dstep$
-		then $\pi(i)<\pi(j)$.\\
-
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
-		if $i$ is an ascent and
-		if $j$ is a descent
-		then $\pi(i)<\pi(j)$.\\
-
-		\textbf{Proof} By induction on the size of the permutation :
-		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
-		Suppose the proposition true for $\Av{n}{213,231}$.
-		Let $\pi \in \Av{n}{213,231}$, 
-		we show that the proposition holds for $\pi$.
-		Let $\pi'$ be the permutation $\pi[2:]$.
-		$\pi' \in \Av{n}{213,231}$, so
-		every element of $p'$ verify our lemma (by induction).
-		We still need to compare the first element with the rest.
-		But the first element
-		is the maximal (minimal) element of all the permutation 
-		(by Lemma \ref{lemma:first element is 1 or n}).
-		Moreover if the first element is the maximal (minimal)
-		it will mapped to an descent (ascent).
-		So the proposition is also true
-		for the first element.
-		$\Box$\\
-
-		\textbf{Lemma \numl{upup} \thenum} Let $\pi \in \Av{n}{213,231}$,
+then $\pi(i)<\pi(j)$.
+\end{lemma}
+
+\begin{proof} 
+By induction on the size of the permutation.
+The proposition is certainly true for the $12$ and $21$.
+Suppose the proposition holds true for $\AV_n(213,231)$.
+Let $\pi \in \AV_{n+1}(213,231)$ and
+$\pi'$ be the permutation $\pi[2:]$.
+$\pi' \in \AV_n(213,231)$.
+By induction hypothesis, we only need to compare the first
+element of $\pi'$ to every element in $\pi'$.
+According to lemma~\ref{lemma:first element is 1 or n},
+the first element of $\pi$ is either $1$ or $n$.
+If the first element of $\pi$ is $1$ then $s_\pi(1) = a$
+and $\pi(i) < \pi(j)$ for every $2 \leq j \leq n$.
+If the first element of $\pi$ is $n$ then
+ $s_\pi(1) = d$.
+\qed
+\end{proof}
+
+		\begin{lemma}
+		\label{lemma:upup}
+		Let $\pi \in \AV_n(213,231)$,
 		$\forall i,j \in [n]$, 
@@
 
-		\textbf{Lemma \numl{downdown} \thenum}  Let $\pi \in \Av{n}{213,231}$,
+		\begin{lemma}
+		\label{lemma:downdown}
+ 		Let $\pi \in \AV_n(213,231)$,
 		$\forall i,j \in [n]$,
@@
 
-		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \Av{n}{213,231}$.
-		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.\\
+		\begin{proposition}
+		\label{proposition:patternMatchingStripe}
+		Let $\ptext, \pmotif \in \AV_n(213,231)$.
+		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+		\end{proposition}
 
@@
 		\textbf{Proof}	
-		To solve the permutation pattern for a permutation in $\Av{n}{213,231}$, 
+		To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
 		we find a find a match of the stripe of the pattern in the stripe of the text.

### 2015-02-02 article.tex
Section 3

@@
 
-We need the following lemmata.
+We need the following lemmata
+(the proofs of Lemma~\ref{lemma:upup} and Lemma~\ref{lemma:downdown} 
+are analogous and we omit them).
 
@@
 	and $\stripe{\pi}{j}=\dstep$
-then $\pi(i)<\pi(j)$.
+	then $\pi[i] < \pi[j]$.
 \end{lemma}
@@
 	\label{lemma:upup}
-		Let $\pi \in \AV_n(213,231)$,
-		$\forall i,j \in [n]$, 
-		$i<j$, 
+	Let $\pi \in \AV_n(213,231)$.
+	For all $1 \leq i < j \leq n$,
 	if $\stripe{\pi}{i}=\ustep$
 	and $\stripe{\pi}{j}=\ustep$
-		then $\pi(i)<\pi(j)$.
+	then $\pi[i] < \pi[j]$.
 \end{lemma}
 
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
-		if $i$ is a ascent
-		and $j$ is a ascent
-		and $ i<j$
-		then $p(i)<p(j)$.\\
+		% In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
+		% if $i$ is a ascent
+		% and $j$ is a ascent
+		% and $ i<j$
+		% then $p(i)<p(j)$.\\
 
@@
 	\label{lemma:downdown}
- 		Let $\pi \in \AV_n(213,231)$,
-		$\forall i,j \in [n]$,
-		$i<j$,
-		if $\stripe{\pi}{i}=\dstep$
-		and $\stripe{\pi}{j}=\dstep$
-		then $\pi(i)>\pi(j)$.
+	Let $\pi \in \AV_n(213,231)$.
+	For all $1 \leq i < j \leq n$,
+	if $\stripe{\pi}{i} = \dstep$
+	and $\stripe{\pi}{j} = \dstep$
+	then $\pi[i] > \pi[j]$.
 \end{lemma}
 
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
-		if $i$ is a descent
-		and $j$ is a descent
-		and $ i<j$
-		then $\pi(i)>\pi(j)$.\\
+		% In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
+		% if $i$ is a descent
+		% and $j$ is a descent
+		% and $ i<j$
+		% then $\pi(i)>\pi(j)$.\\
 
@@
 
+Most of the interest of the above lemmata stems from the following proposition.
+
 \begin{proposition}
@@
 	Let $\ptext, \pmotif \in \AV_n(213,231)$.
-		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+	$\pmotif$ is a motif of $\ptext$ if and only if the 
+	stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
 \end{proposition}

### 2015-02-02 article.tex
modification : proposition sur stripe
Section 3

@@
 $\stripew{\pi} = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
-The stripe $s\stripew{\sigma}$ is a \emph{pattern} of the strip $\stripew{\pi}$
-(or $s\stripew{\sigma}$ \emph{occurs} of the strip $\stripew{\pi}$) if $\stripew{\sigma}$ occurs in
+The stripe $\stripew{\sigma}$ is a \emph{pattern} of the strip $\stripew{\pi}$
+(or $\stripew{\sigma}$ \emph{occurs} of the strip $\stripew{\pi}$) if $\stripew{\sigma}$ occurs in
 $\stripew{\pi}$ as a subsequence.
-
-% For two permutations $\
-% The stripe $s\pi$ of $\pi \in S-n$ is a motif pmotif \in \Perm{m}$ is a motif
-% of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
-% such that : \\
-% $\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
-% If a stripe $S_2$ is a motif of a stripe $S_1$,
-% it means that there exists
-% a subsequence of $S_1$ such as
-% this sequence is equal to $S_2$.
-
-% For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ is a motif of  the stripe \\
-% $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6)$ ,
-% because we can match \\
-% $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
-% \begin{figure}[h!]
-% 	\begin{displaymath}
-% 		\xymatrix@=0.3cm{
-% 			\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]\\
-% 			\\
-% 			\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 \\
-% 		}
-% 	\end{displaymath}     
-% \end{figure}		
-% But the stripe $(\dstep,\ustep,\dstep,\dstep,\dstep)$ is not a motif of the stripe\\ $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$.\\
-
-% A \textbf{bivincular motif} generalize
-% a motif. 
-% A bivincular motif allows 
-% to force element to be adjacent in position
-% or/and in value.
-% A bivincular motif
-% is a motif with two set $\bmotif$,
-% the first set contains the first index 
-% of two consecutive indexes
-% and the second set contains the first indexes
-% of the two consecutive elements.
-% Formally, Let $\bmotif$ 
-% be a bivincular motif 
-% and $\ptext$ a permutation.
-% if $i \in \x$,
-% and $i$ is matched with $j$ in $\ptext$
-% then $i+1$ must be matched with $j+1$,
-% with the special case of $0$ and $|\pmotif|$ :
-% if $0 \in \x$ then the first element of $\pmotif$
-% must be matched with the first element of $\ptext$,
-% and if $|\pmotif| \in \x$ then the last element of $\pmotif$
-% must be matched with the last element of $\ptext$.
-% if $i \in \y$,
-% and $i$ is matched with $j$ in $\ptext$
-% then $i+1$ must be matched with $l$
-% such as $\ptext(l)=\ptext(j)+1$,
-% with the special case of $0$ and $|\pmotif|$ :
-% if $0 \in \y$ then the minimal element of $\pmotif$
-% must be matched with the minimal element of $\ptext$,
-% and if $|\pmotif| \in \y$ then the maximal element of $\pmotif$
-% must be matched with the maximal element of $\ptext$.
 
@@
 	\label{proposition:patternMatchingStripe}
-	Let $\ptext, \pmotif \in \AV_n(213,231)$.
-	$\pmotif$ is a motif of $\ptext$ if and only if the 
-	stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+	Let $\sigma \in \AV_k(213,231)$ and $\pi \in \AV_k(213,231)$.
+	$\sigma$ is a motif of $\pi$ if and only if 
+	$s_\sigma$ is a subsequence of $s_\pi$.
 \end{proposition}
 
-		\textbf{Proof} \\
-		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
-		by subsequence $s$.
-		By definition $s$ normalized is equal to
-		$\pmotif$ so they have the same stripe.\\ 
-		$\Leftarrow$ 
-		Let $\ptext$ be a permutation avoiding $(213,231)$, 
-		$S_1$ be its stripe, 
-		$\pmotif$  be a permutation avoiding $(213,231)$, 
-		and $S_2$ its stripe.
-		Let $\phi$ be the function
-		that match $S_2$ to $S_1$.
-		We define $\varphi$ as, 
-		$\forall x \in [|\pmotif|-1]$,
-		$\varphi(x) = \phi(x)$,
-		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
-		Suppose that $\exists x,y \in [|\pmotif|]$, 
-		$\pmotif(x)<\pmotif(y)$ 
-		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
-		without lost of generality we can suppose that $x<y$,
-		Let see all the case possible that can make this 
-		hypothesis possible :
-		\begin{itemize}		
-			\item if $\pmotif(x)<\pmotif(y)$, 
-			$\stripe{\pmotif}{x}=\ustep$ 
-			and $\stripe{\pmotif}{y}=\ustep$
-			(if x and y are increasing in $\pmotif$),
-			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
-			(the match are also increasing).
-			As $x<y$ and as $\varphi$ is an increasing function, 
-			$\varphi(x) < \varphi(y)$.
-			And thus, by \textbf{Lemma \ref{lemma:upup}},
-			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-			Which contradict our hypothesis,
-			so this case is not possible.
+\begin{proof}
+	The forward direction is essentially obvious.
+	For the reverse direction, assume that $s_\sigma$ is a subsequence 
+	of $s_\pi$ and
+	let $\phi : [k] \to [n]$ be the function describing an occurrence
+	of $s_\sigma$ in $s_\pi$ as a subsequence, \emph{i.e.}
+	$s_\sigma[i] = s_\pi[\phi(i)]$ for $1 \leq i \leq k$.
+	Define $\varphi : [k] \to [n]$ as follows:
+	$\varphi(i) = \phi(i)$ for 1 $\leq i \leq k-1$ and
+	$\varphi(k) = \phi(k-1) + 1$.
+	We show that $\varphi$ describes an occurrence of $\sigma$ in 
+	$\pi$.
+	Suppose, aiming at a contradiction, that there exist
+	$1 \leq i < j \leq k$ such that
+	$\sigma[i] < \sigma[j]$ and
+	$\pi[\varphi(i)] > \pi[\varphi(j)]$.
+	Consider the following cases:
+
+	\begin{enumerate}		
+	\item if $\sigma[i] < \sigma [j]$, 
+	$s_\sigma[i] = \ustep$ and $s_\pi[j] = \ustep$,
+	then $s_\pi[\varphi(i)] = \ustep$ and $s_\pi[\varphi(j)] = \ustep$
+	(by construction of $\varphi$).
+	Since $i < j$ and $\varphi$ is an increasing function, we have
+	$\varphi(i) < \varphi(j)$.
+	Therefore, according to Lemma~\ref{lemma:upup},
+	$\pi[\varphi(i)] < \pi[\varphi(j)]$.
+	This is a contradiction.
 
@@
 	The same idea goes if $\stripe{\pmotif}{x}=\dstep$. 	
-
-		\end{itemize}
+	\end{enumerate}
 		So our hypothesis is not realisable.So our assertion is true. $\Box$\\		
+\end{proof}
+
+		% without lost of generality we can suppose that $x<y$,
+% 		Let see all the case possible that can make this 
+% 		hypothesis possible :
+% 		\begin{itemize}		
+% 			\item if $\pmotif(x)<\pmotif(y)$, 
+% 			$\stripe{\pmotif}{x}=\ustep$ 
+% 			and $\stripe{\pmotif}{y}=\ustep$
+% 			(if x and y are increasing in $\pmotif$),
+% 			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
+% 			(the match are also increasing).
+% 			As $x<y$ and as $\varphi$ is an increasing function, 
+% 			$\varphi(x) < \varphi(y)$.
+% 			And thus, by \textbf{Lemma \ref{lemma:upup}},
+% 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
+% 			Which contradict our hypothesis,
+% 			so this case is not possible.
+
+% 			\item if $\pmotif(x)<\pmotif(y)$, 
+% 			$\stripe{\pmotif}{x}=\ustep$ 
+% 			and $\stripe{\pmotif}{y}=\dstep$
+% 			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
+% 			As $x<y$ and as $\varphi$ is an increasing function, 
+% 			$\varphi(x) < \varphi(y)$.
+% 			And thus, by \textbf{Lemma \ref{lemma:updown}},
+% 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
+% 			Which contradict our hypothesis,
+% 			so this case is not possible.
+
+% 			\item if $\pmotif(x)>\pmotif(y)$, 
+% 			$\stripe{\pmotif}{x}=\dstep$ 
+% 			and $\stripe{\pmotif}{y}=\dstep$
+% 			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
+% 			As $x<y$ and as $\varphi$ is an increasing function, 
+% 			$\varphi(y) < \varphi(x)$.
+% 			And thus, by \textbf{Lemma \ref{lemma:downdown}},
+% 			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
+% 			Which contradict our hypothesis,
+% 			so this case is not possible.
+
+% 			\item if $\pmotif(x)>\pmotif(y)$, 
+% 			$\stripe{\pmotif}{x}=\dstep$ 
+% 			and $\stripe{\pmotif}{y}=\ustep$
+% 			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
+% 			As $x<y$ and as $\varphi$ is an increasing function, 
+% 			$\varphi(y) < \varphi(x)$.
+% 			And thus, by \textbf{Lemma \ref{lemma:updown}},
+% 			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
+% 			Which contradict our hypothesis,
+% 			so this case is not possible.$\Box$
+
+% 			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
+% 			Clearly if $\stripe{\pmotif}{x}=\ustep$,
+% 			then $\pmotif(y)-\pmotif(x)>0$ 
+% 			and because we have a match in the ribbon
+% 			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
+% 			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
+% 			So this case is not possible.
+
+% 			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
+% 			if $\stripe{\pmotif}{x}=\ustep$ ie
+% 			$\pmotif(x+1)-\pmotif(x)>0$. Then
+% 			we must have either
+% 			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
+% 			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
+% 			to avoid $231$ or $213$ in the motif.
+% 			Because we have a match in the stripe
+% 			and what we prove above,
+% 			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
+% 			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
+% 			so we have either 		
+% 			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
+% 			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
+% 			which both lead to a $231$ or a $213$ motif
+% 			in the text which is not possible.
+% 			The same idea goes if $\stripe{\pmotif}{x}=\dstep$. 	
+% 					\end{itemize}
+% 		So our hypothesis is not realisable.So our assertion is true. $\Box$\\		
+% \end{proof}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Pattern Matching With Motif Avoiding (231,213)}	
+\label{section:sigma only avoid 231 and 213}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Pattern Matching With Bivincular Motif Avoiding (231,213)}	
+\label{section:bivincular}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Longest Subsequence Avoiding \\(231,213) for a Permutation}
+\label{section:LCS}
 

### 2015-02-02 article.tex
modification : environement proof used. modification : proof change if both permutation avoid 231,213.

--- 2015-02-02 article.tex
@@
 \begin{corollary}
+\label{corollary:minmaxelement}
 $\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$, 
@@
 
-We need the following lemmata.
-
 \begin{lemma}
-\label{lemma:updown}
-Let $\pi \in \AV_n(213,231)$.
-For all $1 \leq i < j \leq n$, 
-if $\stripe{\pi}{i}=\ustep$
-and $\stripe{\pi}{j}=\dstep$
-then $\pi(i)<\pi(j)$.
+\label{lemma:MatchStripeToPermutation}
+Given two permutations $\ptext$,$\pmotif$ avoiding (231,213), If $\stripew{\pmotif}$ is a motif of stripe $\stripew{\ptext}$ by a subsequence $s$, then $\pmotif$ is a motif of $\ptext$ by subsequence $s$.
 \end{lemma}
@@
 \begin{proof} 
-By induction on the size of the permutation.
-The proposition is certainly true for the $12$ and $21$.
-Suppose the proposition holds true for $\AV_n(213,231)$.
-Let $\pi \in \AV_{n+1}(213,231)$ and
-$\pi'$ be the permutation $\pi[2:]$.
-$\pi' \in \AV_n(213,231)$.
-By induction hypothesis, we only need to compare the first
-element of $\pi'$ to every element in $\pi'$.
-According to lemma~\ref{lemma:first element is 1 or n},
-the first element of $\pi$ is either $1$ or $n$.
-If the first element of $\pi$ is $1$ then $s_\pi(1) = a$
-and $\pi(i) < \pi(j)$ for every $2 \leq j \leq n$.
-If the first element of $\pi$ is $n$ then
- $s_\pi(1) = d$.
-\qed
+We prove the lemma by induction on the size of the motif.
+Suppose that we have the motif $(12)$, thus the stripe is $\ustep$.
+If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation.
+Same goes for the permutation $(21)$.
+Now, suppose that the lemma is true for every motif of size $n$.
+Let $\pmotif$ be a motif of size $n+1$ avoiding $(213,231)$, and $\ptext$ a permutation avoiding $(213,231)$.
+If there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$ by subsequence $s$, then there is a match of $\stripew{\pmotif}[2:]$ in $\stripew{\ptext}[2:]$ by subsequence $s[2:]$, and by induction there is a match of $\pmotif[2:]$ in $\ptext[2:]$ by subsequence $s[2:]$.
+Moreover suppose that the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
 \end{proof}
-
-		\begin{lemma}
-		\label{lemma:upup}
-		Let $\pi \in \AV_n(213,231)$,
-		$\forall i,j \in [n]$, 
-		$i<j$, 
-		if $\stripe{\pi}{i}=\ustep$
-		and $\stripe{\pi}{j}=\ustep$
-		then $\pi(i)<\pi(j)$.
-		\end{lemma}
-
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
-		if $i$ is a ascent
-		and $j$ is a ascent
-		and $ i<j$
-		then $p(i)<p(j)$.\\
-
-		%\textbf{Proof} Same as before.\\
-
-%		\textbf{Proof} By induction on the size of the permutation :
-%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
-%		Suppose the proposition true for $\C{n}$.
-%		Let $p \in \C{n+1}$, 
-%		we show that the proposition holds for $p$.
-%		Let $p'$ be the permutation $p[2:]$.
-%		$p' \in \C{n}$, so
-%		every element of $p'$ verify our lemma (by induction).
-%		We still need to compare the first element with the rest.
-%		Except that the first element
-%		is the maximal (minimal) element of all the permutation 
-%		(by Corollary \ref{stripe}).
-%		Moreover if the first element is the maximal (minimal)
-%		it will mapped to an descent (\pi_2).
-%		So the proposition is also true
-%		for the first element.
-%		$\Box$\\
-
-		\begin{lemma}
-		\label{lemma:downdown}
- 		Let $\pi \in \AV_n(213,231)$,
-		$\forall i,j \in [n]$,
-		$i<j$,
-		if $\stripe{\pi}{i}=\dstep$
-		and $\stripe{\pi}{j}=\dstep$
-		then $\pi(i)>\pi(j)$.
-		\end{lemma}
-
-		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
-		if $i$ is a descent
-		and $j$ is a descent
-		and $ i<j$
-		then $\pi(i)>\pi(j)$.\\
-
-		%\textbf{Proof} Same as before.\\
-
-%		\textbf{Proof} By induction on the size of the permutation :
-%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
-%		Suppose the proposition true for $\C{n}$.
-%		Let $p \in \C{n+1}$, 
-%		we show that the proposition holds for $p$.
-%		Let $p'$ be the permutation $p[2:]$.
-%		$p' \in \C{n}$, so
-%		every element of $p'$ verify our lemma (by induction).
-%		We still need to compare the first element with the rest.
-%		Except that the first element
-%		is the maximal (minimal) element of all the permutation 
-%		(by Corollary \ref{stripe}).
-%		Moreover if the first element is the maximal (minimal)
-%		it will mapped to an descent (ascent).
-%		So the proposition is also true
-%		for the first element.
-%		$\Box$\\
 
@@
 \label{proposition:patternMatchingStripe}
-		Let $\ptext, \pmotif \in \AV_n(213,231)$.
-		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+Let $\ptext$ and $\pmotif$ be two permutations avoiding (213,231).
+$\pmotif$ is a motif of $\ptext$ if and only if the 
+stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
 \end{proposition}
 
-		\textbf{Proof} \\
-		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
-		by subsequence $s$.
-		By definition $s$ normalized is equal to
+\begin{proof}
+$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$ by subsequence $s$. By definition $s$ normalized is equal to
 $\pmotif$ so they have the same stripe.\\ 
-		$\Leftarrow$ 
-		Let $\ptext$ be a permutation avoiding $(213,231)$, 
-		$S_1$ be its stripe, 
-		$\pmotif$  be a permutation avoiding $(213,231)$, 
-		and $S_2$ its stripe.
-		Let $\phi$ be the function
-		that match $S_2$ to $S_1$.
-		We define $\varphi$ as, 
-		$\forall x \in [|\pmotif|-1]$,
-		$\varphi(x) = \phi(x)$,
-		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
-		Suppose that $\exists x,y \in [|\pmotif|]$, 
-		$\pmotif(x)<\pmotif(y)$ 
-		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
-		without lost of generality we can suppose that $x<y$,
-		Let see all the case possible that can make this 
-		hypothesis possible :
-		\begin{itemize}		
-			\item if $\pmotif(x)<\pmotif(y)$, 
-			$\stripe{\pmotif}{x}=\ustep$ 
-			and $\stripe{\pmotif}{y}=\ustep$
-			(if x and y are increasing in $\pmotif$),
-			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
-			(the match are also increasing).
-			As $x<y$ and as $\varphi$ is an increasing function, 
-			$\varphi(x) < \varphi(y)$.
-			And thus, by \textbf{Lemma \ref{lemma:upup}},
-			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-			Which contradict our hypothesis,
-			so this case is not possible.
-
-			\item if $\pmotif(x)<\pmotif(y)$, 
-			$\stripe{\pmotif}{x}=\ustep$ 
-			and $\stripe{\pmotif}{y}=\dstep$
-			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
-			As $x<y$ and as $\varphi$ is an increasing function, 
-			$\varphi(x) < \varphi(y)$.
-			And thus, by \textbf{Lemma \ref{lemma:updown}},
-			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-			Which contradict our hypothesis,
-			so this case is not possible.
-
-			\item if $\pmotif(x)>\pmotif(y)$, 
-			$\stripe{\pmotif}{x}=\dstep$ 
-			and $\stripe{\pmotif}{y}=\dstep$
-			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
-			As $x<y$ and as $\varphi$ is an increasing function, 
-			$\varphi(y) < \varphi(x)$.
-			And thus, by \textbf{Lemma \ref{lemma:downdown}},
-			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
-			Which contradict our hypothesis,
-			so this case is not possible.
-
-			\item if $\pmotif(x)>\pmotif(y)$, 
-			$\stripe{\pmotif}{x}=\dstep$ 
-			and $\stripe{\pmotif}{y}=\ustep$
-			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
-			As $x<y$ and as $\varphi$ is an increasing function, 
-			$\varphi(y) < \varphi(x)$.
-			And thus, by \textbf{Lemma \ref{lemma:updown}},
-			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
-			Which contradict our hypothesis,
-			so this case is not possible.$\Box$
-
-			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
-			Clearly if $\stripe{\pmotif}{x}=\ustep$,
-			then $\pmotif(y)-\pmotif(x)>0$ 
-			and because we have a match in the ribbon
-			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
-			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
-			So this case is not possible.
-
-			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
-			if $\stripe{\pmotif}{x}=\ustep$ ie
-			$\pmotif(x+1)-\pmotif(x)>0$. Then
-			we must have either
-			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
-			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
-			to avoid $231$ or $213$ in the motif.
-			Because we have a match in the stripe
-			and what we prove above,
-			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
-			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
-			so we have either 		
-			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
-			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
-			which both lead to a $231$ or a $213$ motif
-			in the text which is not possible.
-			The same idea goes if $\stripe{\pmotif}{x}=\dstep$.
-
-		\end{itemize}
-		So our hypothesis is not realisable.So our assertion is true. $\Box$\\
+$\Leftarrow$ This is proved by lemma \ref{lemma:MatchStripeToPermutation}.
+\end{proof}
+
+%We need the following lemmata
+%(the proofs of Lemma~\ref{lemma:upup} and Lemma~\ref{lemma:downdown} 
+%are analogous and we omit them).
+%
+%\begin{lemma}
+%	\label{lemma:updown}
+%	Let $\pi \in \AV_n(213,231)$.
+%	For all $1 \leq i < j \leq n$, 
+%	if $\stripe{\pi}{i}=\ustep$
+%	and $\stripe{\pi}{j}=\dstep$
+%	then $\pi[i] < \pi[j]$.
+%\end{lemma}
+%		
+%\begin{proof} 
+%By induction on the size of the permutation.
+%The proposition is certainly true for the $12$ and $21$.
+%Suppose the proposition holds true for $\AV_n(213,231)$.
+%Let $\pi \in \AV_{n+1}(213,231)$ and
+%$\pi'$ be the permutation $\pi[2:]$.
+%$\pi' \in \AV_n(213,231)$.
+%By induction hypothesis, we only need to compare the first
+%element of $\pi'$ to every element in $\pi'$.
+%According to lemma~\ref{lemma:first element is 1 or n},
+%the first element of $\pi$ is either $1$ or $n$.
+%If the first element of $\pi$ is $1$ then $s_\pi(1) = a$
+%and $\pi(i) < \pi(j)$ for every $2 \leq j \leq n$.
+%If the first element of $\pi$ is $n$ then
+% $s_\pi(1) = d$.
+%\qed
+%\end{proof}
+%
+%\begin{lemma}
+%	\label{lemma:upup}
+%	Let $\pi \in \AV_n(213,231)$.
+%	For all $1 \leq i < j \leq n$,
+%	if $\stripe{\pi}{i}=\ustep$
+%	and $\stripe{\pi}{j}=\ustep$
+%	then $\pi[i] < \pi[j]$.
+%\end{lemma}
+%		
+%
+%\begin{lemma}
+%	\label{lemma:downdown}
+%	Let $\pi \in \AV_n(213,231)$.
+%	For all $1 \leq i < j \leq n$,
+%	if $\stripe{\pi}{i} = \dstep$
+%	and $\stripe{\pi}{j} = \dstep$
+%	then $\pi[i] > \pi[j]$.
+%\end{lemma}
+%
+%
+%Most of the interest of the above lemmata stems from the following proposition.
+%
+%\begin{proposition}
+%	\label{proposition:patternMatchingStripe}
+%	Let $\ptext$ and $\pmotif$ be two permutations avoiding (213,231).
+%	$\pmotif$ is a motif of $\ptext$ if and only if the 
+%	stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+%\end{proposition}
+%
+%		
+%		\textbf{Proof} \\
+%		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
+%		by subsequence $s$.
+%		By definition $s$ normalized is equal to
+%		$\pmotif$ so they have the same stripe.\\ 
+%		$\Leftarrow$ 
+%		Let $\ptext$ be a permutation avoiding $(213,231)$, 
+%		$S_1$ be its stripe, 
+%		$\pmotif$  be a permutation avoiding $(213,231)$, 
+%		and $S_2$ its stripe.
+%		Let $\phi$ be the function
+%		that match $S_2$ to $S_1$.
+%		We define $\varphi$ as, 
+%		$\forall x \in [|\pmotif|-1]$,
+%		$\varphi(x) = \phi(x)$,
+%		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
+%		Suppose that $\exists x,y \in [|\pmotif|]$, 
+%		$\pmotif(x)<\pmotif(y)$ 
+%		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
+%		without lost of generality we can suppose that $x<y$,
+%		Let see all the case possible that can make this 
+%		hypothesis possible :
+%		\begin{itemize}		
+%			\item if $\pmotif(x)<\pmotif(y)$, 
+%			$\stripe{\pmotif}{x}=\ustep$ 
+%			and $\stripe{\pmotif}{y}=\ustep$
+%			(if x and y are increasing in $\pmotif$),
+%			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
+%			(the match are also increasing).
+%			As $x<y$ and as $\varphi$ is an increasing function, 
+%			$\varphi(x) < \varphi(y)$.
+%			And thus, by \textbf{Lemma \ref{lemma:upup}},
+%			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
+%			Which contradict our hypothesis,
+%			so this case is not possible.
+%		
+%			\item if $\pmotif(x)<\pmotif(y)$, 
+%			$\stripe{\pmotif}{x}=\ustep$ 
+%			and $\stripe{\pmotif}{y}=\dstep$
+%			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
+%			As $x<y$ and as $\varphi$ is an increasing function, 
+%			$\varphi(x) < \varphi(y)$.
+%			And thus, by \textbf{Lemma \ref{lemma:updown}},
+%			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
+%			Which contradict our hypothesis,
+%			so this case is not possible.			
+%
+%			\item if $\pmotif(x)>\pmotif(y)$, 
+%			$\stripe{\pmotif}{x}=\dstep$ 
+%			and $\stripe{\pmotif}{y}=\dstep$
+%			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
+%			As $x<y$ and as $\varphi$ is an increasing function, 
+%			$\varphi(y) < \varphi(x)$.
+%			And thus, by \textbf{Lemma \ref{lemma:downdown}},
+%			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
+%			Which contradict our hypothesis,
+%			so this case is not possible.
+%			
+%			\item if $\pmotif(x)>\pmotif(y)$, 
+%			$\stripe{\pmotif}{x}=\dstep$ 
+%			and $\stripe{\pmotif}{y}=\ustep$
+%			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
+%			As $x<y$ and as $\varphi$ is an increasing function, 
+%			$\varphi(y) < \varphi(x)$.
+%			And thus, by \textbf{Lemma \ref{lemma:updown}},
+%			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
+%			Which contradict our hypothesis,
+%			so this case is not possible.$\Box$
+%			
+%			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
+%			Clearly if $\stripe{\pmotif}{x}=\ustep$,
+%			then $\pmotif(y)-\pmotif(x)>0$ 
+%			and because we have a match in the ribbon
+%			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
+%			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
+%			So this case is not possible.
+%			
+%			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
+%			if $\stripe{\pmotif}{x}=\ustep$ ie
+%			$\pmotif(x+1)-\pmotif(x)>0$. Then
+%			we must have either
+%			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
+%			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
+%			to avoid $231$ or $213$ in the motif.
+%			Because we have a match in the stripe
+%			and what we prove above,
+%			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
+%			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
+%			so we have either 		
+%			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
+%			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
+%			which both lead to a $231$ or a $213$ motif
+%			in the text which is not possible.
+%			The same idea goes if $\stripe{\pmotif}{x}=\dstep$. 			
+%			
+%		\end{itemize}
+%		So our hypothesis is not realisable.So our assertion is true. $\Box$\\
 
@@
 
-		\textbf{Proof}	
+		\begin{proof}
 		To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
@@
 		by matching a step whenever it is possible.
-		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:stripe}},
+		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:minmaxelement}},
 		we do not have to compute the stripe advance.
-		Therefore we have an linear (online) algorithm.$\Box$\\
+		Therefore we have an linear (online) algorithm.
+		\end{proof}
 
@@
 
-			For the algorithm we introduce a decomposition,
+			For the proof and the algorithm we introduce a decomposition,
 			we decompose the motif into
@@
 
+			\begin{proof}
 			Given a ascent (descent) segment $S(s)$,
@@
 			Moreover the basic case can be computed in $O(|\ptext|^2)$
-			and the induction on $O(|\pmotif|*|\ptext|^2)$ $\Box$.
+			and the induction on $O(|\pmotif|*|\ptext|^2)$.
+			\end{proof}
 
@@
 
-			\textbf{Proof }
+			\begin{proof}
 			We consider the following problem :\\
@@
 			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,k)$
-			is true. $\Box$
+			is true.			
+			\end{proof}
 
@@
 
-	\textbf{Proof} Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
+	\begin{proof}
+	Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
 	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
@@
 	is avoiding (213,231) and is longer than $s$ witch is not possible. 
-	The case for $M(\pi)$ follows the same idea.$\Box$\\
+	The case for $M(\pi)$ follows the same idea.
+	\end{proof}
 
@@
 
-	\textbf{Proof} The proposition \ref{proposition:longestIncreasingSubsequence} lead to algorithm 
+	\begin{proof}
+	The proposition \ref{proposition:longestIncreasingSubsequence} lead to algorithm 
 	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
-	Computing the longest increasing and decreasing can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.$\Box$\\
+	Computing the longest increasing and decreasing can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
+	\end{proof}
 
@@
 
-	\textbf{Proof } Consider the following problem, 
+	\begin{proof}
+	Consider the following problem, 
 	that compute the longest stripe common to $\pi_1$ and $\pi_2$.
@@
 	either we match as the same step (if possible).
-	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.$\Box$
+	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.		
+	\end{proof}
 

### 2015-02-02 article.tex

@@
 \label{lemma:first element is 1 or n}
-The 􏰅first element of any $(213,231)$-avoiding permutation
+The first element of any $(213,231)$-avoiding permutation
 must be either $1$ or $n$.
@@
 $231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
-\qed
 \end{proof}
@@
 \begin{proposition}
-\label{proposition:patternMatchingStripe}
-Let $\ptext$ and $\pmotif$ be two permutations avoiding (213,231).
-$\pmotif$ is a motif of $\ptext$ if and only if the 
-stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
+Let $\sigma \in \AV_k(213,231)$ and $\pi \in \AV_k(213,231)$.
+$\sigma$ is a motif of $\pi$ if and only if 
+$s_\sigma$ is a subsequence of $s_\pi$.
 \end{proposition}
 
-\begin{proof}
-$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$ by subsequence $s$. By definition $s$ normalized is equal to
-$\pmotif$ so they have the same stripe.\\ 
-$\Leftarrow$ This is proved by lemma \ref{lemma:MatchStripeToPermutation}.
-\end{proof}
-
-%We need the following lemmata
-%(the proofs of Lemma~\ref{lemma:upup} and Lemma~\ref{lemma:downdown} 
-%are analogous and we omit them).
-%
-%\begin{lemma}
-%	\label{lemma:updown}
-%	Let $\pi \in \AV_n(213,231)$.
-%	For all $1 \leq i < j \leq n$, 
-%	if $\stripe{\pi}{i}=\ustep$
-%	and $\stripe{\pi}{j}=\dstep$
-%	then $\pi[i] < \pi[j]$.
-%\end{lemma}
-%		
-%\begin{proof} 
-%By induction on the size of the permutation.
-%The proposition is certainly true for the $12$ and $21$.
-%Suppose the proposition holds true for $\AV_n(213,231)$.
-%Let $\pi \in \AV_{n+1}(213,231)$ and
-%$\pi'$ be the permutation $\pi[2:]$.
-%$\pi' \in \AV_n(213,231)$.
-%By induction hypothesis, we only need to compare the first
-%element of $\pi'$ to every element in $\pi'$.
-%According to lemma~\ref{lemma:first element is 1 or n},
-%the first element of $\pi$ is either $1$ or $n$.
-%If the first element of $\pi$ is $1$ then $s_\pi(1) = a$
-%and $\pi(i) < \pi(j)$ for every $2 \leq j \leq n$.
-%If the first element of $\pi$ is $n$ then
-% $s_\pi(1) = d$.
-%\qed
-%\end{proof}
-%
-%\begin{lemma}
-%	\label{lemma:upup}
-%	Let $\pi \in \AV_n(213,231)$.
-%	For all $1 \leq i < j \leq n$,
-%	if $\stripe{\pi}{i}=\ustep$
-%	and $\stripe{\pi}{j}=\ustep$
-%	then $\pi[i] < \pi[j]$.
-%\end{lemma}
-%		
-%
-%\begin{lemma}
-%	\label{lemma:downdown}
-%	Let $\pi \in \AV_n(213,231)$.
-%	For all $1 \leq i < j \leq n$,
-%	if $\stripe{\pi}{i} = \dstep$
-%	and $\stripe{\pi}{j} = \dstep$
-%	then $\pi[i] > \pi[j]$.
-%\end{lemma}
-%
-%
-%Most of the interest of the above lemmata stems from the following proposition.
-%
-%\begin{proposition}
-%	\label{proposition:patternMatchingStripe}
-%	Let $\ptext$ and $\pmotif$ be two permutations avoiding (213,231).
-%	$\pmotif$ is a motif of $\ptext$ if and only if the 
-%	stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
-%\end{proposition}
-%
-%		
-%		\textbf{Proof} \\
-%		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
-%		by subsequence $s$.
-%		By definition $s$ normalized is equal to
-%		$\pmotif$ so they have the same stripe.\\ 
-%		$\Leftarrow$ 
-%		Let $\ptext$ be a permutation avoiding $(213,231)$, 
-%		$S_1$ be its stripe, 
-%		$\pmotif$  be a permutation avoiding $(213,231)$, 
-%		and $S_2$ its stripe.
-%		Let $\phi$ be the function
-%		that match $S_2$ to $S_1$.
-%		We define $\varphi$ as, 
-%		$\forall x \in [|\pmotif|-1]$,
-%		$\varphi(x) = \phi(x)$,
-%		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
-%		Suppose that $\exists x,y \in [|\pmotif|]$, 
-%		$\pmotif(x)<\pmotif(y)$ 
-%		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
 		% without lost of generality we can suppose that $x<y$,
@@
 % 			so this case is not possible.
-%		
-%			\item if $\pmotif(x)<\pmotif(y)$, 
-%			$\stripe{\pmotif}{x}=\ustep$ 
-%			and $\stripe{\pmotif}{y}=\dstep$
-%			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
-%			As $x<y$ and as $\varphi$ is an increasing function, 
-%			$\varphi(x) < \varphi(y)$.
-%			And thus, by \textbf{Lemma \ref{lemma:updown}},
-%			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-%			Which contradict our hypothesis,
-%			so this case is not possible.			
-%
-%			\item if $\pmotif(x)>\pmotif(y)$, 
-%			$\stripe{\pmotif}{x}=\dstep$ 
-%			and $\stripe{\pmotif}{y}=\dstep$
-%			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
-%			As $x<y$ and as $\varphi$ is an increasing function, 
-%			$\varphi(y) < \varphi(x)$.
-%			And thus, by \textbf{Lemma \ref{lemma:downdown}},
-%			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
-%			Which contradict our hypothesis,
-%			so this case is not possible.
-%			
-%			\item if $\pmotif(x)>\pmotif(y)$, 
-%			$\stripe{\pmotif}{x}=\dstep$ 
-%			and $\stripe{\pmotif}{y}=\ustep$
-%			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
-%			As $x<y$ and as $\varphi$ is an increasing function, 
-%			$\varphi(y) < \varphi(x)$.
-%			And thus, by \textbf{Lemma \ref{lemma:updown}},
-%			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
-%			Which contradict our hypothesis,
-%			so this case is not possible.$\Box$
-%			
-%			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
-%			Clearly if $\stripe{\pmotif}{x}=\ustep$,
-%			then $\pmotif(y)-\pmotif(x)>0$ 
-%			and because we have a match in the ribbon
-%			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
-%			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
-%			So this case is not possible.
-%			
-%			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
-%			if $\stripe{\pmotif}{x}=\ustep$ ie
-%			$\pmotif(x+1)-\pmotif(x)>0$. Then
-%			we must have either
-%			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
-%			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
-%			to avoid $231$ or $213$ in the motif.
-%			Because we have a match in the stripe
-%			and what we prove above,
-%			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
-%			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
-%			so we have either 		
-%			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
-%			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
-%			which both lead to a $231$ or a $213$ motif
-%			in the text which is not possible.
-%			The same idea goes if $\stripe{\pmotif}{x}=\dstep$. 			
-%			
-%		\end{itemize}
-%		So our hypothesis is not realisable.So our assertion is true. $\Box$\\
+
+\begin{proof}
+$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$ by subsequence $s$. By definition $s$ normalized is equal to
+$\pmotif$ so they have the same stripe.\\ 
+$\Leftarrow$ This is proved by lemma \ref{lemma:MatchStripeToPermutation}.
+\end{proof}
 

### 2015-02-02 article.tex
modification : used of [] for an element of a permutation instead of ()

@@
 \begin{cases}
-			\ustep & \text{if $\pi(i)$ is the minimal element of $\pi[i:]$}\\    
-			\dstep & \text{if $\pi(i)$ is the maximal element of $\pi[i:]$}\\
+			\ustep & \text{if $\pi[i]$ is the minimal element of $\pi[i:]$}\\    
+			\dstep & \text{if $\pi[i]$ is the maximal element of $\pi[i:]$}\\
 	\end{cases}
@@
 			is to choose the
-			minimal (maximal) element $\ptext(i')$
+			minimal (maximal) element $\ptext[i']$
 			such that :
@@
 						\\
-						\text{ $LIS(i,i',\ptext(i')) \leq S(1)$}\}&\\
+						\text{ $LIS(i,i',\ptext[i']) \leq S(1)$}\}&\\
 
@@
 						\text{if $\stripe{\pmotif}{IMP(1)}=\dstep$} \\
-						\text{ $LDS(i,i',\ptext(i')) \leq S(1)$}\}&\\
+						\text{ $LDS(i,i',\ptext[i']) \leq S(1)$}\}&\\
 
@@
 					\begin{array}{l l}
-						true & \text{if $min<\ptext(j)<max$
+						true & \text{if $min<\ptext[j]<max$
 						}\\
@@
 					\begin{array}{l l}
-						true & \text{if $min<\ptext(|\ptext|)<max$
+						true & \text{if $min<\ptext[|\ptext|]<max$
 						}\\
@@
 			and $|\pmotif| \in  \y$ 
-			and $\pmotif(|\pmotif|)$ is the maximal element: \\		
+			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
 			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $min<\ptext(j)<max$
+						true & \text{if $min<\ptext[j]<max$
 						}\\
-						&\text{$\ptext(j)$ is the maximal element}\\
+						&\text{$\ptext[j]$ is the maximal element}\\
 						false & otherwise\\
@@
 			and $|\pmotif| \in  \y$ 
-			and $\pmotif(|\pmotif|)$ is the maximal element: \\		
+			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
 			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $min<\ptext(|\ptext|)<max$
+						true & \text{if $min<\ptext[|\ptext|]<max$
 						}\\
-						&\text{$\ptext(|\ptext|)$ is the maximal element}\\
+						&\text{$\ptext[|\ptext|]$ is the maximal element}\\
 						false & otherwise\\
@@
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$
@@
 							& \text{and $i \notin \y$ }\\
-							& \text{and $min<\ptext(j)<max$} \\
+							& \text{and $min<\ptext[j]<max$} \\
 						&\\
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							& \text{and $i \notin \x$ and $i \notin \y$  }\\
-							& \text{and $min<\ptext(j)<max$} \\		
+							& \text{and $min<\ptext[j]<max$} \\		
 						&\\
@@
 							& \text{and $i \in \x$ and $i \notin \y$}\\
-							& \text{and $min<\ptext(j)<max$} \\
+							& \text{and $min<\ptext[j]<max$} \\
 						&\\
@@
 							& \text{and $i \in \x$ and $i \notin \y$ }\\
-							& \text{and $min<\ptext(j)<max$} \\
+							& \text{and $min<\ptext[j]<max$} \\
 
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							&\text{and $i \notin \x$ and $i \in \y$}\\
-							& \text{and $min<\ptext(j)<max$} \\
-							&\text{and $\ptext^{-1}(\ptext(j)+1)>j$}\\
+							& \text{and $min<\ptext[j]<max$} \\
+							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
+						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
 							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							&\text{and $i \notin \x$ and $i \in \y$ }\\	
-							& \text{and $min<\ptext(j)<max$} \\
-							&\text{and $\ptext^{-1}(\ptext(j)-1)>j$}\\
+							& \text{and $min<\ptext[j]<max$} \\
+							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext(j)),max}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),max}(i+1,j+1) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							&\text{and $i \in \x$ and $i \in \y$}\\ 
-							&\text{and $\ptext(j)+1=\ptext(j+1)$ }\\
-							& \text{and $min<\ptext(j)<max$} \\
+							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
+							& \text{and $min<\ptext[j]<max$} \\
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,j+1)
+						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,j+1)
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							&\text{and $i \in \x$ and $i \in \y$}\\ 
-							&\text{and $\ptext(j)-1=\ptext(j+1)$ }\\
-							& \text{and $min<\ptext(j)<max$} \\
+							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
+							& \text{and $min<\ptext[j]<max$} \\
 						&\\	
@@
 			If $i \notin \x$ and $i \notin \y$,
-			we match the current element of $\pmotif$ ($\pmotif(i)$)
-			with the current element of $\ptext$ ($\ptext(j)$), if possible.
+			we match the current element of $\pmotif$ ($\pmotif[i]$)
+			with the current element of $\ptext$ ($\ptext[j]$), if possible.
 			Then we match $\pmotif[i+1:]$ with 
@@
 			If $i \in \x$ and $i \notin \y$,
-			we match $\pmotif(i)$ to $\ptext(j)$, 
+			we match $\pmotif[i]$ to $\ptext[j]$, 
 			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
 			with the condition that
-			$\pmotif(i+1)$ is matched to $\ptext(j+1)$.\\
+			$\pmotif[i+1]$ is matched to $\ptext[j+1]$.\\
 
 			If $i \notin \x$, $i \in \y$ and i is a descent,
-			we match $\pmotif(i)$ to $\ptext(j)$, 
+			we match $\pmotif[i]$ to $\ptext[j]$, 
 			then we match $\pmotif[i+1:]$ 
-			with $\ptext[\ptext^{-1}(\ptext(j)-1):]$
+			with $\ptext[\ptext^{-1}(\ptext[j]-1):]$
 			with the condition that
-			$\pmotif(i+1)$ is matched to the element $\ptext(j)-1$.\\
+			$\pmotif[i+1]$ is matched to the element $\ptext[j]-1$.\\
 
 			If $i \notin \x$, $i \in \y$ and i is an ascent,
-			we match $\pmotif(i)$ to $\ptext(j)$, 
+			we match $\pmotif[i]$ to $\ptext[j]$, 
 			then we match $\pmotif[i+1:]$ 
-			with $\ptext[\ptext^{-1}(\ptext(j)+1):]$
+			with $\ptext[\ptext^{-1}(\ptext[j]+1):]$
 			with the condition that
-			$\pmotif(i+1)$ is matched to the element $\ptext(j)+1$.\\
+			$\pmotif[i+1]$ is matched to the element $\ptext[j]+1$.\\
 
 			If $i \in \x$, $i \in \y$ and i is a descent,
-			we match $\pmotif(i)$ to $\ptext(j)$, 
+			we match $\pmotif[i]$ to $\ptext[j]$, 
 			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
 			with the condition that
-			$\pmotif(i+1)$ is matched to $\ptext(j+1)$,
-			and that $\ptext(j+1)=\pmotif(i)-1$.\\
+			$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
+			and that $\ptext[j+1]=\pmotif[i]-1$.\\
 
 			If $i \in \x$, $i \in \y$ and i is an ascent,
-			we match $\pmotif(i)$ to $\ptext(j)$, 
+			we match $\pmotif[i]$ to $\ptext[j]$, 
 			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
 			with the condition that
-			$\pmotif(i+1)$ is matched to $\ptext(j+1)$,
-			and that $\ptext(j+1)=\pmotif(i)+1$.\\
+			$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
+			and that $\ptext[j+1]=\pmotif[i]+1$.\\
 

### 2015-02-03 article.tex
modification : in section 4 used factor instead of segment and used left most element instead of important  \n add : maccro for factor and left most element

@@
 \newcommand{\ustep}{a}
+
+%first
+\DeclareMathOperator{\firsta}{L}
+\newcommand{\first}[1]{\firsta({#1})}
+
+\DeclareMathOperator{\factora}{F}
+\newcommand{\factor}[1]{\factora({#1})}
 
@@
 
-			For the proof and the algorithm we introduce a decomposition,
-			we decompose the motif into
-			adjacent element of same step in the stripe 
-			(called such sequence segment),
-			add the last element to the right most segment,
-			and label them form right to left
-			with increasing number.
-			Let's call this decomposition $S$.
-			For each segment, we call important 
-			the leftmost element denoted by $IMP$.
-			For example, given the motif $(12,11,10,1,2,3,4,9,8,5,6,7)$,
-			$S(1)=(5,6,7)$, $IMP(1)=5$, 
-			$S(2)=(9,8)$, $IMP(2)=9$, 
-			$S(3)=(1,2,3,4)$, $IMP(3)=1$, 
-			$S(4)=(12,11,10)$ and $IMP(4)=12$.\\
+For the proof and the algorithm we introduce a decomposition : we decompose the stripe of the motif into factor of same letter, and label those factor from right to left.
+We also need to add the last index into the first factor.
+For each factor, we denote the left most element by $\firsta$.
+For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$.
+\\
 
 \begin{proof}
-			Given a ascent (descent) segment $S(s)$,
-			if we want to
-			match the suffix $s_ns_{s-1}...s_1$
-			starting with an ascent (descent),
-			and given that we know every
-			match of $s_{s-1}...s_1$,
-			the optimal way of matching
-			$s_{s-1}...s_1$
-			is to choose the match
-			that minimize (maximize)
-			the maximal (minimal)
-			element of the match
-			and that allow a match
-			of $s_n$.			
-			In other word if we want to match 
-			$\pmotif[IMP(s):]$
-			with $\ptext[i:]$
-			and match $IMP(s)$
-			with $i$.
-			The optimal way
-			of matching
-			$\pmotif[IMP(s-1):]$
-			is to choose the
-			minimal (maximal) element $\ptext[i']$
-			such that :
-			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
-			and $IMP(s-1)$ is matched with $e$.
-			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
-			and $IMP(s)$ is matched with $i$.
-			(3) Every elements of the match of (2),
-			is inferior (superior) to the minimal (maximal) element of the match of (1).
-			Indeed when we will 
-			match $s_{n+1}s_ns_{s-1}...s_1$
-			more element will be available,
-			because every matched 
-			element of $s_{n+1}$
-			must be superior (inferior)
-			to every matched element
-			of $s_{s-1}...s_1$.\\
+Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
+In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$.
+The optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
+Indeed when we will match $\factor{i+1}\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$, every elements of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
+Remark that the maximal (minimal) element of $\factor{i}\factor{i-1}\cdots\factor{1}$ is $\first{i-1}$.\\
 
 Consider the following problem :\\
-			$LM(s,i)$ = the optimal match of 	
-				$IMP(s-1)$ 
-				if there exists a match of $\pmotif[IMP(s):]$ 
-				with $\ptext[i:]$
-				and $IMP(s)$ 
-				is matched with element $i$.\\
+$LM(i,j)$ = the optimal match of $\first{i-1}$	
+	if there exists a match of $\pmotif[\first{i}:]$ 
+	with $\ptext[j:]$
+	and element $\first{i}$ 
+	is matched with element at index $j$.\\
 
@@
 \textbf{BASE :} \\
-			$LM(1,i)= \left\{ 
+$LM(1,j)= \left\{ 
 	\begin{array}{l l}
 
-						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
-						\text{if $\stripe{\pmotif}{IMP(1)}=\ustep$}
-						\\
-						\text{ $LIS(i,i',\ptext[i']) \leq S(1)$}\}&\\
+		MIN_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } & 
+		\text{if $\stripe{\pmotif}{\first{1}}=\ustep$}\\
+		\text{ $LIS(j,j',\ptext[j']) \leq \factor{1}$}\}&\\
 
@@
 
-						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
-						\text{if $\stripe{\pmotif}{IMP(1)}=\dstep$} \\
-						\text{ $LDS(i,i',\ptext[i']) \leq S(1)$}\}&\\
+		MAX_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } &
+		\text{if $\stripe{\pmotif}{\first{1}}=\dstep$} \\
+		\text{ $LDS(j,j',\ptext[j']) \leq \factor{1}$}\}&\\
 
@@
 \textbf{STEP :} \\
-			$LM(s,i)= \left\{ 
+$LM(i,j)= \left\{ 
 	\begin{array}{l l}
 
-						MIN \{0\} \cup  I(s,i) & 
-						\text{if $\stripe{\pmotif}{IMP(s)}=\ustep$}\\
-
-						MAX \{0\} \cup  D(s,i) & 
-						\text{if $\stripe{\pmotif}{IMP(s)}=\ustep$}\\
+		MIN \{0\} \cup  I(i,j) & 
+		\text{if $\stripe{\pmotif}{\first{i}}=\ustep$}\\
+
+		MAX \{0\} \cup  D(i,j) & 
+		\text{if $\stripe{\pmotif}{\first{i}}=\dstep$}\\
 
@@
 
-			With $I(s,i)$ ($D(s,i)$) the set of element such that
-			if  $e \in I(s,i)$ then there exists 
-			a match of $\pmotif[IMP(s-1):]$ in $\ptext[e:]$ and
-			there is a match of $s$ in $\ptext[i:e-1]$
-			with every element inferior (superior) to the match of  
-			$\pmotif[IMP(s-1):]$ in $\ptext[e:]$.
+With $I(i,j)$ ($D(i,j)$) the set of element such that
+if  $j' \in I(i,j)$ then there exists 
+a match of $\pmotif[\first{i-1}:]$ in $\ptext[j':]$ and
+the element $\first{i-1}$ is matched with element at index $j'$ and
+there is a match of $\factor{i}$ in $\ptext[j:j'-1]$ and
+the element $\first{i}$ is matched with element at index $j$ and every element is inferior (superior) to the match of  
+$\pmotif[\first{i-1}:]$ in $\ptext[j':]$.
 Formally we define $I(s,i)$ and $D(s,i)$ such as:\\
 
-			$I(s,i)=\{i'|\text{$i<i'$ and $LM(s-1,i')\neq 0$}$ \\
-			\indent \indent \indent and  $LIS(i,i'-1,IMP(s-1)) \leq S(s) \}$ \\
-
-			$D(s,i)=\{i'|\text{$i<i'$ and $LM(s-1,i')\neq 0$}$ \\
-			\indent \indent \indent and  $LDS(i,i'-1,IMP(s-1)) \leq S(s) \}$ \\
+$I(i,j)=\{j'|\text{$j<j'$ and $LM(i-1,j')\neq 0$}$ \\
+\indent \indent \indent and  $LIS(j,j'-1,\first{i-1}) \leq |\factor{i}| \}$ \\
+
+$D(i,j)=\{j'|\text{$j<j'$ and $LM(i-1,j')\neq 0$}$ \\
+\indent \indent \indent and  $LDS(j,j'-1,\first{i-1}) \leq |\factor{i}| \}$ \\
 
@@
 In the base case, 
-			we are looking for a match for the first segment.
-			Each segment is either ascent or descent.
-			If the segment is an ascent (descent)
-			we have to find an increasing (decreasing) sequence
-			in the text of same size of longest that 
-			the size of the segment,
+we are looking for a match for the first factor.
+Each factor is either ascent or descent.
+If the factor is an ascent (descent)
+we have to find an increasing (decreasing) subsequence
+in the text of same size or longest that 
+the size of the factor,
 and to find the optimal solution 
@@
 except that we must assure that 
-			every element of the sequence is superior 
+every element of the subsequence is superior 
 to the maximum element of the rest of the match
-			or inferior to the minimal element of the rest of the match
+ie inferior to the minimal (maximal) element of the rest of the match
 which is given by $LM$ of
-			the previous segment.\\
+the previous factor.\\
 
 There exists a match of $\pmotif$ in $\ptext$ if and only if
-			there exists a $LM(n,i)$ for $1 \leq i \leq |\ptext|$,
-			with $n$ the number of segment in $\pmotif$.
+there exists a $LM(n,i)\neq 0$ for $1 \leq i \leq |\ptext|$,
+with $n$ the number of factor in $\pmotif$.
 Moreover the basic case can be computed in $O(|\ptext|^2)$

### 2015-02-05 article.tex
modification : used of maccro \min and \max \n add : a paragraph at the begining of each section \n modicication : correction of some typo

@@
 
+This section focus on the pattern matching problem when only the motif avoid $(231,213)$.
+
 \begin{proposition}
@@
 with  $\pmotif$ a permutation avoiding (231,213), 
-we can decide in $O(|\pmotif|*|\ptext|^2)$ time
-and $O(|\pmotif|*|\ptext|^2)$ space
+we can decide in $O(|\pmotif||\ptext|^2)$ time
+and $O(|\pmotif||\ptext|^2)$ space
 if $\pmotif$ 
@@
 Moreover the basic case can be computed in $O(|\ptext|^2)$
-and the induction on $O(|\pmotif|*|\ptext|^2)$.
+and the induction on $O(|\pmotif||\ptext|^2)$.
 \end{proof}
@@
 
+This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(231,213)$.
+
 			\begin{proposition}
@@
 			$\ptext$ a permutation,
-			we can decide in $O(|\pmotif|*|\ptext|^3)$ time
+			we can decide in $O(|\pmotif||\ptext|^3)$ time
 			and $O(|\ptext|^3)$ space
@@
 
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \left\{ 
 				\begin{array}{l l}
@@
 						& \text{with every element in}\\ 
-						&[min,max]\\
+						&[\min,\max]\\
 
@@
 
-			$\mathbb{P}_{\pmotif,\ptext,min,max}$ is closed under induction. 
+			$\mathbb{P}_{\pmotif,\ptext,\min,\max}$ is closed under induction. 
 			it can be
@@
 			if $|\pmotif| \notin  \x : $\\		
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $min<\ptext[j]<max$
+						true & \text{if $\min<\ptext[j]<\max$
 						}\\
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\
 
 			if $|\pmotif| \in  \x : $\\		
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $min<\ptext[|\ptext|]<max$
+						true & \text{if $\min<\ptext[|\ptext|]<\max$
 						}\\
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\
 
@@
 			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $min<\ptext[j]<max$
+						true & \text{if $\min<\ptext[j]<\max$
 						}\\
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\
 
@@
 			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $min<\ptext[|\ptext|]<max$
+						true & \text{if $\min<\ptext[|\ptext|]<\max$
 						}\\
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\
 
 			\textbf{STEP :} \\		
-			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \\ \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \\ \left\{ 
 					\begin{array}{l l}
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$
@@
 							& \text{and $i \notin \y$ }\\
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 						&\\
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							& \text{and $i \notin \x$ and $i \notin \y$  }\\
-							& \text{and $min<\ptext[j]<max$} \\		
+							& \text{and $\min<\ptext[j]<\max$} \\		
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,t(j),\max}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							& \text{and $i \in \x$ and $i \notin \y$}\\
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\min,t(j)}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							& \text{and $i \in \x$ and $i \notin \y$ }\\
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
 							&\text{and $i \notin \x$ and $i \in \y$}\\
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
 							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
 							&\text{and $i \notin \x$ and $i \in \y$ }\\	
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),max}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),\max}(i+1,j+1) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,j+1)
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1)
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
-							& \text{and $min<\ptext[j]<max$} \\
+							& \text{and $\min<\ptext[j]<\max$} \\
 						&\\	
@@
 					\end{array} \right. $\\
-
-%			$\mathbb{P}_{\bmotif,\ptext,min,max}(i,j)= \\ \left\{ 
-%					\begin{array}{l l}
-%						False & \text{if $\ptext(j)<min$ or $max<\ptext(j)$}\\
-%						&\\
-%					
-%						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,k) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$
-%							and $i \notin \x$}\\
-%							& \text{and $i \notin \y$ }\\
-%						&\\
-%							
-%						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,k) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
-%							& \text{and $i \notin \x$ and $i \notin \y$  
-%							}\\
-%						&\\
-%							
-%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
-%							& \text{and $i \in \x$ and $i \notin \y$  
-%							}\\
-%						&\\
-%							
-%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
-%							& \text{and $i \in \x$ and $i \notin \y$  
-%							}\\							
-%						&\\
-%							
-%						False 
-%						& \text{if $\ptext^{-1}(\ptext(j)+1)<j$}\\
-%						&\text{and $\mathcal{S}(\pmotif,i)=\ustep$}\\
-%						&\text{and $i \in \y$}\\
-%						&\\
-%							
-%						False 
-%						& \text{if $\ptext^{-1}(\ptext(j)-1)<j$}\\
-%						& \text{and $\mathcal{S}(\pmotif,i)=\dstep$}\\
-%						& \text{and $i \in \y$}\\	
-%						&\\
-%						
-%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
-%							&\text{and $i \notin \x$ and $i \in \y$ 
-%							}\\
-%						&\\
-%							
-%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
-%							&\text{and $i \notin \x$ and $i \in \y$  
-%							}\\	
-%						&\\
-%						
-%						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
-%							& \text{if $\mathcal{S}(\pmotif,i)=\ustep$}\\
-%							&\text{and $i \in \x$ and $i \in \y$}\\ 
-%							&\text{and $\ptext(j)+1=\ptext(j+1)$ 
-%							}\\
-%						&\\
-%							
-%						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1)
-%							& \text{if $\mathcal{S}(\pmotif,i)=\dstep$}\\
-%							&\text{and $i \in \x$ and $i \in \y$}\\ 
-%							&\text{and $\ptext(j)-1=\ptext(j+1)$ 
-%							}\\		
-%						&\\	
-%						False & Otherwise\\																		
-%					\end{array} \right. $\\
 
@@
 			If $|\pmotif| \in \x$ there exists a match
-			if and only if\\ $\bigcup_{0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,0)$ is true.\\
+			if and only if\\ $\bigcup_{0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\
 
-			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,k)$
+			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
 			is true.			
@@
 	\begin{proof}
-	Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
+	Let's $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
 	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
@@
 	finding the longest subsequence avoiding (231,213)
-	can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and in $O(n)$ space.	
+	can be done in $O(|\ptext|log(log(|\ptext|)))$ time and in $O(n)$ space.	
 	\end{proposition}
@@
 	The longest common subsequence
-	avoiding (231,213) can be solve in $O(|\pi_1|^3*|\pi_2|^3)$.	
+	avoiding (231,213) can be solve in $O(|\pi_1|^3|\pi_2|^3)$.	
 	\end{proposition}
@@
 
-	$S_{\pi_1,\pi_2}(min_1,max_1,min_2,min_2,i_1,i_2)$
+	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
 	= max$\{$ $|m|$ $|$ 
@@
 	in  $\pi_1[i_1:]$
-	by the subsequence $s_1$ and $min(s_1)=min_1$ and $max(s_1)=max_1$
+	by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
 	and s is occurring
 	in  $\pi_2[i_2:]$
-	by the subsequence $s_2$ and $min(s_2)=min_2$ and $max(s_2)=max_2$	
+	by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$	
 	$\}$\\
@@
 	\textbf{BASE :} \\
-	$S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(|\pi_1|,|\pi_2|) = \left\{ 
+	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(|\pi_1|,|\pi_2|) = \left\{ 
 			\begin{array}{l l}
-				1 & \text{if $min_1<\pi_1(j)<max_1$  
+				1 & \text{if $\min_1<\pi_1[j]<\max_1$  
 				}\\
-				& \text{ and $min_2<\pi_2(j)<max_2$}\\
+				& \text{ and $\min_2<\pi_2[j]<\max_2$}\\
 				0 & otherwise\\
@@
 
-	$S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2) =$\\
-	\indent $ max \left\{ 
+	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2) =$\\
+	\indent $ \max \left\{ 
 			\begin{array}{l l}
-				S_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2+1) \\
-				S_{\pi_1,\pi_2,min_1,max_1,min_2,max_22}(i_1+1,i_2) \\
-				S'_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2)
+				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2+1) \\
+				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_22}(i_1+1,i_2) \\
+				S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)
 			\end{array} \right. $\vspace{20pt}\\
@@
 	with 
-	$S'_{\pi_1,\pi_2,min_1,max_1,min_2,max_2}(i_1,i_2)=\\ \left\{ 
+	$S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)=\\ \left\{ 
 				\begin{array}{l l}
-					1+S_{\pi_1,\pi_2,\pi_1(i_1),max_1,\pi_2(i_2)}(max_2,i_1+1,i_2+1)  & \text{$\pi_1(i_1)<min_1$ } \\
-					& \text{and $\pi_2(i_2)<min_2$} \\
+					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(\max_2,i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
+					& \text{and $\pi_2[i_2]<\min_2$} \\
 					&\\
-					1+S_{\pi_1,\pi_2,min_1,\pi_1(i_1),min_2,\pi_2(i_2)}(i_1+1,i_2+1)  & \text{$\pi_1(i_1)>max_1$ } \\	
-					&\text{and $\pi_2(i_2)>max_2$}\\	
+					1+S_{\pi_1,\pi_2,\min_1,\pi_1[i_1],\min_2,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]>\max_1$ } \\	
+					&\text{and $\pi_2[i_2]>\max_2$}\\	
 					&\\	
@@
 	either we match as the same step (if possible).
-	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.		
+	Those relation lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.		
 	\end{proof}

### 2015-02-05 article.tex
modification : used of a variable for the size of the text and motif in the bivinvular section \n modification : typo

@@
 
-			Given a bivincular motif $\bmotif$ avoiding $(231,213)$,
-			a text $\ptext$, $i$,$j$ , $i<j$.\\
+			Given a bivincular motif $\bmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
 
@@
 
-			if $|\pmotif| \notin  \x : $\\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
+			if $n_\pmotif \notin  \x : $\\		
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\
 
-			if $|\pmotif| \in  \x : $\\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
+			if $n_\pmotif \in  \x : $\\		
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $\min<\ptext[|\ptext|]<\max$
+						true & \text{if $\min<\ptext[n_\ptext]<\max$
 						}\\
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\
 
-			if $|\pmotif| \notin  \x$  
-			and $|\pmotif| \in  \y$ 
-			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
+			if $n_\pmotif \notin  \x$  
+			and $n_\pmotif \in  \y$ 
+			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\
 
-			if $|\pmotif| \in  \x$  
-			and $|\pmotif| \in  \y$ 
-			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
+			if $n_\pmotif \in  \x$  
+			and $n_\pmotif \in  \y$ 
+			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
 					\begin{array}{l l}
-						true & \text{if $\min<\ptext[|\ptext|]<\max$
+						true & \text{if $\min<\ptext[n_\ptext]<\max$
 						}\\
-						&\text{$\ptext[|\ptext|]$ is the maximal element}\\
+						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
 						false & otherwise\\
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\
 
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}[\ptext[j]+1]) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 							& \text{and $\min<\ptext[j]<\max$} \\
-							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
+							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
 						&\\
 
-						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}[\ptext[j]-1]) 
 							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 							& \text{and $\min<\ptext[j]<\max$} \\
-							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
+							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
 						&\\
@@
 			then we match $\pmotif[i+1:]$ 
-			with $\ptext[\ptext^{-1}(\ptext[j]-1):]$
+			with $\ptext[\ptext^{-1}[\ptext[j]-1]:]$
 			with the condition that
@@
 			then we match $\pmotif[i+1:]$ 
-			with $\ptext[\ptext^{-1}(\ptext[j]+1):]$
+			with $\ptext[\ptext^{-1}[\ptext[j]+1]:]$
 			with the condition that
@@
 			There are two cases to consider searching for a match : \\
-			If $|\pmotif| \in \x$ there exists a match
-			if and only if\\ $\bigcup_{0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\
+			If $n_\pmotif \in \x$ there exists a match
+			if and only if\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\
 
-			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
+			If $n_\pmotif \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
 			is true.			

### 2015-02-05 article.tex
add : some detail for the end of the proof for bivinvular

@@
 
-			There are two cases to consider searching for a match : \\
-			If $n_\pmotif \in \x$ there exists a match
-			if and only if\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\
+			There are two cases to consider searching for a match :
+			\begin{itemize}
+				\item If $n_\pmotif \in \x$ there exists a match if and only if there is a match with the first element of the text with every pair of min max possible :\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.
+				\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating ar any index in the text with every pair of min max possible : \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
+							is true.	
+			\end{itemize}
 
-			If $n_\pmotif \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
-			is true.			
 			\end{proof}

### 2015-02-05 article.tex
modification : typo

--- 2015-02-05 article.tex
@@
 
-			There are two cases to consider searching for a match : \\
-			If $n_\pmotif \in \x$ there exists a match
-			if and only if\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\
+			There are two cases to consider searching for a match :
+			\begin{itemize}
+				\item If $n_\pmotif \in \x$ there exists a match if and only if there is a match starting with the first element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.
+				\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
+							is true.	
+			\end{itemize}
 
-			If $n_\pmotif \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
-			is true.			
 			\end{proof}

### 2015-02-05 article.tex
typos

@@
 
-\title{Pattern matching for\\ $(231,213)$-avoiding permutations}
+\title{Pattern matching for\\ $(213,231)$-avoiding permutations}
 \author{Both Emerite NEOU, Romeo RIZZI}
@@
 	$O(|\pi| \log \log |\pi|)$ bound.)
-	Furthermore, the patterns $132$, $213$, $231$, $312$ can all be handled in linear time
+	Furthermore, the patterns $132$, $213$, $231$, $312$ can all be handled in linear-time
 	by stack sorting algorithms.
@@
 	proved that deciding whether a vincular pattern
-	$\sigma$ of length $k$ occurs in a permutation
-	$\pi \in \mathfrak{S}_n$ is $W[1]$-complete for
+	$\sigma$ of length $k$ occurs in a longer permutation
+	$\pi$ is $W[1]$-complete for
 	parameter $k$.
@@
 and uasually consist of the integers $12\,\ldots\,n$.
-For the sake of convenience, 
-we let 
+We let 
+$\pi[i]$ stands for $\pi_i$.
+For the sake of convenience, we let
 $\pi[i:j]$ stand for 
@@
 $\pi[i:]$ stand for $\pi[i:n]$.
-We let $S_n$ denote the set of all permutations of length $n$.
+As usual, we let $S_n$ denote the set of all permutations of length $n$.
 
@@
 For example the stripe of the permutation 
-$\pi = 12\,11\,10\,1\,2\,3,4\,9\,8\,5\,6\,7$ 
-is 
-$\stripew{\pi} = \dstep\dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep\ustep\ustep$.
+$\pi = 981234765$
+is $\stripew{\pi} = \dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep$.
 The stripe $\stripew{\sigma}$ is a \emph{pattern} of the strip $\stripew{\pi}$
@@
 	Moreover, if the top row of $\sigma$ begins with
-	$^ulcorner{1}$ then
+	$^\ulcorner{1}$ then
 	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
@@
 
-\section{Both $\pi$ and $\sigma$ are $(231,213)$-avoiding}
+\section{Both $\pi$ and $\sigma$ are $(213,231)$-avoiding}
 \label{section:both are (231,213)-avoiding}
@@
 $\sigma \leq \pi$ 
-in case both $\pi$ and $\sigma$ are $(231,213)$-avoiding.
+in case both $\pi$ and $\sigma$ are $(213,231)$-avoiding.
+We begin with an easy structure lemma.
 
@@
 be two permutations avoiding (231,213), 
-we can decide in linear time if $\pmotif$ 
-appear in $\ptext$.\\
+we can decide in linear-time if $\pmotif$ 
+appear in $\ptext$.
 
@@
 %			
-%			Given a motif $\pmotif$ avoiding $(231,213)$,
+%			Given a motif $\pmotif$ avoiding $(213,231)$,
 %			a text $\ptext$, $i$,$j$ , $i<j$.\\
@@
 
-This section focus on the pattern matching problem when only the motif avoid $(231,213)$.
+This section focus on the pattern matching problem when only the motif avoid $(213,231)$.
 
@@
 
-This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(231,213)$.
+This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
 

### 2015-02-05 article.tex
modification : typo modification : readability in some proof

--- 2015-02-05 article.tex
@@
 \begin{proof} 
-We prove the lemma by induction on the size of the motif.
-Suppose that we have the motif $(12)$, thus the stripe is $\ustep$.
+We prove the lemma by induction on the size of the motif.The base case is a motif of size 2.
+Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$.
 If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation.
 Same goes for the permutation $(21)$.
-Now, suppose that the lemma is true for every motif of size $n$.
-Let $\pmotif$ be a motif of size $n+1$ avoiding $(213,231)$, and $\ptext$ a permutation avoiding $(213,231)$.
+Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$.
+Let $\pmotif$ be a motif in $\Av{n+1}{(231,213)}$, and $\ptext$ a permutation avoiding $(213,231)$.
 If there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$ by subsequence $s$, then there is a match of $\stripew{\pmotif}[2:]$ in $\stripew{\ptext}[2:]$ by subsequence $s[2:]$, and by induction there is a match of $\pmotif[2:]$ in $\ptext[2:]$ by subsequence $s[2:]$.
-Moreover suppose that the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
+Moreover if the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
 \end{proof}
@@
 
-\textbf{Proposition  \num \thenum} Let $\pmotif$ and $\ptext$
+\begin{proposition}
+Let $\pmotif$ and $\ptext$
 be two permutations avoiding (231,213), 
@@
 appear in $\ptext$.\\	
+\end{proposition}
 
@@
 \begin{proof}
-Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
-In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$.
-The optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
-Indeed when we will match $\factor{i+1}\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$, every elements of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
-Remark that the maximal (minimal) element of $\factor{i}\factor{i-1}\cdots\factor{1}$ is $\first{i-1}$.\\
+Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
+In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
+Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
+
+\begin{remark}
+Given an ascent (descent) factor $\factor{i}$, the maximal (minimal) element of $\factor{i}\factor{i-1}\cdots\factor{1}$ is $\first{i-1}$.			  
+\end{remark}
+
+\begin{remark}
+An ascent (descent) factor 	$\factor{i}$ is a match in $\ptext[j:j']$  if and only if there exists an increasing (decreasing) subsequence in $\ptext[j:j']$ of size superior or equal to the size of $\factor{i}$.
+\end{remark}
 
@@
 		\text{if $\stripe{\pmotif}{\first{1}}=\ustep$}\\
-		\text{ $LIS(j,j',\ptext[j']) \leq \factor{1}$}\}&\\
+		\text{ $|\factor{1}| \leq LIS(j,j',\ptext[j'])  $}\}&\\
 
@@
 		\text{if $\stripe{\pmotif}{\first{1}}=\dstep$} \\
-		\text{ $LDS(j,j',\ptext[j']) \leq \factor{1}$}\}&\\
+		\text{ $|\factor{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\
 
@@
 $I(i,j)=\{j'|\text{$j<j'$ and $LM(i-1,j')\neq 0$}$ \\
-\indent \indent \indent and  $LIS(j,j'-1,\first{i-1}) \leq |\factor{i}| \}$ \\
+\indent \indent \indent and  $|\factor{i}| \leq LIS(j,j'-1,\first{i-1})\}$ \\
 
 $D(i,j)=\{j'|\text{$j<j'$ and $LM(i-1,j')\neq 0$}$ \\
-\indent \indent \indent and  $LDS(j,j'-1,\first{i-1}) \leq |\factor{i}| \}$ \\
+\indent \indent \indent and  $|\factor{i}| \leq LDS(j,j'-1,\first{i-1}) \}$ \\
 
@@
 except that we must assure that 
-every element of the subsequence is superior 
-to the maximum element of the rest of the match
-ie inferior to the minimal (maximal) element of the rest of the match
+every element of the subsequence is superior (inferior)
+to the maximum (minimal) element of the rest of the match
+ie inferior (superior) to the minimal (maximal) element of the rest of the match
 which is given by $LM$ of
@@
 
-			if $n_\pmotif \notin  \x : $\\		
+			if $n_\pmotif \notin  \x $
+			and $n_\pmotif \notin  \y$ : \\		
 			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
@@
 
-			if $n_\pmotif \in  \x : $\\		
+			if $n_\pmotif \in  \x $
+			and $n_\pmotif \notin  \y$ : \\		
 			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
@@
 						true & \text{if $\min<\ptext[j]<\max$
-						}\\
+						and }\\
 						&\text{$\ptext[j]$ is the maximal element}\\
@@
 						true & \text{if $\min<\ptext[n_\ptext]<\max$
-						}\\
+						and }\\
 						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,t(j),\max}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\min,t(j)}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),\max}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 			$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
-			and that $\ptext[j+1]=\pmotif[i]-1$.\\
+			and that $\ptext[j+1]=\ptext[j]-1$.\\
 
@@
 			$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
-			and that $\ptext[j+1]=\pmotif[i]+1$.\\
+			and that $\ptext[j+1]=\ptext[j]+1$.\\
 
@@
 	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
-	Thus $|s_m|>P(\pi)$, clearly the sequence $s_m \cup M(\pi)$
+	Thus $|s_m|>|P(\pi)|$, clearly the sequence $s_m \cup M(\pi)$
 	is avoiding (213,231) and is longer than $s$ witch is not possible. 
-	The case for $M(\pi)$ follows the same idea.
+	The same idea goes for the demonstration that $M(\pi)$ is the longest decreasing subsequence.
 	\end{proof}
@@
 	\begin{proposition}
-	Given two permutation $\pi_1$ and $\pi_2$
-	The longest common subsequence
-	avoiding (231,213) can be solve in $O(|\pi_1|^3|\pi_2|^3)$.	
+	Given two permutation $\pi_1$ and $\pi_2$,
+	the longest common subsequence
+	avoiding (231,213) can be compute in $O(|\pi_1|^3|\pi_2|^3)$ time and space.	
 	\end{proposition}
@@
 	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
-	= max$\{$ $|m|$ $|$ 
+	= max$\{$ $|s|$ $|$ 
 	s is a pattern occurring 
@@
 			\begin{array}{l l}
-				1 & \text{if $\min_1<\pi_1[j]<\max_1$  
+				1 & \text{if $\min_1=\pi_1[j]=\max_1$  
 				}\\
-				& \text{ and $\min_2<\pi_2[j]<\max_2$}\\
+				& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
 				0 & otherwise\\
@@
 				\begin{array}{l l}
-					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(\max_2,i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
+					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
 					& \text{and $\pi_2[i_2]<\min_2$} \\

### 2015-02-05 article.tex

@@
 be two permutations avoiding (231,213), 
-we can decide in linear time if $\pmotif$ 
-appear in $\ptext$.\\	
+we can decide in linear-time if $\pmotif$ 
+appear in $\ptext$.	
 \end{proposition}

### 2015-02-05 article.tex
typos

--- 2015-02-05 article.tex
@@
 	merely increasing (resp. descreasing).
+	As another example,
+	$6152347$ contains $213$ but not $231$.
 	During the last decade, the study of the pattern containment on permutations has
-	become a very active area of research.
+	become a very active area of research and
+	a whole annual conference (\textsc{Permutation Patterns}) is now devoted 
+	to this topic.
 
@@
 	\cite{Ahal:Rabinovich:2008},
-	the latter describing a $O(|\pi|^{0.47k+o(|\sigma| )})$ time algorithm.
+	the latter describing a $O(|\pi|^{0.47|\sigma|+o(|\sigma|)})$ time algorithm.
 	Bruner and Lackner \cite{Bruner:Lackner:SWAT:2012}
@@
 	brute-force search without imposing restrictions on $\sigma$ and $\pi$.)
-	Of particular importance, it was recently proved that
-	the permutation containment problem is fiexed-parameter tractable for
-	parameter $|\sigma|$
+	A recent major step was taken by􏰂 Marx and Guillemot
 	\cite{Guillemot:Marx:SODA:2014}.
+	They showed that
+	the permutation containment problem is fixed-parameter tractable for
+	parameter $|\sigma|$.
 
@@
 	The pattern containment problem is also solvable in
-	polynomial-time for separable patterns \cite{Ibarra:1997}
-	(see also \cite{Bose:Buss:Lubiw:1998}).
+	polynomial-time for separable patterns \cite{Ibarra:1997,Bose:Buss:Lubiw:1998}
+	(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for LCS-like issues
+	of separable permutations).
 	Separable permutations are those permutations that contain neither
@@
 	The number of $n$-permutations that avoid both 
-	$231$ and $213$ is 
+	$213$ and $231$ is 
 	$t_0 = 1$ for $n = 0$ and 
-	$t_n =2^{n−1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
-	The permutations that do not contain the permutation pattern $231$
+	$t_n =2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
+	On an individual basis,
+	the permutations that do not contain the permutation pattern $231$
 	are exactly the \emph{stack-sortable permutations} and they are counted by 
@@
 	an algorithm whose internal storage is limited to a single stack data structure.
+	As for $213$, it is well-known that 
+ 	if $\pi = \pi_1\pi\,\ldots\,\pi_n$ avoids $132$, then its complement 
+ 	$\pi' = (n+1-\pi_1)(n+1-\pi_2)\,\ldots\,(n+1-\pi_n)$ avoids $312$, and 
+ 	the reverse of $\pi'$ avoids $213$.
+ 	From a combinatorial point of view,
+ 	B\'ona \cite{Bona:ElJC:2012} 
+ 	showed the rather surprising fact that the cumulative number of 
+ 	occurrences of the classical patterns $231$ and $213$ are the same on the 
+ 	set of permutations avoiding $132$, 
+ 	beside the pattern based statistics $231$ and $213$ 
+ 	do not have the same distribution on this set.
+ 	\emph{Almost avoidance} has also been considered;
+ 	a permutation $\pi$ almost avoids a set $X$ of permutations 
+ 	if there is a way to remove a single element of $\pi$ to get a permutation 
+ 	that avoids all elements in $X$
+ 	and $L_n(X)$ denotes the set of permutations of length $n$ that almost avoid 
+ 	$X$.
+ 	It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
+ 	$L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
 

### 2015-02-05 article.tex
abstract

@@
 \begin{abstract}
-bla bla\ldots
+	Given permutations $\sigma \in S_k$ and $\p \in S_n$, the Permutation Pattern (PP)
+	problem is to decide whether $\pi$ contains $\sigma$ as an order-isomorphic pattern.
+	We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid 
+	$213$ and $231$. 
+	For the special where only $\sigma$ avoids $213$ and $231$, we present a 
+	$O(kn^2)$ time algorithm. We extend our research to $(213,231)$-avoiding 
+	bivincular pattern and present a $O(kn^3)$ time algorithm.
 \end{abstract}

### 2015-02-05 article.tex
abstract

@@
 \begin{abstract}
-	Given permutations $\sigma \in S_k$ and $\p \in S_n$, the Permutation Pattern (PP)
+	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the Permutation Pattern (PP)
 	problem is to decide whether $\pi$ contains $\sigma$ as an order-isomorphic pattern.

### 2015-02-05 article.tex
affiliations

@@
 \author{%
-	Both Emerite Neou\inst{1,3}
+	Both Emerite Neou\thanks{On a Co-tutelle  Agreement with the Department of Mathematics of the University of Trento}\inst{1}
   Romeo Rizzi\inst{2} \and
-  St\'ephane Vialette\inst{3}
+  St\'ephane Vialette\inst{1}
 }% end author
 \institute{%
-  Department of Computer Science,
-  Università degli Studi di Trento, Italy \\	
+	Universit\'e Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC, 
+	F-77454, Marne-la-Vallée, France\\
+  \email{\{neou,vialette\}@univ-mY.fr}
   \and
@@
   \email{romeo.rizzi@univr.it}
-  \and
-	Universit\'e' Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC, 
-	F-77454, Marne-la-Vallée, France\\
-  \email{vialette@univ-mY.fr}
 }% end institute

### 2015-02-05 article.tex
affiliations

@@
 \label{lemma:MatchStripeToPermutation}
-Given two permutations $\ptext$,$\pmotif$ avoiding (231,213), If $\stripew{\pmotif}$ is a motif of stripe $\stripew{\ptext}$ by a subsequence $s$, then $\pmotif$ is a motif of $\ptext$ by subsequence $s$.
+	Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations.
+	Then $\pi$ contains $\sigma$ if and only if 
+	$s_\sigma$ is a subsequence of $s_\pi$.
 \end{lemma}
@@
 \begin{proof} 
-We prove the lemma by induction on the size of the motif.The base case is a motif of size 2.
+	The forward direction is obvious.
+	We prove the backward direction by induction on the size of the motif
+	$\sigma$.
+	The base case is a motif of size 2.
 Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$.
@@
 Moreover if the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
+\qed
 \end{proof}
 
-\begin{proposition}
-Let $\sigma \in \AV_k(213,231)$ and $\pi \in \AV_k(213,231)$.
-$\sigma$ is a motif of $\pi$ if and only if 
-$s_\sigma$ is a subsequence of $s_\pi$.
-\end{proposition}
-
-		% without lost of generality we can suppose that $x<y$,
-% 		Let see all the case possible that can make this 
-% 		hypothesis possible :
-% 		\begin{itemize}		
-% 			\item if $\pmotif(x)<\pmotif(y)$, 
-% 			$\stripe{\pmotif}{x}=\ustep$ 
-% 			and $\stripe{\pmotif}{y}=\ustep$
-% 			(if x and y are increasing in $\pmotif$),
-% 			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
-% 			(the match are also increasing).
-% 			As $x<y$ and as $\varphi$ is an increasing function, 
-% 			$\varphi(x) < \varphi(y)$.
-% 			And thus, by \textbf{Lemma \ref{lemma:upup}},
-% 			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
-% 			Which contradict our hypothesis,
-% 			so this case is not possible.
-
-\begin{proof}
-$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$ by subsequence $s$. By definition $s$ normalized is equal to
-$\pmotif$ so they have the same stripe.\\ 
-$\Leftarrow$ This is proved by lemma \ref{lemma:MatchStripeToPermutation}.
-\end{proof}
+We are now ready to solve the pattern containment in case
+both $\pi$ and $\sigma$ are $(213, 231)$-avoiding.
 
 \begin{proposition}
-Let $\pmotif$ and $\ptext$
-be two permutations avoiding (231,213), 
-we can decide in linear-time if $\pmotif$ 
-appear in $\ptext$.	
+	Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations.
+	One can decide whether $\pi$ contains $\sigma$ in linear-time.
 \end{proposition}

### 2015-02-05 article.tex
modification : proof for both permutation in avoiding 213 213 remove : corollary 2

@@
 
-\begin{corollary}
-Let $\pi \in \AV_n(213,231)$. We have
-$$
-\stripe{\pi}{i} =
-\begin{cases}
-			\ustep & \text{if $\pi[i]$ is the minimal element of $\pi[i:]$}\\    
-			\dstep & \text{if $\pi[i]$ is the maximal element of $\pi[i:]$}\\
-	\end{cases}
-	$$
-\end{corollary}
-
 \begin{lemma}
@@
 Let $\pmotif$ be a motif in $\Av{n+1}{(231,213)}$, and $\ptext$ a permutation avoiding $(213,231)$.
-If there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$ by subsequence $s$, then there is a match of $\stripew{\pmotif}[2:]$ in $\stripew{\ptext}[2:]$ by subsequence $s[2:]$, and by induction there is a match of $\pmotif[2:]$ in $\ptext[2:]$ by subsequence $s[2:]$.
-Moreover if the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
+Suppose that there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$, Let's $s$ be the subsequence such that $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$.
+	By induction $\pmotif[2:]$ appears in $\ptext$ by subsequence $s[2:]$.
+	Moreover if the first element the stripe of the motif is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} the first element is the minimal (maximal) element.
+Remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal), element which complete our proof.
 \qed
@@
 And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:minmaxelement}},
-we do not have to compute the stripe advance.
+we do not have to compute the stripe in advance.
 Therefore we have an linear (online) algorithm.

### 2015-02-05 article.tex
Proof of Proposition 1

@@
 \end{itemize}
-A bivincular pattern avoids a set of permutations $P$ if its bottom
-row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.
+% A bivincular pattern avoids a set of permutations $P$ if its bottom
+% row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.
 
@@
 \begin{proof}
-To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
-we find a find a match of the stripe of the pattern in the stripe of the text.
-This can be done linearly by a greedy algorithm, 
-by matching a step whenever it is possible.
-And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:minmaxelement}},
-we do not have to compute the stripe in advance.
-Therefore we have an linear (online) algorithm.
+According to Lemma~\ref{lemma:MatchStripeToPermutation} the problem reduces 
+to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$. 
+A straightforward greedy approach solves this issue in linear-time. 
+Furthermore, in the light of Corollary~\ref{corollary:minmaxelement}, 
+the effective construction of the two stripes is not required, 
+so it is an online algorithm.
+\qed
+% To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
+% we find a find a match of the stripe of the pattern in the stripe of the text.
+% This can be done linearly by a greedy algorithm, 
+% by matching a step whenever it is possible.
+% And thank to the definition of the definition of a stripe in 
+% Corollary~\ref{corollary:minmaxelement},
+% we do not have to compute the stripe in advance.
+% Therefore we have an linear (online) algorithm.
 \end{proof}

### 2015-02-06 article.tex
Proof of Proposition 1
modifciation : precision on which subsequence to take to have a match in lemma 2

@@
 \DeclareMathOperator{\stripea}{s}
-\newcommand{\stripe}[2]{\stripea_{{#1}}({#2})}
+\newcommand{\stripe}[2]{\stripea_{{#1}}[{#2}]}
 \newcommand{\stripew}[1]{\stripea_{{#1}}}
@@
 
+%\begin{corollary}
+%
+%If $\pi \in \Av{n}{(231,213)}$ its stripe can be define such as, \\
+%$\stripe{\pi}{i} = \left\{ 
+%	\begin{array}{l l}
+%			\ustep & \quad \text{if $\pi[i]$ is the minimal element of $\pi[i:]$}\\    
+%			\dstep & \quad \text{if $\pi[i]$ is the maximal element of $\pi[i:]$}\\
+%\end{array} \right.$ 
+%\end{corollary}
+
+The following lemma is central to all our algorithm.
+
 \begin{lemma}
 \label{lemma:MatchStripeToPermutation}
-	Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations.
-	Then $\pi$ contains $\sigma$ if and only if 
-	$s_\sigma$ is a subsequence of $s_\pi$.
+Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations. Then $\pi$ contains $\sigma$ by a subsequence $s$ if and only if $s_\sigma$ is a subsequence of $s_\pi$ by the same subsequence $s$.
 \end{lemma}
@@
 	By induction $\pmotif[2:]$ appears in $\ptext$ by subsequence $s[2:]$.
-	Moreover if the first element the stripe of the motif is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} the first element is the minimal (maximal) element.
-Remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal), element which complete our proof.
+	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif.
+Furthermore $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$ by subsequence $s$, so $\stripe{s}{1}$ is also ascend (descent) thus $s[1]$ is also the minimal (maximal) element of the subsequence $s$ which complete our proof.
 \qed
@@
 
-We are now ready to solve the pattern containment in case
+We are now ready to solve the pattern containment problem in case
 both $\pi$ and $\sigma$ are $(213, 231)$-avoiding.
@@
 
-%		\subsection{With Motif Avoiding (231,213)}	
-%		
-%			\textbf{Proposition \num} Let $\pmotif$, $\ptext$ 
-%			be two permutation,
-%			with  $\pmotif$ a permutation avoiding (231,213), 
-%			we can decide in $O(|\pmotif|*|\ptext|^3)$ time
-%			and $O(|\ptext|^3) space$
-%			if $\pmotif$ 
-%			appear in $\ptext$.\\	
-%
-%			\textbf{Proof}
-%			We consider the following problem :\\
-%			
-%			Given a motif $\pmotif$ avoiding $(213,231)$,
-%			a text $\ptext$, $i$,$j$ , $i<j$.\\
-%			
-%			$\mathbb{P}_{\pmotif,\ptext,min,max}(i,j)= \left\{ 
-%				\begin{array}{l l}
-%					true & \text{If the sufixe of $\pmotif$ starting at $i$}\\
-%						& \text{is a pattern of the suffix of $\ptext$} \\
-%						& \text{with every element in $[min,max]$}\\
-%		
-%					false & otherwise\\
-%				\end{array} \right.$\\
-%		
-%			$\mathbb{P}_{\pmotif,\ptext,min,max}$ is closed under induction. 
-%			it can be
-%			solved by means of the following relations:\\
-%			
-%			
-%			\textbf{BASE :} \\
-%			$\mathbb{P}_{\pmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
-%					\begin{array}{l l}
-%						true & \text{if $min < \ptext(j) < max$
-%						}\\
-%						false & otherwise\\
-%					\end{array} \right. $\\	
-%		
-%			\textbf{STEP :} \\
-%			$\mathbb{P}_{\pmotif,\ptext,min,max}(i,j)= \left\{ 
-%					\begin{array}{l l}
-%						False & \text{if $\ptext(j)<min$ or $max<\ptext(j)$}\\
-%						\bigcup_{j<k}\mathbb{P}_{\pmotif,\ptext,t(j),max}(i+1,k) 
-%							& \text{if $\\mathcal{S}(\pmotif,i)=\ustep$
-%							}\\
-%						\bigcup_{j<k}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(i+1,k) 
-%							& \text{if $\\mathcal{S}(\pmotif,i)=\dstep$
-%							}\\
-%					\end{array} \right. $\\
-%			At each step, 
-%			we are match the current element of $\pmotif$ ($\pmotif(i)$)
-%			with the current element of $\ptext$ ($\ptext(j)$), if possible.
-%			then we are match the rest of $\pmotif$ with 
-%			every suffixes $\ptext$ starting after $j$.
-%			Clearly there is a match if and only if 	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,t(j)}(0,k)$
-%			is true.   
-%			This implies a $O(|\pmotif|*|\ptext|^3)$ time
-%			and $O(|\ptext|^3) space$ algorithm.\\
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Pattern Matching With Motif Avoiding (231,213)}	
+\section{$\sigma$ only is $(231,213)$-avoiding}	
 \label{section:sigma only avoid 231 and 213}

### 2015-02-07 article.tex
add : explication in proof of lemma 2
modification : the proof of lemma 2

@@
 \label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations. Then $\pi$ contains $\sigma$ by a subsequence $s$ if and only if $s_\sigma$ is a subsequence of $s_\pi$ by the same subsequence $s$.
+Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations, given a subsequence $t$ of $\ptext$, $t$ is an occurrence of $\pmotif$ in $\ptext$ if and only if $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$.
 \end{lemma}
@@
 Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$.
-If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation.
-Same goes for the permutation $(21)$.
+Let's $t$ be a subsequence of $\ptext$ such that $\stripew{t}$ is a occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$.
+Because we have $\stripe{t}{1}=\ustep$, so the next element of $t[1]$ in $\ptext$ is superior to  $t[1]$, so we have a match.
+Same idea goes of motif $(21)$.
 	Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$.
-Let $\pmotif$ be a motif in $\Av{n+1}{(231,213)}$, and $\ptext$ a permutation avoiding $(213,231)$.
-Suppose that there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$, Let's $s$ be the subsequence such that $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$.
-	By induction $\pmotif[2:]$ appears in $\ptext$ by subsequence $s[2:]$.
+Suppose that we have a subsequence $t$ of $\ptext$ such that $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$, then $\stripew{t[2:]}$ is an occurrence of $\pmotif[2:]$ in $\ptext$.
+Moreover
+	$\pmotif[2:] \in \Av{n}{(231,213)}$ so by hypothesis of induction $t[2:]$ is an occurrence of $\sigma[2:]$ in $\ptext$.
 	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif.
-Furthermore $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$ by subsequence $s$, so $\stripe{s}{1}$ is also ascend (descent) thus $s[1]$ is also the minimal (maximal) element of the subsequence $s$ which complete our proof.
+Furthermore $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$ , so $\stripe{t}{1}$ is also ascend (descent) thus $t[1]$ is also the minimal (maximal) element of the subsequence $t$ which complete our proof.
+
 \qed

### 2015-02-08 article.tex
correction : some typo
add : definition of set X and Y \n modification : the presentation of the problem of bivincular and LCS

@@
 
-\newcommand{\x}{X}
-\newcommand{\y}{Y}
-\newcommand{\bmotif}{(\sigma,\x,\y)}
-
 %Stripe
@@
 \newcommand{\factor}[1]{\factora({#1})}
+
+%binvincular 
+\newcommand{\x}{X}
+\newcommand{\y}{Y}
+\newcommand{\bmotif}{(\sigma,\x,\y)}
+
+\newcommand{\pbmotif}{\pmotif^+}
+\newcommand{\pbmotifX}{\x_{\pbmotif}}
+\newcommand{\pbmotifY}{\y_{\pbmotif}}
+
+%LSC
+\DeclareMathOperator{\LCSa}{LCS}
+\newcommand{\LCS}[8]{\LCSa_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}
+
+\DeclareMathOperator{\matcha}{MATCH}
+\newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}
 
@@
 \end{itemize}
+Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
+An index $i$ of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
+For example if we have $\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$, then ${i,i+1,\ldots,j-1} \in \y$. 
+We represent the index that need to be overlined by the set $\y$. An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
+For example if we have
+For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
 % A bivincular pattern avoids a set of permutations $P$ if its bottom
@@
 Let's $t$ be a subsequence of $\ptext$ such that $\stripew{t}$ is a occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$.
-Because we have $\stripe{t}{1}=\ustep$, so the next element of $t[1]$ in $\ptext$ is superior to  $t[1]$, so we have a match.
+Because we have $\stripe{t}{1}=\ustep$, the next element of $t[1]$ is $\ptext$ is superior to  $t[1]$, so we have a match.
 Same idea goes of motif $(21)$.
@@
 This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
+We denote $\pbmotif=\bmotif$ the bivincular motif.
 
 \begin{proposition}
-			Let $\bmotif$ be a bivincular motif 
-			avoiding (231,213), 
+Let $\pbmotif$ be a bivincular motif such that $\pmotif$
+avoid (231,213), 
 $\ptext$ a permutation,
@@
 and $O(|\ptext|^3)$ space
-			if $\pmotif$ 
+if $\pbmotif$
 appear in $\ptext$.
@@
 
-			Given a bivincular motif $\bmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
+			Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
 
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \left\{ 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \left\{ 
 				\begin{array}{l l}
-					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
+					true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
 						& \text{with every element in}\\ 
@@
 
-			$\mathbb{P}_{\pmotif,\ptext,\min,\max}$ is closed under induction. 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}$ is closed under induction. 
 			it can be
@@
 			and $n_\pmotif \notin  \y$ : \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
 
@@
 			and $n_\pmotif \notin  \y$ : \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
 
@@
 			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
 					\begin{array}{l l}
@@
 			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
 
 			\textbf{STEP :} \\		
-			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \\ \left\{ 
+			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \\ \left\{ 
 					\begin{array}{l l}
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$
@@
 
-						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
+						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1) 
+						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}[\ptext[j]+1]) 
+						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]+1]) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}[\ptext[j]-1]) 
+						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]-1]) 
 							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
+						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1)
+						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1)
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
+	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}$
 	= max$\{$ $|s|$ $|$ 
@@
 	\textbf{BASE :} \\
-	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(|\pi_1|,|\pi_2|) = \left\{ 
+	$	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} = \left\{ 
 			\begin{array}{l l}
@@
 
-	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2) =$\\
-	\indent $ \max \left\{ 
+	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
+	=$
+	$ \max \left\{ 
 			\begin{array}{l l}
-				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2+1) \\
-				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_22}(i_1+1,i_2) \\
-				S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)
+				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
+				\\
+				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
+				\\
+				\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
 			\end{array} \right. $\vspace{20pt}\\
@@
 	with
-	$S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)=\\ \left\{ 
+	$\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=\\ \left\{ 
 				\begin{array}{l l}
-					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
+					1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} & \text{$\pi_1[i_1]<\min_1$ } \\
 					& \text{and $\pi_2[i_2]<\min_2$} \\
 					&\\
-					1+S_{\pi_1,\pi_2,\min_1,\pi_1[i_1],\min_2,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]>\max_1$ } \\	
+					1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
+					 & \text{$\pi_1[i_1]>\max_1$ } \\	
 					&\text{and $\pi_2[i_2]>\max_2$}\\	

### 2015-02-08 article.tex
add : maccro \n modification : typo

@@
 \newcommand{\pbmotifY}{\y_{\pbmotif}}
+
+%Pattern Marching
+
+\DeclareMathOperator{\PMa}{PM}
+\newcommand{\PM}[6]{\PMa_{{#1}}^{{#2},{#3},{#4}}({#5},{#6})}
 
@@
 We consider the following problem :\\
-
 Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
 
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \left\{ 
+%$
+%\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= 
+%\begin{cases}
+%true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$ with every element in $[\min,\max]$} \\
+%false & otherwise
+%\end{cases}
+%$
+
+$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
+\left\{ 
 \begin{array}{l l}
@@
 
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}$ is closed under induction. 
-			it can be
-			solved by means of the following relations:\\
+$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction. 
+it can be solved by means of the following relations:\\
 
 \textbf{BASE :} \\
-
-			if $n_\pmotif \notin  \x $
-			and $n_\pmotif \notin  \y$ : \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
+if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\	
+$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}	
+= \left\{ 
 		\begin{array}{l l}
-						true & \text{if $\min<\ptext[j]<\max$
-						}\\
+			true 	& \text{if $\min<\ptext[j]<\max$}\\
 			false 	& otherwise\\
 		\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
+%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
+\\
 
-			if $n_\pmotif \in  \x $
-			and $n_\pmotif \notin  \y$ : \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
+if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\		
+$ \PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
+= \left\{ 
 		\begin{array}{l l}
-						true & \text{if $\min<\ptext[n_\ptext]<\max$
-						}\\
+			true 	& \text{if $\min<\ptext[n_\ptext]<\max$}\\
 			false 	& otherwise\\
 		\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
+\\
 
-			if $n_\pmotif \notin  \x$  
-			and $n_\pmotif \in  \y$ 
-			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
+if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
+$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}= \left\{ 
 		\begin{array}{l l}
-						true & \text{if $\min<\ptext[j]<\max$
-						and }\\
+			true 	& \text{if $\min<\ptext[j]<\max$ and }\\
 					&\text{$\ptext[j]$ is the maximal element}\\
@@
 		\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
+%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
 
-			if $n_\pmotif \in  \x$  
-			and $n_\pmotif \in  \y$ 
-			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
+if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
+$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
+= \left\{ 
 		\begin{array}{l l}
-						true & \text{if $\min<\ptext[n_\ptext]<\max$
-						and }\\
+			true 	& \text{if $\min<\ptext[n_\ptext]<\max$and }\\
 					&\text{$\ptext[n_\ptext]$ is the maximal element}\\
@@
 		\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
 
 \textbf{STEP :} \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \\ \left\{ 
+$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}= \\ \left\{ 
 		\begin{array}{l l}
 
-						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,k) 
+			\bigcup_{j<k}
+			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
 				& \text{if $\stripe{\pmotif}{i}=\ustep$
@@
 
-						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,k) 
+			\bigcup_{j<k}
+			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{k}
 				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
+			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}	
 				& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1) 
+			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1} 
 				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]+1]) 
+			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{\ptext^{-1}[\ptext[j]+1]} 
 				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]-1]) 
+			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{\ptext^{-1}[\ptext[j]-1]} 	
 				&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
+			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1} 
 				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1)
+			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1} 
 				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\

### 2015-02-08 article.tex
modifcation : used of environment cases

@@
 
-\DeclareMathOperator{\matcha}{MATCH}
+\DeclareMathOperator{\matcha}{M}
 \newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}
@@
 \textbf{BASE :} \\
-$LM(1,j)= \left\{ 
-	\begin{array}{l l}
-
+$
+LM(1,j)=
+\begin{cases}
 		MIN_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } & 
-		\text{if $\stripe{\pmotif}{\first{1}}=\ustep$}\\
-		\text{ $|\factor{1}| \leq LIS(j,j',\ptext[j'])  $}\}&\\
-
+			\text{if $\stripe{\pmotif}{\first{1}}=\ustep$} \\
+		\text{ $|\factor{1}| \leq LIS(j,j',\ptext[j'])  $}\}& \\
 		&\\	
-
 		MAX_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } &
@@
 		\text{ $|\factor{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\			
-
-	\end{array} \right. $\\
+\end{cases}
+$
 
 \textbf{STEP :} \\
-$LM(i,j)= \left\{ 
-	\begin{array}{l l}
-
+$
+LM(i,j)=
+\begin{cases}
 	MIN \{0\} \cup  I(i,j) & 
 	\text{if $\stripe{\pmotif}{\first{i}}=\ustep$}\\
-
 	MAX \{0\} \cup  D(i,j) & 
 	\text{if $\stripe{\pmotif}{\first{i}}=\dstep$}\\		
-
-	\end{array} \right. $\\
+\end{cases}
+$
 
@@
 
-%$
-%\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= 
-%\begin{cases}
-%true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$ with every element in $[\min,\max]$} \\
-%false & otherwise
-%\end{cases}
-%$
-
-$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
-\left\{ 
-\begin{array}{l l}
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
+\begin{cases}
 	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
@@
 
+			&\\
+
 	false 	& otherwise\\
-\end{array} \right.$\\
+\end{cases}
+$
 
@@
 if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\	
-$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}	
-= \left\{ 
-		\begin{array}{l l}
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
+\begin{cases}
 	true 	& \text{if $\min<\ptext[j]<\max$}\\
 	false 	& otherwise\\
-		\end{array} \right. $\\	
+\end{cases}
+$
 %$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
@@
 if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\		
-$ \PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
-= \left\{ 
-		\begin{array}{l l}
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext} =
+\begin{cases}
 	true 	& \text{if $\min<\ptext[n_\ptext]<\max$}\\
 	false 	& otherwise\\
-		\end{array} \right. $\\	
+\end{cases}
+$
 %$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
@@
 if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}= \left\{ 
-		\begin{array}{l l}
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+\begin{cases}
 	true 	& \text{if $\min<\ptext[j]<\max$ and }\\
@@
 	false 	& otherwise\\
-		\end{array} \right. $\\	
+\end{cases}
+$
 %$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
@@
 if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
-= \left\{ 
-		\begin{array}{l l}
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}=
+\begin{cases}
 	true 	& \text{if $\min<\ptext[n_\ptext]<\max$and }\\
@@
 	false 	& otherwise\\
-		\end{array} \right. $\\	
+\end{cases}
+$
 %$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
@@
 \textbf{STEP :} \\		
-$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}= \\ \left\{ 
-		\begin{array}{l l}
-
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
+\begin{cases}
 \bigcup_{j<k}
@@
 			&\\
+
 			False & Otherwise\\	
-		\end{array} \right. $\\
+\end{cases}
+$
 
@@
 	\item If $n_\pmotif \in \x$ there exists a match if and only if there is a match starting with the first element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.
-				\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
-							is true.	
+	\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$ is true.
 \end{itemize}
@@
 \textbf{BASE :} \\
-	$	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} = \left\{ 
-			\begin{array}{l l}
+$
+\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} =
+\begin{cases}
 	1 & \text{if $\min_1=\pi_1[j]=\max_1$  
@@
 	0 & otherwise\\
-			\end{array} \right. $\\
+\end{cases}
+$
 
@@
 
-	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
-	=$
-	$ \max \left\{ 
-			\begin{array}{l l}
+$
+\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=max
+\begin{cases}
 	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
@@
 	\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
-			\end{array} \right. $\vspace{20pt}\\
+\end{cases}
+$
 
-	with
-	$\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=\\ \left\{ 
-				\begin{array}{l l}
-					1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} & \text{$\pi_1[i_1]<\min_1$ } \\
+with \\
+$
+\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=
+\begin{cases}
+1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} 
+	& \text{$\pi_1[i_1]<\min_1$ } \\
 	& \text{and $\pi_2[i_2]<\min_2$} \\
+
 &\\
+
 1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
@@
 	&\text{and $\pi_2[i_2]>\max_2$}\\
+
 &\\
+
 0 	& \text{otherwise}\\	
-				\end{array} \right.$\\
+\end{cases}
+$
 

### 2015-02-09 article.tex
typos

--- 2015-02-08 article.tex
@@
 
+\newcommand{\x}{X}
+\newcommand{\y}{Y}
+\newcommand{\bmotif}{(\sigma,\x,\y)}
+
 %Stripe
@@
 \newcommand{\factor}[1]{\factora({#1})}
-
-%binvincular 
-\newcommand{\x}{X}
-\newcommand{\y}{Y}
-\newcommand{\bmotif}{(\sigma,\x,\y)}
-
-\newcommand{\pbmotif}{\pmotif^+}
-\newcommand{\pbmotifX}{\x_{\pbmotif}}
-\newcommand{\pbmotifY}{\y_{\pbmotif}}
-
-%LSC
-\DeclareMathOperator{\LCSa}{LCS}
-\newcommand{\LCS}[8]{\LCSa_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}
-
-\DeclareMathOperator{\matcha}{MATCH}
-\newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}
 
@@
 \end{itemize}
-Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
-An index $i$ of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
-For example if we have $\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$, then ${i,i+1,\ldots,j-1} \in \y$. 
-We represent the index that need to be overlined by the set $\y$. An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
-For example if we have
-For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
 % A bivincular pattern avoids a set of permutations $P$ if its bottom
@@
 
-This section focus on the pattern matching problem when only the motif avoid $(213,231)$.
+This section focus on the pattern containment problem 
+in case only the pattern $\sigma$ avoids $231$ and $213$.
 
 \begin{proposition}
-Let $\pmotif$, $\ptext$ 
-be two permutation,
-with  $\pmotif$ a permutation avoiding (231,213), 
-we can decide in $O(|\pmotif||\ptext|^2)$ time
-and $O(|\pmotif||\ptext|^2)$ space
-if $\pmotif$ 
-is a motif of $\ptext$.
+	\label{Proposition:sigma avoids 213 and 231}
+	Let $\sigma \in \AV_k(213,231)$ and $\pi \in S_n$.
+	One can decide in $O(kn^2)$ time
+	and $O(kn^2)$ space if $\pi$ contains $\sigma$.
 \end{proposition}
-
-%			\textbf{Proof}
-%			The main point is that
-%			if we match a ascnt (descent) element $i_{\pmotif}$ of the motif
-%			with an element $i_{\ptext}$ of the text,
-%			the optimal way of matching
-%			the first previous ascnt (descent)
-%			that appear before an descent (ascent)
-%			is to choose the
-%			maximal (minimal) element possible.
-%			Indeed if we do not take
-%			the maximal (minimal) element,
-%			we may prevent some element
-%			in the future matching.\\
 
@@
 For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$.
-\\
 
-\begin{proof}
+\begin{proof}[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
 Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
@@
 and the induction on $O(|\pmotif||\ptext|^2)$.
+\qed
 \end{proof}
@@
 
-\section{Pattern Matching With Bivincular Motif Avoiding (231,213)}	
+\section{$(213,231)$-avoiding bivincular patterns}	
 	\label{section:bivincular}
 
-This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
-We denote $\pbmotif=\bmotif$ the bivincular motif.
+	This section is devoted to presenting a polynomial-time algorithm for deciding whether
+	a $(213,231)$-avoiding bivincular pattern occurs in a permutation.
 
 	\begin{proposition}
-Let $\pbmotif$ be a bivincular motif such that $\pmotif$
-avoid (231,213), 
-$\ptext$ a permutation,
-we can decide in $O(|\pmotif||\ptext|^3)$ time
-and $O(|\ptext|^3)$ space
-if $\pbmotif$
-appear in $\ptext$.
+		\label{Proposition:bivincular pattern}
+			Let $\sigma$ be a $(213,231)$-avoiding bivincular pattern of length $k$
+			and $\pi \in S_n$.
+			One can decide in $O(kn^3)$ time
+			and $O(kn^3)$ space if $\pi$ contains $\sigma$.
 	\end{proposition}
@@
 			\begin{proof}
-			We consider the following problem :\\
+			We consider the following problem :
+			Given a bivincular motif $\bmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
 
-			Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
-
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \left\{ 
 				\begin{array}{l l}
-					true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
+					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
 						& \text{with every element in}\\ 
@@
 
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}$ is closed under induction. 
+			$\mathbb{P}_{\pmotif,\ptext,\min,\max}$ is closed under induction. 
 			it can be
@@
 			and $n_\pmotif \notin  \y$ : \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\
 
@@
 			and $n_\pmotif \notin  \y$ : \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\
 
@@
 			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
 					\begin{array}{l l}
@@
 			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
 					\begin{array}{l l}
@@
 					\end{array} \right. $\\	
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\
 
 			\textbf{STEP :} \\		
-			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \\ \left\{ 
+			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \\ \left\{ 
 					\begin{array}{l l}
 
-						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$
@@
 
-						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,k) 
+						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,k) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1) 
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]+1]) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}[\ptext[j]+1]) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]-1]) 
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}[\ptext[j]-1]) 
 							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
+						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
 							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
@@
 
-						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1)
+						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1)
 							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
@@
 
+			\qed
 			\end{proof}
@@
 
-	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}$
+	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
 	= max$\{$ $|s|$ $|$ 
@@
 	\textbf{BASE :} \\
-	$	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} = \left\{ 
+	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(|\pi_1|,|\pi_2|) = \left\{ 
 			\begin{array}{l l}
@@
 
-	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
-	=$
-	$ \max \left\{ 
+	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2) =$\\
+	\indent $ \max \left\{ 
 			\begin{array}{l l}
-				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
-				\\
-				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
-				\\
-				\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
+				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2+1) \\
+				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_22}(i_1+1,i_2) \\
+				S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)
 			\end{array} \right. $\vspace{20pt}\\
@@
 	with 
-	$\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=\\ \left\{ 
+	$S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)=\\ \left\{ 
 				\begin{array}{l l}
-					1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} & \text{$\pi_1[i_1]<\min_1$ } \\
+					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
 					& \text{and $\pi_2[i_2]<\min_2$} \\
 					&\\
-					1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
-					 & \text{$\pi_1[i_1]>\max_1$ } \\	
+					1+S_{\pi_1,\pi_2,\min_1,\pi_1[i_1],\min_2,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]>\max_1$ } \\	
 					&\text{and $\pi_2[i_2]>\max_2$}\\	

### 2015-02-09 article.tex
end cases

--- 2015-02-08 article.tex
@@
 
-This section focus on the pattern matching problem when only the motif avoid $(213,231)$.
+This section focus on the pattern containment problem
+in case only the pattern $\sigma$ avoids $231$ and $213$.
 
 \begin{proposition}
-Let $\pmotif$, $\ptext$ 
-be two permutation,
-with  $\pmotif$ a permutation avoiding (231,213), 
-we can decide in $O(|\pmotif||\ptext|^2)$ time
-and $O(|\pmotif||\ptext|^2)$ space
-if $\pmotif$ 
-is a motif of $\ptext$.
+	\label{Proposition:sigma avoids 213 and 231}
+	Let $\sigma \in \AV_k(213,231)$ and $\pi \in S_n$.
+	One can decide in $O(kn^2)$ time
+	and $O(kn^2)$ space if $\pi$ contains $\sigma$.
 \end{proposition}
-
-%			\textbf{Proof}
-%			The main point is that
-%			if we match a ascnt (descent) element $i_{\pmotif}$ of the motif
-%			with an element $i_{\ptext}$ of the text,
-%			the optimal way of matching
-%			the first previous ascnt (descent)
-%			that appear before an descent (ascent)
-%			is to choose the
-%			maximal (minimal) element possible.
-%			Indeed if we do not take
-%			the maximal (minimal) element,
-%			we may prevent some element
-%			in the future matching.\\
 
@@
 
-\section{Pattern Matching With Bivincular Motif Avoiding (231,213)}	
+\section{$(213,231)$-avoiding bivincular patterns}
 	\label{section:bivincular}
 
-This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
-We denote $\pbmotif=\bmotif$ the bivincular motif.
+		This section is devoted to presenting a polynomial-time algorithm for deciding whether
+	a $(213,231)$-avoiding bivincular pattern occurs in a permutation.
 
 	\begin{proposition}
-Let $\pbmotif$ be a bivincular motif such that $\pmotif$
-avoid (231,213), 
-$\ptext$ a permutation,
-we can decide in $O(|\pmotif||\ptext|^3)$ time
-and $O(|\ptext|^3)$ space
-if $\pbmotif$
-appear in $\ptext$.
+		\label{Proposition:bivincular pattern}
+			Let $\sigma$ be a $(213,231)$-avoiding bivincular pattern of length $k$
+			and $\pi \in S_n$.
+			One can decide in $O(kn^3)$ time
+			and $O(kn^3)$ space if $\pi$ contains $\sigma$.
 	\end{proposition}
@@
 			&[\min,\max]\\
+>>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac
 
@@
 \end{proof}
+>>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac
 

### 2015-02-09 article.tex
end cases

@@
 \begin{abstract}
-	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the Permutation Pattern (PP)
-	problem is to decide whether $\pi$ contains $\sigma$ as an order-isomorphic pattern.
+	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the
+  \emph{pattern containment} problem is to decide whether $\pi$ contains
+  $\sigma$ as an order-isomorphic subsequence.
 	We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid
@@
 	\emph{pattern} of $\pi$.
-	Otherwise, $\pi$ is said to avoid the permutation $\sigma$.
+	Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
 	For example a permutation contains the pattern $123$ (resp. $321$) if it has
@@
 	Separable permutations are those permutations that contain neither
-	$2413$ nor $3142$, and they are enumerated by the Schröder numbers
+	$2413$ nor $3142$, and they are enumerated by the Schr{\"o}der numbers
 	(sequence A006318 in OEIS).
@@
 We write permutations as words
-$\sigma = \sigma_1\sigma_2\,\ldots\,\sigma_n$, whose letters are distinct
+$\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose letters are distinct
 and uasually consist of the integers $12\,\ldots\,n$.

### 2015-02-09 article.tex
end cases

@@
 \newcommand{\pmotif}{\sigma}
+
+\newcommand\BV[2]{\genfrac{}{}{0pt}{}{#1}{#2}}
 
@@
  	if there is a way to remove a single element of $\pi$ to get a permutation
- 	that avoids all elements in $X$
- 	and $L_n(X)$ denotes the set of permutations of length $n$ that almost avoid
- 	$X$.
+ 	that avoids all elements in $P$
+ 	and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
+ 	$P$.
  	It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
@@
 
-Suppose $P$ is a set of permutations. We let $\AV_n(p)$ denote the
+Suppose $P$ is a set of permutations. We let $\AV_n(P)$ denote the
 set of all $n$-permutations avoiding each permutation in $P$.
-For the sake of convenience, we omit $P$'s braces thus having
+For the sake of convenience
+(and as it is customary), we omit $P$'s braces thus having
 e.g. $\AV_3(132,4312)$ instead of
@@
 A basic example is if
-$\pi = \pi_1\pi_2\,\ldots\,\pi_n$ avoids $321$, i.e.,
+$\pi = \pi_1\pi_2\,\ldots\,\pi_n \in \AV_n(321)$, i.e.,
 has no decreasing subsequence of length $3$, then its reverse,
@@
 For example, the permutation
-$345216$7 has ascents (at positions) $1,2,5,6$.
+$345216$7 has ascents (at positions) $1,2,5$ and $6$.
 Similarly, a \emph{descent} is a position
@@
 is $\stripew{\pi} = \dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep$.
-The stripe $\stripew{\sigma}$ is a \emph{pattern} of the strip $\stripew{\pi}$
-(or $\stripew{\sigma}$ \emph{occurs} of the strip $\stripew{\pi}$) if $\stripew{\sigma}$ occurs in
-$\stripew{\pi}$ as a subsequence.
+The stripe $\stripew{\sigma}$ is said to be a \emph{pattern} of the stripe $\stripew{\pi}$
+(or $\stripew{\sigma}$ \emph{occurs} of the stripe $\stripew{\pi}$)
+if $\stripew{\sigma}$ occurs in $\stripew{\pi}$ as a subsequence.
 
@@
 \end{itemize}
+For example,
+let
+$\sigma = \BV{\overline{123}}{\llcorner 213 \lrcorner}$.
+If $\pi_i\pi_j\pi_\ell$ is an occurrence of $\sigma$ in $\pi \in S_n$,
+then $\pi_i\pi_j\pi_k = (x+1)x(x+2)$ for some $1 \leq x \leq n-2$,
+$i=1$ and $\ell = n$.
+For example $316524$ contains one occurrence of $\sigma$ (the subsequuence $324$),
+whereas $42351$ avoids it.
+It is straightforward to see that an $n$-permutation
+$\pi$ avoids $\BV{\overline{123}}{\llcorner 213 \lrcorner}$ unless
+$n \geq 3$,
+$\pi_1 = x > 1$
+and $\pi_n = x+1$
+(in which case there is one occurrence of the pattern).
+
+For algorithmic treatment, it will be convenient \ldots
 Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
@@
 For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
+
 % A bivincular pattern avoids a set of permutations $P$ if its bottom

### 2015-02-09 article.tex
end cases

@@
 $i=1$ and $\ell = n$.
-For example $316524$ contains one occurrence of $\sigma$ (the subsequuence $324$),
+For example $316524$ contains one occurrence of $\sigma$ (the subsequence $324$),
 whereas $42351$ avoids it.
@@
 in case both $\pi$ and $\sigma$ are $(213,231)$-avoiding.
-We begin with an easy structure lemma.
+We begin with an easy but crucial structure lemma.
 
@@
 
-The above lemma gains in interest in the form of the following corollaries.
+Notice that Lemma~\ref{lemma:first element is 1 or n} gives as an
+immediate consequence that the number of $(213,231)$-avoiding $n$-permutations
+is $2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
+The above lemma also gains in interest in the form of the following corollary.
 
@@
 \label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations, given a subsequence $t$ of $\ptext$, $t$ is an occurrence of $\pmotif$ in $\ptext$ if and only if $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$.
+Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
+and $t$ be a subsequence of $\pi$ of length $\sigma$.
+Then $t$ is an occurrence of $\sigma$ in $\pi$ if and only if
+$\stripew{t}$ is an occurrence of $\stripew{\sigma}$ in $\stripew{\pi}$.
 \end{lemma}
@@
 
+\qed
+\end{proof}
+
+\begin{lemma}
+\label{lemma:MatchStripeToPermutation}
+Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
+and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
+Then, $t$ is an occurrence of $\sigma$ in $\pi$ if and only if
+$s_t$ occurs as a subsequence in $s_\pi$.
+\end{lemma}
+
+\begin{proof}
+  The forward direction is obvious.
+  We prove the backward direction by induction on the size of the motif
+  $\sigma$.
+  The base case is a motif of size $2$.
+  Suppose first that $\sigma = 12$ and hence $s_\sigma = a$.
+  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
+  such that $s_t$ occurs as a subsequence in $s_\pi$.
+  Since $s_\sigma = s_t = a$, this reduces to saying that
+  $\pi_{i_1} < \pi_{i_2}$, and hence $t$ is an occurrence of $\sigma = 12$ in $\pi$.
+  A similar argument shows that the lemma holds true for $\sigma = 21$.
+  Now, assume that the lemma is true for all motifs up to size $k \geq 2$.
+  Let $\sigma \in \Av{k+1}{231,213}$ and
+  let $t = \pi_{i_1}\pi_{i_2}\,\ldots\,\pi_{i_{k+1}}$,
+  $i_1 < i_2 < \ldots < i_{k+1}$,
+  be a subsequence of $\pi$ of length $k+1$ such that
+  $s_t = s_\sigma$.
+  Suppose that $s_t$ occurs in $s_\pi$ as a subsequence.
+  Then, $s_t[2:] = s_\sigma[2:]$ occurs as a subsequence in $s_\pi[2:]$.
+  But $\sigma[2:] \in \Av{k}{231,213}$ and hence,
+  by the inductive hypothesis, it follows that
+  $t[2:]$ is an occurrence of $\sigma[2:]$ in $\pi[2:]$.
+  Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
+  then $\sigma[1]$ is the minimum (resp. maximum) element of $\sigma$
+  (Lemma~\ref{lemma:first element is 1 or n}),
+  and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
+  $t[1]$ is the minimum (resp. maximum) element of $t$.
+  Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
 \qed

### 2015-02-09 article.tex
modifcation : take in account of corner in bivincular

--- 2015-02-09 article.tex
@@
 \begin{abstract}
-	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the
-  \emph{pattern containment} problem is to decide whether $\pi$ contains
-  $\sigma$ as an order-isomorphic subsequence.
+	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the Permutation Pattern (PP)
+	problem is to decide whether $\pi$ contains $\sigma$ as an order-isomorphic pattern.
 	We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid 
@@
 	\emph{pattern} of $\pi$.
-	Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
+	Otherwise, $\pi$ is said to avoid the permutation $\sigma$.
 	For example a permutation contains the pattern $123$ (resp. $321$) if it has
@@
 	Separable permutations are those permutations that contain neither
-	$2413$ nor $3142$, and they are enumerated by the Schr{\"o}der numbers
+	$2413$ nor $3142$, and they are enumerated by the Schröder numbers
 	(sequence A006318 in OEIS).
@@
 We write permutations as words 
-$\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose letters are distinct
+$\sigma = \sigma_1\sigma_2\,\ldots\,\sigma_n$, whose letters are distinct
 and uasually consist of the integers $12\,\ldots\,n$.
@@
 	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
-	$\sigma$ in a permutaton must be adjacent, whereas there is
+	$\sigma$ in a permutation must be adjacent, whereas there is
 	no adjacency condition for
@@
 Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
-An index $i$ of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
-For example if we have $\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$, then ${i,i+1,\ldots,j-1} \in \y$.
-We represent the index that need to be overlined by the set $\y$. An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
-For example if we have
-For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
+An index $i$, $1 \leq i < |\sigma|$, of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
+We also allow $0$ and $|\sigma|$ to be in the set $\x$ such that if $0 \in \x$ then we have $_\llcorner{\sigma_1}$ and if $|\sigma| \in \x$ then ${\sigma_{|\sigma|}}_\lrcorner$.
+We represent the index that need to be overlined by the set $\y$.
+An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
+We also allow $0$ and $|\sigma|$ to be in the set $\y$ such that if $0 \in \y$ then we have $^\ulcorner{1}$ and if $|\sigma| \in \y$ then ${|\sigma|}^\urcorner$.
 % A bivincular pattern avoids a set of permutations $P$ if its bottom
@@
 
-This section focus on the pattern containment problem
-in case only the pattern $\sigma$ avoids $231$ and $213$.
+This section focus on the pattern matching problem when only the motif avoid $(213,231)$.
 
 \begin{proposition}
-	\label{Proposition:sigma avoids 213 and 231}
-	Let $\sigma \in \AV_k(213,231)$ and $\pi \in S_n$.
-	One can decide in $O(kn^2)$ time
-	and $O(kn^2)$ space if $\pi$ contains $\sigma$.
+Let $\pmotif$, $\ptext$ 
+be two permutation,
+with  $\pmotif$ a permutation avoiding (231,213), 
+we can decide in $O(|\pmotif||\ptext|^2)$ time
+and $O(|\pmotif||\ptext|^2)$ space
+if $\pmotif$ 
+is a motif of $\ptext$.
 \end{proposition}
+
+%			\textbf{Proof}
+%			The main point is that
+%			if we match a ascnt (descent) element $i_{\pmotif}$ of the motif
+%			with an element $i_{\ptext}$ of the text,
+%			the optimal way of matching
+%			the first previous ascnt (descent)
+%			that appear before an descent (ascent)
+%			is to choose the
+%			maximal (minimal) element possible.
+%			Indeed if we do not take
+%			the maximal (minimal) element,
+%			we may prevent some element
+%			in the future matching.\\
 
@@
 For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$.
+\\
 
-\begin{proof}[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
+\begin{proof}
 Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
@@
 and the induction on $O(|\pmotif||\ptext|^2)$.
-\qed
 \end{proof}
@@
 
-\section{$(213,231)$-avoiding bivincular patterns}
+\section{Pattern Matching With Bivincular Motif Avoiding (231,213)}	
 \label{section:bivincular}
 
-		This section is devoted to presenting a polynomial-time algorithm for deciding whether
-	a $(213,231)$-avoiding bivincular pattern occurs in a permutation.
+This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
+We denote $\pbmotif=\bmotif$ the bivincular motif.
 
 \begin{proposition}
-		\label{Proposition:bivincular pattern}
-			Let $\sigma$ be a $(213,231)$-avoiding bivincular pattern of length $k$
-			and $\pi \in S_n$.
-			One can decide in $O(kn^3)$ time
-			and $O(kn^3)$ space if $\pi$ contains $\sigma$.
+Let $\pbmotif$ be a bivincular motif such that $\pmotif$
+avoid (231,213), 
+$\ptext$ a permutation,
+we can decide in $O(|\pmotif||\ptext|^3)$ time
+and $O(|\ptext|^3)$ space
+if $\pbmotif$
+appear in $\ptext$.
 \end{proposition}
@@
 			&[\min,\max]\\
->>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac
 
@@
 
-There are two cases to consider searching for a match :
+There are 6 cases to consider to search a match depending of if $0 \in \x$, $0 \in \y$ and if the first element of the motif is ascent or descent :
 \begin{itemize}
-	\item If $n_\pmotif \in \x$ there exists a match if and only if there is a match starting with the first element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.
-	\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$ is true.
+	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}
+	\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$ is true.
+
+	\item If $n_\pmotif \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{k}$ is true.
+
+	\item If $0 \in \x$, $0 \in \y$ and the first element of the motif is ascent there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$:\\ $\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
+
+	\item If $n_\pmotif \notin \x$, $0 \in \y$ and the first element of the motif is ascent there exists a match if and only if there exists a match stating at the index of the minimal element of $\ptext$ : if $j_{\min}$ is the index of the minimal element then \\	$\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{j_{\min}}$ is true.
+
+	\item If $0 \in \x$, $0 \notin \y$  and the first element of the motif is descent then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$:\\ $\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
+
+	\item If $n_\pmotif \notin \x$, $0 \notin \y$ and the first element of the motif is descent there exists a match if and only if there exists a match stating at the index of the maximal element of $\ptext$ : if $j_{\max}$ is the index of the maximal element then  \\	$\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{j_{\max}}$ is true.
+
 \end{itemize}
@@
 \end{proof}
->>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac
 

### 2015-02-09 article.tex
Section 4

--- 2015-02-09 article.tex
@@
 
-This section focus on the pattern containment problem
+This section focuses on the pattern containment problem
 in case only the pattern $\sigma$ avoids $231$ and $213$.
+We need to consider a specific decomposition $F$ of $\sigma$ into factors.
+For $\sigma \in S_k$, the factorization
+$\sigma = F(p) F(p-1) \ldots F(1)$ is defined as follows:
+(i) $\sigma[k]$ is the last letter of $F(1)$,
+(ii) for every $1 \leq i < k$,
+if $s_\sigma[i] = s_\sigma[i+1]$ then
+$\sigma[i]\sigma[i+1]$ is part of the same factor.
+For every factor $F(j)$ of the decomposition, we let
+$L(j)$ stand for the leftmost letter of $F(j)$.
+For example,
+for $\sigma = 981237654$,
+we have
+$\sigma = F(4) F(2) F(1)$ with
+$F(1) =7654$, $F(2) = 123$ and $F(3) = 98$.
+Furthermore,
+$L(1) = 7$, $L(2) = 1$ and $L(3) = 9$.
 
@@
 Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
-
-$
+$$
 \PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
@@
 	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
-			& \text{with every element in}\\
-			&[\min,\max]\\
->>>>>>> f9bc0a20a19c155782e9e48e9d01a9fb6f3718ac
-
-			&\\
-
+			  & \text{with every element in $[\min,\max]$}\\
 	false 	& otherwise\\
 \end{cases}
-$
-
+$$
 $\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction.
-it can be solved by means of the following relations:\\
+It can be solved by means of the following relations:\\
 

### 2015-02-09 article.tex

@@
 \end{itemize}
+
 For example,
@@
 
-For algorithmic treatment, it will be convenient \ldots
+For algorithmic treatment, it will be convenient to have \ldots
 Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
-An index $i$ of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
-For example if we have $\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$, then ${i,i+1,\ldots,j-1} \in \y$.
-We represent the index that need to be overlined by the set $\y$. An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
-For example if we have
-For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
+An index $i$, $1 \leq i < |\sigma|$, of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
+We also allow $0$ and $|\sigma|$ to be in the set $\x$ such that if $0 \in \x$ then we have $_\llcorner{\sigma_1}$ and if $|\sigma| \in \x$ then ${\sigma_{|\sigma|}}_\lrcorner$.
+We represent the index that need to be overlined by the set $\y$.
+An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
+We also allow $0$ and $|\sigma|$ to be in the set $\y$ such that if $0 \in \y$ then we have $^\ulcorner{1}$ and if $|\sigma| \in \y$ then ${|\sigma|}^\urcorner$.
 
@@
 
-There are two cases to consider searching for a match :
+There are 6 cases to consider to search for a match. The 6 cases depend on if $0 \in \x$, $0 \in \y$ and if the first element of the stripe of the motif is ascent or descent :
 \begin{itemize}
-	\item If $n_\pmotif \in \x$ there exists a match if and only if there is a match starting with the first element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.
-	\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$ is true.
+	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}
+	\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$ is true.
+
+	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{k}$ is true.
+
+	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is ascent there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$:\\ $\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
+
+	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is ascent there exists a match if and only if there exists a match stating at the index of the minimal element of $\ptext$ : if $j_{\min}$ is the index of the minimal element then \\	$\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{j_{\min}}$ is true.
+
+	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is descent then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$:\\ $\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
+
+	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is descent there exists a match if and only if there exists a match stating at the index of the maximal element of $\ptext$ : if $j_{\max}$ is the index of the maximal element then  \\	$\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{j_{\max}}$ is true.
+
 \end{itemize}

### 2015-02-09 article.tex
Section 4

--- 2015-02-09 article.tex
@@
 we have
-$\sigma = F(4) F(2) F(1)$ with
+$s_\sigma = ddaaaddd$ and hence
+$\sigma = F(3) F(2) F(1)$ with
 $F(1) =7654$, $F(2) = 123$ and $F(3) = 98$.
@@
 
-For the proof and the algorithm we introduce a decomposition : we decompose the stripe of the motif into factor of same letter, and label those factor from right to left.
+% For the proof and the algorithm we introduce a decomposition : we decompose the stripe of the motif into factor of same letter, and label those factor from right to left.
 We also need to add the last index into the first factor.
@@
 
-\begin{proof}[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
+\begin{proof}%[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
 Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.

### 2015-02-09 article.tex
add : lemma and corollary for section 4 to explain a safe match

@@
 %Pattern Marching
-
 \DeclareMathOperator{\PMa}{PM}
@@
 \newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}
+
+%SET OF OCCURENCE
+\DeclareMathOperator{\SETa}{S}
+\newcommand{\SET}[4]{\SETa_{{#1}}^{{#2}}({#3},{#4})}
 
@@
 Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
-and $t$ be a subsequence of $\pi$ of length $\sigma$.
-Then $t$ is an occurrence of $\sigma$ in $\pi$ if and only if
-$\stripew{t}$ is an occurrence of $\stripew{\sigma}$ in $\stripew{\pi}$.
-\end{lemma}
-
-\begin{proof}
-	The forward direction is obvious.
-	We prove the backward direction by induction on the size of the motif
-	$\sigma$.
-	The base case is a motif of size 2.
-Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$.
-Let's $t$ be a subsequence of $\ptext$ such that $\stripew{t}$ is a occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$.
-Because we have $\stripe{t}{1}=\ustep$, the next element of $t[1]$ is $\ptext$ is superior to  $t[1]$, so we have a match.
-Same idea goes of motif $(21)$.
-	Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$.
-Suppose that we have a subsequence $t$ of $\ptext$ such that $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$, then $\stripew{t[2:]}$ is an occurrence of $\pmotif[2:]$ in $\ptext$.
-Moreover
-	$\pmotif[2:] \in \Av{n}{(231,213)}$ so by hypothesis of induction $t[2:]$ is an occurrence of $\sigma[2:]$ in $\ptext$.
-	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif.
-Furthermore $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$ , so $\stripe{t}{1}$ is also ascend (descent) thus $t[1]$ is also the minimal (maximal) element of the subsequence $t$ which complete our proof.
-
-\qed
-\end{proof}
-
-\begin{lemma}
-\label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
 and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
@@
 
+\begin{lemma}
+\label{lemma:MatchStripeToPermutation}
+Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
+and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
+Then, $t$ is an occurrence of $\sigma$ in $\pi$ if and only if
+$s_t$ occurs as a subsequence in $s_\pi$.
+\end{lemma}
+
+\begin{proof}
+  The forward direction is obvious.
+  We prove the backward direction by induction on the size of the motif
+  $\sigma$.
+  The base case is a motif of size $2$.
+  Suppose first that $\sigma = 12$ and hence $s_\sigma = a$.
+  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
+  such that $s_t$ occurs as a subsequence in $s_\pi$.
+  Since $s_\sigma = s_t = a$, this reduces to saying that
+  $\pi_{i_1} < \pi_{i_2}$, and hence $t$ is an occurrence of $\sigma = 12$ in $\pi$.
+  A similar argument shows that the lemma holds true for $\sigma = 21$.
+  Now, assume that the lemma is true for all motifs up to size $k \geq 2$.
+  Let $\sigma \in \Av{k+1}{231,213}$ and
+  let $t = \pi_{i_1}\pi_{i_2}\,\ldots\,\pi_{i_{k+1}}$,
+  $i_1 < i_2 < \ldots < i_{k+1}$,
+  be a subsequence of $\pi$ of length $k+1$ such that
+  $s_t = s_\sigma$.
+  Suppose that $s_t$ occurs in $s_\pi$ as a subsequence.
+  Then, $s_t[2:] = s_\sigma[2:]$ occurs as a subsequence in $s_\pi[2:]$.
+  But $\sigma[2:] \in \Av{k}{231,213}$ and hence,
+  by the inductive hypothesis, it follows that
+  $t[2:]$ is an occurrence of $\sigma[2:]$ in $\pi[2:]$.
+  Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
+  then $\sigma[1]$ is the minimum (resp. maximum) element of $\sigma$
+  (Lemma~\ref{lemma:first element is 1 or n}),
+  and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
+  $t[1]$ is the minimum (resp. maximum) element of $t$.
+  Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
+\qed
+\end{proof}
+
 We are now ready to solve the pattern containment problem in case
@@
 
+To ease the lemma and its proof we define the set $\SET{\pmotif}{\ptext}{i}{j}$ such that if $s \in S$, then $s$ is an occurrence of $\factor{i} \factor{i-1} \cdots \factor{1}$ in $\ptext[j:]$ and $s[\first{i}]=\ptext[j]$.
+
+\begin{lemma}
+Given a permutation $\pmotif$ and $\factor{i}$ an ascent (descent) factor.
+Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{i-1}]$ is minimal (maximal), given a subsequence
+$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and a subsequence $t=t's'$ of $\ptext$  if $t$ is an occurrence of $\factor{i+1} \factor{i} \factor{i-1} \cdots \factor{1}$ then the subsequence $t's$ is an occurrence of $\factor{i+1} \factor{i} \factor{i-1} \cdots \factor{1}$ in $\ptext$.
+\end{lemma}
+
+\begin{proof}
+Given a permutation $\pmotif$ and $\factor{i}$ an ascent (descent) factor.
+Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{i-1}]$ is minimal (maximal).
+Let's $s' \in \SET{\pmotif}{\ptext}{i}{j}$ and a subsequence $t=t's'$ of $\ptext$ such that $t$ is an occurrence of $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$. 
+Remark that every element of $t'$ must be superior (inferior) to every element of $s'$, and that the maximal element of $s'$ is the element matched to $t[\first{i-1}]$.
+Thus if we have a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$ such that $s[\first{i-1}]$ is minimal (maximal), then $s[\first{i-1}]\leq s'[\first{i-1}]$, so every element of $'t$ is also superior (inferior) to every element of $s$.
+Thus the subsequence $t's$ is an occurrence of $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$ in $\ptext$.
+\end{proof}
+
+\begin{corollary}
+Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{i-1}]$ is minimal (maximal).
+There is a match of $\pmotif$ in $\ptext$ with element $\first{i}$ matched to $\ptext[j]$ if and only if there exists $t$ such that $ts$ is a match of $\pmotif$ in $\ptext$.
+\end{corollary}
+
+This corollary give us a safe way to choose a match.
+
 \begin{proposition}
@@
 \begin{proof}%[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
-Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
+%Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the safest match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
+Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
 In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
-Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
-
-\begin{remark}
-Given an ascent (descent) factor $\factor{i}$, the maximal (minimal) element of $\factor{i}\factor{i-1}\cdots\factor{1}$ is $\first{i-1}$.
-\end{remark}
-
-\begin{remark}
-An ascent (descent) factor 	$\factor{i}$ is a match in $\ptext[j:j']$  if and only if there exists an increasing (decreasing) subsequence in $\ptext[j:j']$ of size superior or equal to the size of $\factor{i}$.
-\end{remark}
+%
+%\begin{remark}
+%Given an ascent (descent) factor $\factor{i}$, the maximal (minimal) element of $\factor{i}\factor{i-1}\cdots\factor{1}$ is $\first{i-1}$.
+%\end{remark}
+%
+%\begin{remark}
+%An ascent (descent) factor 	$\factor{i}$ is a match in $\ptext[j:j']$  if and only if there exists an increasing (decreasing) subsequence in $\ptext[j:j']$ of size superior or equal to the size of $\factor{i}$.
+%\end{remark}
 
 Consider the following problem :\\
-$LM(i,j)$ = the optimal match of $\first{i-1}$
+$LM(i,j)$ = the safest match of $\first{i-1}$
 	if there exists a match of $\pmotif[\first{i}:]$
@@
 inferior (superior) to $k$.
-LIS and LDS can be computed in $O(|\ptext|^2*log(log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
+LIS and LDS can be computed in $O(|\ptext|^2*\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
 
@@
 	finding the longest subsequence avoiding (231,213)
-	can be done in $O(|\ptext|log(log(|\ptext|)))$ time and in $O(n)$ space.
+	can be done in $O(|\ptext|\log(\log(|\ptext|)))$ time and in $O(n)$ space.
 	\end{proposition}
@@
 	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
-	Computing the longest increasing and decreasing can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
+	Computing the longest increasing and decreasing can be done in $O(|\ptext|*\log(\log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
 	\end{proof}

### 2015-02-09 article.tex
organization of the paper

@@
 	This paper is organized as follows.
-
-%	The permutation pattern problem asks if there exists a normalized subsequence of a text $\ptext$ which equals to a motif $\pmotif$.
-%	If so we write $\pmotif \preceq \ptext$.
-%	If not we say that $\ptext$ \textbf{avoid} $\pmotif$.
-%	This was first introduced by Knuth \cite{Knuth:1997:ACP:260999}
-%	who proves that permutation sortable by stacks
-%	avoid the motif $231$.
-%	The problem is NP-hard in general,
-%	but for some classes of permutation,
-%	polynomial time solution exists.
-%	For instance the separable permutation \cite{Bose93patternmatching}.
-%	We contribute studying this problem
-%	and related one for the class of permutation avoiding (231,213).
-%	This is interesting because this class is in linear bijection between the classes of (123,132),(132,213) and (132,213)
-%	avoiding permutation, and all the classes obtainable by reversal or/and
-%	complementation (see \cite{Simion1985383}).\\
-%
-%
-%
-%	This paper is organized as follows.
-%	Section 2 presents the needed definition.
-%	Section 3 solves the permutation pattern problem with
-%	(213,231) avoiding permutations.
-%	Section 4 focus on the problem the
-%	related problem of computing a longest permutation avoiding (213,231).
-%	Finally, section 5 summarizes
-%	results for related problems.
+	In Section~\ref{section:Definitions} the needed definition are presented.
+	Section~\ref{section:both are (231,213)-avoiding} is devoted to presenting 
+	an online linear-time algorithm in case both the pattern and the target
+	permutation are $(213,231)$-avoiding,
+	where Section~\ref{section:sigma only avoid 231 and 213} focuses on the case
+	where the pattern only is $(213,231)$-avoiding.
+	In Section~\ref{section:bivincular} we give a polynomial-time algorithm
+	for $(213,231)$-avoiding bivincular patterns.
+	In Section~\ref{section:LCS} we consider the problem of finding the longest
+	$(213,231)$-avoiding pattern in a permutation.
+	In Section~\ref{section:LCS common 2 permutations} we give a
+	polynomial-time algorithm for computing the longest 
+	$(213,231)$-avoiding pattern common to two permutations.
 
@@
 \end{itemize}
-
 \end{proof}
@@
 \section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutation}
+\label{section:LCS common 2 permutations}
 

### 2015-02-11 article.tex
modification : add lemma for section 4

@@
 \DeclareMathOperator{\firsta}{L}
-\newcommand{\first}[1]{\firsta({#1})}
+\newcommand{\first}[2]{\firsta_{{#1}}({#2})}
+
+\DeclareMathOperator{\firstia}{LI}
+\newcommand{\firsti}[2]{\firstia_{{#1}}({#2})}
 
 \DeclareMathOperator{\factora}{F}
-\newcommand{\factor}[1]{\factora({#1})}
+\newcommand{\factor}[2]{\factora_{{#1}}({#2})}
 
@@
 \newcommand{\PM}[6]{\PMa_{{#1}}^{{#2},{#3},{#4}}({#5},{#6})}
+
+%LM
+\DeclareMathOperator{\LMa}{LM}
+\newcommand{\LM}[4]{\LMa_{{#1}}^{{#2}}(#3,#4)}
+
+\DeclareMathOperator{\AFa}{AF}
+\newcommand{\AF}[4]{\AFa_{{#1}}^{{#2}}(#3,#4)}
+
+\DeclareMathOperator{\DFa}{DF}
+\newcommand{\DF}[4]{\DFa_{{#1}}^{{#2}}(#3,#4)}
 
@@
 
-\begin{lemma}
-\label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
-and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
-Then, $t$ is an occurrence of $\sigma$ in $\pi$ if and only if
-$s_t$ occurs as a subsequence in $s_\pi$.
-\end{lemma}
-
-\begin{proof}
-  The forward direction is obvious.
-  We prove the backward direction by induction on the size of the motif
-  $\sigma$.
-  The base case is a motif of size $2$.
-  Suppose first that $\sigma = 12$ and hence $s_\sigma = a$.
-  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-  such that $s_t$ occurs as a subsequence in $s_\pi$.
-  Since $s_\sigma = s_t = a$, this reduces to saying that
-  $\pi_{i_1} < \pi_{i_2}$, and hence $t$ is an occurrence of $\sigma = 12$ in $\pi$.
-  A similar argument shows that the lemma holds true for $\sigma = 21$.
-  Now, assume that the lemma is true for all motifs up to size $k \geq 2$.
-  Let $\sigma \in \Av{k+1}{231,213}$ and
-  let $t = \pi_{i_1}\pi_{i_2}\,\ldots\,\pi_{i_{k+1}}$,
-  $i_1 < i_2 < \ldots < i_{k+1}$,
-  be a subsequence of $\pi$ of length $k+1$ such that
-  $s_t = s_\sigma$.
-  Suppose that $s_t$ occurs in $s_\pi$ as a subsequence.
-  Then, $s_t[2:] = s_\sigma[2:]$ occurs as a subsequence in $s_\pi[2:]$.
-  But $\sigma[2:] \in \Av{k}{231,213}$ and hence,
-  by the inductive hypothesis, it follows that
-  $t[2:]$ is an occurrence of $\sigma[2:]$ in $\pi[2:]$.
-  Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
-  then $\sigma[1]$ is the minimum (resp. maximum) element of $\sigma$
-  (Lemma~\ref{lemma:first element is 1 or n}),
-  and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
-  $t[1]$ is the minimum (resp. maximum) element of $t$.
-  Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
-\qed
-\end{proof}
-
 We are now ready to solve the pattern containment problem in case
@@
 in case only the pattern $\sigma$ avoids $231$ and $213$.
-We need to consider a specific decomposition $F$ of $\sigma$ into factors.
+We need to consider a specific decomposition $\factora$ of $\sigma$ into factors.
 For $\sigma \in S_k$, the factorization
-$\sigma = F(p) F(p-1) \ldots F(1)$ is defined as follows:
-(i) $\sigma[k]$ is the last letter of $F(1)$,
+$\sigma = \factor{\pmotif}{p} \factor{\pmotif}{p-1} \ldots \factor{\pmotif}{1}$ is defined as follows:
+(i) $\sigma[k]$ is the last letter of $\factor{\pmotif}{1}$,
 (ii) for every $1 \leq i < k$,
@@
 $\sigma[i]\sigma[i+1]$ is part of the same factor.
-For every factor $F(j)$ of the decomposition, we let
-$L(j)$ stand for the leftmost letter of $F(j)$.
+For every factor $\factor{\pmotif}{j}$ of the decomposition, we let
+$\first{\pmotif}{j}$ stand for the leftmost letter of $\factor{\pmotif}{j}$,
+and $\firsti{\pmotif}{j}$ stand for the index of the leftmost letter of $\factor{\pmotif}{j}$.
 For example,
@@
 $s_\sigma = ddaaaddd$ and hence
-$\sigma = F(3) F(2) F(1)$ with
-$F(1) =7654$, $F(2) = 123$ and $F(3) = 98$.
+$\sigma = \factor{\pmotif}{3} \factor{\pmotif}{2} \factor{\pmotif}{1}$ with
+$\factor{\pmotif}{1} =7654$, $\factor{\pmotif}{2} = 123$ and $\factor{\pmotif}{3} = 98$.
 Furthermore,
-$L(1) = 7$, $L(2) = 1$ and $L(3) = 9$.
-
-To ease the lemma and its proof we define the set $\SET{\pmotif}{\ptext}{i}{j}$ such that if $s \in S$, then $s$ is an occurrence of $\factor{i} \factor{i-1} \cdots \factor{1}$ in $\ptext[j:]$ and $s[\first{i}]=\ptext[j]$.
+$\first{\pmotif}{1} = 7$, $\first{\pmotif}{2} = 1$, $\first{\pmotif}{3} = 9$,
+$\firsti{\pmotif}{1} = 6$, $\firsti{\pmotif}{2} = 3$ and $\firsti{\pmotif}{3} = 1$.
+
+\begin{remark}
+A Factor is either an increasing or a decreasing subsequence.
+\end{remark}
 
 \begin{lemma}
-Given a permutation $\pmotif$ and $\factor{i}$ an ascent (descent) factor.
-Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{i-1}]$ is minimal (maximal), given a subsequence
-$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and a subsequence $t=t's'$ of $\ptext$  if $t$ is an occurrence of $\factor{i+1} \factor{i} \factor{i-1} \cdots \factor{1}$ then the subsequence $t's$ is an occurrence of $\factor{i+1} \factor{i} \factor{i-1} \cdots \factor{1}$ in $\ptext$.
+\label{lemma:whereIsMax}
+Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, if
+$\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ ($\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$)  the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
 \end{lemma}
@@
 \begin{proof}
-Given a permutation $\pmotif$ and $\factor{i}$ an ascent (descent) factor.
-Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{i-1}]$ is minimal (maximal).
-Let's $s' \in \SET{\pmotif}{\ptext}{i}{j}$ and a subsequence $t=t's'$ of $\ptext$ such that $t$ is an occurrence of $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$. 
-Remark that every element of $t'$ must be superior (inferior) to every element of $s'$, and that the maximal element of $s'$ is the element matched to $t[\first{i-1}]$.
-Thus if we have a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$ such that $s[\first{i-1}]$ is minimal (maximal), then $s[\first{i-1}]\leq s'[\first{i-1}]$, so every element of $'t$ is also superior (inferior) to every element of $s$.
-Thus the subsequence $t's$ is an occurrence of $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$ in $\ptext$.
+Take the right most element of $\factor{\sigma}{i}$, this element is an ascent (descent),
+so it is inferior (superior) to the next element which is $\first{\sigma}{i-1}$.
+Because $\factor{\sigma}{i}$ is an increasing (decreasing) subsequence, every element of $\factor{\sigma}{i}$ is inferior (superior) to $\first{\sigma}{i-1}$.
+By lemma \ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ thus $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
+
 \end{proof}
 
+To ease the next lemma and its proof we define the set $\SET{\pmotif}{\ptext}{i}{j}$ such that if $s \in S$, then $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element matching $\first{\pmotif}{i}$ is $\ptext[j]$.
+
+\begin{lemma}
+Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (descent) factor.
+Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (maximal), for all subsequence 
+$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequence of $\ptext$ $t$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$.
+\end{lemma}
+
+\begin{proof}
+Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (descent) factor.
+Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (maximal).
+Let's $s' \in \SET{\pmotif}{\ptext}{i}{j}$ and $t$ subsequence of $\ptext$, such that $t=t's'$ and $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ in $\pi$. 
+Remark that every element of $t'$ is superior (inferior) to every element of $s'$.
+Note that the element matching $\first{\pmotif}{i-1}$ in $s$ is minimal (maximal) and it is the maximal (minimal) element of the subsequence (\ref{lemma:whereIsMax}), thus
+it is inferior (superior) to the element matching $\first{\pmotif}{i-1}$ in $s'$.
+So every element of $t'$ is also superior (inferior) to every element of $s$. Thus the subsequence $t's$ is an occurrence of $\pmotif[\first{\pmotif}{i+1}:]$ in $\ptext$.
+\end{proof}
+
 \begin{corollary}
-Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{i-1}]$ is minimal (maximal).
-There is a match of $\pmotif$ in $\ptext$ with element $\first{i}$ matched to $\ptext[j]$ if and only if there exists $t$ such that $ts$ is a match of $\pmotif$ in $\ptext$.
+Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (maximal).
+There is a match of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ matched to $\ptext[j]$ if and only if there exists $t$ such that $ts$ is a match of $\pmotif$ in $\ptext$.
 \end{corollary}
 
-This corollary give us a safe way to choose a match.
+This corollary gives one a safe way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix then there is no match at all.
 
@@
 Consider the following problem :\\
-$LM(i,j)$ = the safest match of $\first{i-1}$
-	if there exists a match of $\pmotif[\first{i}:]$
-	with $\ptext[j:]$
-	and element $\first{i}$
-	is matched with element at index $j$.\\
+$
+\LM{\pmotif}{\ptext}{i}{j} = 
+\begin{cases}
+	\text{The maximal value of a subsequence} 
+		& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ } \\
+	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \\	
+	\text{ and that minimize the maximal value} & \\
+	\text{ and $\first{\sigma}{i}$ is matched with $\ptext[j]$} & \\
+
+	&\\
+
+	\text{The minimal value of a subsequence} 
+		& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$ } \\
+	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \\	
+	\text{ and that maximize the minimal value} & \\
+	\text{ and $\first{\sigma}{i}$ is matched with $\ptext[j]$} & \\
+\end{cases}
+$
 
@@
 $
-LM(1,j)=
-\begin{cases}
-		MIN_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } &
-			\text{if $\stripe{\pmotif}{\first{1}}=\ustep$} \\
-		\text{ $|\factor{1}| \leq LIS(j,j',\ptext[j'])  $}\}& \\
-		&\\
-		MAX_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } &
-			\text{if $\stripe{\pmotif}{\first{1}}=\dstep$} \\
-		\text{ $|\factor{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\
+\LM{\pmotif}{\ptext}{1}{j} = 
+\begin{cases}
+		\min_{j<j'}\{\infty\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
+			& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ }  \\
+		\text{ $|\factor{\pmotif}{1}| \leq LIS(j,j',\ptext[j'])  $}\}& \\
+		&\\
+		\max_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
+			& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$ } \\
+		\text{ $|\factor{\pmotif}{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\
 \end{cases}
@@
 $
-LM(i,j)=
-\begin{cases}
-	MIN \{0\} \cup  I(i,j) &
-	\text{if $\stripe{\pmotif}{\first{i}}=\ustep$}\\
-	MAX \{0\} \cup  D(i,j) &
-	\text{if $\stripe{\pmotif}{\first{i}}=\dstep$}\\
-\end{cases}
-$
-
-With $I(i,j)$ ($D(i,j)$) the set of element such that
-if  $j' \in I(i,j)$ then there exists
-a match of $\pmotif[\first{i-1}:]$ in $\ptext[j':]$ and
-the element $\first{i-1}$ is matched with element at index $j'$ and
-there is a match of $\factor{i}$ in $\ptext[j:j'-1]$ and
-the element $\first{i}$ is matched with element at index $j$ and every element is inferior (superior) to the match of
-$\pmotif[\first{i-1}:]$ in $\ptext[j':]$.
-Formally we define $I(s,i)$ and $D(s,i)$ such as:\\
-
-$I(i,j)=\{j'|\text{$j<j'$ and $LM(i-1,j')\neq 0$}$ \\
-\indent \indent \indent and  $|\factor{i}| \leq LIS(j,j'-1,\first{i-1})\}$ \\
-
-$D(i,j)=\{j'|\text{$j<j'$ and $LM(i-1,j')\neq 0$}$ \\
-\indent \indent \indent and  $|\factor{i}| \leq LDS(j,j'-1,\first{i-1}) \}$ \\
-
-With LIS(i,j,k) (LDS(i,j,k)) is the longest increasing (decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
+\LM{\pmotif}{\ptext}{i}{j} =
+\begin{cases}
+	\min \{\infty\} \cup  \AF{\pmotif}{\ptext}{i}{j} &
+	\text{if $\stripe{\pmotif}{\first{\pmotif}{i}}=\ustep$}\\
+	\max \{0\} \cup  \DF{\pmotif}{\ptext}{i}{j} &
+	\text{if $\stripe{\pmotif}{\first{\pmotif}{i}}=\dstep$}\\
+\end{cases}
+$
+
+With $\AF{\pmotif}{\ptext}{i}{j}$ ($\DF{\pmotif}{\ptext}{i}{j}$) the set of element such that
+if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ then there exists
+a match of $\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$ and
+the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$ and
+there is a match of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ and
+the element $\first{\pmotif}{i}$ is matched with element $\ptext[j]$ and every element is inferior (superior) to the match of
+$\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$.
+Formally we define $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ such as:\\
+
+$\AF{\pmotif}{\ptext}{i}{j}=\{j'|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq 0$}$ \\
+\indent \indent \indent and  $|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$ \\
+
+$\DF{\pmotif}{\ptext}{i}{j}=\{j'|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq \infty$}$ \\
+\indent \indent \indent and  $|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\first{\pmotif}{i-1}) \}$ \\
+
+With $LIS_{\ptext}(i,j,k)$ ($LDS_{\ptext}(i,j,k)$) is the longest increasing (decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
 with every element of this sequence
 inferior (superior) to $k$.
-LIS and LDS can be computed in $O(|\ptext|^2*\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
+$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(|\ptext|^2*\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
 
 In the base case,
-we are looking for a match for the first factor.
-Each factor is either ascent or descent.
-If the factor is an ascent (descent)
-we have to find an increasing (decreasing) subsequence
+one is looking for a match for the first factor.
+If the factor is an ascent (descent),
+one has to find an increasing (decreasing) subsequence
 in the text of same size or longest that
 the size of the factor,
-and to find the optimal solution
-we must assure that the last element
+and to find the best solution
+one must assure that the last element
 of the sequence is minimal (maximal).\\
 For the induction, it is the same idea
-except that we must assure that
+except that one must assure that
 every element of the subsequence is superior (inferior)
-to the maximum (minimal) element of the rest of the match
-ie inferior (superior) to the minimal (maximal) element of the rest of the match
-which is given by $LM$ of
+to the maximum (minimal) element of the rest of the match which is given by $LM$ of
 the previous factor.\\
@@
 There exists a match of $\pmotif$ in $\ptext$ if and only if
-there exists a $LM(n,i)\neq 0$ for $1 \leq i \leq |\ptext|$,
+there exists a $LM(n,i)\neq 0$ and $LM(n,i)\neq \infty$ for $1 \leq i \leq |\ptext|$,
 with $n$ the number of factor in $\pmotif$.
-Moreover the basic case can be computed in $O(|\ptext|^2)$
-and the induction on $O(|\pmotif||\ptext|^2)$.
+Moreover the basic case can be computed in $O(n^2)$
+and the induction on $O(kn^2)$ time and space.
 \qed

### 2015-02-24 article.tex
modif : explaination of proof section 5

@@
 Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, if
-$\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ ($\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$)  the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
+$\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ ($\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$) then the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
 \end{lemma}
@@
 Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (maximal), for all subsequence 
-$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequence of $\ptext$ $t$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$.
+$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequence $t$ of $\ptext$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$.
 \end{lemma}
@@
 Remark that every element of $t'$ is superior (inferior) to every element of $s'$.
-Note that the element matching $\first{\pmotif}{i-1}$ in $s$ is minimal (maximal) and it is the maximal (minimal) element of the subsequence (\ref{lemma:whereIsMax}), thus
+Plus, remark that the element matching $\first{\pmotif}{i-1}$ in $s$ is minimal (maximal) and it is the maximal (minimal) element of the subsequence (\ref{lemma:whereIsMax}), thus
 it is inferior (superior) to the element matching $\first{\pmotif}{i-1}$ in $s'$.
@@
 \begin{corollary}
-Let's choose a subsequence $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (maximal).
+Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (maximal).
 There is a match of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ matched to $\ptext[j]$ if and only if there exists $t$ such that $ts$ is a match of $\pmotif$ in $\ptext$.
@@
 
-This corollary gives one a safe way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix then there is no match at all.
+This corollary gives one a safe way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the motif then there is no match at all.
 
@@
 
-With $\AF{\pmotif}{\ptext}{i}{j}$ ($\DF{\pmotif}{\ptext}{i}{j}$) the set of element such that
-if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ then there exists
-a match of $\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$ and
-the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$ and
-there is a match of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ and
-the element $\first{\pmotif}{i}$ is matched with element $\ptext[j]$ and every element is inferior (superior) to the match of
-$\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$.
+%
+%With $\AF{\pmotif}{\ptext}{i}{j}$ ($\DF{\pmotif}{\ptext}{i}{j}$) the set of element such that
+%if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ then there exists
+%a match of $\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$ and
+%the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$ and
+%there is a match of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ and
+%the element $\first{\pmotif}{i}$ is matched with element $\ptext[j]$ and every element is inferior (superior) to the match of
+%$\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$.
+
+With $\AF{\pmotif}{\ptext}{i}{j}$ ($\DF{\pmotif}{\ptext}{i}{j}$) the set of element such that if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ ($\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$) then there exists a match of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$.
+Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, to decide if $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$, one needs to find an match $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is a match of $\pmotif[\firsti{\pmotif}{i}:]$.
 Formally we define $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ such as:\\
@@
 
-In the base case,
+For the base case,
 one is looking for a match for the first factor.
@@
 the size of the factor,
-and to find the best solution
+and to find the safest solution
 one must assure that the last element
 of the sequence is minimal (maximal).\\
-For the induction, it is the same idea
+For the induction, it follows the same idea
 except that one must assure that
 every element of the subsequence is superior (inferior)
-to the maximum (minimal) element of the rest of the match which is given by $LM$ of
+to the maximum (minimal) element of the rest of the match which is given by $L$ of
 the previous factor.\\
@@
 	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
-			  & \text{with every element in $[\min,\max]$}\\
+			  & \text{with every element in $]\min,\max[$}\\
 	false 	& otherwise\\
@@
 \textbf{BASE :} \\
+
+For the base case, one matches the right most element of the motif.
+If the motif has a right bottom corner (if $n_\pmotif \in  \x$) then one must assure that the right most element of the motif is matched to the right most of the text.
+If the motif has a right top corner (if $n_\pmotif \in  \y$) and the right most element of the motif is maximal (minimal) then one must assure that right most element of the motif is matched to the maximal (minimal) element of the text.
+
 if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\
 $
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
 \begin{cases}
@@
 \begin{cases}
-	true 	& \text{if $\min<\ptext[n_\ptext]<\max$and }\\
+	true 	& \text{if $\min<\ptext[n_\ptext]<\max$ and }\\
 			&\text{$\ptext[n_\ptext]$ is the maximal element}\\
@@
 
+if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+\begin{cases}
+	true 	& \text{if $\min<\ptext[j]<\max$ and }\\
+			&\text{$\ptext[j]$ is the minimal element}\\
+	false 	& otherwise\\
+\end{cases}
+$
+%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
+
+if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
+$
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}=
+\begin{cases}
+	true 	& \text{if $\min<\ptext[n_\ptext]<\max$ and }\\
+			&\text{$\ptext[n_\ptext]$ is the minimal element}\\
+	false 	& otherwise\\
+\end{cases}
+$
+%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+
 \textbf{STEP :} \\
+
+For the induction there are 8 cases to consider, depending on if $\pmotif[i]$ is ascend or descend, if elements $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) and if elements $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$).
+First one must assure that $\pmotif[i]$ can be matched to $\ptext[j]$, this is done by checking that $\ptext[j]$ is in the interval $]\min,\max[$.
+Then one must use the induction.
+The element $\ptext[j]$ gives us a new $\min$ if the element is ascent or a new $\max$ if the element is descent.
+If $\pmotif[i]\pmotif[i+1]$ are not underlined nor overlined, then $\pmotif[i+1]$ can be matched to any upcoming element in the text.
+If $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) then the match of $\pmotif[i+1]$ must be $\ptext[j+1]$.
+If $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$) then ethe match of  $\pmotif[i+1]$ must be $\ptext[j]+1$.
+
 $
@@
 
-At each step (i,j),
-If $i \notin \x$ and $i \notin \y$,
-we match the current element of $\pmotif$ ($\pmotif[i]$)
-with the current element of $\ptext$ ($\ptext[j]$), if possible.
-Then we match $\pmotif[i+1:]$ with
-every suffixes $\ptext$ starting after $j$.\\
-
-If $i \in \x$ and $i \notin \y$,
-we match $\pmotif[i]$ to $\ptext[j]$,
-then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
-with the condition that
-$\pmotif[i+1]$ is matched to $\ptext[j+1]$.\\
-
-If $i \notin \x$, $i \in \y$ and i is a descent,
-we match $\pmotif[i]$ to $\ptext[j]$,
-then we match $\pmotif[i+1:]$
-with $\ptext[\ptext^{-1}[\ptext[j]-1]:]$
-with the condition that
-$\pmotif[i+1]$ is matched to the element $\ptext[j]-1$.\\
-
-If $i \notin \x$, $i \in \y$ and i is an ascent,
-we match $\pmotif[i]$ to $\ptext[j]$,
-then we match $\pmotif[i+1:]$
-with $\ptext[\ptext^{-1}[\ptext[j]+1]:]$
-with the condition that
-$\pmotif[i+1]$ is matched to the element $\ptext[j]+1$.\\
-
-If $i \in \x$, $i \in \y$ and i is a descent,
-we match $\pmotif[i]$ to $\ptext[j]$,
-then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
-with the condition that
-$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
-and that $\ptext[j+1]=\ptext[j]-1$.\\
-
-If $i \in \x$, $i \in \y$ and i is an ascent,
-we match $\pmotif[i]$ to $\ptext[j]$,
-then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
-with the condition that
-$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
-and that $\ptext[j+1]=\ptext[j]+1$.\\
-
-There are 6 cases to consider to search for a match. The 6 cases depend on if $0 \in \x$, $0 \in \y$ and if the first element of the stripe of the motif is ascent or descent :
+There are 6 cases to consider to search for a match.
+Depending on if the motif has a left bottom corner ($0 \in \x$), a left top corner, and if it has a left top corner $0 \notin \y$, if the left most element is minimal or maximal.
+If the motif left bottom corner, then one must assure that the left most element of the motif is matched to the left most element of the text.
+If the motif has a left top corner and the left most element of the motif is minimal (maximal) then one must assure that the left most element of the motif is matched with the minimal (maximal) element of the text :
 \begin{itemize}
-	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}
-	\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$ is true.
-
-	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{k}$ is true.
-
-	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is ascent there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$:\\ $\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
-
-	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is ascent there exists a match if and only if there exists a match stating at the index of the minimal element of $\ptext$ : if $j_{\min}$ is the index of the minimal element then \\	$\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{j_{\min}}$ is true.
-
-	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is descent then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$:\\ $\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{0}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
-
-	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is descent there exists a match if and only if there exists a match stating at the index of the maximal element of $\ptext$ : if $j_{\max}$ is the index of the maximal element then  \\	$\bigcup_{0<\min<\max<n_\ptext}\PM{\pbmotif}{\ptext}{\min}{\max}{0}{j_{\max}}$ is true.
+	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text : $ \PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{0}$ is true.
+
+	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index : 	$\bigcup_{0<k<n_\ptext}\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{k}$ is true.
+
+	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$ : $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{0}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
+
+	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there exists a match stating at the minimal element of the text : if $j_{\min}$ is the index of the minimal element in $\ptext$ then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{j_{\min}}$ is true.
+
+	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is maximal then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$: $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{0}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
+
+	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is maximal there exists a match if and only if there exists a match stating at the maximal element of the text : if $j_{\max}$ is the index of the maximal in $\ptext$ element then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{j_{\max}}$ is true.
 

### 2015-02-24 article.tex
typo

@@
 We consider the following problem :\\
-Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\
+Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$.
 $$
@@
 If the motif has a right top corner (if $n_\pmotif \in  \y$) and the right most element of the motif is maximal (minimal) then one must assure that right most element of the motif is matched to the maximal (minimal) element of the text.
+If there is not corner, there is no condition on the match of the right most element.
 
@@
 $
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext} =
-\begin{cases}
-	true 	& \text{if $\min<\ptext[n_\ptext]<\max$}\\
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
+\begin{cases}
+	true 	& \text{if $\min<\ptext[j]<\max$}\\
+			& \text{and } j=n_\ptext\\	
 	false 	& otherwise\\
@@
 \begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$ and }\\
-			&\text{$\ptext[j]$ is the maximal element}\\
+	true 	& \text{if $\min<\ptext[j]<\max$ }\\
+			& \text{and $\ptext[j]$ is the maximal element}\\
 	false 	& otherwise\\
@@
 $
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[n_\ptext]<\max$ and }\\
-			&\text{$\ptext[n_\ptext]$ is the maximal element}\\
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+\begin{cases}
+	true 	& \text{if $\min<\ptext[j]<\max$}\\
+			& \text{and } j=n_\ptext\\		
+			& \text{and $\ptext[n_\ptext]$ is the maximal element}\\
 	false 	& otherwise\\
@@
 \begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$ and }\\
-			&\text{$\ptext[j]$ is the minimal element}\\
+	true 	& \text{if $\min<\ptext[j]<\max$}\\	
+			& \text{and $\ptext[j]$ is the minimal element}\\
 	false 	& otherwise\\
@@
 $
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[n_\ptext]<\max$ and }\\
-			&\text{$\ptext[n_\ptext]$ is the minimal element}\\
+\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+\begin{cases}
+	true 	& \text{if $\min<\ptext[j]<\max$}\\
+			& \text{and } j=n_\ptext\\	
+			& \text{and $\ptext[n_\ptext]$ is the minimal element}\\
 	false 	& otherwise\\
@@
 Then one must use the induction.
-The element $\ptext[j]$ gives us a new $\min$ if the element is ascent or a new $\max$ if the element is descent.
+The element $\ptext[j]$ gives a new $\min$ if the element is ascent or a new $\max$ if the element is descent.
 If $\pmotif[i]\pmotif[i+1]$ are not underlined nor overlined, then $\pmotif[i+1]$ can be matched to any upcoming element in the text.
@@
 Depending on if the motif has a left bottom corner ($0 \in \x$), a left top corner, and if it has a left top corner $0 \notin \y$, if the left most element is minimal or maximal.
-If the motif left bottom corner, then one must assure that the left most element of the motif is matched to the left most element of the text.
+If the motif has a left bottom corner, then one must assure that the left most element of the motif is matched to the left most element of the text.
 If the motif has a left top corner and the left most element of the motif is minimal (maximal) then one must assure that the left most element of the motif is matched with the minimal (maximal) element of the text :
 \begin{itemize}
-	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text : $ \PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{0}$ is true.
-
-	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index : 	$\bigcup_{0<k<n_\ptext}\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{k}$ is true.
-
-	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$ : $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{0}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
-
-	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there exists a match stating at the minimal element of the text : if $j_{\min}$ is the index of the minimal element in $\ptext$ then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{j_{\min}}$ is true.
-
-	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is maximal then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$: $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{0}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
-
-	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is maximal there exists a match if and only if there exists a match stating at the maximal element of the text : if $j_{\max}$ is the index of the maximal in $\ptext$ element then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{0}{j_{\max}}$ is true.
+	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text : $ \PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true.
+
+	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index : 	$\bigcup_{1<k\leq n_\ptext}\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{k}$ is true.
+
+	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$ : $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
+
+	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there exists a match stating at the minimal element of the text : if $j_{\min}$ is the index of the minimal element in $\ptext$ then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\min}}$ is true.
+
+	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is maximal then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$: $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
+
+	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is maximal there exists a match if and only if there exists a match stating at the maximal element of the text : if $j_{\max}$ is the index of the maximal in $\ptext$ element then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\max}}$ is true.
 

### 2015-04-09 article.tex
refonte de la partie bivincular et modif de la def de bivincular

@@
 \newcommand{\PM}[6]{\PMa_{{#1}}^{{#2},{#3},{#4}}({#5},{#6})}
+
+\DeclareMathOperator{\lb}{lb}
+\DeclareMathOperator{\ub}{ub}
 
@@
 
-For algorithmic treatment, it will be convenient to have \ldots
-Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
+%For algorithmic treatment, it will be convenient to have \ldots
+%Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
 An index $i$, $1 \leq i < |\sigma|$, of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
 We also allow $0$ and $|\sigma|$ to be in the set $\x$ such that if $0 \in \x$ then we have $_\llcorner{\sigma_1}$ and if $|\sigma| \in \x$ then ${\sigma_{|\sigma|}}_\lrcorner$.
-We represent the index that need to be overlined by the set $\y$.
+%We represent the index that need to be overlined by the set $\y$.
 An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
@@
 
+We introduce property of bivincular permutation if the permutation is $(213,231)$-avoiding.
+
+\begin{lemma}
+\label{lemma:ascentDescentAscent}
+If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and if $\sigma[i]$ is ascent (decent) and $\sigma[i]+1$ is ascent (decent) then $i<j$ ($j>i$) and for every $k$, $i<k<j$ ($j>k>i$), $\pi[k]$ is descent (ascent).
+\end{lemma}
+
+\begin{proof}
+Suppose that there exists $k$, $i<k<j$ ($i>k>j$),
+such that $\pmotif[k]$ is ascent (descent).
+Ascent (descent)  elements are increasing (decreasing) so $\sigma[i]<\sigma[k]<\sigma[j]$ ($\sigma[i]<\sigma[k]<\sigma[j]$) which is in contradiction that with $\sigma[j]=\sigma[i]+1$.
+\end{proof}
+
 	\begin{proposition}
@@
 			and $\pi \in S_n$.
-			One can decide in $O(kn^3)$ time
-			and $O(kn^3)$ space if $\pi$ contains $\sigma$.
+			One can decide in $O(kn^4)$ time
+			and $O(kn^4)$ space if $\pi$ contains $\sigma$.
 	\end{proposition}
@@
 $$
-\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
+\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
 \begin{cases}
-	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
-			  & \text{with every element in $]\min,\max[$}\\
+	true 	& \text{If $\pbmotif[i:]$ occurs in $\ptext[j:]$}\\
+			& \text{with every element in $[\lb,\ub]$}\\
+			& \text{and element $\pmotif[i]$ occurs in $\ptext[j]$ }\\
 	false 	& otherwise\\
@@
 $$
-$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction.
+
+$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ is closed under induction.
 It can be solved by means of the following relations:\\
-
 \textbf{BASE :} \\
-
-For the base case, one matches the right most element of the motif.
+$$
+\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}=
+\begin{cases}
+	true 	& \text{if $\ptext[j] \in [\lb,\ub ]$}\\
+			& \text{and if ${\pmotif[n_\pmotif]}_\lrcorner$ then $j=n_\ptext$}\\
+			& \text{and if ${\pmotif[n_\pmotif]}^\urcorner$ then $\ptext[j]=\ub=n_\pmotif$}\\
+			& \text{and if  $^\ulcorner{\pmotif[n_\pmotif]}$ then $\ptext[j]=\lb=1$ } \\
+			& \text{and if  $\overline{(\pmotif[n_\pmotif]-1)\pmotif[n_\pmotif] }$ then $\ptext[j]=\lb$ }  \\
+			& \text{and if  $\overline{(\pmotif[n_\pmotif]\pmotif[n_\pmotif]-1)}$ then $\ptext[j]=\ub$}  \\
+
+	false	& \text{otherwise} \\
+\end{cases}
+$$
+
+The base case finds an occurrence for the right most element of the motif.
+If the last element do not have any restriction on position and on value, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ can occur in $\ptext[j]$.
+This condition is checked by assuring that $\ptext[j] \in [\lb,\ub]$.
+
+\textbf{STEP :} \\
+For clarity of reading we consider 3 cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ :
+\begin{itemize}
+	\item If $\ptext[j] \notin [\lb,\ub]$ then :
+	$$
+	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j} = false
+	$$
+	this is straightforward with the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\pmotif[i:]$ with every element in $[\lb,\ub]$.
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is ascent then :
+	$$
+	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}= 
+	\begin{cases}
+		\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}
+			& \text{if $\pmotif[i]$ is not underlined } \\
+			& \text{ and $\pmotif[i]$ is not overlined} \\ 
+		\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}
+			& \text{if $\pmotif[i]$ is not underlined } \\
+			& \text{ and $\overline{(\pmotif[i]-1)\pmotif[i]}$ or $^\ulcorner{\pmotif[i]}$}\\ 	
+			& \text{ and $\ptext[j]=\lb$} \\
+		\PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}	
+			& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
+			& \text{ and $\overline{(\pmotif[i]-1)\pmotif[i]}$ or $^\ulcorner{\pmotif[i]}$}\\ 	
+			& \text{ and $\ptext[j]=\lb$} \\				
+		\PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}	
+			& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
+			& \text{ and $\pmotif[i]$ is not overlined} \\
+		false & \text{otherwise}
+
+	\end{cases}
+	$$	
+	$\pmotif[i]$ can occur in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
+$\pmotif[i:]$ occurs in $\ptext[j:]$, if and only if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$.
+$\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ if and only if there is an occurrence of $\pmotif[i+1:]$ in $\ptext[j+1:]$ starting at element $k$, $j<k$, which correspond to know if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{*}{*}{i+1}{k}$ is true.
+Because $\pmotif[i]$ is ascent,  $\pmotif[i]$ is the minimal element of $\pmotif[i:]$, thus a match of $\pmotif[i+1:]$ can not use value inferior to $\ptext[j]$ so $\ptext[j]+1$ is the new lower bound.
+The upper bound is unchanged.
+So there is a occurrence of  $\pmotif[i:]$ starting at element $j$ in $\ptext[j:]$ if and only if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}$.
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is descent then :
+	$$
+	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
+	\begin{cases}
+			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
+				& \text{if $\pmotif[i]$ is not underlined } \\
+				& \text{ and $\pmotif[i]$ is not overlined} \\ 
+			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
+				& \text{if $\pmotif[i]$ is not underlined } \\
+				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\ 	
+				& \text{ and $\ptext[j]=\ub$} \\
+			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}	
+				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
+				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\ 	
+				& \text{ and $\ptext[j]=\ub$} \\					
+			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}	
+				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
+				& \text{ and $\pmotif[i]$ is not overlined} \\	
+			false & \text{otherwise}		
+	\end{cases}
+	$$	
+	We prove symmetrically as the last case that 
+	$\pmotif[i:]$ occurs in $\ptext[j:]$ starting at element $j$ if and only if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}$.
+
+\end{itemize}
+
+Clearly if $\bigcup_{0<j} \PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{j}$ is true then $\sigma$ occurs in $\pi$. We now discus about the position and value constraints.
+\paragraph{Position Constraint.} There are 3 types of position constraints 
+\begin{itemize}
+	\item If $_\llcorner{\sigma[1]}$ then the left most element of $\sigma$  must occurs in the left most element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on a occurrence of $\pmotif$ in $\ptext$).
+This constraint is assured by demanding that the occurrence starts at the left most element of $\ptext$ : if and only if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
+
+	\item If ${\pmotif[n_\pmotif]}_\lrcorner$ then the right most element $\sigma$ must occurs in the right most element of $\pi$ ($\pmotif[n_\pmotif]$ occurs in $\ptext[n_\ptext]$ on a occurrence of $\pmotif$ in $\ptext$).
+This constraint is assured in the base case.
+
+	\item If $\underline{\pmotif[i]\pmotif[i+1]}$ then the index of the occurrence of $\pmotif[i]$ and $\pmotif[i+1]$ must be consecutive.
+In other word if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i+1]$ must occur in $\ptext[j+1]$.
+We assure this restriction in the induction by demanding that occurrences of $\pmotif[i+1:]$  start at index $j+1$.
+\end{itemize}
+
+\paragraph{Value Constraint.} There are 3 types of position constraints 
+\begin{itemize}
+	\item If $^\ulcorner{\sigma[i]}$ (and thus $\sigma[i]=1$) then the minimal value of $\pmotif$ must occur in the minimal value of $\ptext$. 
+	\begin{itemize}
+		\item If $\sigma[i]$ is ascent then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the minimal element, because ascent elements are increasing).
+Remark that the problem starts with the lower bound as $1$, and inductive problems before the index $i$ are called with descent elements which do not modified the lower bound, so the lower bound for index $i$ is $1$.
+		$\PM{\pbmotif}{\ptext}{1}{*}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{1}{*}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to lower bound which is  $1$.
+
+		\item If $\sigma[i]$ is descent then $i=n_\pmotif$ ($\sigma[i]$ is the right most element). Which is solved in the case case.
+	\end{itemize}
+
+	\item If ${\pmotif[i]}^\urcorner$ (and thus $\sigma[i]=n_\pmotif$) then the maximal value of $\pmotif$ must occur in the maximal value of $\ptext$.
+	\begin{itemize}
+		\item If $\sigma[i]$ is descent then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the maximal element, because descent elements are decreasing).
+Remark that the problem starts with the upper bound as $n_\ptext$, and any inductive problems before the index $i$ are called with ascent elements which do not modified the upper bound, so the upper bound for index $i$ is $n_\ptext$.
+		$\PM{\pbmotif}{\ptext}{*}{n_\pmotif}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{n_\pmotif}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to upper bound which is  $n_\pmotif$.
+
+		\item If $\sigma[i]$ is ascent then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element) which is solved in the base case.
+	\end{itemize}
+
+	\item  If $\overline{\pmotif[i]\pmotif[i']}$, with $\pmotif[i']=\pmotif[i]+1$ then if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i']$ must occur in $\ptext[j]+1$. 
+		\begin{itemize}
+			\item The case $\pmotif[i]$ is descent, $\pmotif[i']$ is ascent and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is ascent, $\pmotif[i']$ is descent and $i'<i$) is not possible.
+			Indeed $\pmotif[i]$ is the maximal element of $\pmotif[i:]$ thus $\pmotif[i] > \pmotif[i']$ which is in contradiction with 
+			$\pmotif[i']=\pmotif[i]+1$.
+
+			\item If $\pmotif[i]$ is ascent, $\pmotif[i']$ is descent and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is descent, $\pmotif[i']$ is ascent and $i'<i$) , then
+			$\pmotif[i]$ is the right most ascent element and $\pmotif[i']$ is the right most element (or $\pmotif[i'] \neq \pmotif[i]+1$).
+Thus inductive problems between $i+1$ and $i'$ do not modified the lower bound.
+If $\sigma[i]$ occurs in $\ptext[j]$ then the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ have for lower bound $\ptext[i]+1$.
+The problem $\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ is a base case and is true if and only if
+			the occurrence of $\sigma[i']$ is equal the lower bound which is equal to $\ptext[i]+1$ so the occurrence of $\pmotif[i]$ and $\pmotif[i']$ are consecutive in value.
+
+			\item If $\pmotif[i]$ is descent and $\pmotif[i']$ is descent then $i'<i$ and there is no descent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i'+1$ and $i$ do not modified the upper bound.
+Remark that if $\pmotif[i']$ occurs in $\ptext[j]$ then
+			the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ have for upper bound $\ptext[j]-1$.
+$\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to upper bound which is equal to $\sigma[i']-1$ so the occurrence of $\pmotif[i]$ and $\pmotif[i']$ are consecutive in value.
+
+			\item If $\pmotif[i]$ is ascent and $\pmotif[i']$ is ascent then $i<i'$ and there is no ascent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i+1$ and $i'$ do not modified the lower bound.
+Remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then
+			the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ have for lower bound $\ptext[j]+1$.
+$\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ is true if and only if the occurrence of $\sigma[i']$ is equal to lower bound which is equal to $\sigma[i']+1$ so the occurrence of $\pmotif[i]$ and $\pmotif[i']$ are consecutive in value.
+		\end{itemize}
+
+\end{itemize}
+
+\end{proof}
+
+%\begin{proof}
+%We consider the following problem :\\
+%Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$.
+%$$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
+%\begin{cases}
+%	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
+%			  & \text{with every element in $]\min,\max[$}\\
+%	false 	& otherwise\\
+%\end{cases}
+%$$
+%$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction.
+%It can be solved by means of the following relations:\\
+%
+%\textbf{BASE :} \\
+%
+%For the base case, one matches the right most element of the motif.
 If the motif has a right bottom corner (if $n_\pmotif \in  \x$) then one must assure that the right most element of the motif is matched to the right most of the text.
@@
 If there is not corner, there is no condition on the match of the right most element.
-
-if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$}\\
-	false 	& otherwise\\
-\end{cases}
-$
-%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
-\\
-
-if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
-\begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$}\\
-			& \text{and } j=n_\ptext\\	
-	false 	& otherwise\\
-\end{cases}
-$
-%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
-\\
-
-if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$ }\\
-			& \text{and $\ptext[j]$ is the maximal element}\\
-	false 	& otherwise\\
-\end{cases}
-$
-%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
-
-if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$}\\
-			& \text{and } j=n_\ptext\\		
-			& \text{and $\ptext[n_\ptext]$ is the maximal element}\\
-	false 	& otherwise\\
-\end{cases}
-$
-%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
-
-if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$}\\	
-			& \text{and $\ptext[j]$ is the minimal element}\\
-	false 	& otherwise\\
-\end{cases}
-$
-%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
-
-if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-\begin{cases}
-	true 	& \text{if $\min<\ptext[j]<\max$}\\
-			& \text{and } j=n_\ptext\\	
-			& \text{and $\ptext[n_\ptext]$ is the minimal element}\\
-	false 	& otherwise\\
-\end{cases}
-$
-%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
-
-\textbf{STEP :} \\
-
-For the induction there are 8 cases to consider, depending on if $\pmotif[i]$ is ascend or descend, if elements $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) and if elements $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$).
+%
+%if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+%\begin{cases}
+%	true 	& \text{if $\min<\ptext[j]<\max$}\\
+%	false 	& otherwise\\
+%\end{cases}
+%$
+%%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
+%\\
+%
+%if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
+%\begin{cases}
+%	true 	& \text{if $\min<\ptext[j]<\max$}\\
+%			& \text{and } j=n_\ptext\\	
+%	false 	& otherwise\\
+%\end{cases}
+%$
+%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
+%\\
+%
+%if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+%\begin{cases}
+%	true 	& \text{if $\min<\ptext[j]<\max$ }\\
+%			& \text{and $\ptext[j]$ is the maximal element}\\
+%	false 	& otherwise\\
+%\end{cases}
+%$
+%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
+%
+%if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+%\begin{cases}
+%	true 	& \text{if $\min<\ptext[j]<\max$}\\
+%			& \text{and } j=n_\ptext\\		
+%			& \text{and $\ptext[n_\ptext]$ is the maximal element}\\
+%	false 	& otherwise\\
+%\end{cases}
+%$
+%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+%
+%if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+%\begin{cases}
+%	true 	& \text{if $\min<\ptext[j]<\max$}\\	
+%			& \text{and $\ptext[j]$ is the minimal element}\\
+%	false 	& otherwise\\
+%\end{cases}
+%$
+%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
+%
+%if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
+%\begin{cases}
+%	true 	& \text{if $\min<\ptext[j]<\max$}\\
+%			& \text{and } j=n_\ptext\\	
+%			& \text{and $\ptext[n_\ptext]$ is the minimal element}\\
+%	false 	& otherwise\\
+%\end{cases}
+%$
+%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
+%
+%
+%\textbf{STEP :} \\
+%
+%For the induction there are 8 cases to consider, depending on if $\pmotif[i]$ is ascend or descend, if elements $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) and if elements $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$).
 First one must assure that $\pmotif[i]$ can be matched to $\ptext[j]$, this is done by checking that $\ptext[j]$ is in the interval $]\min,\max[$.
@@
 The element $\ptext[j]$ gives a new $\min$ if the element is ascent or a new $\max$ if the element is descent.
-If $\pmotif[i]\pmotif[i+1]$ are not underlined nor overlined, then $\pmotif[i+1]$ can be matched to any upcoming element in the text.
+%If $\pmotif[i]\pmotif[i+1]$ are not underlined nor overlined, then $\pmotif[i+1]$ can be matched to any upcoming element in the text.
 If $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) then the match of $\pmotif[i+1]$ must be $\ptext[j+1]$.
 If $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$) then ethe match of  $\pmotif[i+1]$ must be $\ptext[j]+1$.
-
-$
-\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
-\begin{cases}
-\bigcup_{j<k}
-			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
-				& \text{if $\stripe{\pmotif}{i}=\ustep$
-				and $i \notin \x$}\\
-				& \text{and $i \notin \y$ }\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-			&\\
-
-			\bigcup_{j<k}
-			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{k}
-				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
-				& \text{and $i \notin \x$ and $i \notin \y$  }\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-			&\\
-
-			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}
-				& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
-				& \text{and $i \in \x$ and $i \notin \y$}\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-			&\\
-
-			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1}
-				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
-				& \text{and $i \in \x$ and $i \notin \y$ }\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-
-			&\\
-
-			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{\ptext^{-1}[\ptext[j]+1]}
-				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
-				&\text{and $i \notin \x$ and $i \in \y$}\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-				&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
-			&\\
-
-			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{\ptext^{-1}[\ptext[j]-1]}
-				&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
-				&\text{and $i \notin \x$ and $i \in \y$ }\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-				&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
-			&\\
-
-			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}
-				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
-				&\text{and $i \in \x$ and $i \in \y$}\\
-				&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-			&\\
-
-			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1}
-				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
-				&\text{and $i \in \x$ and $i \in \y$}\\
-				&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
-				& \text{and $\min<\ptext[j]<\max$} \\
-			&\\
-
-			False & Otherwise\\
-\end{cases}
-$
-
-There are 6 cases to consider to search for a match.
-Depending on if the motif has a left bottom corner ($0 \in \x$), a left top corner, and if it has a left top corner $0 \notin \y$, if the left most element is minimal or maximal.
+%
+%$
+%\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
+%\begin{cases}
+%\bigcup_{j<k}
+%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
+%				& \text{if $\stripe{\pmotif}{i}=\ustep$
+%				and $i \notin \x$}\\
+%				& \text{and $i \notin \y$ }\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%			&\\
+%
+%			\bigcup_{j<k}
+%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{k}
+%				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
+%				& \text{and $i \notin \x$ and $i \notin \y$  }\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%			&\\
+%
+%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}
+%				& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
+%				& \text{and $i \in \x$ and $i \notin \y$}\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%			&\\
+%
+%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1}
+%				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
+%				& \text{and $i \in \x$ and $i \notin \y$ }\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%
+%			&\\
+%
+%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{\ptext^{-1}[\ptext[j]+1]}
+%				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
+%				&\text{and $i \notin \x$ and $i \in \y$}\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%				&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
+%			&\\
+%
+%
+%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{\ptext^{-1}[\ptext[j]-1]}
+%				&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
+%				&\text{and $i \notin \x$ and $i \in \y$ }\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%				&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
+%			&\\
+%
+%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}
+%				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
+%				&\text{and $i \in \x$ and $i \in \y$}\\
+%				&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%			&\\
+%
+%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1}
+%				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
+%				&\text{and $i \in \x$ and $i \in \y$}\\
+%				&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
+%				& \text{and $\min<\ptext[j]<\max$} \\
+%			&\\
+%
+%
+%			False & Otherwise\\
+%\end{cases}
+%$
+%		
+%There are 6 cases to consider to search for a match.
+%Depending on if the motif has a left bottom corner ($0 \in \x$), a left top corner, and if it has a left top corner $0 \notin \y$, if the left most element is minimal or maximal.
 If the motif has a left bottom corner, then one must assure that the left most element of the motif is matched to the left most element of the text.
 If the motif has a left top corner and the left most element of the motif is minimal (maximal) then one must assure that the left most element of the motif is matched with the minimal (maximal) element of the text :
-\begin{itemize}
-	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text : $ \PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true.
-
-	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index : 	$\bigcup_{1<k\leq n_\ptext}\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{k}$ is true.
-
-	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$ : $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
-
-	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there exists a match stating at the minimal element of the text : if $j_{\min}$ is the index of the minimal element in $\ptext$ then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\min}}$ is true.
-
-	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is maximal then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$: $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
-
-	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is maximal there exists a match if and only if there exists a match stating at the maximal element of the text : if $j_{\max}$ is the index of the maximal in $\ptext$ element then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\max}}$ is true.
-
-\end{itemize}
-\end{proof}
+%\begin{itemize}
+%	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text : $ \PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true.
+%	
+%	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index : 	$\bigcup_{1<k\leq n_\ptext}\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{k}$ is true.
+%	
+%	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$ : $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
+%	
+%	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there exists a match stating at the minimal element of the text : if $j_{\min}$ is the index of the minimal element in $\ptext$ then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\min}}$ is true.
+%			
+%	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is maximal then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$: $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
+%	
+%	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is maximal there exists a match if and only if there exists a match stating at the maximal element of the text : if $j_{\max}$ is the index of the maximal in $\ptext$ element then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\max}}$ is true.
+%
+%\end{itemize}
+%\end{proof}
 

### 2015-04-13 article.tex
typos

@@
 	We focus in this paper on pattern matching issues for
-	$(213,231)$-avoiding permutations.
+	$(213,231)$-avoiding permutations
+    (\emph{i.e.}, those permutations that avoid both $213$ and $231$).
 	The number of $n$-permutations that avoid both
@@
 	permutation are $(213,231)$-avoiding,
-	where Section~\ref{section:sigma only avoid 231 and 213} focuses on the case
+	whereas Section~\ref{section:sigma only avoid 231 and 213} focuses on the case
 	where the pattern only is $(213,231)$-avoiding.
@@
 
-\section{Definition}
+\section{Definitions}
 \label{section:Definitions}
@@
 $\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose letters are distinct
-and uasually consist of the integers $12\,\ldots\,n$.
-We let
+and uasually consist of the integers $12\,\ldots\,n$, and we let
 $\pi[i]$ stands for $\pi_i$.
@@
 ).
-Each subsequence $(91674$,
+Each subsequence $91674$,
 $91675$,
-$91672$) is called a
+$91672$ in $\pi$ is called a
 \emph{copy},
-\emph{instance}, or
-\emph{occurrence} of $\sigma$.
-Since the permutation $\pi = 391867452$  contains no increasing subsequence of length four, $\pi$ avoids $1234$.
+(or \emph{instance} or \emph{occurrence}) of $\sigma$.
+Since the permutation $\pi = 391867452$  contains no increasing subsequence of
+length four, $\pi$ avoids $1234$.
 
@@
 For the sake of convenience
-(and as it is customary), we omit $P$'s braces thus having
-e.g. $\AV_3(132,4312)$ instead of
-$\AV_3(\{132,4312\})$.
-A basic example is if
-$\pi = \pi_1\pi_2\,\ldots\,\pi_n \in \AV_n(321)$, i.e.,
-has no decreasing subsequence of length $3$, then its reverse,
-$\pi' = \pi_n\pi_{n-1}\,\ldots\,\pi_1$ avoids $123$, i.e.,
-has no increasing subsequence of length $3$.
+(and as it is customary~\cite{Kitaev:book:2011}), we omit $P$'s braces thus having
+e.g. $\AV_3(213,231)$ instead of
+$\AV_3(\{213,231\})$.
+If $\pi \in \AV_n(P)$, we also say that $\pi$ is
+\emph{$P$-avoiding}.
+% A basic example is if
+% $\pi = \pi_1\pi_2\,\ldots\,\pi_n \in \AV_n(321)$, i.e.,
+% has no decreasing subsequence of length $3$, then its reverse,
+% $\pi' = \pi_n\pi_{n-1}\,\ldots\,\pi_1$ avoids $123$, i.e.,
+% has no increasing subsequence of length $3$.
 
@@
 $\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$,
-$\pi[i:]$ start either with the maximal element
-or the minimal element of $\pi[i:]$.
+$\pi[i:]$ starts either with the maximal element
+or with the minimal element of $\pi[i:]$.
 \end{corollary}
@@
 We need to consider a specific decomposition $\factora$ of $\sigma$ into factors.
-For $\sigma \in S_k$, the factorization
-$\sigma = \factor{\pmotif}{p} \factor{\pmotif}{p-1} \ldots \factor{\pmotif}{1}$ is defined as follows:
+For $\sigma \in S_k$, the \emph{factorization}
+$\sigma = \factor{\pmotif}{p} \factor{\pmotif}{p-1} \ldots \factor{\pmotif}{1}$
+is defined as follows:
 (i) $\sigma[k]$ is the last letter of $\factor{\pmotif}{1}$,
@@
 $\first{\pmotif}{j}$ stand for the leftmost letter of $\factor{\pmotif}{j}$,
-and $\firsti{\pmotif}{j}$ stand for the index of the leftmost letter of $\factor{\pmotif}{j}$.
+and $\firsti{\pmotif}{j}$ stand for the index in $\sigma$
+of the leftmost letter of $\factor{\pmotif}{j}$.
 For example,
@@
 \label{lemma:whereIsMax}
-Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, if
-$\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ ($\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$) then the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
+Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$,
+if $\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$
+(resp. $\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$)
+then the maximal (resp. minimal) element of
+$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$
+is $\first{\sigma}{i-1}$.
 \end{lemma}
@@
 \begin{proof}
-Take the right most element of $\factor{\sigma}{i}$, this element is an ascent (descent),
-so it is inferior (superior) to the next element which is $\first{\sigma}{i-1}$.
+Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
+Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
+Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
+$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
+According to Lemma\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, and hence
+$\first{\sigma}{i-1}$ is the maximal  element of
+$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
+
+A similar argument shows that the lemma holds true if the rightmost element
+of $\factor{\sigma}{i}$ is a descent.
+\qed
+% so it is inferior (superior) to the next element which is $\first{\sigma}{i-1}$.
 Because $\factor{\sigma}{i}$ is an increasing (decreasing) subsequence, every element of $\factor{\sigma}{i}$ is inferior (superior) to $\first{\sigma}{i-1}$.
-By lemma \ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ thus $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
-
+% By lemma \ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ thus $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
 \end{proof}
 
-To ease the next lemma and its proof we define the set $\SET{\pmotif}{\ptext}{i}{j}$ such that if $s \in S$, then $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element matching $\first{\pmotif}{i}$ is $\ptext[j]$.
+For easy readability, we now define the set
+$\SET{\pmotif}{\ptext}{i}{j}$ as follows:
+if $s \in \SET{\pmotif}{\ptext}{i}{j}$ then
+$s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$
+and the element matching $\first{\pmotif}{i}$ is $\ptext[j]$.
 
@@
 So every element of $t'$ is also superior (inferior) to every element of $s$. Thus the subsequence $t's$ is an occurrence of $\pmotif[\first{\pmotif}{i+1}:]$ in $\ptext$.
+\qed
 \end{proof}

### 2015-04-19 article.tex
typo

--- 2015-04-09 article.tex
@@
 	$O(kn^2)$ time algorithm. We extend our research to $(213,231)$-avoiding
-	bivincular pattern and present a $O(kn^3)$ time algorithm.
+	bivincular pattern and present a $O(kn^5)$ time algorithm.
 \end{abstract}
@@
 
-This section is devoted to presenting a fast algorithm for deciding
-$\sigma \leq \pi$
+This section is devoted to presenting a fast algorithm for deciding if
+$\sigma \preceq \pi$
 in case both $\pi$ and $\sigma$ are $(213,231)$-avoiding.
@@
 $231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+$\qed$
 \end{proof}
@@
 is $2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
-The above lemma also gains in interest in the form of the following corollary.
+The above lemma also gains in interest in the form of the following corollaries.
 
@@
 $\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$,
-$\pi[i:]$ start either with the maximal element
-or the minimal element of $\pi[i:]$.
+$\pi[i]$ is the minimal or the maximal element of $\pi[i:]$.
+\end{corollary}
+
+\begin{corollary}
+\label{corollary:max_is_ascent}
+For $\pi \in \AV_n(213,231)$ if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimal of $\pi[i:]$
+and if if $\pi[i]$ is a descent element then $\pi[i]$ is the maximal of $\pi[i:]$
 \end{corollary}
@@
 \label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
+If $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
 and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
@@
   Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
-\qed
+$\qed$
 \end{proof}
@@
 so it is an online algorithm.
-\qed
+$\qed$
 % To solve the permutation pattern for a permutation in $\AV_n(213,231)$,
@@
 (i) $\sigma[k]$ is the last letter of $\factor{\pmotif}{1}$,
-(ii) for every $1 \leq i < k$,
+(ii)for every $1 \leq i < k$,
 if $s_\sigma[i] = s_\sigma[i+1]$ then
@@
 Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, if
-$\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ ($\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$) then the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
+$\firsti{\sigma}{i}$ is an ascent element (respectively  if $\firsti{\sigma}{i}$ is a descent element) then the maximal (resp.
+minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
 \end{lemma}
@@
 \begin{proof}
-Take the right most element of $\factor{\sigma}{i}$, this element is an ascent (descent),
-so it is inferior (superior) to the next element which is $\first{\sigma}{i-1}$.
-Because $\factor{\sigma}{i}$ is an increasing (decreasing) subsequence, every element of $\factor{\sigma}{i}$ is inferior (superior) to $\first{\sigma}{i-1}$.
-By lemma \ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ thus $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
-
+Take the right most element of $\factor{\sigma}{i}$, if this element is an ascent element,
+then it is smaller than the next element which is $\first{\sigma}{i-1}$.
+Because $\factor{\sigma}{i}$ is an increasing subsequence, every element of $\factor{\sigma}{i}$ is inferior to $\first{\sigma}{i-1}$.
+By lemma \ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ thus $\first{\sigma}{i-1}$ is the maximal element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
+We use a similar argument if the rightmost element is a decent element.
+$\qed$
 \end{proof}
@@
 \begin{lemma}
-Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (descent) factor.
-Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (maximal), for all subsequence 
+Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (respectively descent) factor.
+If $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (resp. maximal), for all subsequence 
 $s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequence $t$ of $\ptext$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$.
@@
 \begin{proof}
-Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (descent) factor.
-Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (maximal).
-Let's $s' \in \SET{\pmotif}{\ptext}{i}{j}$ and $t$ subsequence of $\ptext$, such that $t=t's'$ and $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ in $\pi$. 
-Remark that every element of $t'$ is superior (inferior) to every element of $s'$.
-Plus, remark that the element matching $\first{\pmotif}{i-1}$ in $s$ is minimal (maximal) and it is the maximal (minimal) element of the subsequence (\ref{lemma:whereIsMax}), thus
-it is inferior (superior) to the element matching $\first{\pmotif}{i-1}$ in $s'$.
-So every element of $t'$ is also superior (inferior) to every element of $s$. Thus the subsequence $t's$ is an occurrence of $\pmotif[\first{\pmotif}{i+1}:]$ in $\ptext$.
+By definition $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$.
+To prove that $ts$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ we prove that every element of t is larger than every element of $s$.
+If $ts'$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ so every element of $t$ is larger than every element of $s'$.
+Moreover the maximal element of $s$ is smaller than  the maximal element of $s'$ so every element of $s$ is smaller than every element of $s'$ thus every element of $s$ is smaller than every element of $t$.
+We use a similar argument if $\factor{\pmotif}{i}$ a descent factor.
+$\qed$
 \end{proof}
@@
 \begin{corollary}
-Let's $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (maximal).
+Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (respectively descent) factor.
+If $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (resp.
+maximal).
 There is a match of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ matched to $\ptext[j]$ if and only if there exists $t$ such that $ts$ is a match of $\pmotif$ in $\ptext$.
@@
 	\text{The maximal value of a subsequence} 
-		& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ } \\
-	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \\	
+		& \text{If $\first{\sigma}{i}$ is  } \\
+	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & 
+		\text{ an ascent element } \\	
 	\text{ and that minimize the maximal value} & \\
@@
 	\text{The minimal value of a subsequence} 
-		& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$ } \\
-	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \\	
+		& \text{If $\first{\sigma}{i}$ is  } \\
+	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \text{ a descent element } \\	
 	\text{ and that maximize the minimal value} & \\
@@
 		\min_{j<j'}\{\infty\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\ustep$ }  \\
-		\text{ $|\factor{\pmotif}{1}| \leq LIS(j,j',\ptext[j'])  $}\}& \\
+			& \text{If $\first{\sigma}{i}$ is}  \\
+		\text{ $|\factor{\pmotif}{1}| \leq LIS(j,j',\ptext[j'])  $}\}&\text{ an ascent element } \\
 		&\\
 		\max_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\stripe{\sigma}{\firsti{\sigma}{i}}=\dstep$ } \\
-		\text{ $|\factor{\pmotif}{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\
+			& \text{If $\first{\sigma}{i}$ is}  \\
+		\text{ $|\factor{\pmotif}{1}| \leq LDS(j,j',\ptext[j']) $}\}&\text{ a descent element }\\
 \end{cases}
@@
 	\min \{\infty\} \cup  \AF{\pmotif}{\ptext}{i}{j} &
-	\text{if $\stripe{\pmotif}{\first{\pmotif}{i}}=\ustep$}\\
+	\text{If $\first{\sigma}{i}$ is an ascent element}\\
 	\max \{0\} \cup  \DF{\pmotif}{\ptext}{i}{j} &
-	\text{if $\stripe{\pmotif}{\first{\pmotif}{i}}=\dstep$}\\
+	\text{If $\first{\sigma}{i}$ is  a descent element}\\
 \end{cases}
@@
 
-With $\AF{\pmotif}{\ptext}{i}{j}$ ($\DF{\pmotif}{\ptext}{i}{j}$) the set of element such that if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ ($\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$) then there exists a match of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$.
-Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, to decide if $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$, one needs to find an match $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is a match of $\pmotif[\firsti{\pmotif}{i}:]$.
+With $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ the set of element such that if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ or if $\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$ then there exists a match of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$.
+Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, to decide if $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$, one needs to find an occurrence $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is a match of $\pmotif[\firsti{\pmotif}{i}:]$.
 Formally we define $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ such as:\\
 
-$\AF{\pmotif}{\ptext}{i}{j}=\{j'|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq 0$}$ \\
+$\AF{\pmotif}{\ptext}{i}{j}=\{\ptext[j']|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq 0$}$ \\
 \indent \indent \indent and  $|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$ \\
 
-$\DF{\pmotif}{\ptext}{i}{j}=\{j'|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq \infty$}$ \\
+$\DF{\pmotif}{\ptext}{i}{j}=\{\ptext[j']|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq \infty$}$ \\
 \indent \indent \indent and  $|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\first{\pmotif}{i-1}) \}$ \\
 
-With $LIS_{\ptext}(i,j,k)$ ($LDS_{\ptext}(i,j,k)$) is the longest increasing (decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
+With $LIS_{\ptext}(i,j,k)$ (respectively $LDS_{\ptext}(i,j,k)$) is the longest increasing (resp. decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
 with every element of this sequence
-inferior (superior) to $k$.
-$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(|\ptext|^2*\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
+smaller (resp. bigger) than $k$.
+$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(|\ptext|^2\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
 
@@
 one is looking for a match for the first factor.
-If the factor is an ascent (descent),
-one has to find an increasing (decreasing) subsequence
+If the factor is an ascent (respectively descent) factor, then
+one has to find an increasing (resp. decreasing) subsequence
 in the text of same size or longest that
-the size of the factor,
-and to find the safest solution
-one must assure that the last element
-of the sequence is minimal (maximal).\\
+the size of the first factor.
+To find the "safest" solution
+one must assure that the right most element
+of the sequence is minimal (resp. maximal).\\
 For the induction, it follows the same idea
 except that one must assure that
-every element of the subsequence is superior (inferior)
-to the maximum (minimal) element of the rest of the match which is given by $L$ of
+every element of the subsequence is larger (resp. smaller)
+than the maximum (resp. minimal) element of the rest of the match which is given by the inductive problem of
 the previous factor.\\
@@
 and the induction on $O(kn^2)$ time and space.
-\qed
+$\qed$
 \end{proof}
@@
 
-We introduce property of bivincular permutation if the permutation is $(213,231)$-avoiding.
+We introduce property of bivincular permutation for a motif avoiding both $213$ and $231$.
 
@@
 \label{lemma:ascentDescentAscent}
-If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and if $\sigma[i]$ is ascent (decent) and $\sigma[i]+1$ is ascent (decent) then $i<j$ ($j>i$) and for every $k$, $i<k<j$ ($j>k>i$), $\pi[k]$ is descent (ascent).
+If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and if $\sigma[i]$ is an ascent (respectively decent) element and $\sigma[i]+1$ is an ascent (resp.
+decent) element then $i<j$ ($j>i$) and for every $k$, $i<k<j$ ($j>k>i$), $\pi[k]$ is a descent (resp.
+ascent) element.
 \end{lemma}
@@
 \begin{proof}
-Suppose that there exists $k$, $i<k<j$ ($i>k>j$),
-such that $\pmotif[k]$ is ascent (descent).
-Ascent (descent)  elements are increasing (decreasing) so $\sigma[i]<\sigma[k]<\sigma[j]$ ($\sigma[i]<\sigma[k]<\sigma[j]$) which is in contradiction that with $\sigma[j]=\sigma[i]+1$.
+Suppose that there exists $k$, $i<k<j$,
+such that $\pmotif[k]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[k]<\sigma[j]$ which is in contradiction that with $\sigma[j]=\sigma[i]+1$.
+We use a similar argument if $\sigma[i]$ is a descent element
+$\qed$
 \end{proof}
@@
 		\label{Proposition:bivincular pattern}
-			Let $\sigma$ be a $(213,231)$-avoiding bivincular pattern of length $k$
+			Let $\sigma$ be a bivincular motif avoiding $213$ and $231$ of length $k$
 			and $\pi \in S_n$.
-			One can decide in $O(kn^4)$ time
-			and $O(kn^4)$ space if $\pi$ contains $\sigma$.
+			One can decide in $O(kn^5)$ time
+			and $O(kn^5)$ space if $\sigma$ occurs in $\pi$.
 	\end{proposition}
@@
 	true 	& \text{If $\pbmotif[i:]$ occurs in $\ptext[j:]$}\\
-			& \text{with every element in $[\lb,\ub]$}\\
+			& \text{with every element is in $[\lb,\ub]$}\\
 			& \text{and element $\pmotif[i]$ occurs in $\ptext[j]$ }\\
@@
 The base case finds an occurrence for the right most element of the motif.
-If the last element do not have any restriction on position and on value, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ can occur in $\ptext[j]$.
+If the last element does not have any restriction on position and on value, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ can occur in $\ptext[j]$.
 This condition is checked by assuring that $\ptext[j] \in [\lb,\ub]$.
@@
 	$$
-	this is straightforward with the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\pmotif[i:]$ with every element in $[\lb,\ub]$.
-
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is ascent then :
+	this is straightforward with the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is in $[\lb,\ub]$.
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is an ascent element then :
 	$$
@@
 $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ if and only if there is an occurrence of $\pmotif[i+1:]$ in $\ptext[j+1:]$ starting at element $k$, $j<k$, which correspond to know if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{*}{*}{i+1}{k}$ is true.
-Because $\pmotif[i]$ is ascent,  $\pmotif[i]$ is the minimal element of $\pmotif[i:]$, thus a match of $\pmotif[i+1:]$ can not use value inferior to $\ptext[j]$ so $\ptext[j]+1$ is the new lower bound.
+Because $\pmotif[i]$ is an ascent element,  $\pmotif[i]$ is the minimal element of $\pmotif[i:]$, thus a match of $\pmotif[i+1:]$ can not use value smaller than $\ptext[j]$, so $\ptext[j]+1$ is a (new) lower bound.
 The upper bound is unchanged.
@@
 
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is descent then :
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then :
 	$$
@@
 	We prove symmetrically as the last case that 
-	$\pmotif[i:]$ occurs in $\ptext[j:]$ starting at element $j$ if and only if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}$.
+	$\pmotif[i:]$ occurs in $\ptext[j:]$
+	with $\sigma[i]$ occurs in $\pi[j]$.
+	 starting at element $j$ if and only if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}$.
 
@@
 
-Clearly if $\bigcup_{0<j} \PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{j}$ is true then $\sigma$ occurs in $\pi$. We now discus about the position and value constraints.
+Clearly if $\bigcup_{0<j} \PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{j}$ is true then $\sigma$ occurs in $\pi$. We now discuss about the position and value constraints.
 \paragraph{Position Constraint.} There are 3 types of position constraints 
 \begin{itemize}
-	\item If $_\llcorner{\sigma[1]}$ then the left most element of $\sigma$  must occurs in the left most element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on a occurrence of $\pmotif$ in $\ptext$).
-This constraint is assured by demanding that the occurrence starts at the left most element of $\ptext$ : if and only if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
+	\item If $_\llcorner{\sigma[1]}$ then the left most element of $\sigma$  must occur in the left most element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on a occurrence of $\pmotif$ in $\ptext$).
+This constraint is assured by demanding that the occurrence starts at the left most element of $\ptext$ : if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
 
@@
 	\begin{itemize}
-		\item If $\sigma[i]$ is ascent then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the minimal element, because ascent elements are increasing).
-Remark that the problem starts with the lower bound as $1$, and inductive problems before the index $i$ are called with descent elements which do not modified the lower bound, so the lower bound for index $i$ is $1$.
+		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the minimal element, because ascent elements are increasing).
+Remark that the problem starts with the lower bound as $1$, and inductive problems before the index $i$ are called with descent elements which do not modified the lower bound, so for every problem with index $i$ has for lower bound $1$.
 		$\PM{\pbmotif}{\ptext}{1}{*}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{1}{*}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to lower bound which is  $1$.
 
-		\item If $\sigma[i]$ is descent then $i=n_\pmotif$ ($\sigma[i]$ is the right most element). Which is solved in the case case.
+		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the right most element). Which is solved in the case case.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item If $\sigma[i]$ is descent then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the maximal element, because descent elements are decreasing).
-Remark that the problem starts with the upper bound as $n_\ptext$, and any inductive problems before the index $i$ are called with ascent elements which do not modified the upper bound, so the upper bound for index $i$ is $n_\ptext$.
+		\item If $\sigma[i]$ is a descent element then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the maximal element, because descent elements are decreasing).
+Remark that the problem starts with the upper bound as $n_\ptext$, and any inductive problems before the index $i$ are called with ascent elements which do not modified the upper bound, every problem with index $i$ has for upper bound $n_\ptext$.
 		$\PM{\pbmotif}{\ptext}{*}{n_\pmotif}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{n_\pmotif}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to upper bound which is  $n_\pmotif$.
 
-		\item If $\sigma[i]$ is ascent then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element) which is solved in the base case.
+		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element) which is solved in the base case.
 	\end{itemize}
@@
 		\begin{itemize}
-			\item The case $\pmotif[i]$ is descent, $\pmotif[i']$ is ascent and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is ascent, $\pmotif[i']$ is descent and $i'<i$) is not possible.
+			\item The case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i'<i$) is not possible.
 			Indeed $\pmotif[i]$ is the maximal element of $\pmotif[i:]$ thus $\pmotif[i] > \pmotif[i']$ which is in contradiction with 
@@
 
-			\item If $\pmotif[i]$ is ascent, $\pmotif[i']$ is descent and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is descent, $\pmotif[i']$ is ascent and $i'<i$) , then
+			\item If $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i'<i$) , then
 			$\pmotif[i]$ is the right most ascent element and $\pmotif[i']$ is the right most element (or $\pmotif[i'] \neq \pmotif[i]+1$).
@@
 
-			\item If $\pmotif[i]$ is descent and $\pmotif[i']$ is descent then $i'<i$ and there is no descent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i'+1$ and $i$ do not modified the upper bound.
+			\item If $\pmotif[i]$ is a descent element and $\pmotif[i']$ is a descent element then $i'<i$ and there is no descent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i'+1$ and $i$ do not modified the upper bound.
 Remark that if $\pmotif[i']$ occurs in $\ptext[j]$ then
@@
 
-			\item If $\pmotif[i]$ is ascent and $\pmotif[i']$ is ascent then $i<i'$ and there is no ascent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i+1$ and $i'$ do not modified the lower bound.
+			\item If $\pmotif[i]$ is an ascent element and $\pmotif[i']$ is an ascent element then $i<i'$ and there is no  ascent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i+1$ and $i'$ do not modified the lower bound.
 Remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then
@@
 \end{itemize}
-
+$\qed$
 \end{proof}
@@
 
-	In this section we present an algorithm to solve the problem
-	of the longest subsequence avoiding (231,213).
-	To do so, we need the set of element
-	that are matched to an ascent and the
-	set of element that are matched to a descent.
-	For a permutation $\pi$ of size $n$, we define
+	This section and the next one are devoted to the longest subsequence avoiding (231,213).
+	The general problem asks to find the longest subsequence that occur in a set of permutations. We add the constraint that this subsequence avoid $213$ and $231$.
+	This section focuses on the case where the set is of size one.
+	To do so, we need the set of descent elements and the set of ascent elements.
 	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
@@
 	\begin{proof}
-	Let's $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
-	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
+	Let $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
+	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
 	Thus $|s_m|>|P(\pi)|$, clearly the sequence $s_m \cup M(\pi)$
-	is avoiding (213,231) and is longer than $s$ witch is not possible.
+	is avoiding (213,231) and is longer than $s$ which is not possible.
 	The same idea goes for the demonstration that $M(\pi)$ is the longest decreasing subsequence.
+	$\qed$
 	\end{proof}
@@
 	\begin{proof}
-	The proposition \ref{proposition:longestIncreasingSubsequence} lead to algorithm
-	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
-	Computing the longest increasing and decreasing can be done in $O(|\ptext|*\log(\log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
+	The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
+	where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
+	Computing the longest increasing subsequence and the  lonfest decreasing subsequence can be done in $O(|\ptext|\log(\log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
+	$\qed$
 	\end{proof}
 
-\section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutation}
+\section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutations}
 \label{section:LCS common 2 permutations}
 
-In this section we present an algorithm to find
-the longest common subsequence avoiding (231,213)
-between two permutations.\\
+This section is devoted to the longest subsequence avoiding (231,213) for two permutations : Given two (random) permutations, find a permutation $\pi$ such that $\pi$ occurs in both permutation and $\pi$ avoids $231$ and $213$.
 
 \begin{proposition}
-Given two permutation $\pi_1$ and $\pi_2$,
+Given two permutations $\pi_1$ and $\pi_2$,
 the longest common subsequence
@@
 that compute the longest stripe common to $\pi_1$ and $\pi_2$.
-Given two permutation $\pi_1$ and $\pi_2$.\\
-
-$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}$
-= max$\{$ $|s|$ $|$
-s is a pattern occurring
-in  $\pi_1[i_1:]$
-by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
-and s is occurring
-in  $\pi_2[i_2:]$
-by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$
-$\}$\\
+Given two permutations $\pi_1$ and $\pi_2$.\\
+
+$$
+\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
+$$
+\begin{center}
+= $\max$ \{$|s|$ $|$ $s$ occurs in $\pi_1[i_1:]$ with every element is in $[\lb_1,\ub_1]$ and $s$ occurs in $\pi_2[i_2:]$ with every element is in $[\lb_2,\ub_2]$ \}
+\end{center}
 
@@
 $
-\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} =
+\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{|\pi_1|}{|\pi_2|} =
 \begin{cases}
-	1 & \text{if $\min_1=\pi_1[j]=\max_1$
+	1 & \text{if $\lb_1 \leq \pi_1[j] \leq \ub_1$
 	}\\
-	& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
+	& \text{ and $\lb_2 \leq \pi_2[j] \leq \ub_2$}\\
 	0 & otherwise\\
@@
 $
-\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=max
+\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=max
 \begin{cases}
-	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
+	\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2+1} \\
 	\\
-	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
+	\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1+1}{i_2} \\
 	\\
-	\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
+	\match{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
 \end{cases}
@@
 $
-\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=
+\match{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=
 \begin{cases}
-1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1}
-	& \text{$\pi_1[i_1]<\min_1$ } \\
-	& \text{and $\pi_2[i_2]<\min_2$} \\
+1+\LCS{\pi_1}{\pi_1[i_1]+1}{\ub_1}{\pi_2}{\pi_2[i_2]+1}{\ub_2}{i_1}{i_2+1}
+	& \text{$\pi_1[i_1]<\lb_1$ } \\
+	& \text{and $\pi_2[i_2]<\lb_2$} \\
 
@@
 
-1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
-	& \text{$\pi_1[i_1]>\max_1$ } \\
-	&\text{and $\pi_2[i_2]>\max_2$}\\
+1+\LCS{\pi_1}{\lb_1}{\pi_1[i_1]-1}{\pi_2}{\lb_2}{\pi_2[i_2]-1}{i_1+1}{i_2}
+	& \text{$\pi_1[i_1]>\ub_1$ } \\
+	&\text{and $\pi_2[i_2]>\ub_2$}\\
 
@@
 For every pair $i,j$ we either ignore the element of $\pi_1$,
-either ignore the element of $\pi_2$,
-either we match as the same step (if possible).
-Those relation lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.
+ot we ignore the element of $\pi_2$,
+or we match as the same step (if possible).
+Those relations lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.
+$\qed$
 \end{proof}

### 2015-04-19 article.tex

@@
 \begin{corollary}
-\label{corollary:max_is_ascent}
+\label{corollary:max is ascent}
 For $\pi \in \AV_n(213,231)$ if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimal of $\pi[i:]$
@@
 \begin{proof}
-Take the right most element of $\factor{\sigma}{i}$, if this element is an ascent element,
-then it is smaller than the next element which is $\first{\sigma}{i-1}$.
-Because $\factor{\sigma}{i}$ is an increasing subsequence, every element of $\factor{\sigma}{i}$ is inferior to $\first{\sigma}{i-1}$.
-By lemma \ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ thus $\first{\sigma}{i-1}$ is the maximal element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
-We use a similar argument if the rightmost element is a decent element.
-$\qed$
+Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
+Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
+Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
+$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
+According to Lemma\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, and hence
+$\first{\sigma}{i-1}$ is the maximal  element of
+$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
+
+A similar argument shows that the lemma holds true if the rightmost element
+of $\factor{\sigma}{i}$ is a descent.
+\qed
 \end{proof}
 
-To ease the next lemma and its proof we define the set $\SET{\pmotif}{\ptext}{i}{j}$ such that if $s \in S$, then $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element matching $\first{\pmotif}{i}$ is $\ptext[j]$.
+For easy readability, we now define the set
+$\SET{\pmotif}{\ptext}{i}{j}$ as follows:
+if $s \in \SET{\pmotif}{\ptext}{i}{j}$ then
+$s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$
+and the element matching $\first{\pmotif}{i}$ is $\ptext[j]$.
 
@@
 \begin{cases}
+
 	\text{The maximal value of a subsequence} 
@@
 	$$
+
 	this is straightforward with the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is in $[\lb,\ub]$.
@@
 	$$
+
 	$\pmotif[i]$ can occur in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
@@
 	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then :
+
 	$$
@@
 	\begin{itemize}
+
 		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the minimal element, because ascent elements are increasing).
@@
 		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the right most element). Which is solved in the case case.
+
 	\end{itemize}
@@
 	\begin{itemize}
+
 		\item If $\sigma[i]$ is a descent element then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the maximal element, because descent elements are decreasing).
@@
 		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element) which is solved in the base case.
+
 	\end{itemize}
@@
 		\begin{itemize}
+
 			\item The case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i'<i$) is not possible.
@@
 Remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then
+
 			the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ have for lower bound $\ptext[j]+1$.

### 2015-06-11 article.tex
corrections section 1, section 2 et section 3

@@
 	We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid
-	$213$ and $231$.
+	the two size-$3$ permutations $213$ and $231$.
 	For the special where only $\sigma$ avoids $213$ and $231$, we present a
-	$O(kn^2)$ time algorithm. We extend our research to $(213,231)$-avoiding
-	bivincular pattern and present a $O(kn^5)$ time algorithm.
+	$O(kn^2)$ time algorithm. 
+	Finally We extend our research to bivincular pattern that avoid $213$ and $231$
+	 and present a $O(kn^5)$ time algorithm.
 \end{abstract}
@@
 	During the last decade, the study of the pattern containment on permutations has
-	become a very active area of research and
+	become a very active area of research \cite{Kitaev:book:2011} and
 	a whole annual conference (\textsc{Permutation Patterns}) is now devoted
@@
 	$\sigma \preceq \pi$ (the problem is ascribed to Wilf in \cite{Bose:Buss:Lubiw:1998}).
-	The permutation containment problem is \NPhard~\cite{Bose:Buss:Lubiw:1998}.
+	The permutation containment problem is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
 	It is, however, polynomial-time solvable by brute-force enumeration
@@
 	They showed that
-	the permutation containment problem is fixed-parameter tractable for
+	the permutation containment problem is fixed-parameter tractable (FPT) for
 	parameter $|\sigma|$.
@@
 	\emph{generalized patterns},
-	resemble (classical) patterns, with the constraint that some of the letters in
+	resemble (classical) patterns with the additional constraint that some of the letters in
 	an occurrence must be consecutive.
@@
 	$\pi$ is $W[1]$-complete for
-	parameter $k$.
+	parameter $k$;
+	for an up to date survey of the $W[1]$ class and related material, see
+	\cite{Downey:Fellows:2013}.
 	\emph{Bivincular patterns} generalize classical patterns even further
@@
 $1 \leq i < n$ with $\pi_i > \pi_{i+1}$,
-so every $i$ with $1 \leq i < n$ either is an ascent or is a descent of
+so every $1 \leq i < n$  is either an ascent or is a descent of
 $\pi$.
-Let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
+To clarify the exposition,
+we let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
 The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
@@
 \end{itemize}
-
 For example,
@@
 (in which case there is one occurrence of the pattern).
+The best general reference is \cite{Kitaev:book:2011}.
 
@@
 $231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
-$\qed$
+\qed
 \end{proof}
@@
 is $2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
-The above lemma also gains in interest in the form of the following corollaries.
+The above structural lemma gains in interest in the form of the following corollaries.
 
@@
 \label{corollary:minmaxelement}
+Let $\pi \in S_n$.
+Then
 $\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$,
@@
 \label{corollary:max is ascent}
-For $\pi \in \AV_n(213,231)$ if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimal of $\pi[i:]$
-and if if $\pi[i]$ is a descent element then $\pi[i]$ is the maximal of $\pi[i:]$
+Let $\pi \in \in \AV_n(213,231)$ and $1 \leq i < n$.
+Then,
+(1) 
+if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimum element 
+of $\pi[i:]$
+and 
+(2)
+if if $\pi[i]$ is a descent element then $\pi[i]$ is the maximum element 
+of $\pi[i:]$
 \end{corollary}
@@
 \label{lemma:MatchStripeToPermutation}
-If $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
+Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
 and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
@@
   Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
-$\qed$
+  \qed
 \end{proof}
@@
 A straightforward greedy approach solves this issue in linear-time.
-Furthermore, in the light of Corollary~\ref{corollary:minmaxelement},
-the effective construction of the two stripes is not required,
-so it is an online algorithm.
-$\qed$
+\qed
 % To solve the permutation pattern for a permutation in $\AV_n(213,231)$,
@@
 \end{proof}
+
+Observe that, according to Corollary~\ref{corollary:minmaxelement},
+the effective construction of the two stripes is not required for the above proposition,
+and hence we have an online algorithm.
 

### 2015-06-11 article.tex
typos

@@
 (1) 
-if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimum element 
+if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimal element 
 of $\pi[i:]$
@@
 (2)
-if if $\pi[i]$ is a descent element then $\pi[i]$ is the maximum element 
+if if $\pi[i]$ is a descent element then $\pi[i]$ is the maximal element 
 of $\pi[i:]$
@@
   Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
-  then $\sigma[1]$ is the minimum (resp. maximum) element of $\sigma$
+  then $\sigma[1]$ is the minimal (resp. maximal) element of $\sigma$
   (Lemma~\ref{lemma:first element is 1 or n}),
   and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
-  $t[1]$ is the minimum (resp. maximum) element of $t$.
+  $t[1]$ is the minimal (resp. maximal) element of $t$.
   Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
@@
 (i) $\sigma[k]$ is the last letter of $\factor{\pmotif}{1}$,
-(ii)for every $1 \leq i < k$,
+(ii) for every $1 \leq i < k$,
 if $s_\sigma[i] = s_\sigma[i+1]$ then
@@
 \label{lemma:whereIsMax}
-Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, if
-$\firsti{\sigma}{i}$ is an ascent element (respectively  if $\firsti{\sigma}{i}$ is a descent element) then the maximal (resp.
-minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is $\first{\sigma}{i-1}$.
+Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its 
+decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, 
+if $\firsti{\sigma}{i}$ is an ascent (resp. descent) element then the maximal 
+(resp. minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is 
+$\first{\sigma}{i-1}$.
 \end{lemma}
@@
 
-For easy readability, we now define the set
+For the sake of readability, we now define the set
 $\SET{\pmotif}{\ptext}{i}{j}$ as follows:
@@
 \begin{lemma}
-Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (respectively descent) factor.
+Let $\pmotif$ be a permutation where 
+$\factor{\pmotif}{i}$ is an ascent (resp. descent) factor.
 If $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (resp. maximal), for all subsequence 
@@
 We use a similar argument if $\factor{\pmotif}{i}$ a descent factor.
-$\qed$
+\qed
 \end{proof}
@@
 \begin{corollary}
-Given a permutation $\pmotif$ and $\factor{\pmotif}{i}$ an ascent (respectively descent) factor.
+Let $\pmotif$ be a permutation where $\factor{\pmotif}{i}$ is an ascent (resp. descent) factor.
 If $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (resp.
@@
 
-This corollary gives one a safe way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the motif then there is no match at all.
+% This corollary allows us to way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the motif then there is no match at all.
 
@@
 
-Consider the following problem :\\
-$
+Consider the following problem :
+$$
 \LM{\pmotif}{\ptext}{i}{j} =
@@
 \end{cases}
-$
-
-This problem can be solve by induction.\\
-
-\textbf{BASE :} \\
-$
-\LM{\pmotif}{\ptext}{1}{j} =
+$$
+
+This problem can be solve by induction as follows:
+
+\noindent\textbf{BASE :}
+\begin{align*}
+\LM{\pmotif}{\ptext}{1}{j} 
+&=
 \begin{cases}
@@
 \end{cases}
-$
-
-\textbf{STEP :} \\
-$
-\LM{\pmotif}{\ptext}{i}{j} =
+\\
+\intertext{\textbf{STEP :}}
+\LM{\pmotif}{\ptext}{i}{j} 
+&=
 \begin{cases}
@@
 \end{cases}
-$
-
-%
-%With $\AF{\pmotif}{\ptext}{i}{j}$ ($\DF{\pmotif}{\ptext}{i}{j}$) the set of element such that
-%if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ then there exists
-%a match of $\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$ and
-%the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$ and
-%there is a match of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ and
-%the element $\first{\pmotif}{i}$ is matched with element $\ptext[j]$ and every element is inferior (superior) to the match of
-%$\pmotif[\firsti{\pmotif}{i-1}:]$ in $\ptext[k:]$.
-
-With $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ the set of element such that if  $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ or if $\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$ then there exists a match of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element $\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$.
-Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, to decide if $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$, one needs to find an occurrence $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is a match of $\pmotif[\firsti{\pmotif}{i}:]$.
-Formally we define $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ such as:\\
-
-$\AF{\pmotif}{\ptext}{i}{j}=\{\ptext[j']|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq 0$}$ \\
-\indent \indent \indent and  $|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$ \\
-
-$\DF{\pmotif}{\ptext}{i}{j}=\{\ptext[j']|\text{$j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq \infty$}$ \\
-\indent \indent \indent and  $|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\first{\pmotif}{i-1}) \}$ \\
-
-With $LIS_{\ptext}(i,j,k)$ (respectively $LDS_{\ptext}(i,j,k)$) is the longest increasing (resp. decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
+\end{align*}
+where $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ are the sets 
+of elements such that if  
+$\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ or if $\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$ 
+then there exists a match of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element 
+$\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$. 
+Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, 
+to decide if $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$, 
+one needs to find an occurrence $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ 
+such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is a match of 
+$\pmotif[\firsti{\pmotif}{i}:]$. 
+Formally we define $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ as follows:
+\begin{align*}
+\AF{\pmotif}{\ptext}{i}{j}
+&=
+\text{$\{\ptext[j'] \;|\; j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq 0$ and} 
+\\
+&\qquad 
+\text{$|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$} 
+\\
+\DF{\pmotif}{\ptext}{i}{j}
+&=
+\text{$\{\ptext[j'] \;|\; j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq \infty$ and}
+\\
+&\qquad
+\text{$|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$}
+\end{align*}
+where $LIS_{\ptext}(i,j,k)$ (resp. $LDS_{\ptext}(i,j,k)$) is the longest increasing 
+(resp. decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
 with every element of this sequence
 smaller (resp. bigger) than $k$.
-$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(|\ptext|^2\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).\\
+$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
+$O(|\ptext|^2\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).
 
@@
 every element of the subsequence is larger (resp. smaller)
-than the maximum (resp. minimal) element of the rest of the match which is given by the inductive problem of
-the previous factor.\\
+than the maximal (resp. minimal) element of the rest of the match which is given by the inductive problem of
+the previous factor.
 
@@
 and the induction on $O(kn^2)$ time and space.
-$\qed$
+\qed
 \end{proof}
@@
 a $(213,231)$-avoiding bivincular pattern occurs in a permutation.
-
-We introduce property of bivincular permutation for a motif avoiding both $213$ and $231$.
+We start by presenting a property of bivincular motifs avoiding both $213$ and $231$.
 
@@
 \label{lemma:ascentDescentAscent}
-If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and if $\sigma[i]$ is an ascent (respectively decent) element and $\sigma[i]+1$ is an ascent (resp.
-decent) element then $i<j$ ($j>i$) and for every $k$, $i<k<j$ ($j>k>i$), $\pi[k]$ is a descent (resp.
-ascent) element.
+If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and 
+if $\sigma[i]$ is an ascent (resp. decent) element and $\sigma[i]+1$ is an ascent 
+(resp. decent) element then 
+$i<j$ ($j>i$) and for every $k$, $i<k<j$ ($j>k>i$), $\pi[k]$ is a descent 
+(resp. ascent) element.    
 \end{lemma}
@@
 We use a similar argument if $\sigma[i]$ is a descent element
-$\qed$
+\qed
 \end{proof}
@@
 \begin{proof}
-We consider the following problem :\\
+We consider the following problem :
 Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$.
@@
 $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ is closed under induction.
-It can be solved by means of the following relations:\\
-\textbf{BASE :} \\
+It can be solved by means by the following relations:
+
+\noindent\textbf{BASE :} \\
 $$
@@
 
-\textbf{STEP :} \\
-For clarity of reading we consider 3 cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ :
+\noindent\textbf{STEP :}
+
+We consider 3 cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ :
 \begin{itemize}
@@
 		\end{itemize}
-
 \end{itemize}
-$\qed$
+\qed
 \end{proof}
 
-%\begin{proof}
-%We consider the following problem :\\
-%Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$.
-%$$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
-%\begin{cases}
-%	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
-%			  & \text{with every element in $]\min,\max[$}\\
-%	false 	& otherwise\\
-%\end{cases}
-%$$
-%$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}$ is closed under induction.
-%It can be solved by means of the following relations:\\
-%
-%\textbf{BASE :} \\
-%
-%For the base case, one matches the right most element of the motif.
-If the motif has a right bottom corner (if $n_\pmotif \in  \x$) then one must assure that the right most element of the motif is matched to the right most of the text.
-If the motif has a right top corner (if $n_\pmotif \in  \y$) and the right most element of the motif is maximal (minimal) then one must assure that right most element of the motif is matched to the maximal (minimal) element of the text.
-If there is not corner, there is no condition on the match of the right most element.
-%
-%if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-%\begin{cases}
-%	true 	& \text{if $\min<\ptext[j]<\max$}\\
-%	false 	& otherwise\\
-%\end{cases}
-%$
-%%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
-%\\
-%
-%if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
-%\begin{cases}
-%	true 	& \text{if $\min<\ptext[j]<\max$}\\
-%			& \text{and } j=n_\ptext\\
-%	false 	& otherwise\\
-%\end{cases}
-%$
-%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
-%\\
-%
-%if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-%\begin{cases}
-%	true 	& \text{if $\min<\ptext[j]<\max$ }\\
-%			& \text{and $\ptext[j]$ is the maximal element}\\
-%	false 	& otherwise\\
-%\end{cases}
-%$
-%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
-%
-%if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-%\begin{cases}
-%	true 	& \text{if $\min<\ptext[j]<\max$}\\
-%			& \text{and } j=n_\ptext\\
-%			& \text{and $\ptext[n_\ptext]$ is the maximal element}\\
-%	false 	& otherwise\\
-%\end{cases}
-%$
-%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
-%
-%if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-%\begin{cases}
-%	true 	& \text{if $\min<\ptext[j]<\max$}\\
-%			& \text{and $\ptext[j]$ is the minimal element}\\
-%	false 	& otherwise\\
-%\end{cases}
-%$
-%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\
-%
-%if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the minimal element: \\
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
-%\begin{cases}
-%	true 	& \text{if $\min<\ptext[j]<\max$}\\
-%			& \text{and } j=n_\ptext\\
-%			& \text{and $\ptext[n_\ptext]$ is the minimal element}\\
-%	false 	& otherwise\\
-%\end{cases}
-%$
-%%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\
-%
-%
-%\textbf{STEP :} \\
-%
-%For the induction there are 8 cases to consider, depending on if $\pmotif[i]$ is ascend or descend, if elements $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) and if elements $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$).
-First one must assure that $\pmotif[i]$ can be matched to $\ptext[j]$, this is done by checking that $\ptext[j]$ is in the interval $]\min,\max[$.
-Then one must use the induction.
-The element $\ptext[j]$ gives a new $\min$ if the element is ascent or a new $\max$ if the element is descent.
-%If $\pmotif[i]\pmotif[i+1]$ are not underlined nor overlined, then $\pmotif[i+1]$ can be matched to any upcoming element in the text.
-If $\pmotif[i]\pmotif[i+1]$ are underlined ($i \in \x$) then the match of $\pmotif[i+1]$ must be $\ptext[j+1]$.
-If $\pmotif[i]\pmotif[i+1]$ are overlined ($i \in \y$) then ethe match of  $\pmotif[i+1]$ must be $\ptext[j]+1$.
-%
-%$
-%\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
-%\begin{cases}
-%\bigcup_{j<k}
-%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
-%				& \text{if $\stripe{\pmotif}{i}=\ustep$
-%				and $i \notin \x$}\\
-%				& \text{and $i \notin \y$ }\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%			&\\
-%
-%			\bigcup_{j<k}
-%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{k}
-%				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
-%				& \text{and $i \notin \x$ and $i \notin \y$  }\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%			&\\
-%
-%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}
-%				& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
-%				& \text{and $i \in \x$ and $i \notin \y$}\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%			&\\
-%
-%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1}
-%				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
-%				& \text{and $i \in \x$ and $i \notin \y$ }\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%
-%			&\\
-%
-%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{\ptext^{-1}[\ptext[j]+1]}
-%				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
-%				&\text{and $i \notin \x$ and $i \in \y$}\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%				&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
-%			&\\
-%
-%
-%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{\ptext^{-1}[\ptext[j]-1]}
-%				&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
-%				&\text{and $i \notin \x$ and $i \in \y$ }\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%				&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
-%			&\\
-%
-%			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{j+1}
-%				&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
-%				&\text{and $i \in \x$ and $i \in \y$}\\
-%				&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%			&\\
-%
-%			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1}
-%				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
-%				&\text{and $i \in \x$ and $i \in \y$}\\
-%				&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
-%				& \text{and $\min<\ptext[j]<\max$} \\
-%			&\\
-%
-%
-%			False & Otherwise\\
-%\end{cases}
-%$
-%
-%There are 6 cases to consider to search for a match.
-%Depending on if the motif has a left bottom corner ($0 \in \x$), a left top corner, and if it has a left top corner $0 \notin \y$, if the left most element is minimal or maximal.
-If the motif has a left bottom corner, then one must assure that the left most element of the motif is matched to the left most element of the text.
-If the motif has a left top corner and the left most element of the motif is minimal (maximal) then one must assure that the left most element of the motif is matched with the minimal (maximal) element of the text :
-%\begin{itemize}
-%	\item If $0 \in \x$ and $0 \notin \y$ there exists a match if and only if there is a match starting with left most element of the text : $ \PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true.
-%
-%	\item If $0 \notin \x$ and $0 \notin \y$ there exists a match if and only if there exists a match stating at any index : 	$\bigcup_{1<k\leq n_\ptext}\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{k}$ is true.
-%
-%	\item If $0 \in \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there is a match starting with the left most element  of $\ptext$, and the left most element  of $\ptext$ is the minimal element  of $\ptext$ : $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$  is true and the left most element of $\ptext$ is the minimal element of $\ptext$.
-%
-%	\item If $0 \notin \x$, $0 \in \y$ and the first element of the stripe of the motif is minimal there exists a match if and only if there exists a match stating at the minimal element of the text : if $j_{\min}$ is the index of the minimal element in $\ptext$ then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\min}}$ is true.
-%
-%	\item If $0 \in \x$, $0 \notin \y$  and the first element of the stripe of the motif is maximal then there exists a match if and only if there is a match starting with the left most element  of $\ptext$ and the left most element  of $\ptext$ is the maximal element  of $\ptext$: $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{1}$ is true and the left most element of $\ptext$ is the maximal element of $\ptext$.
-%
-%	\item If $0 \notin \x$, $0 \notin \y$ and the first element of the stripe of the motif is maximal there exists a match if and only if there exists a match stating at the maximal element of the text : if $j_{\max}$ is the index of the maximal in $\ptext$ element then $\PM{\pbmotif}{\ptext}{0}{n_{\pmotif}}{1}{j_{\max}}$ is true.
-%
-%\end{itemize}
-%\end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Longest Subsequence Avoiding \\(231,213) for a Permutation}
+\section{Computing the longest $(213,231)$-avoiding subsequence}
 \label{section:LCS}
 
-	This section and the next one are devoted to the longest subsequence avoiding (231,213).
-	The general problem asks to find the longest subsequence that occur in a set of permutations. We add the constraint that this subsequence avoid $213$ and $231$.
-	This section focuses on the case where the set is of size one.
-	To do so, we need the set of descent elements and the set of ascent elements.
+	This section is devoted to finding longest $(213,231)$-avoiding subsequences in permutations:
+	Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
+	in each input permutation.
+
+	We start with the easiest case where we are given just one input permutation.
+	We need the set of descent elements and the set of ascent elements.
 	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
@@
 	\label{proposition:longestIncreasingSubsequence}
-	If $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$ then
+	If $s$ is a longest $(213,231)$-avoiding subsequence with last element at index 
+	$f$ in $\pi$ then
 	$P(\pi)$ is a longest increasing subsequence with last element at index $f$ and
@@
 	Thus $|s_m|>|P(\pi)|$, clearly the sequence $s_m \cup M(\pi)$
-	is avoiding (213,231) and is longer than $s$ which is not possible.
-	The same idea goes for the demonstration that $M(\pi)$ is the longest decreasing subsequence.
-	$\qed$
+	is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
+	The same ideacan be used to show that $M(\pi)$ is the longest decreasing subsequence.
+	\qed
 	\end{proof}
@@
 	\begin{proposition}
-	Given a permutation $\pi$,
-	finding the longest subsequence avoiding (231,213)
+	Let $\pi$ be a permutation.
+	Computing the longest $(213,231)$-pattern that occurs in $\pi$
 	can be done in $O(|\ptext|\log(\log(|\ptext|)))$ time and in $O(n)$ space.
@@
 	The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
-	where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
-	Computing the longest increasing subsequence and the  lonfest decreasing subsequence can be done in $O(|\ptext|\log(\log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
-	$\qed$
+	where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
+	Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
+	$O(|\ptext|\log(\log(|\ptext|)))$ time and $O(n)$ space 
+	(see \cite{Bespamyatnikh00enumeratinglongest}), 
+	then finding the maximal can be done in linear time.
+	\qed
 	\end{proof}
 
-\section{Longest Subsequence Avoiding \\(231,213) Common for Two Permutations}
-\label{section:LCS common 2 permutations}
-
-This section is devoted to the longest subsequence avoiding (231,213) for two permutations : Given two (random) permutations, find a permutation $\pi$ such that $\pi$ occurs in both permutation and $\pi$ avoids $231$ and $213$.
+We now turn to considering the case where the input is composed of two permutations.
 
@@
 
-\textbf{BASE :} \\
-$
+\noindent\textbf{BASE :}
+
+$$
 \LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{|\pi_1|}{|\pi_2|} =
@@
 \end{cases}
-$
-
-\textbf{STEP :} \\
-
-$
+$$
+
+\noindent\textbf{STEP :}
+
+$$
 \LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=max
@@
 \end{cases}
-$
+$$
 
@@
 
-%	\section{Related problems}
-%
-%		\textbf{Proposition 3.1} Longest Minimal Common Supersequence, Shortest Maximal Common Subsequence, and Shortest Maximal Common Non-Supersequence are MAX SNP-hard.\\
-%
-%		Clearly every problem over (231,213)-Avoiding permutation
-%		are equivalent to problem over binary word.
-%		The proposition follow what we know about those problem over binary alphabet
-%		\cite{Middendorf1995317}.\\
-
-	\section{Conclusion}
-
 \bibliography{bibli}{}

### 2015-06-11 article.tex
typos

@@
 
-\section{Computing the longest $(213,231)$-avoiding subsequence}
+\section{Computing the longest $(213,231)$-avoiding pattern}
 \label{section:LCS}
 
-	This section is devoted to finding longest $(213,231)$-avoiding subsequences in permutations:
-	Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
-	in each input permutation.
-
-	We start with the easiest case where we are given just one input permutation.
+	This section is devoted to finding longest $(213,231)$-avoiding patterns 
+	in permutations.
+	We start with the easiest case where we are given just one input permutation
+	and we are asked to find the longest $(213,231)$-avoiding pattern that 
+	occurs in the input permutation.
 	We need the set of descent elements and the set of ascent elements.
@@
 Consider the following problem,
-that compute the longest stripe common to $\pi_1$ and $\pi_2$.
-Given two permutations $\pi_1$ and $\pi_2$.\\
-
-$$
+that compute the longest stripe common to $\pi_1$ and $\pi_2$:
+Given two permutations $\pi_1$ and $\pi_2$, we define
+$
 \LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
-$$
-\begin{center}
-= $\max$ \{$|s|$ $|$ $s$ occurs in $\pi_1[i_1:]$ with every element is in $[\lb_1,\ub_1]$ and $s$ occurs in $\pi_2[i_2:]$ with every element is in $[\lb_2,\ub_2]$ \}
-\end{center}
-
-We show that this family of problems are closed under induction.\\
+=
+\max\{|s| \;|\; s \text{ occurs in } \pi_1[i_1:] \text{ with every element is in }
+[\lb_1,\ub_1] \text{ and } s \text{ occurs in } \pi_2[i_2:] \text{ with every element is in }
+[\lb_2,\ub_2]\}$.
+
+We show that this family of problems is closed under induction.
 

### 2015-06-14 article.tex
rewrite some corrolarry

--- 2015-06-11 article.tex
@@
 \label{corollary:minmaxelement}
-Let $\pi \in S_n$.
-Then
 $\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$,
@@
 \label{corollary:max is ascent}
-Let $\pi \in \in \AV_n(213,231)$ and $1 \leq i < n$.
-Then,
+Let $\pi \in \AV_n(213,231)$ and $1 \leq i < n$. Then,
 (1) 
@@
 
-For the sake of readability, we now define the set
+we now define the set
 $\SET{\pmotif}{\ptext}{i}{j}$ as follows:
-if $s \in \SET{\pmotif}{\ptext}{i}{j}$ then
+given a subsequence $s$ of $\ptext[j:]$,
+$s \in \SET{\pmotif}{\ptext}{i}{j}$ if and only if
 $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$
-and the element matching $\first{\pmotif}{i}$ is $\ptext[j]$.
+and the element$\first{\pmotif}{i}$ occurs in $\ptext[j]$.
 
 \begin{lemma}
-Let $\pmotif$ be a permutation where 
-$\factor{\pmotif}{i}$ is an ascent (resp. descent) factor.
-If $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that the element matching $\first{\pmotif}{i-1}$ is minimal (resp. maximal), for all subsequence 
+Let $\pmotif$ be a permutation 
+with $\factor{\pmotif}{i}$ as an ascent (respectively descent) factor,
+$s$ a subsequence such that, $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
+For all subsequence 
 $s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequence $t$ of $\ptext$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$.
@@
 \begin{corollary}
-Let $\pmotif$ be a permutation where $\factor{\pmotif}{i}$ is an ascent (resp. descent) factor.
-If $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (resp.
-maximal).
-There is a match of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ matched to $\ptext[j]$ if and only if there exists $t$ such that $ts$ is a match of $\pmotif$ in $\ptext$.
+Let $\pmotif$ be a permutation 
+with $\factor{\pmotif}{i}$ as an ascent (respectively descent) factor,
+and let $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
+Those following statements are equivalent :
+\begin{itemize}
+	\item There exists an 
+	occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs in $\ptext[j]$.
+	\item There exists a subsequence $t$ of $\ptext[1:j-1]$  such that $ts$ is an occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs in $\ptext[j]$. 
+\end{itemize}
 \end{corollary}
@@
 	\text{ and that minimize the maximal value} & \\
-	\text{ and $\first{\sigma}{i}$ is matched with $\ptext[j]$} & \\
+	\text{ and $\first{\sigma}{i}$ occurs in $\ptext[j]$} & \\
 
@@
 	\text{ and that maximize the minimal value} & \\
-	\text{ and $\first{\sigma}{i}$ is matched with $\ptext[j]$} & \\
+	\text{ and $\first{\sigma}{i}$ occurs in $\ptext[j]$} & \\
 \end{cases}
@@
 $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ or if $\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$ 
-then there exists a match of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element 
-$\first{\pmotif}{i-1}$ is matched with element $\ptext[k]$. 
+then there exists an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element 
+$\first{\pmotif}{i-1}$ occurs in element $\ptext[k]$. 
 Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, 
@@
 one needs to find an occurrence $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ 
-such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is a match of 
+such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is an occurrence of 
 $\pmotif[\firsti{\pmotif}{i}:]$. 
@@
 For the base case,
-one is looking for a match for the first factor.
+one is looking for an occurrence for the first factor.
 If the factor is an ascent (respectively descent) factor, then
@@
 every element of the subsequence is larger (resp. smaller)
-than the maximal (resp. minimal) element of the rest of the match which is given by the inductive problem of
+than the maximal (resp. minimal) element of the rest of the occurrence which is given by the inductive problem of
 the previous factor.
 
-There exists a match of $\pmotif$ in $\ptext$ if and only if
+There exists a occurrence of $\pmotif$ in $\ptext$ if and only if
 there exists a $LM(n,i)\neq 0$ and $LM(n,i)\neq \infty$ for $1 \leq i \leq |\ptext|$,
@@
 If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and 
-if $\sigma[i]$ is an ascent (resp. decent) element and $\sigma[i]+1$ is an ascent 
+if $\sigma[i]$ is an ascent (respectively decent) element and $\sigma[i]+1$ is an ascent 
 (resp. decent) element then 
-$i<j$ ($j>i$) and for every $k$, $i<k<j$ ($j>k>i$), $\pi[k]$ is a descent 
+$i<j$ (resp. $j>i$) and for every $k$, $i<k<j$ (resp. $j>k>i$), $\pi[k]$ is a descent 
 (resp. ascent) element.    
@@
 	$$	
-
-	$\pmotif[i]$ can occur in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
-$\pmotif[i:]$ occurs in $\ptext[j:]$, if and only if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$.
-$\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ if and only if there is an occurrence of $\pmotif[i+1:]$ in $\ptext[j+1:]$ starting at element $k$, $j<k$, which correspond to know if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{*}{*}{i+1}{k}$ is true.
-Because $\pmotif[i]$ is an ascent element,  $\pmotif[i]$ is the minimal element of $\pmotif[i:]$, thus a match of $\pmotif[i+1:]$ can not use value smaller than $\ptext[j]$, so $\ptext[j]+1$ is a (new) lower bound.
-The upper bound is unchanged.
-So there is a occurrence of  $\pmotif[i:]$ starting at element $j$ in $\ptext[j:]$ if and only if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}$.
+	Remark that $\pmotif[i]$ can occur in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
+	Thus if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ with every element in $[\pmotif[i]+1,\ub]$ then 
+ 	$\pmotif[i:]$ occurs in $\ptext[j:]$  	
+ 	which correspond to know if there exists $k$, $j<k$ such that
+	$\PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}$ is true.
 
@@
 	$$	
-	We prove symmetrically as the last case that 
+	We can show symmetrically as the last case that 
 	$\pmotif[i:]$ occurs in $\ptext[j:]$
@@
 \begin{itemize}
-	\item If $_\llcorner{\sigma[1]}$ then the left most element of $\sigma$  must occur in the left most element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on a occurrence of $\pmotif$ in $\ptext$).
+	\item If $_\llcorner{\sigma[1]}$ then the left most element of $\sigma$  must occur in the left most element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on an occurrence of $\pmotif$ in $\ptext$).
 This constraint is assured by demanding that the occurrence starts at the left most element of $\ptext$ : if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
@@
 	\begin{proposition}
-	Let $\pi$ be a permutation.
-	Computing the longest $(213,231)$-pattern that occurs in $\pi$
-	can be done in $O(|\ptext|\log(\log(|\ptext|)))$ time and in $O(n)$ space.
+	Let $\pi$ be a permutation. One can compute the
+	the longest $(213,231)$-pattern that occurs in $\pi$
+	in $O(|\ptext|\log(\log(|\ptext|)))$ time and in $O(n)$ space.
 	\end{proposition}
@@
 Given two permutations $\pi_1$ and $\pi_2$,
+one can compute 
 the longest common subsequence
-avoiding (231,213) can be compute in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
+avoiding (231,213) in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
 \end{proposition}

### 2015-06-16 article.tex
modif proof of proposition 3 plus typos

@@
 
+\DeclareMathOperator{\firstia}{first}
+\newcommand{\firsti}[2]{\firstia_{{#1}}({#2})}
+
+\DeclareMathOperator{\factora}{factor}
+\newcommand{\factor}[2]{\factora_{{#1}}({#2})}
+
 %first
-\DeclareMathOperator{\firsta}{L}
-\newcommand{\first}[2]{\firsta_{{#1}}({#2})}
-
-\DeclareMathOperator{\firstia}{LI}
-\newcommand{\firsti}[2]{\firstia_{{#1}}({#2})}
-
-\DeclareMathOperator{\factora}{F}
-\newcommand{\factor}[2]{\factora_{{#1}}({#2})}
+\DeclareMathOperator{\firsta}{first}
+\newcommand{\first}[2]{\firsta(\factor{#1}{#2})}
 
@@
 	In Section~\ref{section:Definitions} the needed definition are presented.
-	Section~\ref{section:both are (231,213)-avoiding} is devoted to presenting
+	Section~\ref{section:both are (213,231)-avoiding} is devoted to presenting
 	an online linear-time algorithm in case both the pattern and the target
@@
 \section{Both $\pi$ and $\sigma$ are $(213,231)$-avoiding}
-\label{section:both are (231,213)-avoiding}
+\label{section:both are (213,231)-avoiding}
 
@@
 \begin{proposition}
+	\label{Proposition:both permutations are avoiding}
 	Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations.
-	One can decide whether $\pi$ contains $\sigma$ in linear-time.
+	One can decide whether $\pi$ contains $\sigma$ in linear time.
 \end{proposition}
@@
 to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$.
-A straightforward greedy approach solves this issue in linear-time.
+A natural greedy approach solves this issue in linear-time.
 \qed
@@
 Observe that, according to Corollary~\ref{corollary:minmaxelement},
-the effective construction of the two stripes is not required for the above proposition,
+the effective construction of the two stripes is not required in stretch 
+of algorithm given for the proof in the proposition \ref{Proposition:both permutations are avoiding},
 and hence we have an online algorithm.
@@
 
-\section{$\sigma$ only is $(231,213)$-avoiding}
+\section{$\sigma$ only is $(213,231)$-avoiding}
 \label{section:sigma only avoid 231 and 213}
@@
 For $\sigma \in S_k$, the \emph{factorization}
-$\sigma = \factor{\pmotif}{p} \factor{\pmotif}{p-1} \ldots \factor{\pmotif}{1}$
+$\sigma = \factor{\pmotif}{p} \factor{\pmotif}{p-1} \ldots$ $\factor{\pmotif}{1}$
 is defined as follows:
@@
 $s_\sigma = ddaaaddd$ and hence
-$\sigma = \factor{\pmotif}{3} \factor{\pmotif}{2} \factor{\pmotif}{1}$ with
+$\sigma = \factor{\pmotif}{3} \factor{\pmotif}{2}$ $ \factor{\pmotif}{1}$ with
 $\factor{\pmotif}{1} =7654$, $\factor{\pmotif}{2} = 123$ and $\factor{\pmotif}{3} = 98$.
@@
 \begin{remark}
-A Factor is either an increasing or a decreasing subsequence.
+All the elements of a factor are all increasing elements or all decreasing elements
 \end{remark}
@@
 Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its 
-decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, 
+decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots$$\factor{\sigma}{1}$, 
 if $\firsti{\sigma}{i}$ is an ascent (resp. descent) element then the maximal 
-(resp. minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$ is 
+(resp. minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}$ $\ldots$ $\factor{\sigma}{1}$ is 
 $\first{\sigma}{i-1}$.
@@
 $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$
-and the element$\first{\pmotif}{i}$ occurs in $\ptext[j]$.
+and the element $\first{\pmotif}{i}$ occurs in $\ptext[j]$.
 
 \begin{lemma}
-Let $\pmotif$ be a permutation 
-with $\factor{\pmotif}{i}$ as an ascent (respectively descent) factor,
-$s$ a subsequence such that, $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
-For all subsequence 
-$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequence $t$ of $\ptext$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$.
+Let $\pmotif$ be a permutation , 
+$\factor{\pmotif}{i}$ be an ascent (resp. descent) factor,
+$s$ be a subsequence such that $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
+For all subsequences 
+$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequences $t$ of $\ptext$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ in $\ptext[j:]$ such that $\first{\pmotif}{i}$ occurs in $\ptext[j]$.
 \end{lemma}
@@
 \begin{corollary}
-Let $\pmotif$ be a permutation 
-with $\factor{\pmotif}{i}$ as an ascent (respectively descent) factor,
-and let $s \in \SET{\pmotif}{\ptext}{i}{j}$, such that $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
-Those following statements are equivalent :
+Let $\pmotif$ be a permutation , 
+$\factor{\pmotif}{i}$ be an ascent (resp. descent) factor
+and 
+$s$ be a subsequence such that $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
+These following statements are equivalent :
 \begin{itemize}
@@
 		& \text{If $\first{\sigma}{i}$ is  } \\
-	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & 
+	\text{ that is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & 
 		\text{ an ascent element } \\	
@@
 		& \text{If $\first{\sigma}{i}$ is  } \\
-	\text{ which is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \text{ a descent element } \\	
+	\text{ that is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \text{ a descent element } \\	
 	\text{ and that maximize the minimal value} & \\
@@
 \\
+\intertext{
+In the base case,
+one is looking for an occurrence of the first factor.
+If the factor has only ascent (resp. descent) elements, then
+one has to find an increasing (resp. decreasing) subsequence
+in the text of the same size or that is longer that
+the size of the first factor. To find the occurrence that is
+the less restrictive (for the future matching)
+one must find the occurrence with the right most element
+of the sequence minimal (resp. maximal).}
+\\
 \intertext{\textbf{STEP :}}
@@
 $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ or if $\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$ 
-then there exists an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element 
+then there exists an occurrence $t$ of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element 
 $\first{\pmotif}{i-1}$ occurs in element $\ptext[k]$. 
-Given that one has the set $\SET{\pmotif}{\ptext}{i-1}{k}$, 
-to decide if $\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$, 
-one needs to find an occurrence $t$ of $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ 
-such there exists $s \in \SET{\pmotif}{\ptext}{i-1}{k}$ and $ts$ is an occurrence of 
-$\pmotif[\firsti{\pmotif}{i}:]$. 
-Formally we define $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ as follows:
+$t$ exists if and only if $t=t's'$ with $t'$ is an occurrence of  $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ with element
+$\first{\pmotif}{i-1}$ occurs in element $\ptext[k]$
+and $s \in \SET{\pmotif}{\ptext}{i-1}{k}$.
+If $\factor{\pmotif}{i}$ is an increasing (resp. decreasing)
+sequence $t'$ must be an increasing (resp. decreasing) 
+subsequence
+in $\ptext[j:k-1]$ of the same size or that is longer that
+the size of $\factor{\pmotif}{i}$ (denoted $|\factor{\pmotif}{i}|$).
+Moreover one must assure that the elements of subsequence 
+$t'$ are smaller (resp. bigger) than the element of $s'$ 
+in particular the minimal (resp. maximal) element.
+Thus we can compute $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ as follows:
 \begin{align*}
@@
 &\qquad 
-\text{$|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$} 
+\text{$|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\LM{\pmotif}{\ptext}{i-1}{j'})\}$} 
 \\
@@
 &\qquad
-\text{$|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\first{\pmotif}{i-1})\}$}
+\text{$|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\LM{\pmotif}{\ptext}{i-1}{j'})\}$}
 \end{align*}
@@
 $LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
-$O(|\ptext|^2\log(\log(|\ptext|)))$ (see \cite{Bespamyatnikh00enumeratinglongest}).
-
-For the base case,
-one is looking for an occurrence for the first factor.
-If the factor is an ascent (respectively descent) factor, then
-one has to find an increasing (resp. decreasing) subsequence
-in the text of same size or longest that
-the size of the first factor.
-To find the "safest" solution
-one must assure that the right most element
-of the sequence is minimal (resp. maximal).\\
-For the induction, it follows the same idea
-except that one must assure that
-every element of the subsequence is larger (resp. smaller)
-than the maximal (resp. minimal) element of the rest of the occurrence which is given by the inductive problem of
-the previous factor.
+$O(|\ptext|^2\log(\log(|\ptext|)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
 
@@
 there exists a $LM(n,i)\neq 0$ and $LM(n,i)\neq \infty$ for $1 \leq i \leq |\ptext|$,
-with $n$ the number of factor in $\pmotif$.
-Moreover the basic case can be computed in $O(n^2)$
+with $n$ the number of factors in $\pmotif$.
+Moreover the basic case can be computed in $O(n^2)$ time
 and the induction on $O(kn^2)$ time and space.
@@
 
-This section is devoted to presenting a polynomial-time algorithm for deciding whether
-a $(213,231)$-avoiding bivincular pattern occurs in a permutation.
-We start by presenting a property of bivincular motifs avoiding both $213$ and $231$.
+This section is devoted to the pattern matching problem with $(213,231)$-avoiding bivincular motif.
+Recall that a bivincular motif generalise a permutation motif by
+be able to force elements to be consecutive in value or in position.
+Hence,  bivincular motif is stronger in constraint that motif by permutation, intuitively we can not use the previous algorithm.
+As in a $(213,231)$-avoiding permutation, we can describe structural property of a $(213,231)$-avoiding bivincular motif.
 
@@
 \label{lemma:ascentDescentAscent}
-If $\overline{\sigma[i]\sigma[j]}$ (thus $\sigma[j]=\sigma[i]+1$) and 
-if $\sigma[i]$ is an ascent (respectively decent) element and $\sigma[i]+1$ is an ascent 
+Given $\pmotif$ a $(213,231)$-avoiding bivincular,
+If $\overline{\sigma[i]\sigma[j]}$ (this implies that $\sigma[j]=\sigma[i]+1$) and 
+if $\sigma[i]$ is an ascent (resp. decent) element and $\sigma[i]+1$ is an ascent 
 (resp. decent) element then 
@@
 
+A way to understand this lemma is if two ascent (resp. decsent) elements
+need to occur in consecutive elements in value then every element in $\pmotif$ which are between those two elements (if any) are descent (resp. ascent) elements.
+
 \begin{proof}
 Suppose that there exists $k$, $i<k<j$,
-such that $\pmotif[k]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[k]<\sigma[j]$ which is in contradiction that with $\sigma[j]=\sigma[i]+1$.
+such that $\pmotif[k]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[k]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
 We use a similar argument if $\sigma[i]$ is a descent element
@@
 \label{Proposition:bivincular pattern}
-		Let $\sigma$ be a bivincular motif avoiding $213$ and $231$ of length $k$
+Let $\sigma$ be a $(213,231)$-avoiding bivincular of length $k$
 and $\pi \in S_n$.
@@
 We consider the following problem :
-Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$.
+Given $\pmotif$ a $(213,231)$-avoiding bivincular, and a text $\ptext \in \Av{n_\ptext}{231,213}$,
 $$
@@
 
-$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ is closed under induction.
-It can be solved by means by the following relations:
+$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ can be solved by means by the following relations:
 
@@
 
-The base case finds an occurrence for the right most element of the motif.
-If the last element does not have any restriction on position and on value, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ can occur in $\ptext[j]$.
-This condition is checked by assuring that $\ptext[j] \in [\lb,\ub]$.
+The base case finds an occurrence for the rightmost element of the motif.
+If the last element does not have any restriction on positions and on values, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ occurs in $\ptext[j]$.
+This is true if $\ptext[j] \in [\lb,\ub]$.
 
@@
 
-We consider 3 cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ :
+We need to consider 3 cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ :
 \begin{itemize}
@@
 
-	this is straightforward with the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is in $[\lb,\ub]$.
+	which is immediate from the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is in $[\lb,\ub]$.
 
@@
 	$$	
-	Remark that $\pmotif[i]$ can occur in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
+	Remark that $\pmotif[i]$ occurs in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
 	Thus if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ with every element in $[\pmotif[i]+1,\ub]$ then 
@@
 	$$	
-	We can show symmetrically as the last case that 
-	$\pmotif[i:]$ occurs in $\ptext[j:]$
-	with $\sigma[i]$ occurs in $\pi[j]$.
-	 starting at element $j$ if and only if $\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}$.
+	The same remark as the last case holds.
 
@@
 
-Clearly if $\bigcup_{0<j} \PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{j}$ is true then $\sigma$ occurs in $\pi$. We now discuss about the position and value constraints.
+Clearly if $\bigcup_{0<j} \PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{j}$ is true then $\sigma$ occurs in $\pi$. We now discuss the position and value constraints.
 \paragraph{Position Constraint.} There are 3 types of position constraints 
 \begin{itemize}
-	\item If $_\llcorner{\sigma[1]}$ then the left most element of $\sigma$  must occur in the left most element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on an occurrence of $\pmotif$ in $\ptext$).
-This constraint is assured by demanding that the occurrence starts at the left most element of $\ptext$ : if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
-
-	\item If ${\pmotif[n_\pmotif]}_\lrcorner$ then the right most element $\sigma$ must occurs in the right most element of $\pi$ ($\pmotif[n_\pmotif]$ occurs in $\ptext[n_\ptext]$ on a occurrence of $\pmotif$ in $\ptext$).
-This constraint is assured in the base case.
+	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must occur in the leftmost element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on an occurrence of $\pmotif$ in $\ptext$).
+This constraint is checked by requiring the occurrence to starts at the left most element of $\ptext$ : if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
+
+	\item If ${\pmotif[n_\pmotif]}_\lrcorner$ then the rightmost element $\sigma$ must occurs in the rightmost element of $\pi$ ($\pmotif[n_\pmotif]$ occurs in $\ptext[n_\ptext]$ on a occurrence of $\pmotif$ in $\ptext$).
+This constraint is checked in the base case.
 
 	\item If $\underline{\pmotif[i]\pmotif[i+1]}$ then the index of the occurrence of $\pmotif[i]$ and $\pmotif[i+1]$ must be consecutive.
-In other word if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i+1]$ must occur in $\ptext[j+1]$.
-We assure this restriction in the induction by demanding that occurrences of $\pmotif[i+1:]$  start at index $j+1$.
+In other word, if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i+1]$ must occur in $\ptext[j+1]$.
+We assure this restriction in the induction by requiring occurrences of $\pmotif[i+1:]$ to start at index $j+1$.
 \end{itemize}
@@
 
-		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the minimal element, because ascent elements are increasing).
-Remark that the problem starts with the lower bound as $1$, and inductive problems before the index $i$ are called with descent elements which do not modified the lower bound, so for every problem with index $i$ has for lower bound $1$.
-		$\PM{\pbmotif}{\ptext}{1}{*}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{1}{*}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to lower bound which is  $1$.
-
-		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the right most element). Which is solved in the case case.
+		\item If $\sigma[i]$ is an ascent element, then remark that 
+		every problem 
+		$\PM{\pbmotif}{\ptext}{\lb}{*}{i}{*}$ is true if $\sigma[i]$ occurs in element $\lb$ thus it is enough to require that $\lb=1$.
+		Now remark that $\sigma[i]$ is the leftmost ascent element, indeed if not, then there exists an ascent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the minimal element.
+As a consequence every problem $\PM{\pbmotif}{\ptext}{1}{n_{\pi}}{1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ is called with descent thus every problem
+		$\PM{\pbmotif}{\ptext}{\lb}{*}{i}{*}$ has same lower bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ thus for every $\PM{\pbmotif}{\ptext}{\lb}{*}{i}{*}$, $\lb=1$.
+
+		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the right most element).
+Thus every $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ occurs in $1$.
 
@@
 
-		\item If $\sigma[i]$ is a descent element then $\sigma[i]$ is the left most ascent element (if not $\sigma[i]$ would not be the maximal element, because descent elements are decreasing).
-Remark that the problem starts with the upper bound as $n_\ptext$, and any inductive problems before the index $i$ are called with ascent elements which do not modified the upper bound, every problem with index $i$ has for upper bound $n_\ptext$.
-		$\PM{\pbmotif}{\ptext}{*}{n_\pmotif}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{n_\pmotif}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to upper bound which is  $n_\pmotif$.
-
-		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element) which is solved in the base case.
+		\item If $\sigma[i]$ is an descent element, then remark that 
+		every problem 
+		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ occurs in element $\ub$ thus it is enough to require that $\ub=n_{\ptext}$.
+		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal element.
+As a consequence every problem $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ is called with ascent elements thus every problem
+		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ has same upper bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ thus for every $\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$,
+		$\ub=n_{\ptext}$.
+
+		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element).
+Thus every $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ occurs in $n_{\ptext}$.
 
@@
 
-	\item  If $\overline{\pmotif[i]\pmotif[i']}$, with $\pmotif[i']=\pmotif[i]+1$ then if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i']$ must occur in $\ptext[j]+1$.
+	\item  If $\overline{\pmotif[i]\pmotif[i']}$,  (which implies that $\pmotif[i']=\pmotif[i]+1$) then if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i']$ must occur in $\ptext[j]+1$.
 		\begin{itemize}
@@
 
-			\item If $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i'<i$) , then
+			\item If $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i'<i$), then
+			remark that every problem 
+			$\PM{\pbmotif}{\ptext}{\lb}{*}{i'}{*}$ is true if $\sigma[i']$ occur in $\lb$ thus it is enough to require that $\lb=\ptext[j]+1$.
+			Now remark that
 			$\pmotif[i]$ is the right most ascent element and $\pmotif[i']$ is the right most element (or $\pmotif[i'] \neq \pmotif[i]+1$). 
-Thus inductive problems between $i+1$ and $i'$ do not modified the lower bound.
-If $\sigma[i]$ occurs in $\ptext[j]$ then the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ have for lower bound $\ptext[i]+1$.
-The problem $\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ is a base case and is true if and only if
-			the occurrence of $\sigma[i']$ is equal the lower bound which is equal to $\ptext[i]+1$ so the occurrence of $\pmotif[i]$ and $\pmotif[i']$ are consecutive in value.
-
-			\item If $\pmotif[i]$ is a descent element and $\pmotif[i']$ is a descent element then $i'<i$ and there is no descent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i'+1$ and $i$ do not modified the upper bound.
-Remark that if $\pmotif[i']$ occurs in $\ptext[j]$ then
-			the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ have for upper bound $\ptext[j]-1$.
-$\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is true if and only if the occurrence of $\sigma[i]$ is equal to upper bound which is equal to $\sigma[i']-1$ so the occurrence of $\pmotif[i]$ and $\pmotif[i']$ are consecutive in value.
-
-			\item If $\pmotif[i]$ is an ascent element and $\pmotif[i']$ is an ascent element then $i<i'$ and there is no  ascent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), Thus inductive problems between $i+1$ and $i'$ do not modified the lower bound.
-Remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then
-
-			the inductive problems after $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ have for lower bound $\ptext[j]+1$.
-$\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ is either an inductive case or a base case, in either way  $\PM{\pbmotif}{\ptext}{*}{*}{i'}{*}$ is true if and only if the occurrence of $\sigma[i']$ is equal to lower bound which is equal to $\sigma[i']+1$ so the occurrence of $\pmotif[i]$ and $\pmotif[i']$ are consecutive in value.
+			As a consequence every problem $\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ is called with descent elements
+			thus every problem 
+			$\PM{\pbmotif}{\ptext}{\lb}{*}{i'}{*}$ 
+			has the same lower bound as $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$.
+			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.
+
+			\item If $\pmotif[i]$ is an ascent element and $\pmotif[i']$ is an ascent element then
+			first remark that every problem 
+			$\PM{\pbmotif}{\ptext}{*}{\ub}{i'}{*}$ is true if $\sigma[i']$ occurs in $\lb$.
+			Now remark that
+			$i<i'$ and there is no  ascent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), 
+			Thus for every problem $\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ is called with descent elements
+			thus every problem 
+			$\PM{\pbmotif}{\ptext}{\lb}{*}{i'}{*}$ has same lower bound as $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$.
+			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.
+
 		\end{itemize}
@@
 
-	This section is devoted to finding longest $(213,231)$-avoiding subsequences in permutations:
+	This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
 	Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
 	in each input permutation.
+	This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$.
+Thus we focus on the cases where only one or two permutations are given in input.
 
@@
 the longest common subsequence
-avoiding (231,213) in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
+avoiding (213,231) in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
 \end{proposition}
@@
 that compute the longest stripe common to $\pi_1$ and $\pi_2$.
-Given two permutations $\pi_1$ and $\pi_2$.\\
+Given two permutations $\pi_1$ and $\pi_2$,\\
 
@@
 
-We show that this family of problems are closed under induction.\\
+We show that we can compute by induction the problem.\\
 
@@
 or we match as the same step (if possible).
-Those relations lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.
+These relations lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.
+Indeed there is $|\pi_1|^3|\pi_2|^3$ cases possible for the problem
+and each case is solved in constant time.
 $\qed$

### 2015-06-17 article.tex

@@
 
-\section{Computing the longest $(213,231)$-avoiding subsequence}
+\section{Computing the longest $(213,231)$-avoiding pattern}
 \label{section:LCS}
 
-	This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
-	Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
-	in each input permutation.
-	This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$.
+	This section is devoted to finding longest $(213,231)$-avoiding patterns 
+	in permutations.
+	We start with the easiest case where we are given just one input permutation
+	and we are asked to find the longest $(213,231)$-avoiding pattern that 
+	occurs in the input permutation.
+	% This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
+	% Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
+	% in each input permutation.
+	% This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$.
 Thus we focus on the cases where only one or two permutations are given in input.
 
-	We start with the easiest case where we are given just one input permutation.
 	We need the set of descent elements and the set of ascent elements.
@@
 \begin{proof}
-Consider the following problem,
-that compute the longest stripe common to $\pi_1$ and $\pi_2$.
-Given two permutations $\pi_1$ and $\pi_2$,\\
-
-$$
+Consider the following problem
+that computes the longest stripe common to $\pi_1$ and $\pi_2$:
+Given two permutations $\pi_1$ and $\pi_2$, we define
+$
 \LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
-$$
-\begin{center}
-= $\max$ \{$|s|$ $|$ $s$ occurs in $\pi_1[i_1:]$ with every element is in $[\lb_1,\ub_1]$ and $s$ occurs in $\pi_2[i_2:]$ with every element is in $[\lb_2,\ub_2]$ \}
-\end{center}
-
-We show that we can compute by induction the problem.\\
+=
+\max\{|s| \;|\; s \text{ occurs in } \pi_1[i_1:] \text{ with every element is in }
+[\lb_1,\ub_1] \text{ and } s \text{ occurs in } \pi_2[i_2:] \text{ with every element is in }
+[\lb_2,\ub_2]\}$.
+
+We show how to solve this problem by dynamic programming.
 

### 2015-06-18 article.tex
LNCS 12 pages + appendix

@@
 	improving the previous 30-year bound of $O(|\pi| \log |\sigma|)$.
-	(The algorithm also improves on the previous
-	$O(|\pi| \log \log |\pi|)$ bound.)
+	% (The algorithm also improves on the previous
+	% $O(|\pi| \log \log |\pi|)$ bound.)
 	Furthermore, the patterns $132$, $213$, $231$, $312$ can all be handled in linear-time
@@
 	(sequence A006318 in OEIS).
-	To the best of our knowledge,
-	separable permutations first arose in the work of
+	% To the best of our knowledge,
+	Separable permutations first arose in the work of
 	Avis and Newborn~\cite{Avis:Newborn:1981},
@@
  	the reverse of $\pi'$ avoids $213$.
- 	From a combinatorial point of view,
- 	B\'ona \cite{Bona:ElJC:2012}
- 	showed the rather surprising fact that the cumulative number of
- 	occurrences of the classical patterns $231$ and $213$ are the same on the
- 	set of permutations avoiding $132$,
- 	beside the pattern based statistics $231$ and $213$
- 	do not have the same distribution on this set.
- 	\emph{Almost avoidance} has also been considered;
- 	a permutation $\pi$ almost avoids a set $X$ of permutations
- 	if there is a way to remove a single element of $\pi$ to get a permutation
- 	that avoids all elements in $P$
- 	and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
- 	$P$.
- 	It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
- 	$L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
+ 	% From a combinatorial point of view,
+ 	% B\'ona \cite{Bona:ElJC:2012}
+ 	% showed the rather surprising fact that the cumulative number of
+ 	% occurrences of the classical patterns $231$ and $213$ are the same on the
+ 	% set of permutations avoiding $132$,
+ 	% beside the pattern based statistics $231$ and $213$
+ 	% do not have the same distribution on this set.
+ 	% \emph{Almost avoidance} has also been considered;
+ 	% a permutation $\pi$ almost avoids a set $X$ of permutations
+ 	% if there is a way to remove a single element of $\pi$ to get a permutation
+ 	% that avoids all elements in $P$
+ 	% and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
+ 	% $P$.
+ 	% It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
+ 	% $L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
 
@@
 	In Section~\ref{section:LCS} we consider the problem of finding the longest
-	$(213,231)$-avoiding pattern in a permutation.
-	In Section~\ref{section:LCS common 2 permutations} we give a
-	polynomial-time algorithm for computing the longest
-	$(213,231)$-avoiding pattern common to two permutations.
+	$(213,231)$-avoiding pattern that occurs in one or two permutations.
 
@@
 (or \emph{instance} or \emph{occurrence}) of $\sigma$.
-Since the permutation $\pi = 391867452$  contains no increasing subsequence of
-length four, $\pi$ avoids $1234$.
+% Since the permutation $\pi = 391867452$  contains no increasing subsequence of
+% length four, $\pi$ avoids $1234$.
 
@@
 
-\begin{proof}
-Any other initial element would serve as a `$2$' in either a
-$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
-\qed
-\end{proof}
-
 Notice that Lemma~\ref{lemma:first element is 1 or n} gives as an
@@
 \label{corollary:minmaxelement}
-$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$,
+Let $\pi \in S_n$. 
+Then,
+$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$
 $\pi[i]$ is the minimal or the maximal element of $\pi[i:]$.
@@
 Let $\pi \in \AV_n(213,231)$ and $1 \leq i < n$. Then,
-(1) 
-if $\pi[i]$ is an ascent element then $\pi[i]$ is the minimal element 
-of $\pi[i:]$
-and 
-(2)
-if if $\pi[i]$ is a descent element then $\pi[i]$ is the maximal element 
-of $\pi[i:]$
+if $\pi[i]$ is an ascent (resp. descent) element 
+then $\pi[i]$ is the minimal (resp. maximal) element 
+of $\pi[i:]$.
 \end{corollary}
@@
 
-\begin{proof}
-  The forward direction is obvious.
-  We prove the backward direction by induction on the size of the motif
-  $\sigma$.
-  The base case is a motif of size $2$.
-  Suppose first that $\sigma = 12$ and hence $s_\sigma = a$.
-  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-  such that $s_t$ occurs as a subsequence in $s_\pi$.
-  Since $s_\sigma = s_t = a$, this reduces to saying that
-  $\pi_{i_1} < \pi_{i_2}$, and hence $t$ is an occurrence of $\sigma = 12$ in $\pi$.
-  A similar argument shows that the lemma holds true for $\sigma = 21$.
-  Now, assume that the lemma is true for all motifs up to size $k \geq 2$.
-  Let $\sigma \in \Av{k+1}{231,213}$ and
-  let $t = \pi_{i_1}\pi_{i_2}\,\ldots\,\pi_{i_{k+1}}$,
-  $i_1 < i_2 < \ldots < i_{k+1}$,
-  be a subsequence of $\pi$ of length $k+1$ such that
-  $s_t = s_\sigma$.
-  Suppose that $s_t$ occurs in $s_\pi$ as a subsequence.
-  Then, $s_t[2:] = s_\sigma[2:]$ occurs as a subsequence in $s_\pi[2:]$.
-  But $\sigma[2:] \in \Av{k}{231,213}$ and hence,
-  by the inductive hypothesis, it follows that
-  $t[2:]$ is an occurrence of $\sigma[2:]$ in $\pi[2:]$.
-  Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
-  then $\sigma[1]$ is the minimal (resp. maximal) element of $\sigma$
-  (Lemma~\ref{lemma:first element is 1 or n}),
-  and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
-  $t[1]$ is the minimal (resp. maximal) element of $t$.
-  Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
-  \qed
-\end{proof}
-
 We are now ready to solve the pattern containment problem in case
@@
 
-\begin{proof}
-According to Lemma~\ref{lemma:MatchStripeToPermutation} the problem reduces
-to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$.
-A natural greedy approach solves this issue in linear-time.
-\qed
-% To solve the permutation pattern for a permutation in $\AV_n(213,231)$,
-% we find a find a match of the stripe of the pattern in the stripe of the text.
-% This can be done linearly by a greedy algorithm,
-% by matching a step whenever it is possible.
-% And thank to the definition of the definition of a stripe in
-% Corollary~\ref{corollary:minmaxelement},
-% we do not have to compute the stripe in advance.
-% Therefore we have an linear (online) algorithm.
-\end{proof}
-
 Observe that, according to Corollary~\ref{corollary:minmaxelement},
 the effective construction of the two stripes is not required in stretch 
-of algorithm given for the proof in the proposition \ref{Proposition:both permutations are avoiding},
+of algorithm given for the proof in 
+Proposition~
+\ref{Proposition:both permutations are avoiding},
 and hence we have an online algorithm.
@@
 
-\begin{proof}
-Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
-Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
-Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
-$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
-According to Lemma\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, and hence
-$\first{\sigma}{i-1}$ is the maximal  element of
-$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
-
-A similar argument shows that the lemma holds true if the rightmost element
-of $\factor{\sigma}{i}$ is a descent.
-\qed
-\end{proof}
-
-we now define the set
+We now define the set
 $\SET{\pmotif}{\ptext}{i}{j}$ as follows:
@@
 \begin{lemma}
+\label{lemma:ts}
 Let $\pmotif$ be a permutation , 
@@
 
-\begin{proof}
-By definition $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$.
-To prove that $ts$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ we prove that every element of t is larger than every element of $s$.
-If $ts'$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ so every element of $t$ is larger than every element of $s'$.
-Moreover the maximal element of $s$ is smaller than  the maximal element of $s'$ so every element of $s$ is smaller than every element of $s'$ thus every element of $s$ is smaller than every element of $t$.
-We use a similar argument if $\factor{\pmotif}{i}$ a descent factor.
-\qed
-\end{proof}
-
 \begin{corollary}
@@
 $s$ be a subsequence such that $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
-These following statements are equivalent :
-\begin{itemize}
-	\item There exists an 
-	occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs in $\ptext[j]$.
-	\item There exists a subsequence $t$ of $\ptext[1:j-1]$  such that $ts$ is an occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs in $\ptext[j]$. 
-\end{itemize}
+These following statements are equivalent:
+(1)
+There exists an 
+occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs in $\ptext[j]$,
+and (2)
+There exists a subsequence $t$ of $\ptext[1:j-1]$  such that $ts$ is 
+an occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs 
+in $\ptext[j]$. 
 \end{corollary}
@@
 
-% For the proof and the algorithm we introduce a decomposition : we decompose the stripe of the motif into factor of same letter, and label those factor from right to left.
+% For the proof and the algorithm we introduce a decomposition: we decompose the stripe of the motif into factor of same letter, and label those factor from right to left.
 We also need to add the last index into the first factor.
-For each factor, we denote the left most element by $\firsta$.
+For each factor, we denote the leftmost element by $\firsta$.
 For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$.
@@
 Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
-In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
+In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that: (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
 %
@@
 
-Consider the following problem :
+Consider the following problem:
 $$
@@
 
-\noindent\textbf{BASE :}
+\noindent\textbf{BASE:}
 \begin{align*}
@@
 the less restrictive (for the future matching)
-one must find the occurrence with the right most element
+one must find the occurrence with the rightmost element
 of the sequence minimal (resp. maximal).}
 \\
-\intertext{\textbf{STEP :}}
+\intertext{\textbf{STEP:}}
 \LM{\pmotif}{\ptext}{i}{j} 
@@
 be able to force elements to be consecutive in value or in position.
-Hence,  bivincular motif is stronger in constraint that motif by permutation, intuitively we can not use the previous algorithm.
-As in a $(213,231)$-avoiding permutation, we can describe structural property of a $(213,231)$-avoiding bivincular motif.
+Hence,  bivincular motif is stronger in constraint that motif by permutation, 
+intuitively we can not use the previous algorithm.
+As in a $(213,231)$-avoiding permutation, we can describe structural property of 
+a $(213,231)$-avoiding bivincular motif.
 
@@
 
-\begin{proof}
-Suppose that there exists $k$, $i<k<j$,
-such that $\pmotif[k]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[k]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
-We use a similar argument if $\sigma[i]$ is a descent element
-\qed
-\end{proof}
-
 \begin{proposition}
@@
 \begin{proof}
-We consider the following problem :
+We consider the following problem:
 Given $\pmotif$ a $(213,231)$-avoiding bivincular, and a text $\ptext \in \Av{n_\ptext}{231,213}$,
@@
 
-\noindent\textbf{BASE :} \\
+\noindent\textbf{BASE:} \\
 $$
@@
 
-\noindent\textbf{STEP :}
-
-We need to consider 3 cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ :
+\noindent\textbf{STEP:}
+
+We need to consider $3$ cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$:
 \begin{itemize}
-	\item If $\ptext[j] \notin [\lb,\ub]$ then :
-	$$
+	\item If $\ptext[j] \notin [\lb,\ub]$ then
+	$
 	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j} = false
-	$$
-
-	which is immediate from the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is in $[\lb,\ub]$.
-
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is an ascent element then :
+	$
+	which is immediate from the definition. 
+	If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an 
+	occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is 
+	in $[\lb,\ub]$.
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is an ascent element then:
 	$$
@@
 
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then :
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then:
 
@@
 	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must occur in the leftmost element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on an occurrence of $\pmotif$ in $\ptext$).
-This constraint is checked by requiring the occurrence to starts at the left most element of $\ptext$ : if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
+This constraint is checked by requiring the occurrence to starts at the leftmost element of $\ptext$: if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
 
@@
 
-		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the right most element).
+		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the rightmost element).
 Thus every $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ occurs in $1$.
-
 	\end{itemize}
@@
 
-		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the right most element).
+		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the rightmost element).
 Thus every $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ occurs in $n_{\ptext}$.
@@
 			Now remark that
-			$\pmotif[i]$ is the right most ascent element and $\pmotif[i']$ is the right most element (or $\pmotif[i'] \neq \pmotif[i]+1$). 
+			$\pmotif[i]$ is the rightmost ascent element and $\pmotif[i']$ is the rightmost element (or $\pmotif[i'] \neq \pmotif[i]+1$). 
 			As a consequence every problem $\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ is called with descent elements
@@
 			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.			
-
 		\end{itemize}
@@
 	occurs in the input permutation.
-	% This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
-	% Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
-	% in each input permutation.
-	% This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$.
-Thus we focus on the cases where only one or two permutations are given in input.
-
-	We need the set of descent elements and the set of ascent elements.
+	We need the set of descent elements and the set of ascent elements
 	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
@@
 
-	\begin{proof}
-	Let $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
-	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
-	Thus $|s_m|>|P(\pi)|$, clearly the sequence $s_m \cup M(\pi)$
-	is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
-	The same ideacan be used to show that $M(\pi)$ is the longest decreasing subsequence.
-	\qed
-	\end{proof}
-
 	\begin{proposition}
+	\label{proposition:longest 2}
 	Let $\pi$ be a permutation. One can compute the
@@
 	\end{proposition}
-
-	\begin{proof}
-	The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
-	where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
-	Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
-	$O(|\ptext|\log(\log(|\ptext|)))$ time and $O(n)$ space 
-	(see \cite{Bespamyatnikh00enumeratinglongest}), 
-	then finding the maximal can be done in linear time.
-	\qed
-	\end{proof}
 
@@
 
-\noindent\textbf{BASE :}
-
+\noindent\textbf{BASE:}
 $$
@@
 
-\noindent\textbf{STEP :}
-
+\noindent\textbf{STEP:}
 $$
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\section*{Appendix (Reviewers' version only)}
+
+\begin{proof}[of Lemma~\ref{lemma:first element is 1 or n}]
+Any other initial element would serve as a `$2$' in either a
+$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:MatchStripeToPermutation}]
+  The forward direction is obvious.
+  We prove the backward direction by induction on the size of the motif
+  $\sigma$.
+  The base case is a motif of size $2$.
+  Suppose first that $\sigma = 12$ and hence $s_\sigma = a$.
+  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
+  such that $s_t$ occurs as a subsequence in $s_\pi$.
+  Since $s_\sigma = s_t = a$, this reduces to saying that
+  $\pi_{i_1} < \pi_{i_2}$, and hence $t$ is an occurrence of $\sigma = 12$ in $\pi$.
+  A similar argument shows that the lemma holds true for $\sigma = 21$.
+  Now, assume that the lemma is true for all motifs up to size $k \geq 2$.
+  Let $\sigma \in \Av{k+1}{231,213}$ and
+  let $t = \pi_{i_1}\pi_{i_2}\,\ldots\,\pi_{i_{k+1}}$,
+  $i_1 < i_2 < \ldots < i_{k+1}$,
+  be a subsequence of $\pi$ of length $k+1$ such that
+  $s_t = s_\sigma$.
+  Suppose that $s_t$ occurs in $s_\pi$ as a subsequence.
+  Then, $s_t[2:] = s_\sigma[2:]$ occurs as a subsequence in $s_\pi[2:]$.
+  But $\sigma[2:] \in \Av{k}{231,213}$ and hence,
+  by the inductive hypothesis, it follows that
+  $t[2:]$ is an occurrence of $\sigma[2:]$ in $\pi[2:]$.
+  Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
+  then $\sigma[1]$ is the minimal (resp. maximal) element of $\sigma$
+  (Lemma~\ref{lemma:first element is 1 or n}),
+  and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
+  $t[1]$ is the minimal (resp. maximal) element of $t$.
+  Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
+  \qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}
+According to Lemma~\ref{lemma:MatchStripeToPermutation} the problem reduces
+to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$.
+A straightforward greedy approach solves this issue in linear-time.
+\qed
+% To solve the permutation pattern for a permutation in $\AV_n(213,231)$,
+% we find a find a match of the stripe of the pattern in the stripe of the text.
+% This can be done linearly by a greedy algorithm,
+% by matching a step whenever it is possible.
+% And thank to the definition of the definition of a stripe in
+% Corollary~\ref{corollary:minmaxelement},
+% we do not have to compute the stripe in advance.
+% Therefore we have an linear (online) algorithm.
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:whereIsMax}]
+Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
+Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
+Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
+$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
+According to Lemma~
+\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is 
+the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, 
+and hence
+$\first{\sigma}{i-1}$ is the maximal  element of
+$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
+
+A similar argument shows that the lemma holds true if the rightmost element
+of $\factor{\sigma}{i}$ is a descent.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:ts}]
+By definition $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$. 
+To prove that $ts$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$,
+we prove that every element of t is larger than every element of $s$. 
+If $ts'$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ so every element of $t$ 
+is larger than every element of $s'$. 
+Moreover, the maximal element of $s$ is smaller than  the maximal element of $s'$ 
+so every element of $s$ is smaller than every element of $s'$ thus every 
+element of $s$ is smaller than every element of $t$. We use a similar argument 
+if $\factor{\pmotif}{i}$ a descent factor.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:ascentDescentAscent}]
+Suppose that there exists $k$, $i<k<j$,
+such that $\pmotif[k]$ is ascent. 
+Ascent elements are increasing and hence $\sigma[i]<\sigma[k]<\sigma[j]$.
+This is a contradiction since $\sigma[j]=\sigma[i]+1$.
+
+We use a similar argument if $\sigma[i]$ is a descent element
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Proposition~\ref{proposition:longestIncreasingSubsequence}]
+Let $s$ be a longest subsequence avoiding both $213$ and $231$ 
+with last element at index $f$ in $\pi$,
+and
+suppose that $P(\pi)$ is not a longest increasing subsequence
+with last element at index $f$. 
+Let $s_m$ be a longest increasing subsequence with last element $f$.
+Thus $|s_m|>|P(\pi)|$, clearly the sequence $s_m \cup M(\pi)$
+is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
+
+The same idea can be used to show that $M(\pi)$ is the longest decreasing 
+subsequence.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Proposition~\ref{proposition:longest 2}]
+Proposition~\ref{proposition:longestIncreasingSubsequence} leads to an algorithm
+where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
+Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
+$O(|\ptext|\log(\log(|\ptext|)))$ time and $O(n)$ space 
+(see \cite{Bespamyatnikh00enumeratinglongest}), 
+then finding the maximal can be done in linear time.
+\qed
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2015-06-18 article.tex
LNCS 12 pages + appendix

@@
 	F-77454, Marne-la-Vallée, France\\
-  \email{\{neou,vialette\}@univ-mY.fr}
+  \email{\{neou,vialette\}@univ-mlv.fr}
   \and
@@
 
-A way to understand this lemma is if two ascent (resp. decsent) elements
-need to occur in consecutive elements in value then every element in $\pmotif$ which are between those two elements (if any) are descent (resp. ascent) elements.
+According to the above lemma,
+if two ascent (resp. decsent) elements
+have to occur in consecutive elements in value then every element in 
+$\pmotif$ which are between those two elements (if any) are descent (resp. ascent) 
+elements.
 

### 2015-06-18 article.tex
LNCS 12 pages + appendix

@@
 We consider the following problem:
-Given $\pmotif$ a $(213,231)$-avoiding bivincular, and a text $\ptext \in \Av{n_\ptext}{231,213}$,
+Given $\pmotif$ a $(213,231)$-avoiding bivincular, and a 
+text $\ptext \in \Av{n_\ptext}{231,213}$,
 $$
@@
 
-$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ can be solved by means by the following relations:
+$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ can be solved according to  
+the following relations:
 
@@
 The base case finds an occurrence for the rightmost element of the motif. 
-If the last element does not have any restriction on positions and on values, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ occurs in $\ptext[j]$.
+If the last element does not have any restriction on positions and on values, 
+then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if 
+$\pmotif[n_\pmotif]$ occurs in $\ptext[j]$. 
 This is true if $\ptext[j] \in [\lb,\ub]$.
@@
 	Remark that $\pmotif[i]$ occurs in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
-	Thus if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ with every element in $[\pmotif[i]+1,\ub]$ then 
+	Thus if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ with every element 
+	in $[\pmotif[i]+1,\ub]$ then 
  	$\pmotif[i:]$ occurs in $\ptext[j:]$  	
@@
 	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then:
-
 	$$
@@
 
-	\item If ${\pmotif[i]}^\urcorner$ (and thus $\sigma[i]=n_\pmotif$) then the maximal value of $\pmotif$ must occur in the maximal value of $\ptext$.
+	\item If ${\pmotif[i]}^\urcorner$ (and thus $\sigma[i]=n_\pmotif$) 
+	then the maximal value of $\pmotif$ must occur in the maximal value of $\ptext$.
 	\begin{itemize}
@@
 		every problem 
-		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ occurs in element $\ub$ thus it is enough to require that $\ub=n_{\ptext}$.
-		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal element.
-As a consequence every problem $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ is called with ascent elements thus every problem
-		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ has same upper bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ thus for every $\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$,
+		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ occurs 
+		in element $\ub$ thus it is enough to require that $\ub=n_{\ptext}$.
+		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if it is not
+		then there exists an descent element $\sigma[i']$, $i'<i$ and by definition 
+		$\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal
+		element. 
+		As a consequence every problem 
+		$\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$, $\dots$, 
+		$\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ 
+		is called with ascent elements thus every problem 
+		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ 
+		has same upper bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ 
+		thus for every $\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$,
 		$\ub=n_{\ptext}$.
@@
 
-	\item  If $\overline{\pmotif[i]\pmotif[i']}$,  (which implies that $\pmotif[i']=\pmotif[i]+1$) then if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i']$ must occur in $\ptext[j]+1$.
+	\item  If $\overline{\pmotif[i]\pmotif[i']}$
+	(which implies that $\pmotif[i']=\pmotif[i]+1$), 
+	then if $\pmotif[i]$ occurs in $\ptext[j]$ 
+	then $\pmotif[i']$ must occur in $\ptext[j]+1$.
 		\begin{itemize}
@@
 
-			\item If $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i'<i$), then
+			\item If $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element 
+			and $i<i'$ (remark that this case is symmetric to the case $\pmotif[i]$ 
+			is a descent element, $\pmotif[i']$ is an ascent element and $i'<i$), then
 			remark that every problem 
@@
 			$\pmotif[i]$ is the rightmost ascent element and $\pmotif[i']$ is the rightmost element (or $\pmotif[i'] \neq \pmotif[i]+1$). 
-			As a consequence every problem $\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ is called with descent elements
+			As a consequence every problem 
+			$\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ 
+			is called with descent elements
 			thus every problem 
@@
 			has the same lower bound as $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$.
-			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.
+			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  
+			$\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.
 

### 2015-10-08 article.tex
midif reviews

--- 2015-06-18 article.tex
@@
 
+\usepackage{tikz}
+\usetikzlibrary{patterns}
+\usepackage{subcaption} 
+\captionsetup{compatibility=false}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% permutation motif
-\newcommand{\pmotif}{\sigma}
+\newcommand{\bijection}{B}
+
+% permutation pattern
+\newcommand{\ppattern}{\sigma}
 
@@
 
-\DeclareMathOperator{\factora}{factor}
-\newcommand{\factor}[2]{\factora_{{#1}}({#2})}
+%\DeclareMathOperator{\run}{run}
+\DeclareMathOperator{\block}{block}
+\DeclareMathOperator{\LMEi}{LMEi}
+
+\DeclareMathOperator{\factor}{factor}
+%\newcommand{\factor}[2]{\factora_{{#1}}({#2})}
 
@@
 \newcommand{\y}{Y}
-\newcommand{\bmotif}{(\sigma,\x,\y)}
-
-\newcommand{\pbmotif}{\pmotif^+}
-\newcommand{\pbmotifX}{\x_{\pbmotif}}
-\newcommand{\pbmotifY}{\y_{\pbmotif}}
+\newcommand{\bpattern}{(\sigma,\x,\y)}
+
+\newcommand{\sigmaX}{\x_{\sigma}}
+\newcommand{\sigmaY}{\y_{\sigma}}
 
@@
 
-\title{Pattern matching for\\ $(213,231)$-avoiding permutations}
+\title{Pattern matching in\\ $(213,231)$-avoiding permutations}
 \author{Both Emerite NEOU, Romeo RIZZI}
@@
 \begin{abstract}
-	Given permutations $\sigma \in S_k$ and $\pi \in S_n$, the
-  \emph{pattern containment} problem is to decide whether $\pi$ contains
+	Given permutations $\sigma \in S_k$ and $\pi \in S_n$ with $k<n$, the
+  \emph{pattern matching} problem is to decide whether $\pi$ matches
   $\sigma$ as an order-isomorphic subsequence.
@@
 	the two size-$3$ permutations $213$ and $231$.
-	For the special where only $\sigma$ avoids $213$ and $231$, we present a
-	$O(kn^2)$ time algorithm. 
-	Finally We extend our research to bivincular pattern that avoid $213$ and $231$
-	 and present a $O(kn^5)$ time algorithm.
+	For the special case where only $\sigma$ avoids $213$ and $231$, we present a
+	$O(max(kn^2,n^2\log(\log(n)))$ time algorithm. 
+	We extend our research to bivincular patterns that avoid $213$ and $231$ and present a $O(kn^4)$ time algorithm.
+	Finally we look at the related problem of the longest subsequence which avoids $213$ and $231$.  
 \end{abstract}
@@
 
-	A permutation $\pi$ is said to contain another permutation $\sigma$,
+	A permutation $\pi$ is said to match another permutation $\sigma$,
 	in symbols $\sigma \preceq \pi$,
-	if there exists a subsequence of entries of $\pi$ that has the same relative
-	order as $\sigma$, and in this case $\sigma$ is said to be a
-	\emph{pattern} of $\pi$.
+	if there exists a subsequence of elements of $\pi$ that has the same relative
+	order as $\sigma$.
 	Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
-	For example a permutation contains the pattern $123$ (resp. $321$) if it has
+	For example a permutation matches the pattern $123$ (resp. $321$) if it has
 	an increasing (resp. decreasing) subsequence of length $3$.
-	Here, note that members need not actually to be consecutive,
-	merely increasing (resp. descreasing).
 	As another example,
-	$6152347$ contains $213$ but not $231$.
-	During the last decade, the study of the pattern containment on permutations has
+	$6152347$ matches $213$ but not $231$.
+	During the last decade, the study of the pattern matching on permutations has
 	become a very active area of research \cite{Kitaev:book:2011} and
@@
 
-	We consider here the so-called \emph{pattern containment} problem
+	We consider here the so-called \emph{pattern matching} problem
 	(also sometimes referred to as the \emph{pattern involvement problem}):
@@
 	$\sigma \preceq \pi$ (the problem is ascribed to Wilf in \cite{Bose:Buss:Lubiw:1998}).
-	The permutation containment problem is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
+	The permutation matching problem is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
 	It is, however, polynomial-time solvable by brute-force enumeration
@@
 	the latter describing a $O(|\pi|^{0.47|\sigma|+o(|\sigma|)})$ time algorithm.
-	Bruner and Lackner \cite{Bruner:Lackner:SWAT:2012}
-	gave a fixed-parameter algorithm solving the pattern containment problem with
+	Bruner and Lackner $\cite{DBLP:journals/corr/abs-1204-5224}$
+	gave a fixed-parameter algorithm solving the pattern matching problem with
 	an exponential worst-case runtime of $O(1.79^{\RUN(\pi)})$,
@@
 	brute-force search without imposing restrictions on $\sigma$ and $\pi$.)
-	A recent major step was taken by􏰂 Marx and Guillemot
+	A recent major step was taken by Marx and Guillemot
 	\cite{Guillemot:Marx:SODA:2014}.
 	They showed that
-	the permutation containment problem is fixed-parameter tractable (FPT) for
+	the permutation matching problem is fixed-parameter tractable (FPT) for
 	parameter $|\sigma|$.
 
-	A few particular cases of the pattern containment problem have been attacked successfully.
+	A few particular cases of the pattern matching problem have been attacked successfully.
 	The case of increasing patterns is solvable in
@@
 	improving the previous 30-year bound of $O(|\pi| \log |\sigma|)$.
-	% (The algorithm also improves on the previous
-	% $O(|\pi| \log \log |\pi|)$ bound.)
+	(The algorithm also improves on the previous
+	$O(|\pi| \log \log |\pi|)$ bound).
 	Furthermore, the patterns $132$, $213$, $231$, $312$ can all be handled in linear-time
@@
 	\cite{Albert:Aldred:Atkinson:Holton:ISAAC:2001}.
-	Algorithmic issues for $321$-avoiding patterns containment has been investigated in
+	Algorithmic issues for $321$-avoiding patterns matching has been investigated in
 	\cite{Guillemot:Vialette:ISAAC:2009}.
-	The pattern containment problem is also solvable in
+	The pattern matching problem is also solvable in
 	polynomial-time for separable patterns \cite{Ibarra:1997,Bose:Buss:Lubiw:1998}
@@
 	of separable permutations).
-	Separable permutations are those permutations that contain neither
+	Separable permutations are those permutations that match neither
 	$2413$ nor $3142$, and they are enumerated by the Schr{\"o}der numbers
-	(sequence A006318 in OEIS).
+%	(sequence A006318 in OEIS).
 %	To the best of our knowledge,
-	Separable permutations first arose in the work of
-	Avis and Newborn~\cite{Avis:Newborn:1981},
-	who showed that they are precisely the permutations which can be sorted by an
-	arbitrary number of pop-stacks in series,
-	where a pop-stack is a restricted form of stack in which any pop operation
-	pops all items at once.
+%	separable permutations first arose in the work of
+%	Avis and Newborn~\cite{Avis:Newborn:1981},
+%	who showed that they are precisely the permutations which can be sorted by an
+%	arbitrary number of pop-stacks in series,
+%	where a pop-stack is a restricted form of stack in which any pop operation
+%	pops all items at once.
 	(Notice that the separable permutations include as a special case the
@@
 
-	There exist many generalisation of patterns that are worth considering
-	in the context of algorithmic issues in pattern involvement
+	There exists many generalisation of patterns that are worth considering
+	in the context of algorithmic issues in pattern matching
 	(see \cite{Kitaev:book:2011} for an up-to-date survey).
@@
 	\emph{generalized patterns},
-	resemble (classical) patterns with the additional constraint that some of the letters in
-	an occurrence must be consecutive.
+	resemble (classical) patterns with the additional constraint that some of the elements in
+	a matching must be consecutive in postitions.
 	Of particular importance in our context,
-	Bruner and Lackner \cite{Bruner:Lackner:SWAT:2012}
+	Bruner and Lackner \cite{DBLP:journals/corr/abs-1204-5224}
 	proved that deciding whether a vincular pattern
-	$\sigma$ of length $k$ occurs in a longer permutation
+	$\sigma$ of length $k$ can be match to a longer permutation
 	$\pi$ is $W[1]$-complete for
@@
 	than vincular
-	patterns. Indeed, in bivincular patterns,
-	not only positions but also values
-	of elements involved in a matching may be forced to be adjacent
+	patterns by adding a constraint on values.
 
@@
 	On an individual basis,
-	the permutations that do not contain the permutation pattern $231$
+	the permutations that do not match the permutation pattern $231$
 	are exactly the \emph{stack-sortable permutations} and they are counted by
@@
  	the reverse of $\pi'$ avoids $213$.
- 	% From a combinatorial point of view,
- 	% B\'ona \cite{Bona:ElJC:2012}
- 	% showed the rather surprising fact that the cumulative number of
- 	% occurrences of the classical patterns $231$ and $213$ are the same on the
- 	% set of permutations avoiding $132$,
- 	% beside the pattern based statistics $231$ and $213$
- 	% do not have the same distribution on this set.
- 	% \emph{Almost avoidance} has also been considered;
- 	% a permutation $\pi$ almost avoids a set $X$ of permutations
- 	% if there is a way to remove a single element of $\pi$ to get a permutation
- 	% that avoids all elements in $P$
- 	% and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
- 	% $P$.
- 	% It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
- 	% $L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
+ 	From a combinatorial point of view,
+ 	B\'ona \cite{Bona:ElJC:2012}
+ 	showed the rather surprising fact that the cumulative number of
+ 	matching of the classical patterns $231$ and $213$ are the same on the
+ 	set of permutations avoiding $132$,
+ 	beside the pattern based statistics $231$ and $213$
+ 	do not have the same distribution on this set.
+ 	\emph{Almost avoidance} has also been considered;
+ 	a permutation $\pi$ almost avoids a set $X$ of permutations
+ 	if there is a way to remove a single element of $\pi$ to get a permutation
+ 	that avoids all elements in $P$
+ 	and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
+ 	$P$.
+ 	It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
+ 	$L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
 
 	This paper is organized as follows.
-	In Section~\ref{section:Definitions} the needed definition are presented.
+	In Section~\ref{section:Definitions} the needed definitions are presented.
 	Section~\ref{section:both are (213,231)-avoiding} is devoted to presenting
-	an online linear-time algorithm in case both the pattern and the target
-	permutation are $(213,231)$-avoiding,
+	an online linear-time algorithm in case both 
+	permutations are $(213,231)$-avoiding,
 	whereas Section~\ref{section:sigma only avoid 231 and 213} focuses on the case
-	where the pattern only is $(213,231)$-avoiding.
+	where only the pattern is $(213,231)$-avoiding.
 	In Section~\ref{section:bivincular} we give a polynomial-time algorithm
@@
 	In Section~\ref{section:LCS} we consider the problem of finding the longest
-	$(213,231)$-avoiding pattern that occurs in one or two permutations.
+	$(213,231)$-avoiding pattern in permutations.
 
@@
 We write permutations as words
-$\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose letters are distinct
-and uasually consist of the integers $12\,\ldots\,n$, and we let
+$\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose elements are distinct
+and usually consist of the integers $12\,\ldots\,n$, and we let
 $\pi[i]$ stands for $\pi_i$.
@@
 As usual, we let $S_n$ denote the set of all permutations of length $n$.
+It is convenient to use a geometric representation of permutation
+to ease the understanding of algorithms. 
+The geometric representation corresponds to the set of point with coordinate $(i,\pi[i])$
+(see figure \ref{example: pattern matching}).
 
@@
 
-A permutation $\pi$ is said to \emph{contain} the permutation $\sigma$
+A permutation $\pi$ is said to \emph{match} the permutation $\sigma$
 if there exists a subsequence of (not necessarily consecutive)
-entries of $\pi$ that has the same relative order as $\sigma$,
-and in this case $\sigma$ is said to be a \emph{pattern} of
-$\pi$, written $\sigma \preceq \pi$.
+element of $\pi$ that has the same relative order as $\sigma$,
+and in this case $\pi$ is said to match $\sigma$, 
+written $\sigma \preceq \pi$.
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
 For example, the permutation $\pi = 391867452$
-contains the pattern $\sigma = 51342$,
+matches the pattern $\sigma = 51342$,
 as can be seen in the highlighted subsequence of
@@
 or
-$\pi = 3\mathbf{9}\mathbf{1}8\mathbf{6}\mathbf{7}45\mathbf{2}$
+$\pi = 3\mathbf{9}\mathbf{1}8\mathbf{6}\mathbf{7}45\textbf{2}$
+or
+$\pi = 3\mathbf{9}\mathbf{1}867\textbf{4}\textbf{5}\mathbf{2}$
 ).
@@
 $91675$,
-$91672$ in $\pi$ is called a
-\emph{copy},
-(or \emph{instance} or \emph{occurrence}) of $\sigma$.
-% Since the permutation $\pi = 391867452$  contains no increasing subsequence of
-% length four, $\pi$ avoids $1234$.
+$91672$,
+$91452$,
+ in $\pi$ is called a
+\emph{matching}
+of $\sigma$.
+Since the permutation $\pi = 391867452$  contains no increasing subsequence of
+length four, $\pi$ avoids $1234$.
+Geometrically, $\pi$ matches $\sigma$ if there exists
+a set of point in $\pi$ that is isomorph to the set of point of $\sigma$. In other word,
+if there exists a set of point in $\pi$ with the same disposition as the set of point of $\sigma$, without regard to the distance (see figure \ref{example: pattern matching}).
+
+\begin{figure}
+	\centering
+		\begin{tikzpicture}[scale=.25]
+		\draw (0,0) -- (5,0) -- (5,5) -- (0,5) -- cycle;
+		\foreach \i in {1, 2, 3, 4, 5}{
+			\draw[dotted] (0,\i) -- (5, \i);
+			\draw[dotted] (\i,0) -- (\i, 5);
+		}
+		\draw[fill=black] (0.5,4.5) circle (2mm);
+		\draw[fill=black] (1.5,0.5) circle (2mm);
+		\draw[fill=black] (2.5,2.5) circle (2mm);
+		\draw[fill=black] (3.5,3.5) circle (2mm);
+		\draw[fill=black] (4.5,1.5) circle (2mm);
+		\end{tikzpicture} 
+		\begin{tikzpicture}[scale=.25]
+		\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+		\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+			\draw[dotted] (0,\i) -- (9, \i);
+			\draw[dotted] (\i,0) -- (\i, 9);
+		}
+		\draw[fill=black] (0.5,2.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (1.5,8.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (2.5,0.5) circle (2mm);
+		\draw[fill=black] (3.5,7.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (4.5,5.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (5.5,6.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (6.5,3.5) circle (2mm);
+		\draw[fill=black] (7.5,4.5) circle (2mm);
+		\draw[fill=black] (8.5,1.5) circle (2mm);
+		\end{tikzpicture}
+		\begin{tikzpicture}[scale=.25]
+		\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+		\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+			\draw[dotted] (0,\i) -- (9, \i);
+			\draw[dotted] (\i,0) -- (\i, 9);
+		}
+		\draw[fill=black] (0.5,2.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (1.5,8.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (2.5,0.5) circle (2mm);
+		\draw[fill=black] (3.5,7.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (4.5,5.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (5.5,6.5) circle (2mm);
+		\draw[fill=black] (6.5,3.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (7.5,4.5) circle (2mm);
+		\draw[fill=black] (8.5,1.5) circle (2mm);
+		\end{tikzpicture}
+		\begin{tikzpicture}[scale=.25]
+		\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+		\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+			\draw[dotted] (0,\i) -- (9, \i);
+			\draw[dotted] (\i,0) -- (\i, 9);
+		}
+		\draw[fill=black] (0.5,2.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (1.5,8.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (2.5,0.5) circle (2mm);
+		\draw[fill=black] (3.5,7.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (4.5,5.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (5.5,6.5) circle (2mm);
+		\draw[fill=black] (6.5,3.5) circle (2mm);
+		\draw[fill=black] (7.5,4.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (8.5,1.5) circle (2mm);
+		\end{tikzpicture}		
+		\begin{tikzpicture}[scale=.25]
+		\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+		\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+			\draw[dotted] (0,\i) -- (9, \i);
+			\draw[dotted] (\i,0) -- (\i, 9);
+		}
+		\draw[fill=black] (0.5,2.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (1.5,8.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (2.5,0.5) circle (2mm);
+		\draw[fill=black] (3.5,7.5) circle (2mm);
+		\draw[fill=black] (4.5,5.5) circle (2mm);
+		\draw[fill=black] (5.5,6.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (6.5,3.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (7.5,4.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (8.5,1.5) circle (2mm);
+		\end{tikzpicture}
+
+	\caption[Example pattern matching]{
+		The pattern $\sigma=51342$
+		and four matchings of $\sigma$ in $391867452$.} 
+	\label{example: pattern matching}
+\end{figure}
 
@@
 (and as it is customary~\cite{Kitaev:book:2011}), we omit $P$'s braces thus having
-e.g. $\AV_3(213,231)$ instead of
-$\AV_3(\{213,231\})$.
+e.g. $\AV_n(213,231)$ instead of
+$\AV_n(\{213,231\})$.
 If $\pi \in \AV_n(P)$, we also say that $\pi$ is
@@
 
-An \emph{ascent} of a permutation $\pi \in S_n$ is any position
+An \emph{ascent} of a permutation $\pi \in S_n$ is any element
 $1 \leq i < n$ where the following value is bigger than the current one.
 That is, if $\pi = \pi_1\pi_2\,\ldots\,\pi_n$, then
-$i$ is an ascent if $\pi_i < \pi_{i+1}$.
+$\pi_i$ is an ascent if $\pi_i < \pi_{i+1}$.
 For example, the permutation
-$345216$7 has ascents (at positions) $1,2,5$ and $6$.
-Similarly, a \emph{descent} is a position
+$3452167$ has ascents $3$, $4$, $1$ and $6$.
+Similarly, a \emph{descent} is any element
 $1 \leq i < n$ with $\pi_i > \pi_{i+1}$,
-so every $1 \leq i < n$  is either an ascent or is a descent of
+so for every $1 \leq i < n$, $\pi_i$  is either an ascent or is a descent of
 $\pi$.
-To clarify the exposition,
-we let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
-The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
-$\stripe{\pi}{1} \stripe{\pi}{2} \ldots \stripe{\pi}{n-1} \in \{\ustep,\dstep\}^{n-1}$
-defined by
-$ \stripe{\pi}{i}= \ustep$ if $i$ an ascent in $\pi$ and
-$\stripe{\pi}{i} = \dstep$ if $i$ a descent in $\pi$.
-For example the stripe of the permutation
-$\pi = 981234765$
-is $\stripew{\pi} = \dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep$.
-The stripe $\stripew{\sigma}$ is said to be a \emph{pattern} of the stripe $\stripew{\pi}$
-(or $\stripew{\sigma}$ \emph{occurs} of the stripe $\stripew{\pi}$)
-if $\stripew{\sigma}$ occurs in $\stripew{\pi}$ as a subsequence.
-
-A \emph{bivincular pattern} (abbreviated BVP) $\sigma$
+%To clarify the exposition,
+%we let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
+%The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
+%$\stripe{\pi}{1} \stripe{\pi}{2} \ldots \stripe{\pi}{n-1} \in \{\ustep,\dstep\}^{n-1}$
+%defined by
+%$\stripe{\pi}{i}= \ustep$ if $i$ an ascent in $\pi$ and
+%$\stripe{\pi}{i} = \dstep$ if $i$ a descent in $\pi$.
+%For example the stripe of the permutation
+%$\pi = 981234765$
+%is $\stripew{\pi} = \dstep\dstep\ustep\ustep\ustep\ustep\dstep\dstep$.
+
+A $\textit{left to right maxima}$ (abbreviate LRMax) of $\pi$ is a element that does not have any element bigger than it on its right (see fig.
+$\ref{fig:left to right maxima}$).
+Formally, $\pi[i]$ is a LRMax if and only if $\pi[i]$ is the biggest element of $\pi[i:]$.
+Similarly $\pi[i:]$ is a $\textit{left to right minima}$ (abbreviate LRMin) if and only if $\pi[i]$ is the smallest element of $\pi[i:]$.
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[scale=.25]
+	\foreach \i in {1, 2, 3, 4}{
+		\draw[dotted] (0,\i) -- (5, \i);
+		\draw[dotted] (\i,0) -- (\i, 5);
+	}
+	\draw[fill=black] (2.5,2.5) circle (2mm);
+	%\draw (2.5,2.5) -- (2.5,6.5);
+	%\draw (2.5,2.5) -- (6,2.5);
+
+	\draw [pattern=north east lines] (2.5,2.5) rectangle (6,6);
+
+	\end{tikzpicture}
+
+	\caption[Example pattern matching]{
+		The element is a LRMax if and only if the dashed area is empty.} 
+	\label{fig:left to right maxima}
+\end{figure}
+
+A \emph{bivincular pattern} $\sigma$
 of length $k$ is a permutation in $S_k$ written in
@@
 We have the following conditions on the top and bottom rows
-of $\sigma$:
+of $\sigma$, as see in \cite{Kitaev:book:2011} in definition 1.4.1:
 \begin{itemize}
@@
 	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
-	then the letters corresponding to
-	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
-	$\sigma$ in a permutation must be adjacent, whereas there is
+	then the elements corresponding to
+	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in a matching of
+	$\sigma$ in $\pi$ must be adjacent, whereas there is
 	no adjacency condition for
-	non-underlined consecutive letters.
+	non-underlined consecutive elements.
 	Moreover if the bottom row of $\sigma$ begins with
-	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$
+	$_\llcorner{\sigma_1}$ then any matching of $\sigma$
 	in a permutation $\pi$ must begin with the leftmost
-	letter of $\pi$,
+	element of $\pi$,
 	and
 	if the bottom row of $\sigma$ begins with
-	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$
+	${\sigma_k}_\lrcorner$ then any matching of $\sigma$
 	in a permutation $\pi$ must end with the rightmost
-	letter of $\pi$.
+	element of $\pi$.
 	\item
 	If the top line of $\sigma$ contains
-	$\overline{i\,i+1\,\ldots\,j}$ then the letters corresponding to
-	$\sigma_i, \sigma_{i+1}, \ldots, \sigma_j$ in an
-	occurrence of $\sigma$ in a permutation must be adjacent in values,
+	$\overline{i\,i+1\,\ldots\,j}$ then the elements corresponding to
+	$i, i+1, \ldots, j$ in an
+	matching of $\sigma$ in $\pi$ must be adjacent in values,
 	whereas there is no value adjacency restriction for non-overlined
-	letters.
+	elements.
 	Moreover, if the top row of $\sigma$ begins with
 	$^\ulcorner{1}$ then
-	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
-	the smallest letter of $\pi$, and
+	any matching of $\sigma$ is a permutation $\pi$ must contain 
+	the smallest element of $\pi$, and
 	if top row of $\sigma$ ends with $k^\urcorner$ then
-	any occurrence of $\sigma$ is a permutation $\pi$ must end with
-	the largest letter of $\pi$.
+	any matching of $\sigma$ is a permutation $\pi$ must contain
+	the largest element of $\pi$.
+
 \end{itemize}
+
 For example,
 let
-$\sigma = \BV{\overline{123}}{\llcorner 213 \lrcorner}$.
-If $\pi_i\pi_j\pi_\ell$ is an occurrence of $\sigma$ in $\pi \in S_n$,
-then $\pi_i\pi_j\pi_k = (x+1)x(x+2)$ for some $1 \leq x \leq n-2$,
-$i=1$ and $\ell = n$.
-For example $316524$ contains one occurrence of $\sigma$ (the subsequence $324$),
-whereas $42351$ avoids it.
-It is straightforward to see that an $n$-permutation
-$\pi$ avoids $\BV{\overline{123}}{\llcorner 213 \lrcorner}$ unless
-$n \geq 3$,
-$\pi_1 = x > 1$
-and $\pi_n = x+1$
-(in which case there is one occurrence of the pattern).
+$\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$.
+In $3217845$, $\textbf{32}17\textbf{84}5$ is a matching of $\sigma$ but
+ $3\textbf{21}\textbf{7}8\textbf{4}5$ is not.
 The best general reference is \cite{Kitaev:book:2011}.
 
-%For algorithmic treatment, it will be convenient to have \ldots
-%Given a motif $\pmotif$ we represent the elements underlined by the set $\x$.
-An index $i$, $1 \leq i < |\sigma|$, of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
-We also allow $0$ and $|\sigma|$ to be in the set $\x$ such that if $0 \in \x$ then we have $_\llcorner{\sigma_1}$ and if $|\sigma| \in \x$ then ${\sigma_{|\sigma|}}_\lrcorner$.
-%We represent the index that need to be overlined by the set $\y$.
-An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
-We also allow $0$ and $|\sigma|$ to be in the set $\y$ such that if $0 \in \y$ then we have $^\ulcorner{1}$ and if $|\sigma| \in \y$ then ${|\sigma|}^\urcorner$.
-
-% A bivincular pattern avoids a set of permutations $P$ if its bottom
-% row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.
+Geometrically, We represent underlined and overlined elements by \textit{forbidden areas}.
+A vertical area between two points indicates that the two matching of those points must be consecutive in positions, whereas a horizontal area between two points indicates that the two  matching of those points must be consecutive in value.
+The forbidden areas can be understand as follow : in a matching, the forbidden areas must be empty.
+Thus,
+$\pi$ matches a bivincular pattern $\sigma$ if there exists a set of point in $\pi$ that is isomorph to $\sigma$ and if
+the forbidden areas are empty.
+(see figure \ref{example:bivincular pattern matching}).
+
+\begin{figure}[t] 
+	\centering
+
+    	\begin{tikzpicture}[scale=.5]
+    	\draw [pattern=north east lines] (0,1.5) rectangle (4,2.5);
+    	\draw [pattern=north east lines] (0,3.5) rectangle (4,4);
+
+    	\draw [pattern=north west lines] (0,0) rectangle (0.5,4);
+    	\draw [pattern=north west lines] (2.5,0) rectangle (3.5,4);
+
+    	\draw (0,0) -- (4,0) -- (4,4) -- (0,4) -- cycle;
+    	\foreach \i in {1, 2, 3, 4}{
+    		\draw[dotted] (0,\i) -- (4, \i);
+    		\draw[dotted] (\i,0) -- (\i, 4);
+    	}
+    	\draw[fill=black] (0.5,1.5) circle (2mm);
+    	\draw[fill=black] (1.5,0.5) circle (2mm);
+    	\draw[fill=black] (2.5,3.5) circle (2mm);
+    	\draw[fill=black] (3.5,2.5) circle (2mm);
+    	\end{tikzpicture}
+    	\quad
+    	\begin{tikzpicture}[scale=.5]
+    	\draw [pattern=north east lines] (0,6.5) rectangle (7,7);
+    	\draw [pattern=north east lines] (0,2.5) rectangle (7,3.5);
+
+    	\draw [pattern=north west lines] (0,0) rectangle (0.5,7);
+    	\draw [pattern=north west lines] (4.5,0) rectangle (5.5,7);
+
+    	%$3217845$
+
+    	\draw (0,0) -- (7,0) -- (7,7) -- (0,7) -- cycle;
+    	\foreach \i in {1, 2, 3, 4, 5, 6, 7}{
+    		\draw[dotted] (0,\i) -- (7, \i);
+    		\draw[dotted] (\i,0) -- (\i, 7);
+    	}
+
+		\draw[fill=black,double, double distance=1pt] (0.5,2.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (1.5,1.5) circle (2mm);
+		\draw[fill=black] (2.5,0.5) circle (2mm);
+		\draw[fill=black] (3.5,5.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (4.5,6.5) circle (2mm);
+		\draw[fill=black,double, double distance=1pt] (5.5,3.5) circle (2mm);
+		\draw[fill=black] (6.5,4.5) circle (2mm);
+
+    	\end{tikzpicture}  
+    	\quad
+    	\begin{tikzpicture}[scale=.5]
+    	\draw [pattern=north east lines] (0,5.5) rectangle (7,7);
+    	\draw [pattern=north east lines] (0,2.5) rectangle (7,3.5);
+
+    	\draw [pattern=north west lines] (0,0) rectangle (1.5,7);
+    	\draw [pattern=north west lines] (3.5,0) rectangle (5.5,7);
+
+    	%$3217845$
+
+    	\draw (0,0) -- (7,0) -- (7,7) -- (0,7) -- cycle;
+    	\foreach \i in {1, 2, 3, 4, 5, 6, 7}{
+    		\draw[dotted] (0,\i) -- (7, \i);
+    		\draw[dotted] (\i,0) -- (\i, 7);
+    	}
+
+    	\draw[fill=black] (0.5,2.5) circle (2mm);
+    	\draw[fill=black,double, double distance=1pt] (1.5,1.5) circle (2mm);
+    	\draw[fill=black,double, double distance=1pt] (2.5,0.5) circle (2mm);
+    	\draw[fill=black,double, double distance=1pt] (3.5,5.5) circle (2mm);
+    	\draw[fill=black] (4.5,6.5) circle (2mm);
+    	\draw[fill=black,double, double distance=1pt] (5.5,3.5) circle (2mm);
+    	\draw[fill=black] (6.5,4.5) circle (2mm);
+
+    	\end{tikzpicture}
+
+    	\caption[Example pattern matching]{
+    		From left to right,
+    		the bivincular pattern $\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$, A matching of $\sigma$ in $3216745$, A matching of $2143$ in $3216745$ but not a matching of $\sigma$ in $3216745$ because the point $(1,3)$ and $(5,7)$ are in the forbidden area.}
+    	\label{example:bivincular pattern matching}
+\end{figure}
 
@@
 The first element of any $(213,231)$-avoiding permutation
-must be either $1$ or $n$.
+must be either the minimal or the maximal element.
 \end{lemma}
 
-Notice that Lemma~\ref{lemma:first element is 1 or n} gives as an
-immediate consequence that the number of $(213,231)$-avoiding $n$-permutations
-is $2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
-The above structural lemma gains in interest in the form of the following corollaries.
+\begin{proof}
+Any other initial element would serve as a `$2$' in either a
+$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+\qed
+\end{proof}
 
@@
 \label{corollary:minmaxelement}
-Let $\pi \in S_n$. 
-Then,
-$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$
-$\pi[i]$ is the minimal or the maximal element of $\pi[i:]$.
+$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i < n$,
+$\pi[i]$ is a LRMax or a LRMin.
 \end{corollary}
@@
 Let $\pi \in \AV_n(213,231)$ and $1 \leq i < n$. Then,
-if $\pi[i]$ is an ascent (resp. descent) element 
-then $\pi[i]$ is the minimal (resp. maximal) element 
-of $\pi[i:]$.
+(1) 
+$\pi[i]$ is an ascent element if and only if $\pi[i]$ is a LRMin
+and 
+(2)
+$\pi[i]$ is a descent element if and only if $\pi[i]$ is a LRMax
 \end{corollary}
 
-%\begin{corollary}
-%
-%If $\pi \in \Av{n}{(231,213)}$ its stripe can be define such as, \\
-%$\stripe{\pi}{i} = \left\{
-%	\begin{array}{l l}
-%			\ustep & \quad \text{if $\pi[i]$ is the minimal element of $\pi[i:]$}\\
-%			\dstep & \quad \text{if $\pi[i]$ is the maximal element of $\pi[i:]$}\\
-%\end{array} \right.$
-%\end{corollary}
-
-The following lemma is central to all our algorithm.
+Lemma $\ref{corollary:max is ascent}$ gives a bijection between $\AV_n(213,231)$ and the set of binary word of size $n-1$.
+The bijected word $w$ of $\pi$, is the word where each letter at position $i$ represents if $\pi[i]$ is an ascent or descent element (or is a LRMax or a LRMin).
+We call this bijection $\bijection$.
+
+A $(213,231)$-avoiding permutation has a particular form.
+If we take only the descent elements, the points draw a north-east to south-west line
+and if we take only the ascent elements, the points draw a south-east to north-west line.
+This shape the permutation as a $>$. For convenience when drawing a random $(213,231)$-avoiding permutation
+we will sometime represent a sequence of ascent/descent element by lines (see figure \ref{fig:shape of the permutation} and \ref{fig:shape of the permutation plus factor}).
+
+\begin{figure}[t] 
+	\centering
+	\begin{tikzpicture}[scale=.3]
+	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+		\draw[dotted] (0,\i) -- (9, \i);
+		\draw[dotted] (\i,0) -- (\i, 9);
+	}
+	\draw[fill=black] (0.5,0.5) circle (2mm);
+	\draw[fill=black] (1.5,1.5) circle (2mm);
+	\draw[fill=black] (2.5,2.5) circle (2mm);
+	\draw[fill=black] (3.5,8.5) circle (2mm);
+	\draw[fill=black] (4.5,7.5) circle (2mm);
+	\draw[fill=black] (5.5,3.5) circle (2mm);
+	\draw[fill=black] (6.5,6.5) circle (2mm);
+	\draw[fill=black] (7.5,5.5) circle (2mm);
+	\draw[fill=black] (8.5,4.5) circle (2mm);
+
+	\draw (0,0) -- (3,3);
+	\draw (3,9) -- (5,7);
+	\draw (5,3) -- (6,4);
+	\draw (6,7) -- (9,4);
+
+	\end{tikzpicture}
+
+	\caption{The $(213,231)$-avoiding permutation $123984765$, every point which is on a north-east to south-west line represents a descent element and every point which is on a south-east to north-west line represents an ascent element.}
+	\label{fig:shape of the permutation}
+\end{figure}
+
+The following lemma is central to our algorithm.
 
@@
 Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
-and $t$ be a subsequence of $\pi$ of length $|\sigma|$ such that $s_t = s_\sigma$.
-Then, $t$ is an occurrence of $\sigma$ in $\pi$ if and only if
-$s_t$ occurs as a subsequence in $s_\pi$.
+Then, $\pi$ matches $\sigma$ if and only if 
+there exists a subsequence $t$ of $\pi$ such $\bijection(t)=\bijection(\sigma)$.
 \end{lemma}
 
-We are now ready to solve the pattern containment problem in case
+\begin{proof}
+  The forward direction is obvious.
+  We prove the backward direction by induction on the size of the pattern
+  $\sigma$.
+  The base case is a pattern of size $2$.
+  Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = ascent$.
+  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
+  such that $\bijection(t) = ascent$, this reduces to saying that
+  $\pi_{i_1} < \pi_{i_2}$, 
+  and hence that $t$ is a matching of $\sigma = 12$ in $\pi$.
+  A similar argument shows that the lemma holds true for $\sigma = 21$.
+  Now, assume that the lemma is true for all patterns up to size $k \geq 2$.
+  Let $\sigma \in \Av{k+1}{231,213}$ and
+  let $t$,
+  be a subsequence of $\pi$ of length $k+1$ such that
+  $\bijection(t) = \bijection(\sigma)$.
+  As $\bijection(t)[2:] = \bijection(\sigma)[2:]$
+  by the inductive hypothesis, it follows that
+  $t[2:]$ is a matching of $\sigma[2:]$.
+  Moreover $\bijection(t)[1] = \bijection(\sigma)[1]$ 
+  thus $t[1]$ and $\sigma[1]$ are both either the minimal or the maximal
+  element of their respective subsequences.
+  Therefore, $t$ is a matching of $\sigma$ in $\pi$.
+  \qed
+\end{proof}
+
+We are now ready to solve the pattern matching problem in case
 both $\pi$ and $\sigma$ are $(213, 231)$-avoiding.
@@
 	Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations.
-	One can decide whether $\pi$ contains $\sigma$ in linear time.
+	One can decide whether $\pi$ matches $\sigma$ in linear time.
 \end{proposition}
 
-Observe that, according to Corollary~\ref{corollary:minmaxelement},
-the effective construction of the two stripes is not required in stretch 
-of algorithm given for the proof in 
-Proposition~
-\ref{Proposition:both permutations are avoiding},
-and hence we have an online algorithm.
+\begin{proof}
+According to Lemma~\ref{lemma:MatchStripeToPermutation} the problem reduces
+to deciding whether $\bijection(\sigma)$ is a subsequence of $\bijection(\pi)$.
+A natural greedy approach solves this issue in linear-time.
+\qed
+\end{proof}
+
+Thank to Corollary~\ref{corollary:max is ascent},
+we can compute the bijected words in the same time that we running the greedy algorithm, this gives us a on-line algorithm.
 
@@
 
-This section focuses on the pattern containment problem
+This section focuses on the pattern matching problem
 in case only the pattern $\sigma$ avoids $231$ and $213$.
-We need to consider a specific decomposition $\factora$ of $\sigma$ into factors.
-For $\sigma \in S_k$, the \emph{factorization}
-$\sigma = \factor{\pmotif}{p} \factor{\pmotif}{p-1} \ldots$ $\factor{\pmotif}{1}$
-is defined as follows:
-(i) $\sigma[k]$ is the last letter of $\factor{\pmotif}{1}$,
-(ii) for every $1 \leq i < k$,
-if $s_\sigma[i] = s_\sigma[i+1]$ then
-$\sigma[i]\sigma[i+1]$ is part of the same factor.
-For every factor $\factor{\pmotif}{j}$ of the decomposition, we let
-$\first{\pmotif}{j}$ stand for the leftmost letter of $\factor{\pmotif}{j}$,
-and $\firsti{\pmotif}{j}$ stand for the index in $\sigma$
-of the leftmost letter of $\factor{\pmotif}{j}$.
+We need to consider a specific decomposition of $\sigma$ into \textit{factor} :
+we split the permutation into largest sequences of ascent element and descent element, respectively called an ascent factor and a descent factor.
+This correspond to split the permutation between every pair of ascent-descent element and descent-ascent element (see figure \ref{fig:shape of the permutation plus factor}).
+For the special case of $(213,231)$-avoiding, this correspond to split the permutation into largest sequence of consecutive element.
+We will label the factors from right to left.
+
+We introduce the notation $\LMEi(s)$ : Suppose that $s$ is a subsequence of $S$, $\LMEi(s)$ is the index of the left most element of $s$ in $S$. Thus
+for every $\factor$, $\LMEi(\factor(j))$ stand for the index in $\sigma$
+of the leftmost element of $\factor(j)$.
 For example,
-for $\sigma = 981237654$,
-we have
-$s_\sigma = ddaaaddd$ and hence
-$\sigma = \factor{\pmotif}{3} \factor{\pmotif}{2}$ $ \factor{\pmotif}{1}$ with
-$\factor{\pmotif}{1} =7654$, $\factor{\pmotif}{2} = 123$ and $\factor{\pmotif}{3} = 98$.
+$\sigma = 123984765$ is split as
+ $123-98-4-765$. 
+Hence
+$\sigma =$ $\factor(4)$ $\factor(3)$ $\factor(2)$ $\factor(1)$ with
+$\factor(4) =123$, $\factor(3) = 98$, $\factor(2) = 4$ and $\factor(1) = 765$.
 Furthermore,
-$\first{\pmotif}{1} = 7$, $\first{\pmotif}{2} = 1$, $\first{\pmotif}{3} = 9$,
-$\firsti{\pmotif}{1} = 6$, $\firsti{\pmotif}{2} = 3$ and $\firsti{\pmotif}{3} = 1$.
+$\LMEi(\factor(4)) = 1$, $\LMEi(\factor(3)) = 4$, $\LMEi(\factor(2)) = 6$ and $\LMEi(\factor(1)) = 7$.
+We represent elements matching an ascent (resp. descent) factor 
+by a rectangle which has the left most matched point of the factor as the left bottom (resp. top) corner and the right most matched point of the factor as the right top (resp. bottom) corner.
+We can remove the two right most rectangles and replace it by the smallest rectangle that contains both of them and repeat this operation to represent part of a matching (see figure \ref{fig:shape of the permutation plus factor plus factor}).
 
 \begin{remark}
-All the elements of a factor are all increasing elements or all decreasing elements
+A factor is either an increasing or a decreasing sequence of element.
+Thus while matching a factor, it is enough to find an increasing or a decreasing subsequence of same size or bigger than the factor.
 \end{remark}
 
+\begin{figure}[t] 
+	\centering
+	\begin{tikzpicture}[scale=.3]
+	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+		\draw[dotted] (0,\i) -- (9, \i);
+		\draw[dotted] (\i,0) -- (\i, 9);
+	}
+	\draw[fill=black,double, double distance=1pt] (0.5,0.5) circle (2mm);
+	\draw[fill=black] (1.5,1.5) circle (2mm);
+	\draw[fill=black] (2.5,2.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (3.5,8.5) circle (2mm);
+	\draw[fill=black] (4.5,7.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (5.5,3.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (6.5,6.5) circle (2mm);
+	\draw[fill=black] (7.5,5.5) circle (2mm);
+	\draw[fill=black] (8.5,4.5) circle (2mm);
+
+	\draw (0,0) -- (3,3);
+	\draw (3,9) -- (5,7);
+	\draw (5,3) -- (6,4);
+	\draw (6,7) -- (9,4);
+
+	\end{tikzpicture}	
+	\begin{tikzpicture}[scale=.3]
+
+	\draw (0,0) -- (1,1);
+	\draw (1,9) -- (2,8);
+	\draw (2,1) -- (3,2);
+	\draw (4,8) -- (5,7);
+
+	\draw[fill=black] (6.5,5) circle (1mm);
+	\draw[fill=black] (7,5) circle (1mm);
+	\draw[fill=black] (7.5,5) circle (1mm);
+
+	\draw (9,6) -- (10,5);
+	\draw (10,4) -- (11,5);
+
+	\draw[fill=black,double, double distance=0.5pt] (0,0) circle (1mm);
+	\draw[fill=black,double, double distance=0.5pt] (1,9) circle (1mm);
+	\draw[fill=black,double, double distance=0.5pt] (2,1) circle (1mm);
+	\draw[fill=black,double, double distance=0.5pt] (4,8) circle (1mm);
+	\draw[fill=black,double, double distance=0.5pt] (9,6) circle (1mm);
+	\draw[fill=black,double, double distance=0.5pt] (10,4) circle (1mm);
+
+	\end{tikzpicture}	
+	\begin{tikzpicture}[scale=.3]
+
+	\fill[blue!40!white] (1.5,1.5) rectangle (2.5,0.5);
+	\fill[blue!40!white] (4.5,8.5) rectangle (6.5,6.5);
+	\fill[blue!40!white] (7.5,3.5) rectangle (8.5,5.5);
+
+	\draw[red,dashed] (1.5,1.5) rectangle (2.5,0.5);
+	\draw[red,dashed] (4.5,8.5) rectangle (8.5,3.5);
+
+	\draw[green,dashed] (1.5,0.5) rectangle (8.5,8.5);
+
+	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+		\draw[dotted] (0,\i) -- (9, \i);
+		\draw[dotted] (\i,0) -- (\i, 9);
+	}
+	\draw[fill=black] (0.5,2.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (1.5,0.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (2.5,1.5) circle (2mm);
+	\draw[fill=black] (3.5,4.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (4.5,8.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (5.5,7.5) circle (2mm);
+	\draw[fill=black,double, double distance=1pt] (6.5,6.5) circle (2mm);
+	\draw[fill=black, double distance=1pt] (7.5,3.5) circle (2mm);
+	\draw[fill=black, double distance=1pt] (8.5,5.5) circle (2mm);
+
+	\end{tikzpicture}
+
+	\caption{The left figure is the  $(213,231)$-avoiding permutation $123984765$. Every line represents a factor, every circled point represents the left most element of each factor. 
+	The central figure is a generalisation of $(213,231)$-avoiding permutation.	
+	The right figure represents a matching of $1276534$ in $312598746$, the blue rectangles represent the matching, the red dotted rectangles represent the matching after the first replacement and the green rectangle represents the matching after the second replacement.}
+	\label{fig:shape of the permutation plus factor}
+\end{figure}
+
+\begin{corollary}
+\label{corollary:whereIsMax}
+Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its 
+decomposition $\factor(i)$ $\factor(i-1)$ $\ldots$ $\factor(1)$, 
+if $\factor(i)$ is an ascent (respectively descent) factor 
+then the maximal (resp. minimal) element of $\factor(i)$ $\factor(i-1)$ $\ldots$ $\factor(1)$
+is the left most element of $\factor(i-1)$
+\end{corollary}
+
+This is a corollary of lemma \ref{lemma:first element is 1 or n}.
+This states that given a permutation in $\AV(213,231)$ 
+if the permutation starts with ascent (respectively descent) elements then the maximal (resp.
+minimal) element of this permutation is the first descent (resp.
+ascent) element (see figure \ref{fig:where to find the max}).
+
+\begin{figure}[t] 
+	\centering	
+	\begin{tikzpicture}[scale=.3]
+
+	\draw (0,0) -- (1,1);
+	\draw (2,10) -- (3,9);
+
+	\draw[fill=black] (3.5,5) circle (1mm);
+	\draw[fill=black] (4,5) circle (1mm);
+	\draw[fill=black] (4.5,5) circle (1mm);
+
+	\draw [blue] (6,2) -- (7,3);
+	\draw (7,7) -- (8,6);
+	\draw (8,3) -- (9,4);
+	\draw (9,6) -- (10,5);
+	\draw (10,4) -- (11,5);
+
+	\draw[fill=black] (7,7) circle (2mm);
+	\draw[fill=blue] (6,2) circle (2mm);
+
+	\draw[dotted,-] (0,7) -- (13,7) node[right] {Maximal y-coordinate};
+	\draw[dotted,-] (0,2) -- (13,2) node[right] {Minimal y-coordinate};
+
+	\draw[|->] (6,0) -- (13,0) node[below] {Suffix starting at $\factor(i)$};
+
+%	\draw (6.2,2.2) -- (6.5,10);
+%	\path (6.2,10) node[above] {$x$};
+
+	\end{tikzpicture}
+
+	\caption{
+		The maximal element of the suffix starting at  $\factor(i)$ (represented by the blue line)
+		is the left most element of $\factor(i-1)$ (represented by the the black dot).
+		$\LM{\ppattern}{\ptext}{i}{j}$ is the minimal value of the matching of the maximal element (the black dot) in all the matchings of the suffix starting at $\LMEi(\factor(i))$ (the blue dot) in $\pi[j:]$.
+	}	
+	\label{fig:where to find the max}
+\end{figure}
+
+We now define the set
+$\SET{\ppattern}{\ptext}{i}{j}$ 
+as the set of every subsequence $s$ of $\ptext[j:]$ that starts at $\ptext[j]$ and
+that is a matching of $\factor(i)$ $\factor(i-1)$ $\ldots$ $\factor(1)$ and .
+
 \begin{lemma}
-\label{lemma:whereIsMax}
-Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its 
-decomposition $\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots$$\factor{\sigma}{1}$, 
-if $\firsti{\sigma}{i}$ is an ascent (resp. descent) element then the maximal 
-(resp. minimal) element of $\factor{\sigma}{i}\factor{\sigma}{i-1}$ $\ldots$ $\factor{\sigma}{1}$ is 
-$\first{\sigma}{i-1}$.
+Let $\ppattern$ be a permutation, 
+$\factor(i)$ be an ascent (respectively descent) factor,
+$s$ be a subsequence of $\pi$ such that $s \in \SET{\ppattern}{\ptext}{i}{j}$ and
+that minimizes (resp. maximizes) the match of the left most element of $\factor(i-1)$.
+For all subsequences 
+$s' \in \SET{\ppattern}{\ptext}{i}{j}$ and for all subsequences $t$ of $\ptext$, such that $t=t's'$, 
+if $t$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ such that the left most element of $\factor(i)$ is matched to $\ptext[j]$ then the subsequence $t's$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ such that the left most element of $\factor(i)$ is matched to $\ptext[j]$.
 \end{lemma}
 
-We now define the set
-$\SET{\pmotif}{\ptext}{i}{j}$ as follows:
-given a subsequence $s$ of $\ptext[j:]$,
-$s \in \SET{\pmotif}{\ptext}{i}{j}$ if and only if
-$s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$
-and the element $\first{\pmotif}{i}$ occurs in $\ptext[j]$.
-
-\begin{lemma}
-\label{lemma:ts}
-Let $\pmotif$ be a permutation , 
-$\factor{\pmotif}{i}$ be an ascent (resp. descent) factor,
-$s$ be a subsequence such that $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
-For all subsequences 
-$s' \in \SET{\pmotif}{\ptext}{i}{j}$ and for all subsequences $t$ of $\ptext$, such that $t=t's'$, if $t$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ then the subsequence $t's$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ in $\ptext[j:]$ such that $\first{\pmotif}{i}$ occurs in $\ptext[j]$.
-\end{lemma}
+This lemma states that given any matching of $\factor(i+1)$ $\factor(i)$ $\ldots$ $\factor(1)$,
+where $\factor(i)$ is an ascent (resp. descent) factor,
+we can replace the part of the match that match $\factor(i)$ $\ldots$ $\factor(1)$ by any match
+that minimise (resp.
+maximise) the left most element of $\factor(i-1)$.
+Indeed the left most element of $\factor(i-1)$ is the maximal (resp.
+minimal) element of  $\factor(i)$ $\ldots$ $\factor(1)$ (see figure \ref{fig:minimise the max}).
+
+\begin{proof}
+By definition $s$ is a matching of $\ppattern[\LMEi(\factor(i)):]$.
+To prove that $ts$ is an matching of $\ppattern[\LMEi(\factor(i+1)):]$ we need to prove that every element of t is larger than every element of $s$.
+If $ts'$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ then every element of $t$ is larger than every element of $s'$.
+Moreover the maximal element of $s$ is smaller than  the maximal element of $s'$ so every element of $s$ is smaller than every element of $s'$ thus every element of $s$ is smaller than every element of $t$.
+We use a similar argument if $\factor(i)$ is a descent factor.
+\qed
+\end{proof}
 
 \begin{corollary}
-Let $\pmotif$ be a permutation , 
-$\factor{\pmotif}{i}$ be an ascent (resp. descent) factor
+\label{corollary:we can chose a matching}	
+Let $\ppattern$ be a permutation, 
+$\factor(i)$ be an ascent (respectively descent) factor
 and 
-$s$ be a subsequence such that $s \in \SET{\pmotif}{\ptext}{i}{j}$ and $s[\first{\pmotif}{i-1}]$ is minimal (resp. maximal). 
-These following statements are equivalent:
-(1)
-There exists an 
-occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs in $\ptext[j]$,
-and (2)
-There exists a subsequence $t$ of $\ptext[1:j-1]$  such that $ts$ is 
-an occurrence of $\pmotif$ in $\ptext$ with element $\first{\pmotif}{i}$ occurs 
-in $\ptext[j]$. 
+$s$ be a subsequence of $\pi$ such that $s \in \SET{\ppattern}{\ptext}{i}{j}$ and
+that minimizes (resp. maximizes) the match of the left most element of $\factor(i-1)$.
+These following statements are equivalent :
+\begin{itemize}
+	\item There exists a 
+	matching of $\ppattern$ in $\ptext$ with the left most element of $\factor(i)$ is matched to $\ptext[j]$.
+	\item There exists a matching $t$ of $\sigma[:\LMEi(\factor(i))-1]$ in $\ptext[:j-1]$  such that $ts$ is a matching of $\ppattern$ in $\ptext$ with the left most element of $\factor(i)$ matched to $\ptext[j]$.
+\end{itemize}
 \end{corollary}
 
-% This corollary allows us to way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the motif then there is no match at all.
+This corollary takes a step further from the previous one, it states that if there is no matching using any match that maximise (resp.
+minimise) the left most element of $\factor(i-1)$ then there does not exist any matching at all.
+This is central to the algorithm because it allows to test only the matching that  maximise (resp.
+minimise) the left most element of $\factor(i-1)$ (see figure \ref{fig:minimise the max}).
+
+\begin{figure}[t] 
+	\centering	
+	\begin{tikzpicture}[scale=.3]
+
+	\fill[blue!40!white] (0,9) rectangle (3,7);
+	\fill[blue!40!white] (4,0) rectangle (6,3);
+	\fill[green!40!white] (6,3) rectangle (12,7);
+
+	%		\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	%		\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+	%			\draw[dotted] (0,\i) -- (9, \i);
+	%			\draw[dotted] (\i,0) -- (\i, 9);
+	%		}
+	\draw[red,dashed] (6,3) rectangle (12,6);
+
+	\end{tikzpicture}
+
+	\caption{In a matching, we can replace the green area by the red dashed area.}
+	\label{fig:minimise the max}
+\end{figure}
+
+% This corollary allows us to way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the pattern then there is no match at all.
 
@@
 	Let $\sigma \in \AV_k(213,231)$ and $\pi \in S_n$.
-	One can decide in $O(kn^2)$ time
-	and $O(kn^2)$ space if $\pi$ contains $\sigma$.
+	\\ One can decide in $O(max(kn^2,n^2\log(\log(n)))$ time
+	and $O(kn^2)$ space if $\pi$ matches $\sigma$.
 \end{proposition}
 
-% For the proof and the algorithm we introduce a decomposition: we decompose the stripe of the motif into factor of same letter, and label those factor from right to left.
-We also need to add the last index into the first factor.
-For each factor, we denote the leftmost element by $\firsta$.
-For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$.
-
-\begin{proof}%[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
-%Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the safest match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$.
-Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.
-In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that: (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1).
-%
-%\begin{remark}
-%Given an ascent (descent) factor $\factor{i}$, the maximal (minimal) element of $\factor{i}\factor{i-1}\cdots\factor{1}$ is $\first{i-1}$.
-%\end{remark}
-%
-%\begin{remark}
-%An ascent (descent) factor 	$\factor{i}$ is a match in $\ptext[j:j']$  if and only if there exists an increasing (decreasing) subsequence in $\ptext[j:j']$ of size superior or equal to the size of $\factor{i}$.
-%\end{remark}
-
-Consider the following problem:
-$$
-\LM{\pmotif}{\ptext}{i}{j} =
+\begin{proof}
+
+We first introduce a set of values needed to our proof.
+Let $LIS_{\ptext}(i,j,bound)$ (resp. $LDS_{\ptext}(i,j,bound)$) be the longest increasing 
+(resp. decreasing) sequence in $\ptext[i:j]$ starting at $i$,
+with every element of this sequence
+smaller (resp. bigger) than $bound$.
+$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
+$O(n^2\log(\log(n)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
+As stated before, those values allow us to find a matching of a factor.
+
+Now consider the following set of values (see figure \ref{fig: algo 1 fig}) :
+$$
+\LM{\ppattern}{\ptext}{i}{j} =
 \begin{cases}
 
-	\text{The maximal value of a subsequence} 
-		& \text{If $\first{\sigma}{i}$ is  } \\
-	\text{ that is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & 
-		\text{ an ascent element } \\	
-	\text{ and that minimize the maximal value} & \\
-	\text{ and $\first{\sigma}{i}$ occurs in $\ptext[j]$} & \\
+	\text{The match of $\LMEi(\factor(i-1))$ } 
+		& \text{If $\factor(i)$ is} \\
+	\text{ in a matching of $\sigma[\LMEi(\factor(i)):]$ in $\pi[j:]$} 
+		& \text{an ascent factor} \\	
+	\text{ and that minimizes the match } & \\
+	\text{ $\LMEi(\factor(i-1))$} & \\
+	\text{ and starts with $\ptext[j]$} & \\
+	\text{Or $\infty$ if no such matching exists} & \text{} \\
 
@@
 
-	\text{The minimal value of a subsequence} 
-		& \text{If $\first{\sigma}{i}$ is  } \\
-	\text{ that is an occurence of $\sigma[\firsti{\sigma}{i}:]$ in $\pi[j:]$} & \text{ a descent element } \\	
-	\text{ and that maximize the minimal value} & \\
-	\text{ and $\first{\sigma}{i}$ occurs in $\ptext[j]$} & \\
+	\text{The match of $\LMEi(\factor(i-1))$ } 
+	& \text{If $\factor(i)$ is} \\
+	\text{ in a matching of $\sigma[\LMEi(\factor(i)):]$ in $\pi[j:]$} 
+	& \text{a descent factor} \\	
+	\text{ and that maximizes the match } & \\
+	\text{ $\LMEi(\factor(i-1))$} & \\
+	\text{ and starts with $\ptext[j]$} & \\
+	\text{Or $\infty$ if no such matching exists} & \text{} \\
+
 \end{cases}
@@
 
-This problem can be solve by induction as follows:
-
-\noindent\textbf{BASE:}
+\begin{figure}[t] 
+	\centering	
+	\begin{tikzpicture}[scale=.3]
+
+	\fill[red!40!white] (2,3) rectangle (5.5,5);
+	\fill[blue!40!white] (6,10) rectangle (12,5);
+
+	\draw[dotted,-] (0,10) -- (13,10) node[right] {$\LM{\ppattern}{\ptext}{i}{j}$};
+
+	\draw[dotted,-] (0,5) -- (13,5) node[right] {$\LM{\ppattern}{\ptext}{i-1}{j'+1}$};
+
+	\draw[dotted,-] (2,12) -- (2,0) node[below] {$j$};
+	\draw[dotted,-] (5.5,12) -- (5.5,0) node[below] {$j'$};
+	\draw[dotted,-] (6,12) -- (6,-2) node[below] {$j'+1$};
+
+	%	\draw (6.2,2.2) -- (6.5,10);
+	%	\path (6.2,10) node[above] {$x$};
+
+	\end{tikzpicture}
+
+	\caption{
+		When looking for a matching of $\sigma[\LMEi(\factor(i)):]$ (red and blue areas) starting at $\pi[j:]$, (1) the red area is a matching of $\factor(i)$ ie. if and only if
+		its contains an increasing subsequence of size equal or bigger than $|\factor(i)|$.
+		(2) the red and blue areas have to be "compatible" (their x-coordinates and y-coordinates have to be disjoint and the red area has to be before the blue area in the x-coordinate and y-coordinate).
+		$\AF{\ppattern}{\ptext}{i}{j}$ is the set of every top y-coordinate of every blue area which is compatible.
+$\LM{\ppattern}{\ptext}{i}{j}$ is the minimal value of $\AF{\ppattern}{\ptext}{i}{j}$ if he set is not void.}
+	\label{fig: algo 1 fig}	
+\end{figure}
+
+Clearly there exists a matching of $\ppattern$ in $\ptext$ if and only if
+there exists a $1 \leq i \leq n$ such that $LM(n_{factors},i)$ $\neq$ $0$ and $LM(n_{factors},i)\neq \infty$
+with $n_{factors}$ the number of factor in $\ppattern$.
+We show how to compute recursively those values.
+
+\noindent\textbf{BASE :}
 \begin{align*}
-\LM{\pmotif}{\ptext}{1}{j} 
+\LM{\ppattern}{\ptext}{1}{j} 
 &=
@@
 		\min_{j<j'}\{\infty\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\first{\sigma}{i}$ is}  \\
-		\text{ $|\factor{\pmotif}{1}| \leq LIS(j,j',\ptext[j'])  $}\}&\text{ an ascent element } \\
+			& \text{If $\factor(i)$ is}  \\
+		\text{ $|\factor(1)| \leq LIS(j,j',\ptext[j']+1)  $}\}
+			&\text{ an ascent factor} \\
 		&\\
 		\max_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\first{\sigma}{i}$ is}  \\
-		\text{ $|\factor{\pmotif}{1}| \leq LDS(j,j',\ptext[j']) $}\}&\text{ a descent element }\\
+			& \text{If $\factor(i)$ is}  \\
+		\text{ $|\factor(1)| \leq LDS(j,j',\ptext[j']-1) $}\}
+			&\text{ a descent factor}\\
 \end{cases}
@@
 In the base case,
-one is looking for an occurrence of the first factor.
-If the factor has only ascent (resp. descent) elements, then
-one has to find an increasing (resp. decreasing) subsequence
-in the text of the same size or that is longer that
-the size of the first factor. To find the occurrence that is
-the less restrictive (for the future matching)
-one must find the occurrence with the rightmost element
-of the sequence minimal (resp. maximal).}
+one is looking for a matching of the first factor.
+}
 \\
-\intertext{\textbf{STEP:}}
-\LM{\pmotif}{\ptext}{i}{j} 
+\intertext{\textbf{STEP :}}
+\LM{\ppattern}{\ptext}{i}{j} 
 &=
 \begin{cases}
-	\min \{\infty\} \cup  \AF{\pmotif}{\ptext}{i}{j} &
-	\text{If $\first{\sigma}{i}$ is an ascent element}\\
-	\max \{0\} \cup  \DF{\pmotif}{\ptext}{i}{j} &
-	\text{If $\first{\sigma}{i}$ is  a descent element}\\
+	\min \{\infty\} \cup  \AF{\ppattern}{\ptext}{i}{j} &
+	\text{If $\factor(i)$ is an ascent factor}\\
+	\max \{0\} \cup  \DF{\ppattern}{\ptext}{i}{j} &
+	\text{If $\factor(i)$ is a descent factor}\\
 \end{cases}
 \end{align*}
-where $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ are the sets 
-of elements such that if  
-$\ptext[k] \in \AF{\pmotif}{\ptext}{i}{j}$ or if $\ptext[k] \in \DF{\pmotif}{\ptext}{i}{j}$ 
-then there exists an occurrence $t$ of $\pmotif[\firsti{\pmotif}{i}:]$ in $\ptext[j:]$ and the element 
-$\first{\pmotif}{i-1}$ occurs in element $\ptext[k]$. 
-$t$ exists if and only if $t=t's'$ with $t'$ is an occurrence of  $\factor{\pmotif}{i}$ in $\ptext[j:k-1]$ with element
-$\first{\pmotif}{i-1}$ occurs in element $\ptext[k]$
-and $s \in \SET{\pmotif}{\ptext}{i-1}{k}$.
-If $\factor{\pmotif}{i}$ is an increasing (resp. decreasing)
-sequence $t'$ must be an increasing (resp. decreasing) 
-subsequence
-in $\ptext[j:k-1]$ of the same size or that is longer that
-the size of $\factor{\pmotif}{i}$ (denoted $|\factor{\pmotif}{i}|$).
-Moreover one must assure that the elements of subsequence 
-$t'$ are smaller (resp. bigger) than the element of $s'$ 
-in particular the minimal (resp. maximal) element.
-Thus we can compute $\AF{\pmotif}{\ptext}{i}{j}$ and $\DF{\pmotif}{\ptext}{i}{j}$ as follows:
+where $\AF{\ppattern}{\ptext}{i}{j}$ and $\DF{\ppattern}{\ptext}{i}{j}$ are the sets 
+of elements matching the left most element of $\factor(i-1)$ in a match of $\sigma[\LMEi(\factor(i)):]$ starting at $\ptext[j:]$.
+Suppose that $\factor(i)$ is an ascent (resp descent) factor, index $j'$ and matching $t$ exists if and only if
+$\ptext[j:j']$ contains a matching of $\factor(i)$ "compatibles" with a matching in $\ptext[j'+1:]$ of $\sigma[\LMEi(\factor(i-1)):]$.
+It is enough to assure that every element of the matching of $\factor(i)$ are smaller (resp.
+bigger) than the element of the matching of $\sigma[\LMEi(\factor(i-1)):]$.
+
+Thus we can compute $\AF{\ppattern}{\ptext}{i}{j}$ and $\DF{\ppattern}{\ptext}{i}{j}$ as follows:
 \begin{align*}
-\AF{\pmotif}{\ptext}{i}{j}
+\AF{\ppattern}{\ptext}{i}{j}
 &=
-\text{$\{\ptext[j'] \;|\; j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq 0$ and} 
+\text{$\{\ptext[j'+1] \;|\; j<j'<n$ and $\LM{\ppattern}{\ptext}{i-1}{j'+1} \neq 0$ and} 
 \\
 &\qquad 
-\text{$|\factor{\pmotif}{i}| \leq LIS_{\ptext}(j,j'-1,\LM{\pmotif}{\ptext}{i-1}{j'})\}$} 
+\text{$|\factor(i)| \leq LIS_{\ptext}(j,j',\LM{\ppattern}{\ptext}{i-1}{j'+1})\}$} 
 \\
-\DF{\pmotif}{\ptext}{i}{j}
+\DF{\ppattern}{\ptext}{i}{j}
 &=
-\text{$\{\ptext[j'] \;|\; j<j'$ and $\LM{\pmotif}{\ptext}{i-1}{j'} \neq \infty$ and}
+\text{$\{\ptext[j'+1] \;|\; j<j'<n$ and $\LM{\ppattern}{\ptext}{i-1}{j'+1} \neq \infty$ and}
 \\
 &\qquad
-\text{$|\factor{\pmotif}{i}| \leq LDS_{\ptext}(j,j'-1,\LM{\pmotif}{\ptext}{i-1}{j'})\}$}
+\text{$|\factor(i)| \leq LDS_{\ptext}(j,j',\LM{\ppattern}{\ptext}{i-1}{j'+1})\}$}
 \end{align*}
-where $LIS_{\ptext}(i,j,k)$ (resp. $LDS_{\ptext}(i,j,k)$) is the longest increasing 
-(resp. decreasing) sequence in $\ptext$ starting at $i$ and ending at $j$,
-with every element of this sequence
-smaller (resp. bigger) than $k$.
-$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
-$O(|\ptext|^2\log(\log(|\ptext|)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
-
-There exists a occurrence of $\pmotif$ in $\ptext$ if and only if
-there exists a $LM(n,i)\neq 0$ and $LM(n,i)\neq \infty$ for $1 \leq i \leq |\ptext|$,
-with $n$ the number of factors in $\pmotif$.
-Moreover the basic case can be computed in $O(n^2)$ time
-and the induction on $O(kn^2)$ time and space.
+
+The number of factor is bound by $k$.
+Every instance of $LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(n^2\log(\log(n))$.
+There are $n$ base cases that can be computed $O(n)$ time, thus computing every base cases
+takes $O(n^2)$ time.
+There are $kn$ different instance of $\AFa$ and each one of them take $O(n)$ time to compute, 
+thus computing every instance of $\AFa$ takes $O(kn^2)$ time.
+There are $kn$ different instance of $\LMa$ and each one of them take $O(n)$, because the size of an $\AFa$
+is bounded by $n$, thus computing every $\LMa$ takes $O(kn^2)$ time.
+Thus computing all the values takes $O(max(kn^2,n^2\log(\log(n)))$.
+Every value takes $O(1)$ space, thus the whole problem takes $O(kn^2)$ space.
 \qed
@@
 
-This section is devoted to the pattern matching problem with $(213,231)$-avoiding bivincular motif.
-Recall that a bivincular motif generalise a permutation motif by
-be able to force elements to be consecutive in value or in position.
-Hence,  bivincular motif is stronger in constraint that motif by permutation, 
-intuitively we can not use the previous algorithm.
-As in a $(213,231)$-avoiding permutation, we can describe structural property of 
-a $(213,231)$-avoiding bivincular motif.
+This section is devoted to the pattern matching problem with $(213,231)$-avoiding bivincular pattern.
+Recall that a bivincular pattern generalises a permutation pattern by
+being able to force elements to be consecutive in value or in position.
+Hence,  bivincular pattern is stronger in constraint than permutation pattern, intuitively we can not use the previous algorithm.
+As in a $(213,231)$-avoiding permutation, we can describe structural property of a $(213,231)$-avoiding bivincular pattern.
 
@@
 \label{lemma:ascentDescentAscent}
-Given $\pmotif$ a $(213,231)$-avoiding bivincular,
+Given $\ppattern$ a $(213,231)$-avoiding bivincular pattern,
 If $\overline{\sigma[i]\sigma[j]}$ (this implies that $\sigma[j]=\sigma[i]+1$) and 
 if $\sigma[i]$ is an ascent (resp. decent) element and $\sigma[i]+1$ is an ascent 
-(resp. decent) element then 
-$i<j$ (resp. $j>i$) and for every $k$, $i<k<j$ (resp. $j>k>i$), $\pi[k]$ is a descent 
-(resp. ascent) element.    
+(resp. decent) element then :  
+\begin{itemize}
+	\item $i<j$ (resp. $j>i$)
+	\item For every $l$, $i<l<j$ (resp. $j>l>i$), $\pi[l]$ is a descent (resp. ascent) element.    
+\end{itemize}
+
 \end{lemma}
 
-A way to understand this lemma is if two ascent (resp. decsent) elements
-need to occur in consecutive elements in value then every element in $\pmotif$ which are between those two elements (if any) are descent (resp. ascent) elements.
+This lemma states that if two ascent (resp. decsent) elements
+need to be matched to consecutive elements in value then every element between those two elements (if any) is a descent (resp. ascent) element.
+
+\begin{proof}
+Suppose that there exists $l$, $i<l<j$,
+such that $\ppattern[l]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[l]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
+We use a similar argument if $\sigma[i]$ is a descent element
+\qed
+\end{proof}
 
@@
 and $\pi \in S_n$.
-One can decide in $O(kn^5)$ time
-and $O(kn^5)$ space if $\sigma$ occurs in $\pi$.
+One can decide in $O(kn^4)$ time
+and $O(kn^3)$ space if $\pi$ matches $\sigma$.
 \end{proposition}
@@
 \begin{proof}
-We consider the following problem:
-Given $\pmotif$ a $(213,231)$-avoiding bivincular, and a text $\ptext \in \Av{n_\ptext}{231,213}$,
-$$
-\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
+
+\begin{figure}[t] 
+	\centering	
+	\begin{tikzpicture}[scale=.3]
+	\fill[blue!40!white] (0,12) rectangle (1,11);
+	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
+
+	\fill[blue!40!white] (2,0) rectangle (3,1);
+	\draw[dotted,-] (0,1.5) -- (14,1.5) node[right] {$\lb$};
+
+	\draw[fill=black] (3,1) circle (1mm) ;
+
+	\draw[dotted,-] (3.5,12) -- (3.5,-1);
+
+	% le reste du match
+	\fill[red!40!white] (5,8) rectangle (12,4);
+	\draw (5,4) -- (7.7,7);
+
+	%point du bot
+	\draw[fill=black] (5,4) circle (1mm) node[above] {$\pi[l]$} ;
+
+	\draw[thick,<->] (5,3.9) -- (5,1.5) ;	
+	\draw (5,2.7) node[right] {$\overline{(\sigma[i]-1)\sigma[i]}$};
+
+	\draw[thick,<->] (4.9,4) -- (3.5,4)  node[left] {$\underline{\sigma[i-1]\sigma[i]}$};
+
+	% point du top
+	\draw[fill=black] (8,8) circle (1mm) ;
+	\draw[thick,<->] (8,8.1) -- (8,10.5) ;	
+	\draw (8,9) node[right] {$\overline{\sigma[i'](\sigma[i']+1)}$};
+
+	\end{tikzpicture}		
+	\begin{tikzpicture}[scale=.3]
+	\fill[blue!40!white] (0,12) rectangle (1,11);
+	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
+
+	\fill[blue!40!white] (2,0) rectangle (5,4);
+	\draw[dotted,-] (0,4.5) -- (14,4.5) node[right] {$\lb=\pi[l]+1$};
+
+	%\draw[fill=black] (3,1) circle (1mm) node[left] {$\pi[j]$};
+
+	\draw[dotted,-] (5.5,12) -- (5.5,-1);
+
+	% le reste du match
+	%\draw[dashed,red] (5,8) rectangle (12,4);
+	\fill[red!40!white] (7,6) rectangle (12,8);
+	\draw (7,6) -- (7.7,7);
+
+	\draw[fill=black] (5,4) circle (1mm) ;
+
+	%point du bot
+	\draw[fill=black] (7,6) circle (1mm) node[above] {$\pi[l']$};
+
+	\draw[thick,<->] (7,5.9) -- (7,4.5) ;	
+	\draw (7,5.3) node[right] {$\overline{\sigma[i]\sigma[i+1]}$};
+
+	\draw[thick,<->] (5.5,6)   node[left] {$\underline{\sigma[i]\sigma[i+1]}$} -- (6.9,6) ;
+
+	% point du top
+	\draw[fill=black] (8,8) circle (1mm) ;
+	\draw[thick,<->] (8,8.1) -- (8,10.5) ;	
+	\draw (8,9) node[right] {$\overline{\sigma[i'](\sigma[i']+1)}$};
+
+	\end{tikzpicture}
+
+	\caption{When matching an ascent element, the value of $ub$ does not change,
+		and the lb is equal to the last match plus one. Note that there is only ascent element before $\sigma[i']$}	
+	\label{fig:ub dont change}
+\end{figure}
+
+We consider the following set of boolean :
+Given $\ppattern$ a $(213,231)$-avoiding bivincular pattern, and a text $\ptext \in \Av{n}{231,213}$,
+$$
+\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}=
 \begin{cases}
-	true 	& \text{If $\pbmotif[i:]$ occurs in $\ptext[j:]$}\\
-			& \text{with every element is in $[\lb,\ub]$}\\
-			& \text{and element $\pmotif[i]$ occurs in $\ptext[j]$ }\\
+	true 	& \text{If $\ptext[j:]$ matches $\sigma[i:]$ }\\
+			& \text{with every element of the matching is in $[\lb,\ub]$}\\
+			& \text{and starting $\pi[j]$}\\
 	false 	& otherwise\\
@@
 
-$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ can be solved by means by the following relations:
-
-\noindent\textbf{BASE:} \\
-$$
-\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}=
+The argument $\lb$ (respectively $\ub$) stands for 
+the match of the last ascent (resp. decsent) element matched
+plus (resp. minus) one.
+We now show how to compute recursively those boolean (see fig. \ref{fig:ub dont change}).
+
+\noindent\textbf{BASE :} \\
+$$
+\PM{\sigma}{\ptext}{\lb}{\ub}{k}{j}=
 \begin{cases}
 	true 	& \text{if $\ptext[j] \in [\lb,\ub ]$}\\
-			& \text{and if ${\pmotif[n_\pmotif]}_\lrcorner$ then $j=n_\ptext$}\\
-			& \text{and if ${\pmotif[n_\pmotif]}^\urcorner$ then $\ptext[j]=\ub=n_\pmotif$}\\
-			& \text{and if  $^\ulcorner{\pmotif[n_\pmotif]}$ then $\ptext[j]=\lb=1$ } \\
-			& \text{and if  $\overline{(\pmotif[n_\pmotif]-1)\pmotif[n_\pmotif] }$ then $\ptext[j]=\lb$ }  \\
-			& \text{and if  $\overline{(\pmotif[n_\pmotif]\pmotif[n_\pmotif]-1)}$ then $\ptext[j]=\ub$}  \\
+			& \text{and if ${\ppattern[k]}_\lrcorner$ then $j=n$}\\
+			& \text{and if ${\ppattern[k]}^\urcorner$ then $\ptext[j]=\ub=k$}\\
+			& \text{and if  $^\ulcorner{\ppattern[k]}$ then $\ptext[j]=\lb=1$ } \\
+			& \text{and if  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then $\ptext[j]=\lb$ }  \\
+			& \text{and if  $\overline{(\ppattern[k]\ppattern[k]-1)}$ then $\ptext[j]=\ub$}  \\
 
@@
 
-The base case finds an occurrence for the rightmost element of the motif.
-If the last element does not have any restriction on positions and on values, then $\PM{\pbmotif}{\ptext}{\lb}{\ub}{n_\pmotif}{j}$ is true if and only if $\pmotif[n_\pmotif]$ occurs in $\ptext[j]$.
-This is true if $\ptext[j] \in [\lb,\ub]$.
-
-\noindent\textbf{STEP:}
-
-We need to consider $3$ cases for the problem $\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$:
+The base case finds an matching for the rightmost element of the pattern.
+If the last element does not have any restriction on positions and on values, then $\PM{\sigma}{\ptext}{\lb}{\ub}{k}{j}$ is true if and only if $\ppattern[k]$ is matched $\ptext[j]$.
+Which is true if $\ptext[j] \in [\lb,\ub]$.
+If ${\ppattern[k]}_\lrcorner$ then $\ppattern[k]$ must be matched to the right most element of $\pi$ thus $j$ must be the $n$.
+If ${\ppattern[k]}^\urcorner$ then $\ppattern[k]$ must be matched to the largest element which is $k$.
+If $^\ulcorner{\ppattern[k]}$ then $\ppattern[k]$ must be matched to the smallest element which is $1$.
+If  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then the matched element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the matched element of $\ppattern[k]-1$ will be recorded in $\lb$ and by adding $1$ to it thus $\ppattern[k]$ must be matched to $\lb$.
+If  $\overline{(\ppattern[k]\ppattern[k]-1)}$ then the matched element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the matched element of $\ppattern[k]-1$ will be recorded in $\ub$ and by removing $1$ to it thus $\ppattern[k]$ must be matched to $\ub$.
+
+\noindent\textbf{STEP :}
+
+We need to consider 3 cases for the problem $\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}$ :
 \begin{itemize}
-	\item If $\ptext[j] \notin [\lb,\ub]$ then
-	$
-	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j} = false
-	$
-	which is immediate from the definition. 
-	If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of an 
-	occurrence of  $\pmotif[i:]$ in $\ptext[i:]$ with every element is 
-	in $[\lb,\ub]$.
-
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is an ascent element then:
-	$$
-	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
+	\item If $\ptext[j] \notin [\lb,\ub]$ then :
+	$$
+	\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j} = false
+	$$
+
+	which is immediate from the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of a matching of  $\ppattern[i:]$ in $\ptext[i:]$ with every matched element in $[\lb,\ub]$.
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is an ascent element then :
+	$$
+	\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}=
 	\begin{cases}
-		\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}
-			& \text{if $\pmotif[i]$ is not underlined } \\
-			& \text{ and $\pmotif[i]$ is not overlined} \\
-		\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}
-			& \text{if $\pmotif[i]$ is not underlined } \\
-			& \text{ and $\overline{(\pmotif[i]-1)\pmotif[i]}$ or $^\ulcorner{\pmotif[i]}$}\\
+		\bigcup_{j<l} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{l}
+			& \text{if $\ppattern[i]$ is not underlined } \\
+			& \text{ and $\ppattern[i]$ is not overlined} \\
+		\bigcup_{j<l} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{l}
+			& \text{if $\ppattern[i]$ is not underlined } \\
+			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
 			& \text{ and $\ptext[j]=\lb$} \\
-		\PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
-			& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
-			& \text{ and $\overline{(\pmotif[i]-1)\pmotif[i]}$ or $^\ulcorner{\pmotif[i]}$}\\
+		\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
+			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
+			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
 			& \text{ and $\ptext[j]=\lb$} \\
-		\PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
-			& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
-			& \text{ and $\pmotif[i]$ is not overlined} \\
+		\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
+			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
+			& \text{ and $\ppattern[i]$ is not overlined} \\
 		false & \text{otherwise}
@@
 	$$	
-	Remark that $\pmotif[i]$ occurs in $\ptext[j]$ because $\ptext[j] \in [\lb,\ub]$.
-	Thus if $\pmotif[i+1:]$ occurs in $\ptext[j+1:]$ with every element in $[\pmotif[i]+1,\ub]$ then 
- 	$\pmotif[i:]$ occurs in $\ptext[j:]$  	
- 	which correspond to know if there exists $k$, $j<k$ such that
-	$\PM{\pbmotif}{\ptext}{\ptext[j]+1}{\ub}{i+1}{k}$ is true.
-
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then:
-
-	$$
-	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
+	Remark that $\ptext[j]$ can be matched to $\ppattern[i]$ because $\ptext[j] \in [\lb,\ub]$.
+	Thus if $\ptext[j+1:]$ matches $\ppattern[i+1:]$  with every element of the matching in $[\ppattern[i]+1,\ub]$ then 
+ 	$\ptext[j:]$ matches $\ppattern[i:]$. The last condition correspond 
+ 	to know if there exists $l$, $j<l$ such that
+	$\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{l}$ is true.
+	The first case correspond to a matching without restriction on position and on value.
+The second case asks for the match of $\ppattern[i]-1$ and $\ppattern[i]$ to be consecutive in value, but the match of $\ppattern[i]-1$
+	is $lb-1$ thus we want $\ptext[j]=\lb$.
+The fourth case asks for the match of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in index, thus the match of $\ppattern[i+1]$ must be $j+1$.
+The third case is an union of the second and fourth case.
+Note that if $\pi[j]$ is an ascent element we can not have the condition that the match of $\ppattern[i]$ and $\ppattern[i]+1$ have to consecutive in value.
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a descent element then :
+
+	$$
+	\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}=
 	\begin{cases}
-			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
-				& \text{if $\pmotif[i]$ is not underlined } \\
-				& \text{ and $\pmotif[i]$ is not overlined} \\
-			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
-				& \text{if $\pmotif[i]$ is not underlined } \\
-				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\
+			\bigcup_{j<l} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{l}
+				& \text{if $\ppattern[i]$ is not underlined } \\
+				& \text{ and $\ppattern[i]$ is not overlined} \\
+			\bigcup_{j<l} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{l}
+				& \text{if $\ppattern[i]$ is not underlined } \\
+				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
 				& \text{ and $\ptext[j]=\ub$} \\
-			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
-				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
-				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\
+			\PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
+				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
 				& \text{ and $\ptext[j]=\ub$} \\
-			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
-				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
-				& \text{ and $\pmotif[i]$ is not overlined} \\
+			\PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
+				& \text{ and $\ppattern[i]$ is not overlined} \\
 			false & \text{otherwise}
@@
 
-Clearly if $\bigcup_{0<j} \PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{j}$ is true then $\sigma$ occurs in $\pi$. We now discuss the position and value constraints.
-\paragraph{Position Constraint.} There are 3 types of position constraints 
+Clearly if $\bigcup_{0<j} \PM{\sigma}{\ptext}{1}{n}{1}{j}$ is true then $\pi$ matches $\sigma$. We now discuss the position and value constraints.
+\paragraph{Position Constraint.} There are 3 types of position constraints that can be added by underlined elements.
 \begin{itemize}
-	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must occur in the leftmost element of $\pi$ ($\pmotif[1]$ occurs in $\ptext[1]$ on an occurrence of $\pmotif$ in $\ptext$).
-This constraint is checked by requiring the occurrence to starts at the leftmost element of $\ptext$: if  $\PM{\pbmotif}{\ptext}{1}{n_\ptext}{1}{1}$ is true.
-
-	\item If ${\pmotif[n_\pmotif]}_\lrcorner$ then the rightmost element $\sigma$ must occurs in the rightmost element of $\pi$ ($\pmotif[n_\pmotif]$ occurs in $\ptext[n_\ptext]$ on a occurrence of $\pmotif$ in $\ptext$).
+	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ on a matching of $\ppattern$ in $\ptext$).
+This constraint is satisfied by requiring that the matching starts at the left most element of $\ptext$ : if  $\PM{\sigma}{\ptext}{1}{n}{1}{1}$ is true.
+
+	\item If ${\ppattern[k]}_\lrcorner$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a matching of $\ppattern$ in $\ptext$).
 This constraint is checked in the base case.
 
-	\item If $\underline{\pmotif[i]\pmotif[i+1]}$ then the index of the occurrence of $\pmotif[i]$ and $\pmotif[i+1]$ must be consecutive.
-In other word, if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i+1]$ must occur in $\ptext[j+1]$.
-We assure this restriction in the induction by requiring occurrences of $\pmotif[i+1:]$ to start at index $j+1$.
+	\item If $\underline{\ppattern[i]\ppattern[i+1]}$ then the index of the matched elements of $\ppattern[i]$ and $\ppattern[i+1]$ must be consecutive.
+In other word, if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i+1]$ must be matched to $\ptext[j+1]$.
+We assure this restriction by recursion by requiring that the matching of $\ppattern[i+1:]$ to start at index $j+1$ (see figure $\ref{fig:ub dont change}$).
 \end{itemize}
 
-\paragraph{Value Constraint.} There are 3 types of position constraints
+\paragraph{Value Constraint.} There are 3 types of position constraints that can be added by overlined elements.
 \begin{itemize}
-	\item If $^\ulcorner{\sigma[i]}$ (and thus $\sigma[i]=1$) then the minimal value of $\pmotif$ must occur in the minimal value of $\ptext$.
+	\item If $^\ulcorner{\sigma[i]}$ (and thus $\sigma[i]=1$) then the minimal value of $\ppattern$ must be matched to the minimal value of $\ptext$.
 	\begin{itemize}
@@
 		every problem 
-		$\PM{\pbmotif}{\ptext}{\lb}{*}{i}{*}$ is true if $\sigma[i]$ occurs in element $\lb$ thus it is enough to require that $\lb=1$.
+		$\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ is true if $\sigma[i]$ is matched to element with value $\lb$ (by recursion) thus it is enough to require that $\lb=1$.
 		Now remark that $\sigma[i]$ is the leftmost ascent element, indeed if not, then there exists an ascent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the minimal element.
-As a consequence every problem $\PM{\pbmotif}{\ptext}{1}{n_{\pi}}{1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ is called with descent thus every problem
-		$\PM{\pbmotif}{\ptext}{\lb}{*}{i}{*}$ has same lower bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ thus for every $\PM{\pbmotif}{\ptext}{\lb}{*}{i}{*}$, $\lb=1$.
-
-		\item If $\sigma[i]$ is a descent element then $i=n_\pmotif$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ occurs in $1$.
+		As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are descent elements.
+		Moreover the recursive call from a descent element does not modified the lower bound
+		thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$, $\lb=1$ (see figure $\ref{fig:ub dont change}$).
+
+		\item If $\sigma[i]$ is a descent element then $i=k$ ($\sigma[i]$ is the right most element).
+Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $1$.
+
 	\end{itemize}
 
-	\item If ${\pmotif[i]}^\urcorner$ (and thus $\sigma[i]=n_\pmotif$) then the maximal value of $\pmotif$ must occur in the maximal value of $\ptext$.
+	\item If ${\ppattern[i]}^\urcorner$ (and thus $\sigma[i]=k$) then the maximal value of $\ppattern$ must be matched to the maximal value of $\ptext$.
 	\begin{itemize}
@@
 		\item If $\sigma[i]$ is an descent element, then remark that 
-		every problem 
-		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ occurs in element $\ub$ thus it is enough to require that $\ub=n_{\ptext}$.
+		every recursive call \\ $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ is matched to element with value $\ub$ (by recursion) thus it is enough to require that $\ub=n_{\ptext}$.
 		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal element.
-As a consequence every problem $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ is called with ascent elements thus every problem
-		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ has same upper bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ thus for every $\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$,
-		$\ub=n_{\ptext}$.
-
-		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=n_\pmotif$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\pbmotif}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ occurs in $n_{\ptext}$.
+		As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are ascent elements.
+		Moreover the recursive call from a ascent element does not modified the upper bound
+		thus for every $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$, $\ub=n$ (see figure $\ref{fig:ub dont change}$.
+
+		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=k$ ($\sigma[i]$ is the right most element).
+Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n_{\ptext}$.
 
@@
 
-	\item  If $\overline{\pmotif[i]\pmotif[i']}$,  (which implies that $\pmotif[i']=\pmotif[i]+1$) then if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i']$ must occur in $\ptext[j]+1$.
+	\item  If $\overline{\ppattern[i]\ppattern[i']}$,  (which implies that $\ppattern[i']=\ppattern[i]+1$) then if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i']$ must be matched to $\ptext[j]+1$.
 		\begin{itemize}
 
-			\item The case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i'<i$) is not possible.
-			Indeed $\pmotif[i]$ is the maximal element of $\pmotif[i:]$ thus $\pmotif[i] > \pmotif[i']$ which is in contradiction with 
-			$\pmotif[i']=\pmotif[i]+1$.
-
-			\item If $\pmotif[i]$ is an ascent element, $\pmotif[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case $\pmotif[i]$ is a descent element, $\pmotif[i']$ is an ascent element and $i'<i$), then
-			remark that every problem 
-			$\PM{\pbmotif}{\ptext}{\lb}{*}{i'}{*}$ is true if $\sigma[i']$ occur in $\lb$ thus it is enough to require that $\lb=\ptext[j]+1$.
+			\item The case $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i'<i$) is not possible.
+			Indeed $\ppattern[i]$ is the maximal element of $\ppattern[i:]$ thus $\ppattern[i] > \ppattern[i']$ which is in contradiction with 
+			$\ppattern[i']=\ppattern[i]+1$.
+
+			\item If $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i'<i$), then
+			remark that every recursive call
+			$\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$ is true if $\sigma[i']$ is matched to the element with $\lb$ (by recursion) thus it is enough to require that $\lb=\ptext[j]+1$.
 			Now remark that
-			$\pmotif[i]$ is the rightmost ascent element and $\pmotif[i']$ is the rightmost element (or $\pmotif[i'] \neq \pmotif[i]+1$). 
-			As a consequence every problem $\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ is called with descent elements
-			thus every problem 
-			$\PM{\pbmotif}{\ptext}{\lb}{*}{i'}{*}$ 
-			has the same lower bound as $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$.
-			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.
-
-			\item If $\pmotif[i]$ is an ascent element and $\pmotif[i']$ is an ascent element then
-			first remark that every problem 
-			$\PM{\pbmotif}{\ptext}{*}{\ub}{i'}{*}$ is true if $\sigma[i']$ occurs in $\lb$.
+			$\ppattern[i]$ is the right most ascent element and $\ppattern[i']$ is the right most element (or $\ppattern[i'] \neq \ppattern[i]+1$). 
+			As a consequence $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are descent elements.
+Moreover the recursive call from a descent element does not modified the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$
+			thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see figure $\ref{fig:ub dont change}$.
+
+			\item If $\ppattern[i]$ is an ascent element and $\ppattern[i']$ is an ascent element then
+			first remark that every recursive call
+			$\PM{\sigma}{\ptext}{*}{\ub}{i'}{*}$ is true if $\sigma[i']$ is matched to element with value $\lb$. 
 			Now remark that
-			$i<i'$ and there is no  ascent element between $\pmotif[i]$ and $\pmotif[i']$ (lemma \ref{lemma:ascentDescentAscent}), 
-			Thus for every problem $\PM{\pbmotif}{\ptext}{*}{*}{i+1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i'-1}{*}$ is called with descent elements
-			thus every problem 
-			$\PM{\pbmotif}{\ptext}{\lb}{*}{i'}{*}$ has same lower bound as $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$.
-			Finally remark that if $\pmotif[i]$ occurs in $\ptext[j]$ then  $\PM{\pbmotif}{\ptext}{\lb}{*}{i+1}{*}$ has for lower bound $\ptext[j]+1$.			
+			$i<i'$ and there is no  ascent element between $\ppattern[i]$ and $\ppattern[i']$ (lemma \ref{lemma:ascentDescentAscent}), 
+			As a consequence $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are descent elements.
+Moreover the recursive call from a descent element does not modified the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$ thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see figure $\ref{fig:ub dont change}$.
+
 		\end{itemize}
 \end{itemize}
+
+There are $n^3$ base cases that can be computed in constant time.
+There are $kn^3$ different cases. Each case takes up to $O(n)$ time to compute.
+Thus computing all the cases take $O(kn^4)$ time.
+Each case take $O(1)$ space, thus we need $O(kn^3)$ space.
 \qed
@@
 
-\section{Computing the longest $(213,231)$-avoiding pattern}
+\section{Computing the longest $(213,231)$-avoiding subsequence}
 \label{section:LCS}
 
-	This section is devoted to finding longest $(213,231)$-avoiding patterns 
-	in permutations.
-	We start with the easiest case where we are given just one input permutation
-	and we are asked to find the longest $(213,231)$-avoiding pattern that 
-	occurs in the input permutation.
-	We need the set of descent elements and the set of ascent elements
-	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
-	$M(\pi) = \{i | \stripe{\pi}{i} = \dstep \} \cup \{n\}$.\\
+	This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
+	Given a set of permutations, find a longest $(213,231)$-avoiding that can be matched
+	by each input permutation.
+	This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$.
+Thus we focus on the cases where only one or two permutations are given in input.
+	We start with the easiest case where we are given just one input permutation.
+	We need the set of descent elements and the set of ascent elements.
+	$A(\pi) = \{i | \text{$\pi[i]$ is an ascent element} \} \cup \{n\}$ and
+	$D(\pi) = \{i | \text{$\pi[i]$ is a descent element} \cup \{n\}$.\\
 
@@
 	$f$ in $\pi$ then
-	$P(\pi)$ is a longest increasing subsequence with last element at index $f$ and
-	$M(\pi)$ is a longest decreasing subsequence with last element at index $f$.
+	$A(\pi)$ is a longest increasing subsequence with last element at index $f$ and
+	$D(\pi)$ is a longest decreasing subsequence with last element at index $f$.
 	\end{proposition}
 
+	\begin{proof}
+	Let $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
+	suppose that $P(s)$ is not a longest increasing subsequence with last element at index $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
+	Thus $|s_m|>|A(s)|$, clearly the sequence $s_m \cup D(s)$
+	is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
+	The same idea can be used to show that $D(\pi)$ is the longest decreasing subsequence.
+	\qed
+	\end{proof}
+
 	\begin{proposition}
-	\label{proposition:longest 2}
-	Let $\pi$ be a permutation. One can compute the
-	the longest $(213,231)$-pattern that occurs in $\pi$
-	in $O(|\ptext|\log(\log(|\ptext|)))$ time and in $O(n)$ space.
+	Let $\pi$ be a permutation. One can compute
+	the longest $(213,231)$-avoiding subsequence that can be matched in $\pi$
+	in $O(n\log(\log(n)))$ time and in $O(n)$ space.
 	\end{proposition}
 
-We now turn to considering the case where the input is composed of two permutations.
+	\begin{proof}
+	The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
+	where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
+	Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
+	$O(n\log(\log(n)))$ time and $O(n)$ space 
+	(see \cite{Bespamyatnikh00enumeratinglongest}), 
+	then finding the maximal can be done in linear time.
+	\qed
+	\end{proof}
+
+We  now consider the case where the input is composed of two permutations.
 
@@
 one can compute 
-the longest common subsequence
-avoiding (213,231) in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
+the longest common $(213,231)$-avoiding subsequence
+in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
 \end{proposition}
@@
 \begin{proof}
-Consider the following problem
-that computes the longest stripe common to $\pi_1$ and $\pi_2$:
-Given two permutations $\pi_1$ and $\pi_2$, we define
-$
+Consider the following problem,
+that compute the longest stripe common to $\pi_1$ and $\pi_2$.
+Given two permutations $\pi_1$ and $\pi_2$,\\
+
+$$
 \LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
-=
-\max\{|s| \;|\; s \text{ occurs in } \pi_1[i_1:] \text{ with every element is in }
-[\lb_1,\ub_1] \text{ and } s \text{ occurs in } \pi_2[i_2:] \text{ with every element is in }
-[\lb_2,\ub_2]\}$.
-
-We show how to solve this problem by dynamic programming.
-
-\noindent\textbf{BASE:}
+$$
+\begin{center}
+= $\max$ \{$|s|$ $|$ $s$ can be matched $\pi_1[i_1:]$ with every element of the match in $[\lb_1,\ub_1]$ and $s$ can be matched $\pi_2[i_2:]$ with every element of the match in $[\lb_2,\ub_2]$ \}
+\end{center}
+
+We show that we can compute by induction the problem.\\
+
+\noindent\textbf{BASE :}
+
 $$
@@
 
-\noindent\textbf{STEP:}
+\noindent\textbf{STEP :}
+
 $$
@@
 For every pair $i,j$ we either ignore the element of $\pi_1$,
-ot we ignore the element of $\pi_2$,
+or we ignore the element of $\pi_2$,
 or we match as the same step (if possible).
@@
 \bibliographystyle{plain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\section*{Appendix (Reviewers' version only)}
-
-\begin{proof}[of Lemma~\ref{lemma:first element is 1 or n}]
-Any other initial element would serve as a `$2$' in either a
-$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:MatchStripeToPermutation}]
-  The forward direction is obvious.
-  We prove the backward direction by induction on the size of the motif
-  $\sigma$.
-  The base case is a motif of size $2$.
-  Suppose first that $\sigma = 12$ and hence $s_\sigma = a$.
-  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-  such that $s_t$ occurs as a subsequence in $s_\pi$.
-  Since $s_\sigma = s_t = a$, this reduces to saying that
-  $\pi_{i_1} < \pi_{i_2}$, and hence $t$ is an occurrence of $\sigma = 12$ in $\pi$.
-  A similar argument shows that the lemma holds true for $\sigma = 21$.
-  Now, assume that the lemma is true for all motifs up to size $k \geq 2$.
-  Let $\sigma \in \Av{k+1}{231,213}$ and
-  let $t = \pi_{i_1}\pi_{i_2}\,\ldots\,\pi_{i_{k+1}}$,
-  $i_1 < i_2 < \ldots < i_{k+1}$,
-  be a subsequence of $\pi$ of length $k+1$ such that
-  $s_t = s_\sigma$.
-  Suppose that $s_t$ occurs in $s_\pi$ as a subsequence.
-  Then, $s_t[2:] = s_\sigma[2:]$ occurs as a subsequence in $s_\pi[2:]$.
-  But $\sigma[2:] \in \Av{k}{231,213}$ and hence,
-  by the inductive hypothesis, it follows that
-  $t[2:]$ is an occurrence of $\sigma[2:]$ in $\pi[2:]$.
-  Moreover, if $s_\sigma[1] = a$ (resp. $s_\sigma[1] = d$)
-  then $\sigma[1]$ is the minimal (resp. maximal) element of $\sigma$
-  (Lemma~\ref{lemma:first element is 1 or n}),
-  and hence, since $s_t = s_\sigma$ occurs as a subsequence in $s_\pi$,
-  $t[1]$ is the minimal (resp. maximal) element of $t$.
-  Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
-  \qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}
-According to Lemma~\ref{lemma:MatchStripeToPermutation} the problem reduces
-to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$.
-A straightforward greedy approach solves this issue in linear-time.
-\qed
-% To solve the permutation pattern for a permutation in $\AV_n(213,231)$,
-% we find a find a match of the stripe of the pattern in the stripe of the text.
-% This can be done linearly by a greedy algorithm,
-% by matching a step whenever it is possible.
-% And thank to the definition of the definition of a stripe in
-% Corollary~\ref{corollary:minmaxelement},
-% we do not have to compute the stripe in advance.
-% Therefore we have an linear (online) algorithm.
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:whereIsMax}]
-Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
-Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
-Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
-$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
-According to Lemma~
-\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is 
-the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, 
-and hence
-$\first{\sigma}{i-1}$ is the maximal  element of
-$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
-
-A similar argument shows that the lemma holds true if the rightmost element
-of $\factor{\sigma}{i}$ is a descent.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:ts}]
-By definition $s$ is an occurrence of $\pmotif[\firsti{\pmotif}{i}:]$. 
-To prove that $ts$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$,
-we prove that every element of t is larger than every element of $s$. 
-If $ts'$ is an occurrence of $\pmotif[\firsti{\pmotif}{i+1}:]$ so every element of $t$ 
-is larger than every element of $s'$. 
-Moreover, the maximal element of $s$ is smaller than  the maximal element of $s'$ 
-so every element of $s$ is smaller than every element of $s'$ thus every 
-element of $s$ is smaller than every element of $t$. We use a similar argument 
-if $\factor{\pmotif}{i}$ a descent factor.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:ascentDescentAscent}]
-Suppose that there exists $k$, $i<k<j$,
-such that $\pmotif[k]$ is ascent. 
-Ascent elements are increasing and hence $\sigma[i]<\sigma[k]<\sigma[j]$.
-This is a contradiction since $\sigma[j]=\sigma[i]+1$.
-
-We use a similar argument if $\sigma[i]$ is a descent element
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Proposition~\ref{proposition:longestIncreasingSubsequence}]
-Let $s$ be a longest subsequence avoiding both $213$ and $231$ 
-with last element at index $f$ in $\pi$,
-and
-suppose that $P(\pi)$ is not a longest increasing subsequence
-with last element at index $f$. 
-Let $s_m$ be a longest increasing subsequence with last element $f$.
-Thus $|s_m|>|P(\pi)|$, clearly the sequence $s_m \cup M(\pi)$
-is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
-
-The same idea can be used to show that $M(\pi)$ is the longest decreasing 
-subsequence.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Proposition~\ref{proposition:longest 2}]
-Proposition~\ref{proposition:longestIncreasingSubsequence} leads to an algorithm
-where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
-Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
-$O(|\ptext|\log(\log(|\ptext|)))$ time and $O(n)$ space 
-(see \cite{Bespamyatnikh00enumeratinglongest}), 
-then finding the maximal can be done in linear time.
-\qed
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 

### 2015-10-08 article.tex

@@
 	improving the previous 30-year bound of $O(|\pi| \log |\sigma|)$.
-	(The algorithm also improves on the previous
-	$O(|\pi| \log \log |\pi|)$ bound).
+	% (The algorithm also improves on the previous
+	% $O(|\pi| \log \log |\pi|)$ bound.)
 	Furthermore, the patterns $132$, $213$, $231$, $312$ can all be handled in linear-time
@@
  	the reverse of $\pi'$ avoids $213$.
- 	From a combinatorial point of view,
- 	B\'ona \cite{Bona:ElJC:2012}
- 	showed the rather surprising fact that the cumulative number of
- 	matching of the classical patterns $231$ and $213$ are the same on the
- 	set of permutations avoiding $132$,
- 	beside the pattern based statistics $231$ and $213$
- 	do not have the same distribution on this set.
- 	\emph{Almost avoidance} has also been considered;
- 	a permutation $\pi$ almost avoids a set $X$ of permutations
- 	if there is a way to remove a single element of $\pi$ to get a permutation
- 	that avoids all elements in $P$
- 	and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
- 	$P$.
- 	It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
- 	$L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
-
+ 	% From a combinatorial point of view,
+ 	% B\'ona \cite{Bona:ElJC:2012}
+ 	% showed the rather surprising fact that the cumulative number of
+ 	% occurrences of the classical patterns $231$ and $213$ are the same on the
+ 	% set of permutations avoiding $132$,
+ 	% beside the pattern based statistics $231$ and $213$
+ 	% do not have the same distribution on this set.
+ 	% \emph{Almost avoidance} has also been considered;
+ 	% a permutation $\pi$ almost avoids a set $X$ of permutations
+ 	% if there is a way to remove a single element of $\pi$ to get a permutation
+ 	% that avoids all elements in $P$
+ 	% and $L_n(P)$ denotes the set of permutations of length $n$ that almost avoid
+ 	% $P$.
+ 	% It is shown in \cite{Griffiths:Smith:Warren:PMA:2011} that
+ 	% $L_n(213, 231) = L_n(132, 231) = L_n(132, 312) = L_n(213, 312)$.
 	This paper is organized as follows.
@@
 
-\begin{proof}
-Any other initial element would serve as a `$2$' in either a
-$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
-\qed
-\end{proof}
-
 \begin{corollary}
@@
 
-\begin{proof}
-  The forward direction is obvious.
-  We prove the backward direction by induction on the size of the pattern
-  $\sigma$.
-  The base case is a pattern of size $2$.
-  Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = ascent$.
-  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-  such that $\bijection(t) = ascent$, this reduces to saying that
-  $\pi_{i_1} < \pi_{i_2}$, 
-  and hence that $t$ is a matching of $\sigma = 12$ in $\pi$.
-  A similar argument shows that the lemma holds true for $\sigma = 21$.
-  Now, assume that the lemma is true for all patterns up to size $k \geq 2$.
-  Let $\sigma \in \Av{k+1}{231,213}$ and
-  let $t$,
-  be a subsequence of $\pi$ of length $k+1$ such that
-  $\bijection(t) = \bijection(\sigma)$.
-  As $\bijection(t)[2:] = \bijection(\sigma)[2:]$
-  by the inductive hypothesis, it follows that
-  $t[2:]$ is a matching of $\sigma[2:]$.
-  Moreover $\bijection(t)[1] = \bijection(\sigma)[1]$ 
-  thus $t[1]$ and $\sigma[1]$ are both either the minimal or the maximal
-  element of their respective subsequences.
-  Therefore, $t$ is a matching of $\sigma$ in $\pi$.
-  \qed
-\end{proof}
-
 We are now ready to solve the pattern matching problem in case
@@
 \end{proposition}
-
-\begin{proof}
-According to Lemma~\ref{lemma:MatchStripeToPermutation} the problem reduces
-to deciding whether $\bijection(\sigma)$ is a subsequence of $\bijection(\pi)$.
-A natural greedy approach solves this issue in linear-time.
-\qed
-\end{proof}
 
@@
 \begin{lemma}
+\label{lemma:ts}
 Let $\ppattern$ be a permutation, 
@@
 minimal) element of  $\factor(i)$ $\ldots$ $\factor(1)$ (see figure \ref{fig:minimise the max}).
-
-\begin{proof}
-By definition $s$ is a matching of $\ppattern[\LMEi(\factor(i)):]$.
-To prove that $ts$ is an matching of $\ppattern[\LMEi(\factor(i+1)):]$ we need to prove that every element of t is larger than every element of $s$.
-If $ts'$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ then every element of $t$ is larger than every element of $s'$.
-Moreover the maximal element of $s$ is smaller than  the maximal element of $s'$ so every element of $s$ is smaller than every element of $s'$ thus every element of $s$ is smaller than every element of $t$.
-We use a similar argument if $\factor(i)$ is a descent factor.
-\qed
-\end{proof}
 
@@
 
-\begin{proof}
-Suppose that there exists $l$, $i<l<j$,
-such that $\ppattern[l]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[l]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
-We use a similar argument if $\sigma[i]$ is a descent element
-\qed
-\end{proof}
-
 \begin{proposition}
@@
 
-\noindent\textbf{STEP :}
+\noindent\textbf{STEP:}
 
@@
 	\item  If $\overline{\ppattern[i]\ppattern[i']}$,  (which implies that $\ppattern[i']=\ppattern[i]+1$) then if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i']$ must be matched to $\ptext[j]+1$.
+
 		\begin{itemize}
@@
 			Now remark that
+
 			$i<i'$ and there is no  ascent element between $\ppattern[i]$ and $\ppattern[i']$ (lemma \ref{lemma:ascentDescentAscent}), 
@@
 Moreover the recursive call from a descent element does not modified the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$ thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see figure $\ref{fig:ub dont change}$.
-
 		\end{itemize}
@@
 
-\section{Computing the longest $(213,231)$-avoiding subsequence}
+\section{Computing the longest $(213,231)$-avoiding pattern}
 \label{section:LCS}
@@
 
-	\begin{proof}
-	Let $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
-	suppose that $P(s)$ is not a longest increasing subsequence with last element at index $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
-	Thus $|s_m|>|A(s)|$, clearly the sequence $s_m \cup D(s)$
-	is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
-	The same idea can be used to show that $D(\pi)$ is the longest decreasing subsequence.
-	\qed
-	\end{proof}
-
 	\begin{proposition}
+	\label{proposition:longest 2}
 	Let $\pi$ be a permutation. One can compute
@@
 	\end{proposition}
-
-	\begin{proof}
-	The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
-	where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
-	Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
-	$O(n\log(\log(n)))$ time and $O(n)$ space 
-	(see \cite{Bespamyatnikh00enumeratinglongest}), 
-	then finding the maximal can be done in linear time.
-	\qed
-	\end{proof}
 
@@
 \begin{proof}
-Consider the following problem,
-that compute the longest stripe common to $\pi_1$ and $\pi_2$.
-Given two permutations $\pi_1$ and $\pi_2$,\\
-
-$$
+Consider the following problem
+that computes the longest stripe common to $\pi_1$ and $\pi_2$:
+Given two permutations $\pi_1$ and $\pi_2$, we define
+$
 \LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
-$$
+$
 \begin{center}
@@
 
-We show that we can compute by induction the problem.\\
-
-\noindent\textbf{BASE :}
-
+We show how to solve this problem by dynamic programming.
+
+\noindent\textbf{BASE:}
 $$
@@
 \bibliographystyle{plain}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\section*{Appendix (Reviewers' version only)}
+
+\begin{proof}[of Lemma~\ref{lemma:first element is 1 or n}]
+Any other initial element would serve as a `$2$' in either a
+$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:MatchStripeToPermutation}]
+  The forward direction is obvious.
+  We prove the backward direction by induction on the size of the pattern
+  $\sigma$.
+  The base case is a pattern of size $2$.
+  Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = ascent$.
+  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
+  such that $\bijection(t) = ascent$, this reduces to saying that
+  $\pi_{i_1} < \pi_{i_2}$, 
+  and hence that $t$ is a matching of $\sigma = 12$ in $\pi$.
+  A similar argument shows that the lemma holds true for $\sigma = 21$.
+  Now, assume that the lemma is true for all patterns up to size $k \geq 2$.
+  Let $\sigma \in \Av{k+1}{231,213}$ and
+  let $t$,
+  be a subsequence of $\pi$ of length $k+1$ such that
+  $\bijection(t) = \bijection(\sigma)$.
+  As $\bijection(t)[2:] = \bijection(\sigma)[2:]$
+  by the inductive hypothesis, it follows that
+  $t[2:]$ is a matching of $\sigma[2:]$.
+  Moreover $\bijection(t)[1] = \bijection(\sigma)[1]$ 
+  thus $t[1]$ and $\sigma[1]$ are both either the minimal or the maximal
+  element of their respective subsequences.
+  Therefore, $t$ is a matching of $\sigma$ in $\pi$.
+  \qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}
+According to Lemma~\ref{Proposition:both permutations are avoiding} the problem reduces
+to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$.
+A straightforward greedy approach solves this issue in linear-time.
+\qed
+\end{proof}
+
+\bigskip
+
+%\begin{proof}[of Lemma~\ref{lemma:whereIsMax}]
+%Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
+%Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
+%Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
+%$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
+%According to Lemma~
+%\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is 
+%the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, 
+%and hence
+%$\first{\sigma}{i-1}$ is the maximal  element of
+%$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
 %
+%A similar argument shows that the lemma holds true if the rightmost element
+%of $\factor{\sigma}{i}$ is a descent.
+%\qed
+%\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:ts}]
+By definition $s$ is a matching of $\ppattern[\LMEi(\factor(i)):]$.
+To prove that $ts$ is an matching of $\ppattern[\LMEi(\factor(i+1)):]$ we need to prove that every element of t is larger than every element of $s$.
+If $ts'$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ then every element of $t$ is larger than every element of $s'$.
+Moreover the maximal element of $s$ is smaller than  the maximal element of $s'$ so every element of $s$ is smaller than every element of $s'$ thus every element of $s$ is smaller than every element of $t$.
+We use a similar argument if $\factor(i)$ is a descent factor.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Lemma~\ref{lemma:ascentDescentAscent}]
+Suppose that there exists $l$, $i<l<j$,
+such that $\ppattern[l]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[l]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
+We use a similar argument if $\sigma[i]$ is a descent element
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Proposition~\ref{proposition:longestIncreasingSubsequence}]
+Let $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
+suppose that $P(s)$ is not a longest increasing subsequence with last element at index $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
+Thus $|s_m|>|A(s)|$, clearly the sequence $s_m \cup D(s)$
+is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
+The same idea can be used to show that $D(\pi)$ is the longest decreasing subsequence.
+\qed
+\end{proof}
+
+\bigskip
+
+\begin{proof}[of Proposition~\ref{proposition:longest 2}]
+The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
+where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
+Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
+$O(n\log(\log(n)))$ time and $O(n)$ space 
+(see \cite{Bespamyatnikh00enumeratinglongest}), 
+then finding the maximal can be done in linear time.
+\qed
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-03-24 article.tex
merge appendix
correction from the reviews

@@
 \newcommand{\ustep}{a}
+
+% MACRO % % % % % % % % % % % % % % % % % % % % % %
+\newcommand{\isbelow}{<_y}
+\newcommand{\isabove}{>_y}
+
+\newcommand{\ontheleft}{<_x}
+\newcommand{\ontheright}{>_x}
+
+\newcommand{\borneinf}{inf}
+\newcommand{\bornesup}{sup}
 
@@
 Given permutations $\sigma \in S_k$ and $\pi \in S_n$ with $k<n$, the
-  \emph{pattern matching} problem is to decide whether $\pi$ matches
-  $\sigma$ as an order-isomorphic subsequence.
+\emph{pattern matching} problem is to decide whether $\sigma$ occurs
+$\pi$ as an order-isomorphic subsequence.
 We give a linear-time algorithm in case both $\pi$ and $\sigma$ avoid
@@
 
-	A permutation $\pi$ is said to match another permutation $\sigma$,
-	in symbols $\sigma \preceq \pi$,
+A permutation $\sigma$ is said to occur in another permutation $\pi$,
+denoted $\sigma \preceq \pi$,
 if there exists a subsequence of elements of $\pi$ that has the same relative
@@
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
-	For example a permutation matches the pattern $123$ (resp. $321$) if it has
+For example a permutation has an occurrence of the pattern $123$ (resp. $321$) if it has
 an increasing (resp. decreasing) subsequence of length $3$.
-	As another example,
-	$6152347$ matches $213$ but not $231$.
-	During the last decade, the study of the pattern matching on permutations has
-	become a very active area of research \cite{Kitaev:book:2011} and
-	a whole annual conference (\textsc{Permutation Patterns}) is now devoted
-	to this topic.
+Similarly,
+$6152347$ has an occurrence of $213$ but not $231$.
+During the last decade, the study of the pattern matching for permutations has
+become a very active area of research \cite{Kitaev:book:2011}. and
+a whole annual conference (\textsc{Permutation Patterns}) focuses
+on pattern in permutation.
 
@@
 Given two permutations $\sigma$ and $\pi$, this problem is to decide whether
-	$\sigma \preceq \pi$ (the problem is ascribed to Wilf in \cite{Bose:Buss:Lubiw:1998}).
-	The permutation matching problem is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
+$\sigma \preceq \pi$ (the problem is attributed to Wilf in \cite{Bose:Buss:Lubiw:1998}).
+The pattern matching for permutations is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
 It is, however, polynomial-time solvable by brute-force enumeration
@@
 the latter describing a $O(|\pi|^{0.47|\sigma|+o(|\sigma|)})$ time algorithm.
-	Bruner and Lackner $\cite{DBLP:journals/corr/abs-1204-5224}$
-	gave a fixed-parameter algorithm solving the pattern matching problem with
-	an exponential worst-case runtime of $O(1.79^{\RUN(\pi)})$,
-	where $\RUN(\pi)$ denotes the number of alternating runs of $\pi$.
+Bruner and Lackner \cite{DBLP:journals/corr/abs-1204-5224}
+gave a fixed-parameter algorithm solving the pattern matching for permutations problem with
+an exponential worst-case runtime of $O(1.52^{n}.n.k)$,
 (This is an improvement upon the $O(2^{|\pi|})$ runtime required by
@@
 They showed that
-	the permutation matching problem is fixed-parameter tractable (FPT) for
+the pattern matching for permutations problem is fixed-parameter tractable (FPT) for
 parameter $|\sigma|$.
 
-	A few particular cases of the pattern matching problem have been attacked successfully.
+A few particular cases of the pattern matching for permutations problem have been attacked successfully.
 The case of increasing patterns is solvable in
@@
 \cite{Albert:Aldred:Atkinson:Holton:ISAAC:2001}.
-	Algorithmic issues for $321$-avoiding patterns matching has been investigated in
-	\cite{Guillemot:Vialette:ISAAC:2009}.
-	The pattern matching problem is also solvable in
+Algorithmic issues for $321$-avoiding patterns matching for permutations have been investigated in
+\cite{Guillemot:Vialette:ISAAC:2009} and more recently in \cite{2015arXiv151006051A}.
+The pattern matching for permutation problem is also solvable in
 polynomial-time for separable patterns \cite{Ibarra:1997,Bose:Buss:Lubiw:1998}
-	(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for LCS-like issues
-	of separable permutations).
-	Separable permutations are those permutations that match neither
-	$2413$ nor $3142$, and they are enumerated by the Schr{\"o}der numbers
+(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for Longest common subsequence problem and related one on separable permutations).
+Separable permutations are permutations that do not have an occurrence of
+$2413$ nor $3142$, and they are enumerated by the Schr{\"o}der numbers.
 %	(sequence A006318 in OEIS).
@@
 
-	There exists many generalisation of patterns that are worth considering
+There exist many generalisations of patterns that are worth considering
 in the context of algorithmic issues in pattern matching
@@
 resemble (classical) patterns with the additional constraint that some of the elements in
-	a matching must be consecutive in postitions.
+a occurrence must be consecutive in postitions.
 Of particular importance in our context,
@@
 proved that deciding whether a vincular pattern
-	$\sigma$ of length $k$ can be match to a longer permutation
+$\sigma$ of length $k$ can occur in a longer permutation
 $\pi$ is $W[1]$-complete for
 parameter $k$;
-	for an up to date survey of the $W[1]$ class and related material, see
+for an up-to-date survey of the $W[1]$ class and related material, see
 \cite{Downey:Fellows:2013}.
@@
 We focus in this paper on pattern matching issues for
-	$(213,231)$-avoiding permutations
+$(213,231)$-avoiding permutations that we call wedge permutations.
 (\emph{i.e.}, those permutations that avoid both $213$ and $231$).
-	The number of $n$-permutations that avoid both
-	$213$ and $231$ is
+The number of $n$-wedge permutations is
 $t_0 = 1$ for $n = 0$ and
-	$t_n =2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985}.
+$t_n =2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985},
+as they are in bijection with binary word of size $n-1$.
 On an individual basis,
-	the permutations that do not match the permutation pattern $231$
+the permutations that do not have an occurrence of the permutation pattern $231$
 are exactly the \emph{stack-sortable permutations} and they are counted by
 the Catalan numbers \cite{Knuth:1997:ACP:260999}.
-	A stack-sortable permutation is a permutation whose elements may be sorted by
-	an algorithm whose internal storage is limited to a single stack data structure.
-	As for $213$, it is well-known that
- 	if $\pi = \pi_1\pi\,\ldots\,\pi_n$ avoids $132$, then its complement
- 	$\pi' = (n+1-\pi_1)(n+1-\pi_2)\,\ldots\,(n+1-\pi_n)$ avoids $312$, and
- 	the reverse of $\pi'$ avoids $213$.
+%	A stack-sortable permutation is a permutation whose elements may be sorted by
+%	an algorithm whose internal storage is limited to a single stack data structure.
+%	As for $213$, it is well-known that
+% 	if $\pi = \pi_1\pi\,\ldots\,\pi_n$ avoids $132$, then its complement
+% 	$\pi' = (n+1-\pi_1)(n+1-\pi_2)\,\ldots\,(n+1-\pi_n)$ avoids $312$, and
+% 	the reverse of $\pi'$ avoids $213$.
 % From a combinatorial point of view,
@@
 an online linear-time algorithm in case both 
-	permutations are $(213,231)$-avoiding,
+permutations are wedge permutations,
 whereas Section~\ref{section:sigma only avoid 231 and 213} focuses on the case
-	where only the pattern is $(213,231)$-avoiding.
+where only the pattern is a wedge permutation.
 In Section~\ref{section:bivincular} we give a polynomial-time algorithm
-	for $(213,231)$-avoiding bivincular patterns.
+for a bivincular wedge permutations pattern.
 In Section~\ref{section:LCS} we consider the problem of finding the longest
-	$(213,231)$-avoiding pattern in permutations.
+wedge permutations pattern in permutations.
 
@@
 
-A \emph{permutation} of length $n$ is a one-to-one function from an
-$n$-element set to itself.
-We write permutations as words
+A \textit{permutation} of size $n$ is a linear ordering of an ordered set of size $n$.
+When writing the permutation we omit the $<$ sign, thus
+writing the permutation as a word  :
 $\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose elements are distinct
-and usually consist of the integers $12\,\ldots\,n$, and we let
-$\pi[i]$ stands for $\pi_i$.
-For the sake of convenience, we let
-$\pi[i:j]$ stand for
+and usually consist of the integers $12\,\ldots\,n$. 
+We let $\pi[i]$ stands for $\pi_i$.
+Conveniently, we let
+$\pi[i:j]$ stands for
 $\pi_i\pi_{i+1}\,\ldots\,\pi_j$,
-$\pi[:j]$ stand for $\pi[1:j]$ and
-$\pi[i:]$ stand for $\pi[i:n]$.
-As usual, we let $S_n$ denote the set of all permutations of length $n$.
+$\pi[:j]$ stands for $\pi[1:j]$ and
+$\pi[i:]$ stands for $\pi[i:n]$.
+
+We need to consider both the natural order of the set
+and the linear order given by the permutation.
+When talking about an element,
+we refer to the relative position in
+the natural order of the set
+as its value 
+and 
+we refer to the relative position
+in the order given by the permutation 
+as its position.
+We write 
+$\pi[i]$ to indicate the value of the element 
+at position $i$.  
+For example, in the permutation $\pi = 51342$,
+The element $1$ is at position $2$
+and the element at position $1$ has for value $5$.
+
 It is convenient to use a geometric representation of permutation
 to ease the understanding of algorithms. 
-The geometric representation corresponds to the set of point with coordinate $(i,\pi[i])$
-(see figure \ref{example: pattern matching}).
+The geometric representation corresponds to the set of points with coordinate $(i,\pi[i])$
+(see Figure \ref{example: pattern matching}).
+
+When an element $e_1$ is smaller (resp. bigger)
+than an element $e_2$  by value (in the natural order of the set),
+we say that $e_1$ is below (resp. above) $e_2$,
+as a reference to the figure of the permutation.
+Besides, the element with the biggest value is called
+the topmost element and the element with the smallest value
+is called the bottommost element.
+For example, in the permutation $\pi = 51342$,
+$2$ is below $4$, the topmost element is $5$
+and the bottommost element is $1$.
+
+When an element $e_1$ is smaller (resp. bigger)
+than an element $e_2$  by position (in the order given by the permutation),
+we say that $e_1$ is on the left of (resp. on the right of) $e_2$.
+Besides, the element with the biggest position is called the rightmost element
+and the element with the smallest position is called the leftmost element.
+For example, in the permutation $\pi = 51342$,
+$5$ is on the left of $3$, the leftmost element is $5$
+and the rightmost element is $2$.
 
@@
 
-A permutation $\pi$ is said to \emph{match} the permutation $\sigma$
+A permutation $\sigma$ is said to \emph{occur} in the permutation $\pi$, written $\sigma \preceq \pi$,
 if there exists a subsequence of (not necessarily consecutive)
-element of $\pi$ that has the same relative order as $\sigma$,
-and in this case $\pi$ is said to match $\sigma$, 
-written $\sigma \preceq \pi$.
+elements of $\pi$ that has the same relative order as $\sigma$.
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
 For example, the permutation $\pi = 391867452$
-matches the pattern $\sigma = 51342$,
+has an occurrence of the pattern $\sigma = 51342$,
 as can be seen in the highlighted subsequence of
@@
 $91452$,
- in $\pi$ is called a
-\emph{matching}
+ in $\pi$ is called an
+\emph{occurrence}
 of $\sigma$.
@@
 length four, $\pi$ avoids $1234$.
-Geometrically, $\pi$ matches $\sigma$ if there exists
-a set of point in $\pi$ that is isomorph to the set of point of $\sigma$. In other word,
-if there exists a set of point in $\pi$ with the same disposition as the set of point of $\sigma$, without regard to the distance (see figure \ref{example: pattern matching}).
+
+For an occurrence $s$ of $\sigma$ in $\pi$, 
+we say that $\pi[j]$ is a matching of $\sigma[i]$ or 
+that $\sigma[i]$ is matched to $\pi[j]$  
+if and only if $\pi[j]=s[i]$.
+
+Geometrically, $\pi$ has an occurrence of $\sigma$ if there exists
+a set of points in $\pi$ that is isomorphic to the set of points of $\sigma$. 
+In other words,
+if there exists a set of points in $\pi$ with the same disposition as the set of points of $\sigma$, 
+regardless of the distance (see Figure \ref{example: pattern matching}).
 
@@
 		The pattern $\sigma=51342$
-		and four matchings of $\sigma$ in $391867452$.} 
+		and four occurrences of $\sigma$ in $391867452$.} 
 	\label{example: pattern matching}
@@
 
-Suppose $P$ is a set of permutations. We let $\AV_n(P)$ denote the
-set of all $n$-permutations avoiding each permutation in $P$.
-For the sake of convenience
-(and as it is customary~\cite{Kitaev:book:2011}), we omit $P$'s braces thus having
-e.g. $\AV_n(213,231)$ instead of
-$\AV_n(\{213,231\})$.
-If $\pi \in \AV_n(P)$, we also say that $\pi$ is
-\emph{$P$-avoiding}.
+%Suppose $P$ is a set of permutations. We let $\AV_n(P)$ denote the
+%set of all $n$-permutations avoiding each permutation in $P$.
+%For the sake of convenience
+%(and as it is customary~\cite{Kitaev:book:2011}), we omit $P$'s braces thus having
+%e.g. $\AV_n(213,231)$ instead of
+%$\AV_n(\{213,231\})$.
+%If $\pi \in \AV_n(P)$, we also say that $\pi$ is
+%\emph{$P$-avoiding}.
+
 % A basic example is if
@@
 
-An \emph{ascent} of a permutation $\pi \in S_n$ is any element
-$1 \leq i < n$ where the following value is bigger than the current one.
-That is, if $\pi = \pi_1\pi_2\,\ldots\,\pi_n$, then
-$\pi_i$ is an ascent if $\pi_i < \pi_{i+1}$.
+An \emph{ascent element} of an $n$-permutation $\pi \in S_n$ is any element
+$\pi[i]$ such that $i<n$ and $\pi[i] < \pi[i+1]$.
 For example, the permutation
@@
 Similarly, a \emph{descent} is any element
-$1 \leq i < n$ with $\pi_i > \pi_{i+1}$,
-so for every $1 \leq i < n$, $\pi_i$  is either an ascent or is a descent of
+$\pi[i]$ such that $i<n$ and $\pi[i] > \pi[i+1]$.
+So for every $1 \leq i < n$, $\pi[i]$  is either an ascent or a descent of
 $\pi$.
@@
 
-A $\textit{left to right maxima}$ (abbreviate LRMax) of $\pi$ is a element that does not have any element bigger than it on its right (see fig.
-$\ref{fig:left to right maxima}$).
-Formally, $\pi[i]$ is a LRMax if and only if $\pi[i]$ is the biggest element of $\pi[i:]$.
-Similarly $\pi[i:]$ is a $\textit{left to right minima}$ (abbreviate LRMin) if and only if $\pi[i]$ is the smallest element of $\pi[i:]$.
+A $\textit{right to left maximum}$ (abbreviate RLMax) of $\pi$ is an element that does not have any element above it at its right (see Figure $\ref{fig:left to right maxima}$).
+Formally, $\pi[i]$ is a RLMax if and only if $\pi[i]$ is topmost element of $\pi[i:]$.
+Similarly $\pi[i]$ is a $\textit{left to right minima}$ (abbreviate RLMin) if and only if $\pi[i]$ is the bottommost element of $\pi[i:]$.
 
@@
 	\caption[Example pattern matching]{
-		The element is a LRMax if and only if the dashed area is empty.} 
+		The element is a RLMax if and only if the dashed area is empty.} 
 	\label{fig:left to right maxima}
@@
 two-line notation
-(that is the top row is $12\,\ldots\,k$ and the bottom row
-is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$).
+(the top row is $12\,\ldots\,k$ and the bottom row
+is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$)
+with overlined elements in the top row and underlined element in the bottom row.
 We have the following conditions on the top and bottom rows
-of $\sigma$, as see in \cite{Kitaev:book:2011} in definition 1.4.1:
+of $\sigma$, as see in \cite{Kitaev:book:2011} in Definition 1.4.1:
 \begin{itemize}
@@
 	then the elements corresponding to
-	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in a matching of
+	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in a occurrence of
 	$\sigma$ in $\pi$ must be adjacent, whereas there is
@@
 	Moreover if the bottom row of $\sigma$ begins with
-	$_\llcorner{\sigma_1}$ then any matching of $\sigma$
+	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$
 	in a permutation $\pi$ must begin with the leftmost
@@
 	if the bottom row of $\sigma$ begins with
-	${\sigma_k}_\lrcorner$ then any matching of $\sigma$
+	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$
 	in a permutation $\pi$ must end with the rightmost
@@
 	$i, i+1, \ldots, j$ in an
-	matching of $\sigma$ in $\pi$ must be adjacent in values,
+	occurrence of $\sigma$ in $\pi$ must be adjacent in values,
 	whereas there is no value adjacency restriction for non-overlined
@@
 	$^\ulcorner{1}$ then
-	any matching of $\sigma$ is a permutation $\pi$ must contain 
-	the smallest element of $\pi$, and
+	any occurrence of $\sigma$ is a permutation $\pi$ must contain 
+	the bottommost element of $\pi$, and
 	if top row of $\sigma$ ends with $k^\urcorner$ then
-	any matching of $\sigma$ is a permutation $\pi$ must contain
-	the largest element of $\pi$.
-
+	any occurrence of $\sigma$ is a permutation $\pi$ must contain
+	the topmost element of $\pi$.
 \end{itemize}
@@
 $\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$.
-In $3217845$, $\textbf{32}17\textbf{84}5$ is a matching of $\sigma$ but
+In $3217845$, $\textbf{32}17\textbf{84}5$ is an occurrence  of $\sigma$ but
  $3\textbf{21}\textbf{7}8\textbf{4}5$ is not.
@@
 Geometrically, We represent underlined and overlined elements by \textit{forbidden areas}.
-A vertical area between two points indicates that the two matching of those points must be consecutive in positions, whereas a horizontal area between two points indicates that the two  matching of those points must be consecutive in value.
-The forbidden areas can be understand as follow : in a matching, the forbidden areas must be empty.
-Thus,
-$\pi$ matches a bivincular pattern $\sigma$ if there exists a set of point in $\pi$ that is isomorph to $\sigma$ and if
-the forbidden areas are empty.
-(see figure \ref{example:bivincular pattern matching}).
+If two elements are overlined then we draw a vertical forbidden areas between those two points.
+In an occurrence, we also draw the forbidden area between the matching of two overlined elements.
+This area must be empty for an occurrence to be called so. 
+If the area is empty then there is no element between them when reading the permutation
+from bottom to top, 
+in other words the matching elements are consecutive in value.
+If two elements are underlined then we draw an horizontal forbidden area.
+(See figure \ref{example:bivincular pattern matching}).
 
@@
     		From left to right,
-    		the bivincular pattern $\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$, A matching of $\sigma$ in $3216745$, A matching of $2143$ in $3216745$ but not a matching of $\sigma$ in $3216745$ because the point $(1,3)$ and $(5,7)$ are in the forbidden area.}
+    		the bivincular pattern $\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$, An occurrence of $\sigma$ in $3216745$, An occurrence of $2143$ in $3216745$ but not an occurrence of $\sigma$ in $3216745$ because the point $(1,3)$ and $(5,7)$ are in the forbidden area.}
     	\label{example:bivincular pattern matching}
@@
 
-\section{Both $\pi$ and $\sigma$ are $(213,231)$-avoiding}
+\section{Both $\pi$ and $\sigma$ are wedge permutation}
 \label{section:both are (213,231)-avoiding}
@@
 $\sigma \preceq \pi$
-in case both $\pi$ and $\sigma$ are $(213,231)$-avoiding.
+in case both $\pi$ and $\sigma$ are wedge permutations.
 We begin with an easy but crucial structure lemma.
 
-\begin{lemma}[Folklore]
+\begin{lemma} %[Folklore]
 \label{lemma:first element is 1 or n}
-The first element of any $(213,231)$-avoiding permutation
-must be either the minimal or the maximal element.
+The first element of any wedge permutations
+must be either the bottommost or the topmost element.
 \end{lemma}
+
+\begin{proof}[of Lemma~\ref{lemma:first element is 1 or n}]
+Any other initial element would serve as a `$2$' in either a
+$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+\qed
+\end{proof}
 
@@
 \label{corollary:minmaxelement}
-$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i < n$,
-$\pi[i]$ is a LRMax or a LRMin.
+$\pi$ is a wedge permutation if and only if for $1 \leq i \leq n$,
+$\pi[i]$ is a RLMax or a RLMin.
 \end{corollary}
@@
 \label{corollary:max is ascent}
-Let $\pi \in \AV_n(213,231)$ and $1 \leq i < n$. Then,
+Let $\pi$ be a wedge permutation and $1 \leq i < n$. Then,
 (1) 
-$\pi[i]$ is an ascent element if and only if $\pi[i]$ is a LRMin
+$\pi[i]$ is an ascent element if and only if $\pi[i]$ is a RLMin
 and 
 (2)
-$\pi[i]$ is a descent element if and only if $\pi[i]$ is a LRMax
+$\pi[i]$ is a descent element if and only if $\pi[i]$ is a RLMax
 \end{corollary}
 
-Lemma $\ref{corollary:max is ascent}$ gives a bijection between $\AV_n(213,231)$ and the set of binary word of size $n-1$.
-The bijected word $w$ of $\pi$, is the word where each letter at position $i$ represents if $\pi[i]$ is an ascent or descent element (or is a LRMax or a LRMin).
+Corollary $\ref{corollary:max is ascent}$ gives a bijection between the set of wedge permutations and the set of binary word of size $n-1$.
+The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$ represents whether $\pi[i]$ is an ascent or descent element (equivalently, is a RLMax or a RLMin).
 We call this bijection $\bijection$.
 
-A $(213,231)$-avoiding permutation has a particular form.
-If we take only the descent elements, the points draw a north-east to south-west line
-and if we take only the ascent elements, the points draw a south-east to north-west line.
-This shape the permutation as a $>$. For convenience when drawing a random $(213,231)$-avoiding permutation
-we will sometime represent a sequence of ascent/descent element by lines (see figure \ref{fig:shape of the permutation} and \ref{fig:shape of the permutation plus factor}).
+A wedge permutation has a particular form that gives its name.
+If we take only the descent elements, 
+they form a decreasing subsequence
+and the ascent elements form an increasing subsequence.
+Moreover the descent elements are above the ascent elements.
+This shapes the permutation as a $>$.
+
+%For convenience when drawing a random wedge permutation
+%we will sometime represent a sequence of ascent/descent element by lines (see Figure \ref{fig:shape of the permutation} and \ref{fig:shape of the permutation plus factor}).
 
@@
 
-	\caption{The $(213,231)$-avoiding permutation $123984765$, every point which is on a north-east to south-west line represents a descent element and every point which is on a south-east to north-west line represents an ascent element.}
+	\caption{The wedge permutation $123984765$, every point which is on a north-west to south-east line represents a descent element and every point which is on a south-west to north-east line represents an ascent element.}
 	\label{fig:shape of the permutation}
@@
 \label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations,
-Then, $\pi$ matches $\sigma$ if and only if 
+Let $\pi$ and $\sigma$ be two wedge permutations,
+Then, $\pi$ has an occurrence of $\sigma$ if and only if 
 there exists a subsequence $t$ of $\pi$ such $\bijection(t)=\bijection(\sigma)$.
@@
 
+\begin{proof}[of Lemma~\ref{lemma:MatchStripeToPermutation}]
+The forward direction is obvious.
+We prove the backward direction by induction on the size of the pattern
+$\sigma$.
+The base case is a pattern of size $2$.
+Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = ascent$.
+Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
+such that $\bijection(t) = ascent$, this reduces to saying that
+$\pi_{i_1} < \pi_{i_2}$, 
+and hence that $t$ is an occurrence of $\sigma = 12$ in $\pi$.
+A similar argument shows that the lemma holds for $\sigma = 21$.
+Now, assume that the lemma is true for all patterns up to size $k \geq 2$.
+Let $\sigma$ be an k-wedge permutation and
+let $t$,
+be a subsequence of $\pi$ of length $k+1$ such that
+$\bijection(t) = \bijection(\sigma)$.
+As $\bijection(t)[2:] = \bijection(\sigma)[2:]$
+by the inductive hypothesis, it follows that
+$t[2:]$ is an occurrence of $\sigma[2:]$.
+Moreover $\bijection(t)[1] = \bijection(\sigma)[1]$ 
+thus $t[1]$ and $\sigma[1]$ are both either the bottommost or the topmost
+element of their respective subsequences.
+Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
+\qed
+\end{proof}
+
 We are now ready to solve the pattern matching problem in case
-both $\pi$ and $\sigma$ are $(213, 231)$-avoiding.
+both $\pi$ and $\sigma$ are wedge permutations.
 
@@
 \label{Proposition:both permutations are avoiding}
-	Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations.
-	One can decide whether $\pi$ matches $\sigma$ in linear time.
+Let $\pi$ and $\sigma$ be two wedge permutations.
+One can decide whether $\pi$ has an occurrence of $\sigma$ in linear time.
 \end{proposition}
 
+\begin{proof}
+According to Lemma~\ref{Proposition:both permutations are avoiding} the problem reduces
+to deciding whether $\bijection(\sigma)$ occurs as a subsequence in $\bijection(\pi)$.
+A straightforward greedy approach solves this issue in linear-time,
+by reading both words from left to right and matching two letters when they are equal then passing
+to the next letters for both words
+or passing to the next letter in the word of the text.
+\qed
+\end{proof}
+
 Thank to Corollary~\ref{corollary:max is ascent},
-we can compute the bijected words in the same time that we running the greedy algorithm, this gives us a on-line algorithm.
+we do not need to compute the word corresponding to the permutations before running the greedy algorithm. This computation can be done in the same time with the algorithm,
+thus, this gives on-line algorithm.
 
@@
 
-\section{$\sigma$ only is $(213,231)$-avoiding}
+\section{Only $\sigma$ is a wedge permutation}
 \label{section:sigma only avoid 231 and 213}
@@
 This section focuses on the pattern matching problem
-in case only the pattern $\sigma$ avoids $231$ and $213$.
+in case only the pattern $\sigma$ is a wedge permutation.
 We need to consider a specific decomposition of $\sigma$ into \textit{factor} :
-we split the permutation into largest sequences of ascent element and descent element, respectively called an ascent factor and a descent factor.
-This correspond to split the permutation between every pair of ascent-descent element and descent-ascent element (see figure \ref{fig:shape of the permutation plus factor}).
-For the special case of $(213,231)$-avoiding, this correspond to split the permutation into largest sequence of consecutive element.
+we split the permutation into maximal sequences of consecutive ascent and descent elements, respectively called an ascent factor and a descent factor.
+This corresponds to splitting the permutation between every pair of ascent-descent and descent-ascent element (see Figure \ref{fig:shape of the permutation plus factor}).
+For the special case of a wedge permutation, this also corresponds to split the permutation into maximal sequences of element consecutive in value.
 We will label the factors from right to left.
-
-We introduce the notation $\LMEi(s)$ : Suppose that $s$ is a subsequence of $S$, $\LMEi(s)$ is the index of the left most element of $s$ in $S$. Thus
-for every $\factor$, $\LMEi(\factor(j))$ stand for the index in $\sigma$
-of the leftmost element of $\factor(j)$.
 For example,
@@
 $\factor(4) =123$, $\factor(3) = 98$, $\factor(2) = 4$ and $\factor(1) = 765$.
-Furthermore,
-$\LMEi(\factor(4)) = 1$, $\LMEi(\factor(3)) = 4$, $\LMEi(\factor(2)) = 6$ and $\LMEi(\factor(1)) = 7$.
-We represent elements matching an ascent (resp. descent) factor 
-by a rectangle which has the left most matched point of the factor as the left bottom (resp. top) corner and the right most matched point of the factor as the right top (resp. bottom) corner.
-We can remove the two right most rectangles and replace it by the smallest rectangle that contains both of them and repeat this operation to represent part of a matching (see figure \ref{fig:shape of the permutation plus factor plus factor}).
-
-\begin{remark}
-A factor is either an increasing or a decreasing sequence of element.
-Thus while matching a factor, it is enough to find an increasing or a decreasing subsequence of same size or bigger than the factor.
-\end{remark}
 
@@
 	\end{tikzpicture}		
+	\caption{The  wedge permutation $123984765$. Every line represents a factor, every circled point represents the leftmost element of each factor. }
+	\label{fig:shape of the permutation plus factor}
+\end{figure}
+
+We introduce the notation $\LMEi(s)$ : Suppose that $s$ is a subsequence of $S$, $\LMEi(s)$ is the position of the leftmost element of $s$ in $S$. Thus
+for every $\factor$, $\LMEi(\factor(j))$ stands for the position in $\sigma$
+of the leftmost element of $\factor(j)$.
+From the above example,
+$\LMEi(\factor(4)) = 1$, $\LMEi(\factor(3)) = 4$, $\LMEi(\factor(2)) = 6$ and $\LMEi(\factor(1)) = 7$.
+
+To lighten the figure of a wedge permutation, 
+we represent the elements of an ascent (resp. descent) factor 
+by a rectangle which has the matching of the leftmost point of the factor as the left bottom (resp.
+top) corner and the matching of the rightmost point of the factor as the right top (resp.
+bottom) corner.
+We can merge the two rightmost rectangles and replace them by the smallest rectangle that contains both of them and repeat this operation to represent part of an occurrence (see Figure \ref{fig:decomposition of an occurrence}).
+
+\begin{figure}[t] 
+	\centering	
 	\begin{tikzpicture}[scale=.3]
-
-	\draw (0,0) -- (1,1);
-	\draw (1,9) -- (2,8);
-	\draw (2,1) -- (3,2);
-	\draw (4,8) -- (5,7);
-
-	\draw[fill=black] (6.5,5) circle (1mm);
-	\draw[fill=black] (7,5) circle (1mm);
-	\draw[fill=black] (7.5,5) circle (1mm);
-
-	\draw (9,6) -- (10,5);
-	\draw (10,4) -- (11,5);
-
-	\draw[fill=black,double, double distance=0.5pt] (0,0) circle (1mm);
-	\draw[fill=black,double, double distance=0.5pt] (1,9) circle (1mm);
-	\draw[fill=black,double, double distance=0.5pt] (2,1) circle (1mm);
-	\draw[fill=black,double, double distance=0.5pt] (4,8) circle (1mm);
-	\draw[fill=black,double, double distance=0.5pt] (9,6) circle (1mm);
-	\draw[fill=black,double, double distance=0.5pt] (10,4) circle (1mm);
-
-	\end{tikzpicture}	
-	\begin{tikzpicture}[scale=.3]
-
-	\fill[blue!40!white] (1.5,1.5) rectangle (2.5,0.5);
-	\fill[blue!40!white] (4.5,8.5) rectangle (6.5,6.5);
-	\fill[blue!40!white] (7.5,3.5) rectangle (8.5,5.5);
-
-	\draw[red,dashed] (1.5,1.5) rectangle (2.5,0.5);
-	\draw[red,dashed] (4.5,8.5) rectangle (8.5,3.5);
-
-	\draw[green,dashed] (1.5,0.5) rectangle (8.5,8.5);
 
@@
 	\draw[fill=black, double distance=1pt] (8.5,5.5) circle (2mm);
-
-	\end{tikzpicture}
-
-	\caption{The left figure is the  $(213,231)$-avoiding permutation $123984765$. Every line represents a factor, every circled point represents the left most element of each factor. 
-	The central figure is a generalisation of $(213,231)$-avoiding permutation.	
-	The right figure represents a matching of $1276534$ in $312598746$, the blue rectangles represent the matching, the red dotted rectangles represent the matching after the first replacement and the green rectangle represents the matching after the second replacement.}
-	\label{fig:shape of the permutation plus factor}
+	\end{tikzpicture}				
+	\begin{tikzpicture}[scale=.3]
+
+	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+		\draw[dotted] (0,\i) -- (9, \i);
+		\draw[dotted] (\i,0) -- (\i, 9);
+	}
+	\draw[fill=black] (0.5,2.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (1.5,0.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (2.5,1.5) circle (2mm);
+	\draw[fill=black] (3.5,4.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (4.5,8.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (5.5,7.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (6.5,6.5) circle (2mm);
+%	\draw[fill=black, double distance=1pt] (7.5,3.5) circle (2mm);
+%	\draw[fill=black, double distance=1pt] (8.5,5.5) circle (2mm);
+	\draw [pattern=north east lines] (1.5,1.5) rectangle (2.5,0.5);
+	\draw [pattern=north east lines] (4.5,8.5) rectangle (6.5,6.5);
+	\draw [pattern=north east lines] (7.5,3.5) rectangle (8.5,5.5);
+
+	\end{tikzpicture}
+	\begin{tikzpicture}[scale=.3]
+
+	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+		\draw[dotted] (0,\i) -- (9, \i);
+		\draw[dotted] (\i,0) -- (\i, 9);
+	}
+	\draw[fill=black] (0.5,2.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (1.5,0.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (2.5,1.5) circle (2mm);
+	\draw[fill=black] (3.5,4.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (4.5,8.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (5.5,7.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (6.5,6.5) circle (2mm);
+%	\draw[fill=black, double distance=1pt] (7.5,3.5) circle (2mm);
+%	\draw[fill=black, double distance=1pt] (8.5,5.5) circle (2mm);
+
+	\draw [pattern=north east lines] (1.5,1.5) rectangle (2.5,0.5);
+	\draw [pattern=north east lines] (4.5,8.5) rectangle (8.5,3.5);
+	%\fill[black] (7.5,3.5) rectangle (8.5,5.5);
+
+	\end{tikzpicture}
+	\begin{tikzpicture}[scale=.3]
+
+	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+		\draw[dotted] (0,\i) -- (9, \i);
+		\draw[dotted] (\i,0) -- (\i, 9);
+	}
+	\draw[fill=black] (0.5,2.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (1.5,0.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (2.5,1.5) circle (2mm);
+	\draw[fill=black] (3.5,4.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (4.5,8.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (5.5,7.5) circle (2mm);
+%	\draw[fill=black,double, double distance=1pt] (6.5,6.5) circle (2mm);
+%	\draw[fill=black, double distance=1pt] (7.5,3.5) circle (2mm);
+%	\draw[fill=black, double distance=1pt] (8.5,5.5) circle (2mm);
+
+	\draw [pattern=north east lines] (1.5,1.5) rectangle (8.5,8.5);
+	%\draw [pattern=north east lines] (4.5,8.5) rectangle (8.5,3.5);
+	%\fill[black] (7.5,3.5) rectangle (8.5,5.5);
+
+	\end{tikzpicture}
+
+	\caption{The operation of merging the two rightmost rectangle.}
+	\label{fig:decomposition of an occurrence}
 \end{figure}
+
+\begin{remark}
+A factor is either an increasing or a decreasing sequence of element. 
+Thus to find an occurrence for a factor, one must find an increasing or a decreasing subsequence of same size or bigger than the factor.
+\end{remark}
 
@@
 \label{corollary:whereIsMax}
-Given a permutation $\sigma \in \AV(213,231)$ and a suffix of its 
-decomposition $\factor(i)$ $\factor(i-1)$ $\ldots$ $\factor(1)$, 
+Given a wedge permutation $\sigma$, 
 if $\factor(i)$ is an ascent (respectively descent) factor 
-then the maximal (resp. minimal) element of $\factor(i)$ $\factor(i-1)$ $\ldots$ $\factor(1)$
-is the left most element of $\factor(i-1)$
+then topmost (resp. bottommost) element of $\ppattern[\LMEi(\factor(i+1)):]$
+is the leftmost element of $\factor(i-1)$.
 \end{corollary}
 
-This is a corollary of lemma \ref{lemma:first element is 1 or n}.
-This states that given a permutation in $\AV(213,231)$ 
-if the permutation starts with ascent (respectively descent) elements then the maximal (resp.
-minimal) element of this permutation is the first descent (resp.
-ascent) element (see figure \ref{fig:where to find the max}).
+\begin{proof}[of Corollary~\ref{corollary:whereIsMax}]
+This corollary states that, given a wedge permutation 
+if the permutation starts with an ascent (respectively descent) elements then the topmost (resp.
+bottommost) element of this permutation is the first descent (resp.
+ascent) element (see Figure \ref{fig:where to find the max}).
+This is easy to see from Corollary  \ref{corollary:max is ascent}.
+The ascent elements are below the descent element, thus the topmost element must be 
+the first descent element, which is the leftmost element of $\factor(i-1)$.
+\qed
+\end{proof}
 
@@
 
-	\draw (0,0) -- (1,1);
-	\draw (2,10) -- (3,9);
+%	\draw (0,0) -- (1,1);
+%	\draw (2,10) -- (3,9);
 
@@
 
-	\draw [blue] (6,2) -- (7,3);
+	\draw (6,2) -- (7,3);
 	\draw (7,7) -- (8,6);
@@
 
-	\draw[fill=black] (7,7) circle (2mm);
-	\draw[fill=blue] (6,2) circle (2mm);
-
-	\draw[dotted,-] (0,7) -- (13,7) node[right] {Maximal y-coordinate};
-	\draw[dotted,-] (0,2) -- (13,2) node[right] {Minimal y-coordinate};
+	\draw[fill=gray] (7,7) circle (2mm) node[above] {factor(i-1)};
+	\draw[fill=black] (6,2) circle (0mm) node[below] {factor(i)};;
+
+	\draw[dotted,-] (0,7) -- (13,7) node[right] {topmost element};
+	\draw[dotted,-] (0,2) -- (13,2) node[right] {bottommost element};
 
@@
 	\caption{
-		The maximal element of the suffix starting at  $\factor(i)$ (represented by the blue line)
-		is the left most element of $\factor(i-1)$ (represented by the the black dot).
-		$\LM{\ppattern}{\ptext}{i}{j}$ is the minimal value of the matching of the maximal element (the black dot) in all the matchings of the suffix starting at $\LMEi(\factor(i))$ (the blue dot) in $\pi[j:]$.
+		The topmost element of the suffix starting at  $\factor(i)$ 
+		is the leftmost element of $\factor(i-1)$ (represented by the grey dot).
+		$\LM{\ppattern}{\ptext}{i}{j}$ is the smallest value of the matching of the topmost element (the grey dot) in all the occurrences of the suffix starting at $\LMEi(\factor(i))$ in $\pi[j:]$.
 	}	
@@
 
-We now define the set
+We define the set
 $\SET{\ppattern}{\ptext}{i}{j}$ 
 as the set of every subsequence $s$ of $\ptext[j:]$ that starts at $\ptext[j]$ and
-that is a matching of $\factor(i)$ $\factor(i-1)$ $\ldots$ $\factor(1)$ and .
+that is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$.
 
@@
 $s$ be a subsequence of $\pi$ such that $s \in \SET{\ppattern}{\ptext}{i}{j}$ and
-that minimizes (resp. maximizes) the match of the left most element of $\factor(i-1)$.
+that minimizes (resp. maximizes) the matching of the leftmost element of $\factor(i-1)$.
 For all subsequences 
 $s' \in \SET{\ppattern}{\ptext}{i}{j}$ and for all subsequences $t$ of $\ptext$, such that $t=t's'$, 
-if $t$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ such that the left most element of $\factor(i)$ is matched to $\ptext[j]$ then the subsequence $t's$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ such that the left most element of $\factor(i)$ is matched to $\ptext[j]$.
+if $t$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ such that the leftmost element of $\factor(i)$ is matched to $\ptext[j]$ then the subsequence $t's$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ such that the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
 \end{lemma}
 
-This lemma states that given any matching of $\factor(i+1)$ $\factor(i)$ $\ldots$ $\factor(1)$,
+This lemma states that given any occurrence of $\factor(i+1)$ $\factor(i)$ $\ldots$ $\factor(1)$,
 where $\factor(i)$ is an ascent (resp. descent) factor,
-we can replace the part of the match that match $\factor(i)$ $\ldots$ $\factor(1)$ by any match
-that minimise (resp.
-maximise) the left most element of $\factor(i-1)$.
-Indeed the left most element of $\factor(i-1)$ is the maximal (resp.
-minimal) element of  $\factor(i)$ $\ldots$ $\factor(1)$ (see figure \ref{fig:minimise the max}).
+we can replace the part of the occurrence where $\factor(i)$ $\ldots$ $\factor(1)$ occurs, by any occurrence
+that minimises (resp.
+maximises) the leftmost element of $\factor(i-1)$.
+Indeed the leftmost element of $\factor(i-1)$ is the topmost (resp.
+bottommost) element of  $\factor(i)$ $\ldots$ $\factor(1)$ (see Figure \ref{fig:where to find the max}).
+
+\begin{proof}[of Lemma~\ref{lemma:ts}]
+Let us consider the case where $\factor(i)$ is an ascent factor.
+By definition $s$ is an occurrence of $\ppattern[\LMEi(\factor(i)):]$.
+To prove that $t's$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ we need to prove that the elements of t' are above the elements of $s$.
+If $t's'$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ then the elements of $t'$ are above the elements of $s'$.
+Moreover the topmost element of $s$ is below (or equal to) the topmost element of $s'$ thus the elements of $s$ are below the elements of $t$.
+We use a similar argument if $\factor(i)$ is a descent factor.
+\qed
+\end{proof}
 
@@
 $s$ be a subsequence of $\pi$ such that $s \in \SET{\ppattern}{\ptext}{i}{j}$ and
-that minimizes (resp. maximizes) the match of the left most element of $\factor(i-1)$.
+that minimizes (resp. maximizes) the matching of the leftmost element of $\factor(i-1)$.
 These following statements are equivalent :
 \begin{itemize}
-	\item There exists a 
-	matching of $\ppattern$ in $\ptext$ with the left most element of $\factor(i)$ is matched to $\ptext[j]$.
-	\item There exists a matching $t$ of $\sigma[:\LMEi(\factor(i))-1]$ in $\ptext[:j-1]$  such that $ts$ is a matching of $\ppattern$ in $\ptext$ with the left most element of $\factor(i)$ matched to $\ptext[j]$.
+	\item There exists an occurrence
+	 of $\ppattern$ in $\ptext$ where the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
+	\item There exists an occurrence $t$ of $\sigma[:\LMEi(\factor(i))-1]$ in $\ptext[:j-1]$  such that $ts$ is an occurrence of $\ppattern$ in $\ptext$ with the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
 \end{itemize}
@@
 
-This corollary takes a step further from the previous one, it states that if there is no matching using any match that maximise (resp.
-minimise) the left most element of $\factor(i-1)$ then there does not exist any matching at all.
-This is central to the algorithm because it allows to test only the matching that  maximise (resp.
-minimise) the left most element of $\factor(i-1)$ (see figure \ref{fig:minimise the max}).
+\begin{proof}[of Corollary~\ref{corollary:we can chose a matching}]
+This corollary takes a step further from the previous one, as it states that if there is no occurrence using any occurrence that maximises (resp.
+minimises) the leftmost element of $\factor(i-1)$ then there does not exist any occurrence at all.
+The backward direction is trivial and the forward direction is applying the Lemma~\ref{lemma:ts}.
+\qed
+\end{proof}
+
+This corollary is central to the algorithm because it allows to test only the occurrence that  maximises (resp. minimises) the leftmost element of $\factor(i-1)$.
+
+%\begin{figure}[t] 
+%	\centering	
+%	\begin{tikzpicture}[scale=.3]
+%	
+%	\draw (0,9) rectangle (3,7);
+%	\draw (4,0) rectangle (6,3);
+%	\draw (6,3) rectangle (12,7);
+%	\draw [pattern=north east lines] (6,3) rectangle (12,6);
+%
+%	\end{tikzpicture}
+%
+%	
+%	\caption{In an occurrence, we can replace the rightmost rectangle by the dashed rectangle.}
+%	\label{fig:minimise the max}
+%\end{figure}
+
+% This corollary allows us to way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the pattern then there is no match at all.
+
+\begin{proposition}
+\label{Proposition:sigma avoids 213 and 231}
+Let $\sigma$ be a wedge permutation and $\pi \in S_n$.
+One can decide in $O(max(kn^2,n^2\log(\log(n)))$ time
+and $O(kn^2)$ space if $\pi$ has an occurrence $\sigma$.
+\end{proposition}
+
+\begin{proof}
+
+We first introduce a set of values needed to our proof.
+Let $LIS_{\ptext}(i,j,bound)$ (resp. $LDS_{\ptext}(i,j,bound)$) be the longest increasing 
+(resp. decreasing) sequence in $\ptext[i:j]$ starting at $i$,
+with every element of this sequence being
+smaller (resp. bigger) than $bound$.
+$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
+$O(n^2\log(\log(n)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
+As stated before, those values allow us to find an occurrence of a factor.
+
+Given a factor $i$ of $\sigma$ and a position j of $\pi$,
+we want the optimal value of the matching of $\LMEi(\factor(i-1))$
+in any occurrence of  $\sigma[\LMEi(\factor(i)):]$
+in $\pi[j:]$ starting at $\pi[j]$ (see Figure \ref{fig: algo 1 fig}),
+which we denote as:
+
+$$
+\LM{\ppattern}{\ptext}{i}{j} =
+\begin{cases}
+
+	\text{The minimal value of the matching } 
+		& \text{If $\factor(i)$ is} \\
+	\text{ of $\LMEi(\factor(i-1))$ } 
+		& \text{an ascent factor} \\	
+	\text{ in any occurrence of  $\sigma[\LMEi(\factor(i)):]$ } & \\
+	\text{ in $\pi[j:]$ strarting at $\pi[j]$} & \\
+	\text{Or $\infty$ if no occurrence exists} & \text{} \\
+
+	&\\
+
+	\text{The maximal value of the matching } 
+		& \text{If $\factor(i)$ is} \\
+	\text{ of $\LMEi(\factor(i-1))$ } 
+		& \text{an descent factor} \\	
+	\text{ in any occurrence of  $\sigma[\LMEi(\factor(i)):]$ } & \\
+	\text{ in $\pi[j:]$ strarting at $\pi[j]$} & \\
+	\text{Or $0$ if no occurrence exists} & \text{} \\
+
+\end{cases}
+$$
 
@@
 
-	\fill[blue!40!white] (0,9) rectangle (3,7);
-	\fill[blue!40!white] (4,0) rectangle (6,3);
-	\fill[green!40!white] (6,3) rectangle (12,7);
-
-	%		\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
-	%		\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
-	%			\draw[dotted] (0,\i) -- (9, \i);
-	%			\draw[dotted] (\i,0) -- (\i, 9);
-	%		}
-	\draw[red,dashed] (6,3) rectangle (12,6);
-
-	\end{tikzpicture}
-
-	\caption{In a matching, we can replace the green area by the red dashed area.}
-	\label{fig:minimise the max}
-\end{figure}
-
-% This corollary allows us to way to choose a match. Indeed if one does not find a match such that a well chosen subsequence is a suffix of the pattern then there is no match at all.
-
-\begin{proposition}
-	\label{Proposition:sigma avoids 213 and 231}
-	Let $\sigma \in \AV_k(213,231)$ and $\pi \in S_n$.
-	\\ One can decide in $O(max(kn^2,n^2\log(\log(n)))$ time
-	and $O(kn^2)$ space if $\pi$ matches $\sigma$.
-\end{proposition}
-
-\begin{proof}
-
-We first introduce a set of values needed to our proof.
-Let $LIS_{\ptext}(i,j,bound)$ (resp. $LDS_{\ptext}(i,j,bound)$) be the longest increasing 
-(resp. decreasing) sequence in $\ptext[i:j]$ starting at $i$,
-with every element of this sequence
-smaller (resp. bigger) than $bound$.
-$LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
-$O(n^2\log(\log(n)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
-As stated before, those values allow us to find a matching of a factor.
-
-Now consider the following set of values (see figure \ref{fig: algo 1 fig}) :
-$$
-\LM{\ppattern}{\ptext}{i}{j} =
-\begin{cases}
-
-	\text{The match of $\LMEi(\factor(i-1))$ } 
-		& \text{If $\factor(i)$ is} \\
-	\text{ in a matching of $\sigma[\LMEi(\factor(i)):]$ in $\pi[j:]$} 
-		& \text{an ascent factor} \\	
-	\text{ and that minimizes the match } & \\
-	\text{ $\LMEi(\factor(i-1))$} & \\
-	\text{ and starts with $\ptext[j]$} & \\
-	\text{Or $\infty$ if no such matching exists} & \text{} \\
-
-	&\\
-
-	\text{The match of $\LMEi(\factor(i-1))$ } 
-	& \text{If $\factor(i)$ is} \\
-	\text{ in a matching of $\sigma[\LMEi(\factor(i)):]$ in $\pi[j:]$} 
-	& \text{a descent factor} \\	
-	\text{ and that maximizes the match } & \\
-	\text{ $\LMEi(\factor(i-1))$} & \\
-	\text{ and starts with $\ptext[j]$} & \\
-	\text{Or $\infty$ if no such matching exists} & \text{} \\
-
-\end{cases}
-$$
-
-\begin{figure}[t] 
-	\centering	
-	\begin{tikzpicture}[scale=.3]
-
-	\fill[red!40!white] (2,3) rectangle (5.5,5);
-	\fill[blue!40!white] (6,10) rectangle (12,5);
+	\draw[pattern=north east lines] (2,3) rectangle (5.5,5);
+	\draw[pattern=grid] (6,10) rectangle (12,5);
 
@@
 	\caption{
-		When looking for a matching of $\sigma[\LMEi(\factor(i)):]$ (red and blue areas) starting at $\pi[j:]$, (1) the red area is a matching of $\factor(i)$ ie. if and only if
-		its contains an increasing subsequence of size equal or bigger than $|\factor(i)|$.
-		(2) the red and blue areas have to be "compatible" (their x-coordinates and y-coordinates have to be disjoint and the red area has to be before the blue area in the x-coordinate and y-coordinate).
-		$\AF{\ppattern}{\ptext}{i}{j}$ is the set of every top y-coordinate of every blue area which is compatible.
-$\LM{\ppattern}{\ptext}{i}{j}$ is the minimal value of $\AF{\ppattern}{\ptext}{i}{j}$ if he set is not void.}
+		When looking for an occurrence of $\sigma[\LMEi(\factor(i)):]$ (represented by the dashed and gridded rectangle) starting at $\pi[j:]$, (1) the dashed rectangle is an occurrence of $\factor(i)$ if and only if
+		it contains an increasing subsequence of size equal or bigger than $|\factor(i)|$.
+		(2) the dashed and gridded rectangles have to be "compatible": their x-coordinates and y-coordinates have to be disjoint and the dashed rectangle has to be on the left and below the gridded rectangle.
+		$\AF{\ppattern}{\ptext}{i}{j}$ is the set of y-coordinates of every top edge of the gridded rectangle which is compatible.
+$\LM{\ppattern}{\ptext}{i}{j}$ is the minimal element of $\AF{\ppattern}{\ptext}{i}{j}$ if the set is not empty.}
 	\label{fig: algo 1 fig}	
@@
 
-Clearly there exists a matching of $\ppattern$ in $\ptext$ if and only if
+There exists an occurrence of $\ppattern$ in $\ptext$ if and only if
 there exists a $1 \leq i \leq n$ such that $LM(n_{factors},i)$ $\neq$ $0$ and $LM(n_{factors},i)\neq \infty$
@@
 		\min_{j<j'}\{\infty\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\factor(i)$ is}  \\
+			& \text{If $\factor(1)$ is}  \\
 		\text{ $|\factor(1)| \leq LIS(j,j',\ptext[j']+1)  $}\}
@@
 		\max_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\factor(i)$ is}  \\
+			& \text{If $\factor(1)$ is}  \\
 		\text{ $|\factor(1)| \leq LDS(j,j',\ptext[j']-1) $}\}
@@
 In the base case,
-one is looking for a matching of the first factor.
+one is looking for an occurrence of the first factor.
 }
@@
 where $\AF{\ppattern}{\ptext}{i}{j}$ and $\DF{\ppattern}{\ptext}{i}{j}$ are the sets 
-of elements matching the left most element of $\factor(i-1)$ in a match of $\sigma[\LMEi(\factor(i)):]$ starting at $\ptext[j:]$.
-Suppose that $\factor(i)$ is an ascent (resp descent) factor, index $j'$ and matching $t$ exists if and only if
-$\ptext[j:j']$ contains a matching of $\factor(i)$ "compatibles" with a matching in $\ptext[j'+1:]$ of $\sigma[\LMEi(\factor(i-1)):]$.
-It is enough to assure that every element of the matching of $\factor(i)$ are smaller (resp.
-bigger) than the element of the matching of $\sigma[\LMEi(\factor(i-1)):]$.
+of elements matching the leftmost element of $\factor(i-1)$ in an occurrence of $\sigma[\LMEi(\factor(i)):]$ starting at $\ptext[j:]$.
+$\LM{\ppattern}{\ptext}{i}{j}$  has a solution
+if and only if
+$\ptext[j:j']$ contains an occurrence of $\factor(i)$ "compatibles" with an occurrence in $\ptext[j'+1:]$ of $\sigma[\LMEi(\factor(i-1)):]$.
+It is enough to ensure that every element of the occurrence of $\factor(i)$ is below (resp.
+above) the elements of the occurrence of $\sigma[\LMEi(\factor(i-1)):]$.
 
@@
 
-The number of factor is bound by $k$.
+The number of factors is bound by $k$.
 Every instance of $LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(n^2\log(\log(n))$.
-There are $n$ base cases that can be computed $O(n)$ time, thus computing every base cases
+There are $n$ base cases that can be computed in $O(n)$ time, thus computing every base case
 takes $O(n^2)$ time.
-There are $kn$ different instance of $\AFa$ and each one of them take $O(n)$ time to compute, 
+There are $kn$ different instances of $\AFa$ and each one of them takes $O(n)$ time to compute, 
 thus computing every instance of $\AFa$ takes $O(kn^2)$ time.
-There are $kn$ different instance of $\LMa$ and each one of them take $O(n)$, because the size of an $\AFa$
-is bounded by $n$, thus computing every $\LMa$ takes $O(kn^2)$ time.
-Thus computing all the values takes $O(max(kn^2,n^2\log(\log(n)))$.
+There are $kn$ different instances of $\LMa$ and each one of them takes $O(n)$, 
+thus computing every $\LMa$ takes $O(kn^2)$ time.
+Thus computing all the values takes $O(max(kn^2,n^2\log(\log(n)))$ time.
 Every value takes $O(1)$ space, thus the whole problem takes $O(kn^2)$ space.
@@
 
-\section{$(213,231)$-avoiding bivincular patterns}
+\section{Bivincular wedge permutation patterns}
 	\label{section:bivincular}
 
-This section is devoted to the pattern matching problem with $(213,231)$-avoiding bivincular pattern.
+This section is devoted to the pattern matching problem with bivincular wedge permutation pattern.
 Recall that a bivincular pattern generalises a permutation pattern by
-being able to force elements to be consecutive in value or in position.
-Hence,  bivincular pattern is stronger in constraint than permutation pattern, intuitively we can not use the previous algorithm.
-As in a $(213,231)$-avoiding permutation, we can describe structural property of a $(213,231)$-avoiding bivincular pattern.
+being able to force elements to be consecutive in value or/and in position.
+Hence,  bivincular pattern adds more restrictions on what the occurrence must look like.
+As a consequence it is easier to avoid a bivincular permutation pattern than
+the same permutation pattern.
+Intuitively we cannot use the previous algorithm, as the restrictions on position and value are not managed.
+As in a wedge permutation, we can describe the structural property of a  bivincular wedge permutation pattern.
 
@@
 \label{lemma:ascentDescentAscent}
-Given $\ppattern$ a $(213,231)$-avoiding bivincular pattern,
-If $\overline{\sigma[i]\sigma[j]}$ (this implies that $\sigma[j]=\sigma[i]+1$) and 
-if $\sigma[i]$ is an ascent (resp. decent) element and $\sigma[i]+1$ is an ascent 
+Given $\ppattern$ a bivincular wedge permutation pattern,
+if $\overline{m(m+1)}$ such that $\sigma[i]=m$ and $\sigma[j]=m+1$,
+if $\sigma[i]$ is an ascent (resp. decent) element and if $\sigma[i]+1$ is an ascent 
 (resp. decent) element then :  
@@
 	\item $i<j$ (resp. $j>i$)
-	\item For every $l$, $i<l<j$ (resp. $j>l>i$), $\pi[l]$ is a descent (resp. ascent) element.    
+	\item For every $\ell$, $i<\ell<j$ (resp. $j>\ell>i$), $\sigma[\ell]$ is a descent (resp. ascent) element.    
 \end{itemize}
-
 \end{lemma}
 
-This lemma states that if two ascent (resp. decsent) elements
+This lemma states that if two ascent (resp. descent) elements
 need to be matched to consecutive elements in value then every element between those two elements (if any) is a descent (resp. ascent) element.
+
+\begin{proof}[of Lemma~\ref{lemma:ascentDescentAscent}]
+The first statement is explained by the fact that ascent elements are increasing,
+as $\sigma[i]<\sigma[j]$ then
+$\sigma[i]$ is at the left of $\sigma[j]$ thus $i<j$. 
+Suppose that there exists $\ell$, $i<\ell<j$,
+such that $\ppattern[\ell]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[\ell]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
+We use a similar argument if $\sigma[i]$ is a descent element.
+\qed
+\end{proof}
 
@@
 \label{Proposition:bivincular pattern}
-Let $\sigma$ be a $(213,231)$-avoiding bivincular of length $k$
-and $\pi \in S_n$.
+Let $\sigma$ be a bivincular wedge permutation pattern of length $k$
+and $\pi$ an $n$-sized permutation.
 One can decide in $O(kn^4)$ time
-and $O(kn^3)$ space if $\pi$ matches $\sigma$.
+and $O(kn^3)$ space if $\pi$ has an occurrence $\sigma$.
 \end{proposition}
@@
 	\begin{tikzpicture}[scale=.3]
-	\fill[blue!40!white] (0,12) rectangle (1,11);
+	\draw[pattern=north east lines] (0,12) rectangle (1,11);
 	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
 
-	\fill[blue!40!white] (2,0) rectangle (3,1);
+	\draw[pattern=north east lines] (2,0) rectangle (3,1);
 	\draw[dotted,-] (0,1.5) -- (14,1.5) node[right] {$\lb$};
@@
 	% le reste du match
-	\fill[red!40!white] (5,8) rectangle (12,4);
+	\draw[pattern=grid] (5,8) rectangle (12,4);
 	\draw (5,4) -- (7.7,7);
@@
 	%point du bot
-	\draw[fill=black] (5,4) circle (1mm) node[above] {$\pi[l]$} ;
+	\draw[fill=black] (5,4) circle (1mm) node[above] {$\pi[\ell]$} ;
 
@@
 	\begin{tikzpicture}[scale=.3]
-	\fill[blue!40!white] (0,12) rectangle (1,11);
+	\draw[pattern=north east lines] (0,12) rectangle (1,11);
 	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
 
-	\fill[blue!40!white] (2,0) rectangle (5,4);
-	\draw[dotted,-] (0,4.5) -- (14,4.5) node[right] {$\lb=\pi[l]+1$};
+	\draw[pattern=north east lines] (2,0) rectangle (5,4);
+	\draw[dotted,-] (0,4.5) -- (14,4.5) node[right] {$\lb=\pi[\ell]+1$};
 
@@
 	%\draw[dashed,red] (5,8) rectangle (12,4);
-	\fill[red!40!white] (7,6) rectangle (12,8);
+	\draw[pattern=grid] (7,6) rectangle (12,8);
 	\draw (7,6) -- (7.7,7);
@@
 	%point du bot
-	\draw[fill=black] (7,6) circle (1mm) node[above] {$\pi[l']$};
+	\draw[fill=black] (7,6) circle (1mm) node[above] {$\pi[\ell']$};
 
@@
 
-	\caption{When matching an ascent element, the value of $ub$ does not change,
-		and the lb is equal to the last match plus one. Note that there is only ascent element before $\sigma[i']$}	
+\caption{When solving $\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}$, with $\sigma[i]$ an ascent element, 
+the recursive calls of $\PM{*}{*}{*}{*}{*}{*}$ will have the same $\ub$ value,
+and the $\lb$ will be equal to the matching of $\pi[i]$ plus one. %Note that there is only ascent element before $\sigma[i']$
+}	
 \label{fig:ub dont change}
@@
 
-We consider the following set of boolean :
-Given $\ppattern$ a $(213,231)$-avoiding bivincular pattern, and a text $\ptext \in \Av{n}{231,213}$,
+Given a lower bound $\lb$, a upper bound $\ub$, a position i of $\sigma$
+and a position $j$ of $\pi$, we want to know if
+there exists an occurrence of $\sigma[i:]$ in $\ptext[j:]$
+with every element of the occurrence is in $[\lb,\ub]$
+and starting at $\pi[j]$,
+which we denote as:
+
 $$
@@
 \begin{cases}
-	true 	& \text{If $\ptext[j:]$ matches $\sigma[i:]$ }\\
-			& \text{with every element of the matching is in $[\lb,\ub]$}\\
-			& \text{and starting $\pi[j]$}\\
+	true 	& \text{If $\ptext[j:]$ has an occurrance of $\sigma[i:]$ }\\
+			& \text{with every element of the occurrence is in $[\lb,\ub]$}\\
+			& \text{and starting at $\pi[j]$}\\
 	false 	& otherwise\\
@@
 
-The argument $\lb$ (respectively $\ub$) stands for 
-the match of the last ascent (resp. decsent) element matched
-plus (resp. minus) one.
-We now show how to compute recursively those boolean (see fig. \ref{fig:ub dont change}).
+We now show how to compute recursively those values (see Figure \ref{fig:ub dont change}).
 
@@
 			& \text{and if ${\ppattern[k]}_\lrcorner$ then $j=n$}\\
-			& \text{and if ${\ppattern[k]}^\urcorner$ then $\ptext[j]=\ub=k$}\\
+			& \text{and if ${\ppattern[k]}^\urcorner$ then $\ptext[j]=\ub=n$}\\
 			& \text{and if  $^\ulcorner{\ppattern[k]}$ then $\ptext[j]=\lb=1$ } \\
 			& \text{and if  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then $\ptext[j]=\lb$ }  \\
-			& \text{and if  $\overline{(\ppattern[k]\ppattern[k]-1)}$ then $\ptext[j]=\ub$}  \\
+			& \text{and if  $\overline{(\ppattern[k]\ppattern[k]+1)}$ then $\ptext[j]=\ub$}  \\
 
@@
 
-The base case finds an matching for the rightmost element of the pattern.
-If the last element does not have any restriction on positions and on values, then $\PM{\sigma}{\ptext}{\lb}{\ub}{k}{j}$ is true if and only if $\ppattern[k]$ is matched $\ptext[j]$.
-Which is true if $\ptext[j] \in [\lb,\ub]$.
-If ${\ppattern[k]}_\lrcorner$ then $\ppattern[k]$ must be matched to the right most element of $\pi$ thus $j$ must be the $n$.
-If ${\ppattern[k]}^\urcorner$ then $\ppattern[k]$ must be matched to the largest element which is $k$.
-If $^\ulcorner{\ppattern[k]}$ then $\ppattern[k]$ must be matched to the smallest element which is $1$.
-If  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then the matched element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the matched element of $\ppattern[k]-1$ will be recorded in $\lb$ and by adding $1$ to it thus $\ppattern[k]$ must be matched to $\lb$.
-If  $\overline{(\ppattern[k]\ppattern[k]-1)}$ then the matched element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the matched element of $\ppattern[k]-1$ will be recorded in $\ub$ and by removing $1$ to it thus $\ppattern[k]$ must be matched to $\ub$.
+The base case finds an occurrence for the rightmost element of the pattern.
+If the rightmost element does not have any restriction on positions and on values, then $\PM{\sigma}{\ptext}{\lb}{\ub}{k}{j}$ is true if and only if $\ppattern[k]$ is matched to $\ptext[j]$.
+This is true if $\ptext[j] \in [\lb,\ub]$.
+If ${\ppattern[k]}_\lrcorner$ then $\ppattern[k]$ must be matched to the rightmost element of $\pi$ thus $j$ must be $n$.
+If ${\ppattern[k]}^\urcorner$ then $\ppattern[k]$ must be matched to the topmost element which is $n$.
+If $^\ulcorner{\ppattern[k]}$ then $\ppattern[k]$ must be matched to the bottommost element which is $1$.
+If  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then the matching element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the element matching $\ppattern[k]-1$ will be recorded in $\lb$ and by adding $1$ to it thus $\ppattern[k]$ must be matched to $\lb$.
+If  $\overline{(\ppattern[k]\ppattern[k]+1)}$ then the element matching $\ppattern[k]$ and $\ppattern[k]+1$ must be consecutive in value, by recursion the value of the  element matching $\ppattern[k]+1$ will be recorded in $\ub$ and by removing $1$ to it thus $\ppattern[k]$ must be matched to $\ub$.
 
@@
 \begin{itemize}
-	\item If $\ptext[j] \notin [\lb,\ub]$ then :
+	\item If $\ptext[j] \notin [\lb,\ub]$ then:
 	$$
@@
 
-	which is immediate from the definition. If $\ptext[j] \notin [\lb,\ub]$ then it can not be part of a matching of  $\ppattern[i:]$ in $\ptext[i:]$ with every matched element in $[\lb,\ub]$.
+	which is immediate from the definition.
+If $\ptext[j] \notin [\lb,\ub]$ then it cannot be part of an occurrence of  $\ppattern[i:]$ in $\ptext[j:]$ with every element of the occurrence in $[\lb,\ub]$.
 
@@
 	\begin{cases}
-		\bigcup_{j<l} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{l}
+		\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
 			& \text{if $\ppattern[i]$ is not underlined } \\
 			& \text{ and $\ppattern[i]$ is not overlined} \\
-		\bigcup_{j<l} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{l}
+		\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
 			& \text{if $\ppattern[i]$ is not underlined } \\
@@
 	$$	
-	Remark that $\ptext[j]$ can be matched to $\ppattern[i]$ because $\ptext[j] \in [\lb,\ub]$.
-	Thus if $\ptext[j+1:]$ matches $\ppattern[i+1:]$  with every element of the matching in $[\ppattern[i]+1,\ub]$ then 
- 	$\ptext[j:]$ matches $\ppattern[i:]$. The last condition correspond 
- 	to know if there exists $l$, $j<l$ such that
-	$\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{l}$ is true.
-	The first case correspond to a matching without restriction on position and on value.
-The second case asks for the match of $\ppattern[i]-1$ and $\ppattern[i]$ to be consecutive in value, but the match of $\ppattern[i]-1$
+	Remark that $\ppattern[i]$  can be matched to $\pi[i]$ because $\ptext[j] \in [\lb,\ub]$.
+	Thus if $\ptext[j+1:]$ has an occurrence of $\ppattern[i+1:]$  with every element of the occurrence in $[\pi[i]+1,\ub]$ then 
+ 	$\ptext[j:]$ has an occurrence $\ppattern[i:]$. The last condition corresponds 
+ 	to know if there exists $\ell$, $j<\ell$ such that
+	$\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}$ is true.
+	The first case corresponds to an occurrence without restriction on position and on value.
+The second case asks for the matching of $\ppattern[i]-1$ and $\ppattern[i]$ to be consecutive in value, but the matching of $\ppattern[i]-1$
 	is $lb-1$ thus we want $\ptext[j]=\lb$.
-The fourth case asks for the match of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in index, thus the match of $\ppattern[i+1]$ must be $j+1$.
-The third case is an union of the second and fourth case.
-Note that if $\pi[j]$ is an ascent element we can not have the condition that the match of $\ppattern[i]$ and $\ppattern[i]+1$ have to consecutive in value.
+The fourth case asks for the matching of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in positions, thus the matching of $\ppattern[i+1]$ must be $\pi[j+1]$.
+The third case is a union of the second and fourth case.
+	Note that we do not have to consider the case $\overline{\ppattern[i](\ppattern[i]+1)}$
+	as the element $(\ppattern[i]+1)$ is on the right of $\ppattern[i]$ and thus will
+	be taken care of later on.
 
@@
 	\begin{cases}
-			\bigcup_{j<l} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{l}
+			\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
 				& \text{if $\ppattern[i]$ is not underlined } \\
 				& \text{ and $\ppattern[i]$ is not overlined} \\
-			\bigcup_{j<l} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{l}
+			\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
 				& \text{if $\ppattern[i]$ is not underlined } \\
@@
 
-Clearly if $\bigcup_{0<j} \PM{\sigma}{\ptext}{1}{n}{1}{j}$ is true then $\pi$ matches $\sigma$. We now discuss the position and value constraints.
+Clearly if $\bigcup_{0<j} \PM{\sigma}{\ptext}{1}{n}{1}{j}$ is true then $\pi$ has an occurrence $\sigma$. We now discuss the position and value constraints.
 \paragraph{Position Constraint.} There are 3 types of position constraints that can be added by underlined elements.
 \begin{itemize}
-	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ on a matching of $\ppattern$ in $\ptext$).
-This constraint is satisfied by requiring that the matching starts at the left most element of $\ptext$ : if  $\PM{\sigma}{\ptext}{1}{n}{1}{1}$ is true.
-
-	\item If ${\ppattern[k]}_\lrcorner$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a matching of $\ppattern$ in $\ptext$).
+	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ on a occurrence of $\ppattern$ in $\ptext$).
+This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$ : if  $\PM{\sigma}{\ptext}{1}{n}{1}{1}$ is true.
+
+	\item If ${\ppattern[k]}_\lrcorner$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a occurrence of $\ppattern$ in $\ptext$).
 This constraint is checked in the base case.
 
-	\item If $\underline{\ppattern[i]\ppattern[i+1]}$ then the index of the matched elements of $\ppattern[i]$ and $\ppattern[i+1]$ must be consecutive.
-In other word, if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i+1]$ must be matched to $\ptext[j+1]$.
-We assure this restriction by recursion by requiring that the matching of $\ppattern[i+1:]$ to start at index $j+1$ (see figure $\ref{fig:ub dont change}$).
+	\item If $\underline{\ppattern[i]\ppattern[i+1]}$ then the positions of the element matching $\ppattern[i]$ and $\ppattern[i+1]$ must be consecutive.
+In other words, if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i+1]$ must be matched to $\ptext[j+1]$.
+We ensure this restriction by recursion by requiring that the matching of $\ppattern[i+1:]$ starts at position $j+1$ (see Figure $\ref{fig:ub dont change}$).
 \end{itemize}
@@
 \begin{itemize}
-	\item If $^\ulcorner{\sigma[i]}$ (and thus $\sigma[i]=1$) then the minimal value of $\ppattern$ must be matched to the minimal value of $\ptext$.
+	\item If $^\ulcorner{\sigma[i]}$ (and thus $\sigma[i]=1$) then the bottommost element of $\ppattern$ must be matched to the bottommost element of $\ptext$.
 	\begin{itemize}
@@
 		every problem 
-		$\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ is true if $\sigma[i]$ is matched to element with value $\lb$ (by recursion) thus it is enough to require that $\lb=1$.
-		Now remark that $\sigma[i]$ is the leftmost ascent element, indeed if not, then there exists an ascent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the minimal element.
+		$\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ is true if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion) thus it is enough to require that $\lb=1$.
+		Now remark that $\sigma[i]$ is the leftmost ascent element, indeed if not, then there exists an ascent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
 		As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are descent elements.
-		Moreover the recursive call from a descent element does not modified the lower bound
-		thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$, $\lb=1$ (see figure $\ref{fig:ub dont change}$).
-
-		\item If $\sigma[i]$ is a descent element then $i=k$ ($\sigma[i]$ is the right most element).
-Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $1$.
+		Moreover the recursive calls from a descent element do not change the lower bound
+		thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$, $\lb=1$ (see Figure $\ref{fig:ub dont change}$).
+
+		\item If $\sigma[i]$ is a descent element then $i=k$ ($\sigma[i]$ is the rightmost element). Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $1$.
 
@@
 
-	\item If ${\ppattern[i]}^\urcorner$ (and thus $\sigma[i]=k$) then the maximal value of $\ppattern$ must be matched to the maximal value of $\ptext$.
+	\item If ${\ppattern[i]}^\urcorner$ (and thus $\sigma[i]=k$) then the topmost element of $\ppattern$ must be matched to the topmost element of $\ptext$.
 	\begin{itemize}
@@
 		every recursive call \\ $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ is matched to element with value $\ub$ (by recursion) thus it is enough to require that $\ub=n_{\ptext}$.
-		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal element.
+		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
 		As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are ascent elements.
-		Moreover the recursive call from a ascent element does not modified the upper bound
-		thus for every $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$, $\ub=n$ (see figure $\ref{fig:ub dont change}$.
-
-		\item If $\sigma[i]$ is an ascent element then $\sigma[i]$ then $i=k$ ($\sigma[i]$ is the right most element).
+		Moreover the recursive calls from a ascent element do not change the upper bound
+		thus for every $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$, $\ub=n$ (see Figure $\ref{fig:ub dont change})$.
+
+		\item If $\sigma[i]$ is an ascent element then $i=k$ ($\sigma[i]$ is the rightmost element).
 Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n_{\ptext}$.
@@
 
-			\item The case $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i'<i$) is not possible.
-			Indeed $\ppattern[i]$ is the maximal element of $\ppattern[i:]$ thus $\ppattern[i] > \ppattern[i']$ which is in contradiction with 
+			\item The case $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case where  $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i'<i$) is not possible.
+			Indeed $\ppattern[i]$ is the topmost element of $\ppattern[i:]$ thus $\ppattern[i] > \ppattern[i']$ which is in contradiction with 
 			$\ppattern[i']=\ppattern[i]+1$.
 
-			\item If $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i'<i$), then
+			\item If $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i'<i$), then
 			remark that every recursive call
@@
 			Now remark that
-			$\ppattern[i]$ is the right most ascent element and $\ppattern[i']$ is the right most element (or $\ppattern[i'] \neq \ppattern[i]+1$). 
+			$\ppattern[i]$ is the rightmost ascent element and $\ppattern[i']$ is the rightmost element (or $\ppattern[i'] \neq \ppattern[i]+1$). 
 			As a consequence $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are descent elements.
-Moreover the recursive call from a descent element does not modified the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$
-			thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see figure $\ref{fig:ub dont change}$.
+Moreover the recursive calls from a descent element do not change the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$
+			thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see Figure $\ref{fig:ub dont change}$).
 
@@
 			As a consequence $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are descent elements.
-Moreover the recursive call from a descent element does not modified the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$ thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see figure $\ref{fig:ub dont change}$.
+Moreover the recursive calls from a descent element do not change the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$ thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see Figure $\ref{fig:ub dont change}$).
 		\end{itemize}
@@
 
-\section{Computing the longest $(213,231)$-avoiding pattern}
+\section{Computing the longest wedge permutation pattern}
 \label{section:LCS}
 
-	This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
-	Given a set of permutations, find a longest $(213,231)$-avoiding that can be matched
-	by each input permutation.
-	This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$.
+This section is focused on a problem related to the pattern matching problem, finding the longest wedge permutation occurring in permutations:
+Given a set of permutations, find a longest wedge permutation that occurs in
+each input permutations.
+This problem is known to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint that the subsequence must avoid $(213,231)$, as for a fixed number of permutations
+(in our case, we have two permutations) the number of permutation appear in the exponent of the complexity of the algorithm.
 Thus we focus on the cases where only one or two permutations are given in input.
+
+Conveniently, we say that a subsequence is
+a wedge subsequence if and only if the permutation represented by the subsequence
+is a wedge permutation.
+
 We start with the easiest case where we are given just one input permutation.
@@
 $A(\pi) = \{i | \text{$\pi[i]$ is an ascent element} \} \cup \{n\}$ and
-	$D(\pi) = \{i | \text{$\pi[i]$ is a descent element} \cup \{n\}$.\\
+$D(\pi) = \{i | \text{$\pi[i]$ is a descent element} \} \cup \{n\}$.\\
 
@@
 \label{proposition:longestIncreasingSubsequence}
-	If $s$ is a longest $(213,231)$-avoiding subsequence with last element at index 
-	$f$ in $\pi$ then
-	$A(\pi)$ is a longest increasing subsequence with last element at index $f$ and
-	$D(\pi)$ is a longest decreasing subsequence with last element at index $f$.
+If $s_i$ is the longest increasing subsequence with last element at position $f$ in $\pi$
+and $s_d$ is the longest decreasing subsequence with last element at position $f$ in $\pi$
+then $s_i \cup s_d$ is a longest wedge subsequence with last element at position $f$ in $\pi$.
 \end{proposition}
+
+\begin{proof}
+Let us first prove that we have a wedge subsequence.
+$s_i$ is an increasing subsequence with values below or equal $\pi[f]$ and
+$s_d$ is an decreasing subsequence with values above or equal $\pi[f]$,
+so $s_i \cup s_d$ is a wedge subsequence.
+Let us prove that this is a longest.
+Let $s$ be a wedge subsequence with its rightmost element at position $f$ in $\pi$ such
+that $|s|>|s_i \cup s_d|$,
+first note that $A(s)$ is also an increasing subsequence with its rightmost  at position $f$ in $\pi$
+and $D(s)$ is also an decreasing subsequence with its rightmost  at position $f$ in $\pi$,
+then as $|s|>|s_i \cup s_d|$ then either $|A(s)| > |s_i|$ or $|D(s)| > |s_d|$,
+which is in contradiction with the definition of $s_i$ and $s_d$. 
+\end{proof}
+
+%\begin{proposition}
+%\label{proposition:longestIncreasingSubsequence}
+%If $s$ is an occurrence of a  longest $(213,231)$-avoiding subsequence with last element at position 
+%$f$ in $\pi$ then
+%$A(s)$ is a longest increasing subsequence with last element at position $f$ and
+%$D(s)$ is a longest decreasing subsequence with last element at position $f$.
+%\end{proposition}
+%
+%\begin{proof}[of Proposition~\ref{proposition:longestIncreasingSubsequence}]
+%Let $s$ be a longest subsequence avoiding (213,231) with last element at position $f$ in $\pi$,
+%suppose that $A(s)$ is not a longest increasing subsequence with last element at position $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
+%Thus $|s_m|>|A(s)|$, clearly the sequence $s_m \cup D(s)$ is longer than $s$.
+%Moreover the sequence $s_m \cup D(s)$ avoid both $213$ and $231$ as  $s_m$ is an increasing
+%subsequence with value lower and equal than $\pi[f]$ and $D(s)$ is an decreasing subsequence
+%with value above or equal than $\pi[f]$.
+%In other words $s$ is not the longest subsequence avoiding (213,231) with last element at position $f$ in $\pi$. Which is a contradiction.
+%The same idea can be used to show that $D(\pi)$ is the longest decreasing subsequence.
+%\qed
+%\end{proof}
 
@@
 Let $\pi$ be a permutation. One can compute
-	the longest $(213,231)$-avoiding subsequence that can be matched in $\pi$
+the longest $(213,231)$-avoiding subsequence that can occur in $\pi$
 in $O(n\log(\log(n)))$ time and in $O(n)$ space.
 \end{proposition}
+
+\begin{proof}[of Proposition~\ref{proposition:longest 2}]
+The Proposition \ref{proposition:longestIncreasingSubsequence} leads to an algorithm
+where one has to compute longest increasing and decreasing subsequence endings at every position possible. 
+Then finding the maximum sum of longest increasing and decreasing subsequence endings at the same position.
+Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
+$O(n\log(\log(n)))$ time and $O(n)$ space 
+(see \cite{Bespamyatnikh00enumeratinglongest}), 
+then finding the maximal can be done in linear time.
+\qed
+\end{proof}
 
@@
 Consider the following problem
-that computes the longest stripe common to $\pi_1$ and $\pi_2$:
+that computes the longest wedge subsequence common to $\pi_1$ and $\pi_2$:
 Given two permutations $\pi_1$ and $\pi_2$, we define
@@
 \begin{center}
-= $\max$ \{$|s|$ $|$ $s$ can be matched $\pi_1[i_1:]$ with every element of the match in $[\lb_1,\ub_1]$ and $s$ can be matched $\pi_2[i_2:]$ with every element of the match in $[\lb_2,\ub_2]$ \}
+= $\max$ \{$|s|$ $|$ $s$ occurs $\pi_1[i_1:]$ with every element of the occurrence in $[\lb_1,\ub_1]$ and $s$ occurs $\pi_2[i_2:]$ with every element of the occurrence in $[\lb_2,\ub_2]$ \}
 \end{center}
@@
 $
-\match{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=
+\match{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=\max
 \begin{cases}
-1+\LCS{\pi_1}{\pi_1[i_1]+1}{\ub_1}{\pi_2}{\pi_2[i_2]+1}{\ub_2}{i_1}{i_2+1}
+1+\LCS{\pi_1}{\pi_1[i_1]+1}{\ub_1}{\pi_2}{\pi_2[i_2]+1}{\ub_2}{i_1+1}{i_2+1}
 	& \text{$\pi_1[i_1]<\lb_1$ } \\
@@
 
-1+\LCS{\pi_1}{\lb_1}{\pi_1[i_1]-1}{\pi_2}{\lb_2}{\pi_2[i_2]-1}{i_1+1}{i_2}
+1+\LCS{\pi_1}{\lb_1}{\pi_1[i_1]-1}{\pi_2}{\lb_2}{\pi_2[i_2]-1}{i_1+1}{i_2+1}
 	& \text{$\pi_1[i_1]>\ub_1$ } \\
@@
 
-For every pair $i,j$ we either ignore the element of $\pi_1$,
-or we ignore the element of $\pi_2$,
-or we match as the same step (if possible).
+%For every pair $i,j$ we either ignore the element of $\pi_1$,
+%or we ignore the element of $\pi_2$,
+%or we match as the same step (if possible).
+
+The solution to the problem relies on the fact
+that the longest wedge subsequence is found
+either by considering the problem with $\pi_1[i_1:]$ and $\pi_2[i_2+1:]$
+or by considering the problem with $\pi_1[i_1+1:]$ and $\pi_2[i_2:]$
+or by matching  $\pi_1[i_1]$ and $\pi_2[i_2]$ and adding
+to the solution the LCS for $\pi_1[i_1+1:]$ and $\pi_2[i_2+1:]$ which is compatible,
+meaning that if the matching element is an ascent (resp. descent) element
+then we consider only the solution with elements above (below)
+$\pi_1[i_1]$ for the occurrence in $\pi_1[i_1+1:]$
+and $\pi_2[i_2]$ for the occurrence in $\pi_2[i_2+1:]$.
+
 These relations lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.
-Indeed there is $|\pi_1|^3|\pi_2|^3$ cases possible for the problem
+Indeed there are $|\pi_1|^3|\pi_2|^3$ cases possible for the problem
 and each case is solved in constant time.
@@
 
-\newpage
-\section*{Appendix (Reviewers' version only)}
-
-\begin{proof}[of Lemma~\ref{lemma:first element is 1 or n}]
-Any other initial element would serve as a `$2$' in either a
-$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:MatchStripeToPermutation}]
-  The forward direction is obvious.
-  We prove the backward direction by induction on the size of the pattern
-  $\sigma$.
-  The base case is a pattern of size $2$.
-  Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = ascent$.
-  Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-  such that $\bijection(t) = ascent$, this reduces to saying that
-  $\pi_{i_1} < \pi_{i_2}$, 
-  and hence that $t$ is a matching of $\sigma = 12$ in $\pi$.
-  A similar argument shows that the lemma holds true for $\sigma = 21$.
-  Now, assume that the lemma is true for all patterns up to size $k \geq 2$.
-  Let $\sigma \in \Av{k+1}{231,213}$ and
-  let $t$,
-  be a subsequence of $\pi$ of length $k+1$ such that
-  $\bijection(t) = \bijection(\sigma)$.
-  As $\bijection(t)[2:] = \bijection(\sigma)[2:]$
-  by the inductive hypothesis, it follows that
-  $t[2:]$ is a matching of $\sigma[2:]$.
-  Moreover $\bijection(t)[1] = \bijection(\sigma)[1]$ 
-  thus $t[1]$ and $\sigma[1]$ are both either the minimal or the maximal
-  element of their respective subsequences.
-  Therefore, $t$ is a matching of $\sigma$ in $\pi$.
-  \qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}
-According to Lemma~\ref{Proposition:both permutations are avoiding} the problem reduces
-to deciding whether $s_\sigma$ occurs as a subsequence in $s_\pi$.
-A straightforward greedy approach solves this issue in linear-time.
-\qed
-\end{proof}
-
-\bigskip
-
-%\begin{proof}[of Lemma~\ref{lemma:whereIsMax}]
-%Consider the rightmost element of $\factor{\sigma}{i}$ and assume this element is an ascent.
-%Then, it follows that it is smaller than the following element which is $\first{\sigma}{i-1}$.
-%Now, since $\factor{\sigma}{i}$ is an increasing subsequence, every element of
-%$\factor{\sigma}{i}$ is smaller than $\first{\sigma}{i-1}$.
-%According to Lemma~
-%\ref{lemma:first element is 1 or n}, $\first{\sigma}{i-1}$ is 
-%the maximal (minimal) element of $\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$, 
-%and hence
-%$\first{\sigma}{i-1}$ is the maximal  element of
-%$\factor{\sigma}{i}\factor{\sigma}{i-1}\ldots\factor{\sigma}{1}$.
-%
-%A similar argument shows that the lemma holds true if the rightmost element
-%of $\factor{\sigma}{i}$ is a descent.
-%\qed
-%\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:ts}]
-By definition $s$ is a matching of $\ppattern[\LMEi(\factor(i)):]$.
-To prove that $ts$ is an matching of $\ppattern[\LMEi(\factor(i+1)):]$ we need to prove that every element of t is larger than every element of $s$.
-If $ts'$ is a matching of $\ppattern[\LMEi(\factor(i+1)):]$ then every element of $t$ is larger than every element of $s'$.
-Moreover the maximal element of $s$ is smaller than  the maximal element of $s'$ so every element of $s$ is smaller than every element of $s'$ thus every element of $s$ is smaller than every element of $t$.
-We use a similar argument if $\factor(i)$ is a descent factor.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Lemma~\ref{lemma:ascentDescentAscent}]
-Suppose that there exists $l$, $i<l<j$,
-such that $\ppattern[l]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[l]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
-We use a similar argument if $\sigma[i]$ is a descent element
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Proposition~\ref{proposition:longestIncreasingSubsequence}]
-Let $s$ be a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$,
-suppose that $P(s)$ is not a longest increasing subsequence with last element at index $f$. Let $s_m$ be a longest increasing subsequence with last element $f$.
-Thus $|s_m|>|A(s)|$, clearly the sequence $s_m \cup D(s)$
-is $(213,231)$-avoiding and is longer than $s$, this is a contradiction.
-The same idea can be used to show that $D(\pi)$ is the longest decreasing subsequence.
-\qed
-\end{proof}
-
-\bigskip
-
-\begin{proof}[of Proposition~\ref{proposition:longest 2}]
-The proposition \ref{proposition:longestIncreasingSubsequence} lead to an algorithm
-where one has to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximal sum of longest increasing and decreasing subsequence ending at the same index.
-Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
-$O(n\log(\log(n)))$ time and $O(n)$ space 
-(see \cite{Bespamyatnikh00enumeratinglongest}), 
-then finding the maximal can be done in linear time.
-\qed
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2016-06-22 article.tex
modif des reviews 2

@@
 
+\newcommand{\PM}{PM}
+
 \DeclareMathOperator{\firstia}{first}
@@
 \DeclareMathOperator{\block}{block}
-\DeclareMathOperator{\LMEi}{LMEi}
+\DeclareMathOperator{\LMEi}{LMEp}
 
 \DeclareMathOperator{\factor}{factor}
-%\newcommand{\factor}[2]{\factora_{{#1}}({#2})}
 
@@
 \DeclareMathOperator{\PMa}{PM}
-\newcommand{\PM}[6]{\PMa_{{#1}}^{{#2},{#3},{#4}}({#5},{#6})}
+%\newcommand{\PM}[6]{\PMa_{{#1}}^{{#2},{#3},{#4}}({#5},{#6})}
 
@@
 
-\title{Pattern matching in\\ $(213,231)$-avoiding permutations}
+\title{Permutation Pattern matching in\\ $(213,231)$-avoiding permutations}
 \author{Both Emerite NEOU, Romeo RIZZI}
@@
   Department of Computer Science,
-  Università degli Studi di Verona, Italy \\
+  Universit\`a degli Studi di Verona, Italy \\
   \email{romeo.rizzi@univr.it}
@@
 \begin{abstract}
-Given permutations $\sigma \in S_k$ and $\pi \in S_n$ with $k<n$, the
-\emph{pattern matching} problem is to decide whether $\sigma$ occurs
+Given permutations $\sigma$ of size $k$ and $\pi$ of size $n$ with $k<n$, the
+\emph{permutation pattern matching} problem is to decide whether $\sigma$ occurs
 $\pi$ as an order-isomorphic subsequence.
@@
 For the special case where only $\sigma$ avoids $213$ and $231$, we present a
-$O(max(kn^2,n^2\log(\log(n)))$ time algorithm. 
-We extend our research to bivincular patterns that avoid $213$ and $231$ and present a $O(kn^4)$ time algorithm.
+$O(max(kn^2,n^2\log(\log(n)))$-time algorithm. 
+We extend our research to bivincular patterns that avoid $213$ and $231$ and present a $O(kn^4)$-time algorithm.
 Finally we look at the related problem of the longest subsequence which avoids $213$ and $231$.  
@@
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
-For example a permutation has an occurrence of the pattern $123$ (resp. $321$) if it has
-an increasing (resp. decreasing) subsequence of length $3$.
-Similarly,
-$6152347$ has an occurrence of $213$ but not $231$.
-During the last decade, the study of the pattern matching for permutations has
-become a very active area of research \cite{Kitaev:book:2011}. and
+For example the permutation $123$ (resp. $321$) occurs in a second permutation if
+the second permutation has an increasing (resp. a decreasing) subsequence of size $3$.
+Similarly, $213$ occurs in $6152347$, but $231$ does not occurs in $6152347$.
+During the last decade, the study of patterns in permutations has
+become a very active area of research \cite{Kitaev:book:2011} and
 a whole annual conference (\textsc{Permutation Patterns}) focuses
-on pattern in permutation.
-
-We consider here the so-called \emph{pattern matching} problem
+on patterns in permutations.
+
+We consider here the so-called \emph{permutation pattern matching} problem
 (also sometimes referred to as the \emph{pattern involvement problem}):
-Given two permutations $\sigma$ and $\pi$, this problem is to decide whether
+Given two permutations $\sigma$ of size $k$ and $\pi$ of size $n$, the problem is to decide whether
 $\sigma \preceq \pi$ (the problem is attributed to Wilf in \cite{Bose:Buss:Lubiw:1998}).
-The pattern matching for permutations is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
-It is, however, polynomial-time solvable by brute-force enumeration
+The permutation pattern matching is known to be \NPhard~\cite{Bose:Buss:Lubiw:1998}.
+It is however polynomial-time solvable by brute-force enumeration
 if $\sigma$ has bounded size.
@@
 \cite{Ahal:Rabinovich:2008},
-the latter describing a $O(|\pi|^{0.47|\sigma|+o(|\sigma|)})$ time algorithm.
+the latter describing a $O(n^{0.47k+o(k)})$-time algorithm.
 Bruner and Lackner \cite{DBLP:journals/corr/abs-1204-5224}
-gave a fixed-parameter algorithm solving the pattern matching for permutations problem with
-an exponential worst-case runtime of $O(1.52^{n}.n.k)$,
-(This is an improvement upon the $O(2^{|\pi|})$ runtime required by
-brute-force search without imposing restrictions on $\sigma$ and $\pi$.)
+gave a fixed-parameter algorithm solving the permutation pattern matching problem with
+an exponential worst-case runtime of $O(1.52^{n}.n.k)$.
+This is an improvement upon the $O(k {n \choose k})$ runtime required by
+brute-force search without imposing restrictions on $\sigma$ and $\pi$,
+where one has to enumerate all the ${n \choose k}$ different subsequences of size $k$ in $\pi$
+and test if one of them has the same relative
+order as $\sigma$.  
 A recent major step was taken by Marx and Guillemot
@@
 They showed that
-the pattern matching for permutations problem is fixed-parameter tractable (FPT) for
-parameter $|\sigma|$.
-
-A few particular cases of the pattern matching for permutations problem have been attacked successfully.
-The case of increasing patterns is solvable in
-$O(|\pi| \log \log |\sigma|)$ time in the RAM model \cite{Crochemore:Porat:2010},
-improving the previous 30-year bound of $O(|\pi| \log |\sigma|)$.
+the permutation pattern matching is fixed-parameter tractable (FPT) for by the size of $\sigma$.
+
+A few particular cases of the permutation pattern matching problem have been attacked successfully.
+The case of any increasing pattern is solvable in 
+$O(n \log \log k)$ time in the RAM model \cite{Crochemore:Porat:2010},
+improving the previous 30-year bound of $O(n \log k)$.
 % (The algorithm also improves on the previous
@@
 by stack sorting algorithms.
-Any pattern of length $4$ can be detected in $O(|\pi| \log |\pi|)$ time
+Any pattern of size $4$ can be detected in $O(n \log n)$ time
 \cite{Albert:Aldred:Atkinson:Holton:ISAAC:2001}.
@@
 \cite{Guillemot:Vialette:ISAAC:2009} and more recently in \cite{2015arXiv151006051A}.
-The pattern matching for permutation problem is also solvable in
+The permutation pattern matching problem is also solvable in
 polynomial-time for separable patterns \cite{Ibarra:1997,Bose:Buss:Lubiw:1998}
-(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for Longest common subsequence problem and related one on separable permutations).
+(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for the longest common subsequence problem and related ones on separable permutations).
 Separable permutations are permutations that do not have an occurrence of
@@
 resemble (classical) patterns with the additional constraint that some of the elements in
-a occurrence must be consecutive in postitions.
+a occurrence must be consecutive in positions.
 Of particular importance in our context,
@@
 proved that deciding whether a vincular pattern
-$\sigma$ of length $k$ can occur in a longer permutation
+$\sigma$ of size $k$ occurs in a longer permutation
 $\pi$ is $W[1]$-complete for
@@
 (\emph{i.e.}, those permutations that avoid both $213$ and $231$).
-The number of $n$-wedge permutations is
-$t_0 = 1$ for $n = 0$ and
-$t_n =2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985},
-as they are in bijection with binary word of size $n-1$.
-On an individual basis,
-the permutations that do not have an occurrence of the permutation pattern $231$
-are exactly the \emph{stack-sortable permutations} and they are counted by
-the Catalan numbers \cite{Knuth:1997:ACP:260999}.
+%The number of $n$-wedge permutations is
+%$t_0 = 1$ for $n = 0$ and
+%$t_n =2^{n-1}$ for $n\geq 1$ \cite{Simion:Schmidt:EJC:1985},
+%as they are in bijection with binary word of size $n-1$.
+%On an individual basis,
+%the permutations that do not have an occurrence of the permutation pattern $231$
+%are exactly the \emph{stack-sortable permutations} and they are counted by
+%the Catalan numbers \cite{Knuth:1997:ACP:260999}.
 %	A stack-sortable permutation is a permutation whose elements may be sorted by
@@
 In Section~\ref{section:bivincular} we give a polynomial-time algorithm
-for a bivincular wedge permutations pattern.
+for a bivincular wedge permutation pattern.
 In Section~\ref{section:LCS} we consider the problem of finding the longest
-wedge permutations pattern in permutations.
+wedge permutation pattern in permutations.
 
@@
 When writing the permutation we omit the $<$ sign, thus
-writing the permutation as a word  :
+writing the permutation as a word:
 $\pi = \pi_1\pi_2\,\ldots\,\pi_n$, whose elements are distinct
-and usually consist of the integers $12\,\ldots\,n$. 
-We let $\pi[i]$ stands for $\pi_i$.
-Conveniently, we let
-$\pi[i:j]$ stands for
-$\pi_i\pi_{i+1}\,\ldots\,\pi_j$,
-$\pi[:j]$ stands for $\pi[1:j]$ and
-$\pi[i:]$ stands for $\pi[i:n]$.
+and usually consist of the integers $1,2,\ldots,n$.
 
@@
 $\pi[i]$ to indicate the value of the element 
-at position $i$.  
+at position $i$ (\emph{i.e.} $\pi_i$).  
 For example, in the permutation $\pi = 51342$,
@@
 and the element at position $1$ has for value $5$.
-
-It is convenient to use a geometric representation of permutation
+Conveniently, we let
+$\pi[i:j]$ stand for
+$\pi_i\pi_{i+1}\,\ldots\,\pi_j$,
+$\pi[:j]$ stand for $\pi[1:j]$ and
+$\pi[i:]$ stand for $\pi[i:n]$.
+
+It is convenient to use a geometric representation of permutations
 to ease the understanding of algorithms. 
@@
 
-When an element $e_1$ is smaller (resp. bigger)
-than an element $e_2$  by value (in the natural order of the set),
-we say that $e_1$ is below (resp. above) $e_2$,
-as a reference to the figure of the permutation.
-Besides, the element with the biggest value is called
+When an element $\pi[\alpha]$ is smaller (resp. larger)
+than an element $\pi[\beta]$  by value (in the natural order of the set),
+we say that $\pi[\alpha]$ is below (resp. above) $\pi[\beta]$,
+as a reference to the geometric representation of the permutation.
+Besides, the element with the largest value is called
 the topmost element and the element with the smallest value
@@
 
-When an element $e_1$ is smaller (resp. bigger)
-than an element $e_2$  by position (in the order given by the permutation),
-we say that $e_1$ is on the left of (resp. on the right of) $e_2$.
-Besides, the element with the biggest position is called the rightmost element
+When an element $\pi[\alpha]$ is smaller (resp. larger)
+than an element $\pi[\beta]$  by position (in the order given by the permutation),
+we say that $\pi_\alpha$ is on the left of (resp. on the right of) $\pi[\beta]$.
+Besides, the element with the largest position is called the rightmost element
 and the element with the smallest position is called the leftmost element.
@@
 elements of $\pi$ that has the same relative order as $\sigma$.
+Such subsequence is called an \emph{occurrence} of $\sigma$ in $\pi$.
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
@@
 ).
-Each subsequence $91674$,
-$91675$,
-$91672$,
-$91452$,
- in $\pi$ is called an
-\emph{occurrence}
-of $\sigma$.
 Since the permutation $\pi = 391867452$  contains no increasing subsequence of
-length four, $\pi$ avoids $1234$.
+size four, $\pi$ avoids $1234$.
 
 For an occurrence $s$ of $\sigma$ in $\pi$, 
-we say that $\pi[j]$ is a matching of $\sigma[i]$ or 
-that $\sigma[i]$ is matched to $\pi[j]$  
+we say that $\pi[j]$ correspond $\sigma[i]$ in the occurrence or 
+that $\sigma[i]$ is matched to $\pi[j]$  in the occurrence
 if and only if $\pi[j]=s[i]$.
@@
 
-An \emph{ascent element} of an $n$-permutation $\pi \in S_n$ is any element
-$\pi[i]$ such that $i<n$ and $\pi[i] < \pi[i+1]$.
-For example, the permutation
-$3452167$ has ascents $3$, $4$, $1$ and $6$.
-Similarly, a \emph{descent} is any element
-$\pi[i]$ such that $i<n$ and $\pi[i] > \pi[i+1]$.
-So for every $1 \leq i < n$, $\pi[i]$  is either an ascent or a descent of
-$\pi$.
+%An \emph{ascent element} of an $n$-permutation $\pi \in S_n$ is any element
+%$\pi[i]$ such that $i<n$ and $\pi[i] < \pi[i+1]$.
+%For example, the permutation
+%$3452167$ has ascents $3$, $4$, $1$ and $6$.
+%Similarly, a \emph{descent} is any element
+%$\pi[i]$ such that $i<n$ and $\pi[i] > \pi[i+1]$.
+%So for every $1 \leq i < n$, $\pi[i]$  is either an ascent or a descent of
+%$\pi$.
+
 %To clarify the exposition,
-%we let $\ustep$ and $\dstep$ denote an ascend and a descend, respectively.
+%we let $\ustep$ and $\dstep$ denote an ascend and a descend, resp..
 %The \emph{stripe} $s_\pi$ of a permutation $\pi \in S_n$ is the word
@@
 
-A $\textit{right to left maximum}$ (abbreviate RLMax) of $\pi$ is an element that does not have any element above it at its right (see Figure $\ref{fig:left to right maxima}$).
+A $\textit{right-to-left maximum}$ (abbreviated to RLMax) of $\pi$ is an element that does not have any element above it and to its right (see Figure $\ref{fig:left to right maxima}$).
 Formally, $\pi[i]$ is a RLMax if and only if $\pi[i]$ is topmost element of $\pi[i:]$.
-Similarly $\pi[i]$ is a $\textit{left to right minima}$ (abbreviate RLMin) if and only if $\pi[i]$ is the bottommost element of $\pi[i:]$.
+Similarly $\pi[i]$ is a $\textit{right-to-left minimum}$ (abbreviate RLMin) if and only if $\pi[i]$ is the bottommost element of $\pi[i:]$.
 
@@
 	\caption[Example pattern matching]{
-		The element is a RLMax if and only if the dashed area is empty.} 
+		The element is a RLMax if and only if the hashed area is empty.} 
 	\label{fig:left to right maxima}
@@
 
-A \emph{bivincular pattern} $\sigma$
-of length $k$ is a permutation in $S_k$ written in
+A \emph{bivincular permutation pattern} $\widetilde{\sigma}$
+of size $k$ is a permutation written in
 two-line notation
@@
 is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$)
-with overlined elements in the top row and underlined element in the bottom row.
+with overlined elements in the top row and underlined elements in the bottom row.
 We have the following conditions on the top and bottom rows
-of $\sigma$, as see in \cite{Kitaev:book:2011} in Definition 1.4.1:
+of $\sigma$, as seen in \cite{Kitaev:book:2011} in Definition 1.4.1:
 \begin{itemize}
@@
 	and
-	if the bottom row of $\sigma$ begins with
+	if the bottom row of $\sigma$ ends with
 	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$
@@
 	$^\ulcorner{1}$ then
-	any occurrence of $\sigma$ is a permutation $\pi$ must contain 
+	any occurrence of $\sigma$ in a permutation $\pi$ must contain 
 	the bottommost element of $\pi$, and
 	if top row of $\sigma$ ends with $k^\urcorner$ then
-	any occurrence of $\sigma$ is a permutation $\pi$ must contain
+	any occurrence of $\sigma$ in a permutation $\pi$ must contain
 	the topmost element of $\pi$.
@@
 
+Given a bivincular permutation pattern $\widetilde{\sigma}$,
+$\sigma$ refers to the bottom line of $\widetilde{\sigma}$
+without any element underlined.
 For example,
 let
-$\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$.
-In $3217845$, $\textbf{32}17\textbf{84}5$ is an occurrence  of $\sigma$ but
- $3\textbf{21}\textbf{7}8\textbf{4}5$ is not.
-The best general reference is \cite{Kitaev:book:2011}.
-
-Geometrically, We represent underlined and overlined elements by \textit{forbidden areas}.
-If two elements are overlined then we draw a vertical forbidden areas between those two points.
+$\widetilde{\sigma} = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}}$,
+in $3217845$, $\textbf{32}17\textbf{84}5$ is an occurrence  of $\widetilde{\sigma}$ but $3\textbf{21}\textbf{7}8\textbf{4}5$ is not 
+and $\sigma = 2143$.
+The best general reference for bivincular pattern is \cite{Kitaev:book:2011}.
+
+Geometrically, we represent underlined and overlined elements by \textit{forbidden areas}.
+If two elements are overlined then we draw a horizontal forbidden area between those two points.
 In an occurrence, we also draw the forbidden area between the matching of two overlined elements.
-This area must be empty for an occurrence to be called so. 
+This area must be empty to have a valid occurrence of the bivincular pattern. 
 If the area is empty then there is no element between them when reading the permutation
@@
 in other words the matching elements are consecutive in value.
-If two elements are underlined then we draw an horizontal forbidden area.
-(See figure \ref{example:bivincular pattern matching}).
+If two elements are underlined then we draw an vertical forbidden area.
+(See Figure \ref{example:bivincular pattern matching}).
 
@@
     		From left to right,
-    		the bivincular pattern $\sigma = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$, An occurrence of $\sigma$ in $3216745$, An occurrence of $2143$ in $3216745$ but not an occurrence of $\sigma$ in $3216745$ because the point $(1,3)$ and $(5,7)$ are in the forbidden area.}
+    		the bivincular pattern $\widetilde{\sigma} = \BV{1\overline{23}4\urcorner}{\llcorner 21\underline{43}  }$, an occurrence of $\widetilde{\sigma}$ in $3216745$, an occurrence of $\sigma$ in $3216745$ but not an occurrence of $\widetilde{\sigma}$ because the points $(1,3)$ and $(5,7)$ are in the forbidden areas.}
     	\label{example:bivincular pattern matching}
@@
 
-This section is devoted to presenting a fast algorithm for deciding if
+This section is devoted to present a fast algorithm for deciding if
 $\sigma \preceq \pi$
 in case both $\pi$ and $\sigma$ are wedge permutations.
-We begin with an easy but crucial structure lemma.
+We begin with an easy and folk  but crucial structure lemma.
 
@@
 
-\begin{proof}[of Lemma~\ref{lemma:first element is 1 or n}]
+\begin{proof} %[of Lemma~\ref{lemma:first element is 1 or n}]
 Any other initial element would serve as a `$2$' in either a
-$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' respectively.
+$231$ or $213$ with $1$ and $n$ as the `$1$' and `$3$' resp..
 \qed
@@
 \label{corollary:minmaxelement}
-$\pi$ is a wedge permutation if and only if for $1 \leq i \leq n$,
+$\pi$ is a wedge permutation of size $n$ if and only if for $1 \leq i \leq n$,
 $\pi[i]$ is a RLMax or a RLMin.
 \end{corollary}
+
+\begin{proof} %[of Lemma~\ref{lemma:first element is 1 or n}]
+Given a position $i$, $\pi[i:]$ is a wedge permutation,
+so it either starts with the maximal or the minimal element.
+\qed
+\end{proof}
+
+As a consequence, every element of a wedge permutation can be partitioned 
+into three sets: the set of RLMax elements, the set of RLMin elements and the 
+rightmost element which can be both a RLMax element and a RLMin element.
+
+\begin{remark}
+The set of RLMax elements is a decreasing subsequence,
+indeed each element is left above the next RLMax element by definition
+of a RLMax element. In the same fashion, 
+the set of RLMin elements is an increasing subsequence.
+See Figure~\ref{fig:shape of the permutation plus factor}.
+\end{remark}
+
+\begin{remark}
+Every element of the set of RLMax elements is above the elements
+of the set of the RLMin elements. 
+In other words, a wedge permutations
+can be cut in half horizontally on the rightmost element such that the upper half contains a decreasing  
+subsequence and the lower half contains an increasing subsequence.
+This shape the permutation as a $>$, 
+hence the name of wedge permutations. 
+See Figure~\ref{fig:shape of the permutation plus factor}.
+\end{remark}
+
+\begin{remark}
+The partition gives a bijection between the set of wedge permutations of size $n$ where the elements are $1,\ldots,n$
+and the set of binary word of size $n-1$.
+The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$ 
+represents whether $\pi[i]$ is a RLMax element or a RLMin element.
+We call this bijection $\bijection$.
+\end{remark}
+
+To figure out whether or not an element is a RLMax element or a RLMin element,
+one has to run the whole permutation from left to right starting 
+from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time.
 
@@
 Let $\pi$ be a wedge permutation and $1 \leq i < n$. Then,
-(1) 
-$\pi[i]$ is an ascent element if and only if $\pi[i]$ is a RLMin
-and 
-(2)
-$\pi[i]$ is a descent element if and only if $\pi[i]$ is a RLMax
+\begin{enumerate}
+\item $\pi[i]$ is a RLMin element if and only if $\pi[i]<\pi[i+1]$
+\item $\pi[i]$ is a RLMax element if and only if $\pi[i]>\pi[i+1]$ is a RLMax
+\end{enumerate}
+
 \end{corollary}
 
-Corollary $\ref{corollary:max is ascent}$ gives a bijection between the set of wedge permutations and the set of binary word of size $n-1$.
-The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$ represents whether $\pi[i]$ is an ascent or descent element (equivalently, is a RLMax or a RLMin).
-We call this bijection $\bijection$.
-
-A wedge permutation has a particular form that gives its name.
-If we take only the descent elements, 
-they form a decreasing subsequence
-and the ascent elements form an increasing subsequence.
-Moreover the descent elements are above the ascent elements.
-This shapes the permutation as a $>$.
+%\begin{remark}
+%Corollary~\ref{corollary:max is ascent} allows to compute 
+%\end{remark}
 
@@
 
-\begin{figure}[t] 
-	\centering
-	\begin{tikzpicture}[scale=.3]
-	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
-	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
-		\draw[dotted] (0,\i) -- (9, \i);
-		\draw[dotted] (\i,0) -- (\i, 9);
-	}
-	\draw[fill=black] (0.5,0.5) circle (2mm);
-	\draw[fill=black] (1.5,1.5) circle (2mm);
-	\draw[fill=black] (2.5,2.5) circle (2mm);
-	\draw[fill=black] (3.5,8.5) circle (2mm);
-	\draw[fill=black] (4.5,7.5) circle (2mm);
-	\draw[fill=black] (5.5,3.5) circle (2mm);
-	\draw[fill=black] (6.5,6.5) circle (2mm);
-	\draw[fill=black] (7.5,5.5) circle (2mm);
-	\draw[fill=black] (8.5,4.5) circle (2mm);
-
-	\draw (0,0) -- (3,3);
-	\draw (3,9) -- (5,7);
-	\draw (5,3) -- (6,4);
-	\draw (6,7) -- (9,4);
-
-	\end{tikzpicture}
-
-	\caption{The wedge permutation $123984765$, every point which is on a north-west to south-east line represents a descent element and every point which is on a south-west to north-east line represents an ascent element.}
-	\label{fig:shape of the permutation}
-\end{figure}
-
-The following lemma is central to our algorithm.
+%\begin{figure}[t] 
+%	\centering
+%	\begin{tikzpicture}[scale=.3]
+%	\draw (0,0) -- (9,0) -- (9,9) -- (0,9) -- cycle;
+%	\foreach \i in {1, 2, 3, 4, 5, 6, 7, 8, 9}{
+%		\draw[dotted] (0,\i) -- (9, \i);
+%		\draw[dotted] (\i,0) -- (\i, 9);
+%	}
+%	\draw[fill=black] (0.5,0.5) circle (2mm);
+%	\draw[fill=black] (1.5,1.5) circle (2mm);
+%	\draw[fill=black] (2.5,2.5) circle (2mm);
+%	\draw[fill=black] (3.5,8.5) circle (2mm);
+%	\draw[fill=black] (4.5,7.5) circle (2mm);
+%	\draw[fill=black] (5.5,3.5) circle (2mm);
+%	\draw[fill=black] (6.5,6.5) circle (2mm);
+%	\draw[fill=black] (7.5,5.5) circle (2mm);
+%	\draw[fill=black] (8.5,4.5) circle (2mm);
+%	
+%	\draw (0,0) -- (3,3);
+%	\draw (3,9) -- (5,7);
+%	\draw (5,3) -- (6,4);
+%	\draw (6,7) -- (9,4);
+%	
+%	
+%	\end{tikzpicture}	
+%	
+%	
+%	\caption{The wedge permutation $123984765$, every point which is on a north-west to south-east line represents a descent element and every point which is on a south-west to north-east line represents an ascent element.}
+%	\label{fig:shape of the permutation}
+%\end{figure}
+
+Now that we had highlight some structural point of a wedge permutation,
+we can use this structure to solve the permutation pattern matching.
+More precisely, we use the bijection on binary word to solve this problem,
+thank to the following lemma.
 
@@
 \label{lemma:MatchStripeToPermutation}
-Let $\pi$ and $\sigma$ be two wedge permutations,
+Let $\pi$ and $\sigma$ be two wedge permutations.
 Then, $\pi$ has an occurrence of $\sigma$ if and only if 
@@
 
-\begin{proof}[of Lemma~\ref{lemma:MatchStripeToPermutation}]
+\begin{proof} %[of Lemma~\ref{lemma:MatchStripeToPermutation}]
 The forward direction is obvious.
-We prove the backward direction by induction on the size of the pattern
-$\sigma$.
+We prove the backward direction by induction on the size of
+$\sigma$: if $\bijection(t)=\bijection(\sigma)$ then $t$ is an occurrence of $\sigma$.
 The base case is a pattern of size $2$.
-Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = ascent$.
+Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = RLMin$.
 Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-such that $\bijection(t) = ascent$, this reduces to saying that
+such that $\bijection(t) = RLMin$, this reduces to saying that
 $\pi_{i_1} < \pi_{i_2}$, 
@@
 Now, assume that the lemma is true for all patterns up to size $k \geq 2$.
-Let $\sigma$ be an k-wedge permutation and
-let $t$,
-be a subsequence of $\pi$ of length $k+1$ such that
+Let $\sigma$ be a wedge permutation of size $k+1$ and
+let $t$
+be a subsequence of $\pi$ of size $k+1$ such that
 $\bijection(t) = \bijection(\sigma)$.
 As $\bijection(t)[2:] = \bijection(\sigma)[2:]$
-by the inductive hypothesis, it follows that
+by the induction hypothesis, it follows that
 $t[2:]$ is an occurrence of $\sigma[2:]$.
@@
 thus $t[1]$ and $\sigma[1]$ are both either the bottommost or the topmost
-element of their respective subsequences.
+element of their respective sequences.
 Therefore, $t$ is an occurrence of $\sigma$ in $\pi$.
@@
 
-We are now ready to solve the pattern matching problem in case
+We are now ready to solve the permutation pattern matching problem in case
 both $\pi$ and $\sigma$ are wedge permutations.
@@
 to deciding whether $\bijection(\sigma)$ occurs as a subsequence in $\bijection(\pi)$.
-A straightforward greedy approach solves this issue in linear-time,
-by reading both words from left to right and matching two letters when they are equal then passing
-to the next letters for both words
-or passing to the next letter in the word of the text.
+This can be solved in linear time with a straightforward greedy approach as follows. 
+We read both $\bijection(\sigma)$ and $\bijection(\pi)$ from left to right; 
+when two letters are equal, we match them, and move to the next in both 
+$\bijection(\sigma)$ and $\bijection(\pi)$ (if such letters exist);
+otherwise we stay at the same letter of $\bijection(\sigma)$
+but move to the next one in $\bijection(\pi)$ (if it exists);
+we accept exactly when all letters of B(sigma) have been matched.
 \qed
@@
 
-Thank to Corollary~\ref{corollary:max is ascent},
-we do not need to compute the word corresponding to the permutations before running the greedy algorithm. This computation can be done in the same time with the algorithm,
-thus, this gives on-line algorithm.
+Thanks to Corollary~\ref{corollary:max is ascent},
+we do not need to compute the words $\bijection(\sigma)$ and $\bijection(\pi)$ before running the greedy algorithm. 
+This computation can be done at the same time as running the algorithm,
+thus, giving an on-line algorithm.
 
@@
 
-This section focuses on the pattern matching problem
+This section focuses on the permutation pattern matching problem
 in case only the pattern $\sigma$ is a wedge permutation.
-We need to consider a specific decomposition of $\sigma$ into \textit{factor} :
-we split the permutation into maximal sequences of consecutive ascent and descent elements, respectively called an ascent factor and a descent factor.
-This corresponds to splitting the permutation between every pair of ascent-descent and descent-ascent element (see Figure \ref{fig:shape of the permutation plus factor}).
-For the special case of a wedge permutation, this also corresponds to split the permutation into maximal sequences of element consecutive in value.
-We will label the factors from right to left.
+We need to consider a specific decomposition of $\sigma$ into \textit{factors}:
+we split the permutation into maximal sequences of consecutive RLMin and RLMax elements, respectively called a RLMin factor and a RLMax factor.
+This corresponds to splitting the permutation between every pair of RLMin-RLMax and RLMax-RLMin elements (see Figure \ref{fig:shape of the permutation plus factor}).
+For the special case of a wedge permutation, this also corresponds to split the permutation into maximal sequences of elements consecutive in value.
+We label the factors from right to left.
+Note that the rightmost element can be both a RLMin or a RLMax,
+we take the convention that it is as the same type as the element before it for the factorization,
+such that the first factor (the rightmost factor) always contains at least two
+elements.
 For example,
@@
 $\factor(4) =123$, $\factor(3) = 98$, $\factor(2) = 4$ and $\factor(1) = 765$.
+
+\begin{remark}
+A factor is either an increasing or a decreasing sequence of elements. 
+\end{remark}
+
+To lighten a figure of an occurrence 
+and to help the comprehension, 
+we represent
+an occurrence in $\pi$ (or a part of it) by any rectangle $((A_x,A_y),(B_x,B_y))$ that 
+contains
+at least all the points of the elements of the occurrence,
+where $A$ is the bottom left corner and 
+$B$ is the top right corner.
+Formally the rectangle $((A_x,A_y),(B_x,B_y))$
+is the set of points in $\pi[A_x:B_x]$
+where each element is in $[A_y,B_y]$.
+Especially we say that a rectangle is minimal
+if and only if it is the smallest rectangle
+that contains all of the elements of the occurrence.
+Moreover, the minimal rectangle of an occurrence
+is $((lm,bm),(rm,tm))$ where
+$lm$ stands for the position of the leftmost element,
+$bm$ stands for the value of the bottommost element,
+$rm$ stands for the position of the rightmost element and
+$tm$ stands for the value of the topmost element.
+See Figure \ref{fig:decomposition of an occurrence}.
+
+\begin{remark}
+A rectangle contains
+an occurrence of a RLMin (resp. RLMax) factor if and only if 
+the rectangle contains an increasing (resp. decreasing) subsequence
+of same size or larger than the size of the factor. 
+\end{remark}
+
+We give a property of a wedge permutation that
+allows us to decide whether a rectangle 
+contains an occurrence of the wedge permutation:
+given a rectangle we show that we can spilt the 
+rectangle in two smaller rectangles.
+The splitting transforms the problem
+in deciding whether or not each of the two rectangles
+contains part of the wedge permutation.
+Intuitively, the problems on the two rectangles
+are easier than the problem on the original rectangle.
+
+\begin{lemma}
+There exists an occurrence of a wedge permutation
+starting with a leftmost RLmin (resp. RLmax) factor
+if and only if
+there exists two rectangles $R_1$ and $R_2$,
+such that $R_1$ is left below (resp. left above) $R_2$,
+$R_1$ contains an occurrence of the leftmost factor
+and $R_2$ contains an occurrence of the rest.
+\end{lemma}
+
+\begin{proof}
+This is true as the leftmost factor is left bellow (resp. left above)
+the rest of the wedge permutation.
+\end{proof}
+
+We show how to compute the permutation pattern matching
+using this lemma. Note that the algorithm given in the proof is not the best we can do
+in respect to the time and space complexity,
+but it helps to understand the best version.
+
+\begin{lemma}
+Let $\sigma$ be a wedge permutation of size $k$ 
+and $\pi$ a permutation of size $n$.
+One can decide in polynomial time and space whether
+$\pi$ contains an occurrence $\sigma$.
+\end{lemma}
+
+\begin{proof}
+We introduce a set of values needed in computing the permutation patten matching.
+Let $LIS_{\ptext}(((j,lb),(j',up)))$ (resp. $LDS_{\ptext}(((j,lb),(j',up)))$) be the size of the longest increasing 
+(resp. decreasing) subsequence in $((j,lb),(j',up))$.
+For all the rectangles
+$LIS_{\ptext}(((j,lb),(j',up)))$ and $LDS_{\ptext}(((j,lb),(j',up)))$ are computed in 
+$O(n^2\log(\log(n)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
+$LIS_{\ptext}(((j,lb),(j',up)))$ 
+(resp. $LDS_{\ptext}$ $(((j,lb),(j',up)))$) 
+allow us to decide 
+the existence of an occurrence of any LRMin (resp. LRMax) factor
+in the rectangle $((j,lb),(j',ub))$ in constant time
+if we precomputed it for all the rectangles.
+
+We solve the problem of deciding whether 
+a rectangle $((j,lb),(n,ub))$ contains
+an occurrence of $\factor(i)\ldots\factor(i')$,
+More formally:
+
+$$
+\PM^\pi_\sigma(i,i',((j,lb),(n,ub))) = 
+\begin{cases}
+True & \text{if and only if $((j,lb),(n,ub))$ contains } \\
+ & \text{an occurrence of $\factor(i)\ldots\factor(i')$}\\
+ False & \text{Otherwise}
+\end{cases}
+$$
+
+By definition $\pi$ contains an occurrence of $\sigma$
+if and only if $\PM^\pi_\sigma(\ell,1,((1,1),$ $(n,n)))$
+is true
+where $\ell$ is the number of factors in $\sigma$.
+We show how to compute $\PM^\pi_\sigma(i,i',((j,lb),(n,up)))$ recursively.
+\begin{itemize}
+\item If the permutation is reduced to a factor
+then one has to decide if the rectangle
+contains an increasing or a decreasing factor
+with the same size or larger than the 
+size of the unique factor. 
+This case happens when $i=i'$:
+\begin{itemize}
+\item if $factor(i)$ is a LRMin factor:
+$$
+\PM^\pi_\sigma(i,i,((j,lb),(n,up))) = 
+$$
+$$
+\begin{cases}
+True & \text{ $|factor(i)| \leq LIS_{\ptext}(((j,lb),(n,up)))$ } \\
+False & \text{Otherwise}
+\end{cases}
+$$
+\item if $factor(i)$ is a LRMin factor:
+$$
+\PM^\pi_\sigma(i,i,((j,lb),(n,up))) = 
+$$
+$$
+\begin{cases}
+True & \text{ $|factor(i)| \leq LDS_{\ptext}(((j,lb),(n,up)))$ } \\
+False & \text{Otherwise}
+\end{cases}
+$$
+\end{itemize}
+
+\item Otherwise, assuming that $\factor(i)$ is a LRMin (resp. LRMax) factor,
+we need to decide if there exists a spitting of $((j,lb),(n,up))$  into two rectangle $R_1$ and $R_2$ such that 
+$R_1$ is left below (resp above) $R_2$,
+ $R_1$ contains an occurrence of $\factor(i)$
+and  $R_2$ contains an occurrence of 
+$\factor(i-1)\ldots \factor(i')$.
+A direct strategy is to try every pair of rectangles where one rectangle is left below (resp. above) the other
+and to decide whether the first one contains a occurrence of $\factor(i)$
+and the second one contains an occurrence of 
+$\factor(i-1)\ldots \factor(i')$.
+Note that to reduce the number of pair of rectangles to test,
+it is better to consider the biggest rectangles possible
+as long as the positions of the two rectangles are respected.
+Indeed if $R'$ is contained in $R$ and $R'$ contains an occurrence then
+$R$ also contains this occurrence, 
+so we do not
+need to find an occurrence in both $R$ and $R'$ 
+but only in $R$.  
+Especially we can always consider that $R_1$ has for 
+left bottom corner $(j,lb)$ (resp. right top corner  $(j,up)$)
+and that $R_2$ has for right top corner $(n,up)$ 
+(resp. right bottom corner $(n,lb)$)
+and $R_1$ is next to $R_2$.
+More formally:
+\begin{itemize}
+\item if $factor(i)$ is a LRMin factor:
+$$
+\PM^\pi_\sigma(i,i',((j,lb),(n,up))) =
+$$
+$$
+\bigvee_{
+\substack{
+j\leq j'<n\\ up' < up
+}	} \PM^\pi_\sigma(i,i,((j,lb),(j',up'))) \wedge 
+\PM^\pi_\sigma(i-1,i',((j'+1,up'+1),(n,up)))
+$$
+
+\item if $factor(i)$ is a LRMax factor:
+$$
+\PM^\pi_\sigma(i,i',((j,lb),(n,up))) =
+$$
+$$
+\bigvee_{\substack{
+j\leq j'<n \\ lb'>lb
+	}	} \PM^\pi_\sigma(i,i,((j,lb'),(j',up))) \wedge 
+\PM^\pi_\sigma(i-1,i',((j'+1,lb),(n,lb'-1)))
+$$
+\end{itemize}
+\end{itemize}
+
+Remark that by modifying the definition of $\PM^\pi_\sigma(i,i',((j,lb),(n,up)))$
+we can reduce the computational time of the algorithm.
+Instead of asking for any occurrence in $((j,lb),(n,up)))$,
+we ask for the occurrences that start at $\pi[j]$.
+As any element in the pattern is a RLMax or a RLMin,
+the value of $\pi[j]$ can be used has a top or a bottom edge 
+of a rectangle.
+So we can remove one argument from the problem,
+reducing the maximal number of different problems that we have to compute.
+%The new definition gives us:
+%$\pi$ contains an occurrence of $\sigma$
+%if and only if $\bigvee_{1 \leq j \leq n}  \PM^\pi_\sigma(\ell,1,((j,1),(n,n)))$
+%is true
+%where $\ell$ is the number of factors in $\sigma$.
+\qed
+\end{proof}
+
+We extend our research to reduce the number of pairs of rectangles 
+that we have to test.
+Informally, 
+given that the leftmost factor is a RLMin (resp. RLMax) factor and
+given that the left top (resp. bottom left) corner of the second rectangle is fixed and 
+that the second rectangle contains the occurrence of the 
+rest of the permutation, it is in the interest of finding an occurrence in the whole rectangle
+that the bottom (resp. top) edge of the second rectangle is the highest (resp. lowest) possible.
+Indeed, the first rectangle will have 
+a highest top (resp. a lowest bottom) edge so it will contains more elements
+which is better to find an occurrence.
+The next lemma indicates which element is the topmost and the bottommost,
+and the next one and its corollary formalise what said above.
+But first we introduce another notation.
+
+We introduce the notation $\LMEi(s)$ (which stands for the left most element position): Suppose that $s$ is a subsequence of $S$, $\LMEi(s)$ is the position of the leftmost element of $s$ in $S$. Thus
+for every $\factor$, $\LMEi(\factor(j))$ stands for the position in $\sigma$
+of the leftmost element of $\factor(j)$.
+From the above example,
+$\LMEi(\factor(4)) = 1$, $\LMEi(\factor(3)) = 4$, $\LMEi(\factor(2)) = 6$ and $\LMEi(\factor(1)) = 7$.
+
+%\begin{lemma}
+%Given an occurrence of a wedge permutation
+%starting with a RLMin (resp. RLMax) factor,
+%the minimal rectangle containing the occurrence
+%of leftmost factor is left bellow (resp. left above)
+%the minimal rectangle containing the rest of the occurrence.
+%\end{lemma}
+%
+%\begin{proof}
+%This is true as the leftmost factor is left bellow (resp. left above)
+%the rest of the wedge permutation.
+%\end{proof}
+
+%\begin{lemma}
+%Given an occurrence of a wedge permutation
+%where we represent the occurrence of each factor
+%by the minimal rectangle containing all
+%the elements of the occurrence of this factor.
+%Then, two different rectangles are always comparable.
+%
+%
+%If $R_\alpha$ and $R_\beta$ are two different rectangles
+%of this occurrence 
+%such that the factor of $R_\alpha$ is on the left
+%of the factor of $R_\beta$
+%then:
+%\begin{itemize}
+%\item either $R_\beta$ is right below $R_\beta$.
+%\item or $R_\beta$ is right above $R_\alpha$.
+%\end{itemize}
+%\end{lemma}
+%
+%\begin{proof}
+%We prove that two rectangles can
+%always be compared to each other 
+%horizontally.
+%Suppose that we cannot compare them,
+%in other words $R_alpha$ has for right edge
+%$a$ and $R_beta$ has for left edge $b$
+%and $b<a$
+%\end{proof}
 
@@
 
-We introduce the notation $\LMEi(s)$ : Suppose that $s$ is a subsequence of $S$, $\LMEi(s)$ is the position of the leftmost element of $s$ in $S$. Thus
-for every $\factor$, $\LMEi(\factor(j))$ stands for the position in $\sigma$
-of the leftmost element of $\factor(j)$.
-From the above example,
-$\LMEi(\factor(4)) = 1$, $\LMEi(\factor(3)) = 4$, $\LMEi(\factor(2)) = 6$ and $\LMEi(\factor(1)) = 7$.
-
-To lighten the figure of a wedge permutation, 
-we represent the elements of an ascent (resp. descent) factor 
-by a rectangle which has the matching of the leftmost point of the factor as the left bottom (resp.
-top) corner and the matching of the rightmost point of the factor as the right top (resp.
-bottom) corner.
-We can merge the two rightmost rectangles and replace them by the smallest rectangle that contains both of them and repeat this operation to represent part of an occurrence (see Figure \ref{fig:decomposition of an occurrence}).
+%\begin{remark}
+%In a representation of an occurrence, 
+%we merge the two rightmost rectangles and replace them by the smallest rectangle that contains both of them and repeat this operation.
+%Such that the right most rectangle represents the elements of the occurrence of a suffix of factor $\sigma$. See Figure \ref{fig:decomposition of an occurrence}.
+%\end{remark}
 
@@
 
-	\caption{The operation of merging the two rightmost rectangle.}
+	\caption{From left ro right, an occurrence of a permutation
+		the same occurrence where each occurrence of a factor is represented by the minimal rectangle,
+		the same occurrence where the occurrence of the first two factor are represented by the minimal rectangle 
+		and the same occurrence represented by its minimal rectangle.}
 	\label{fig:decomposition of an occurrence}
@@
 
-\begin{remark}
-A factor is either an increasing or a decreasing sequence of element. 
-Thus to find an occurrence for a factor, one must find an increasing or a decreasing subsequence of same size or bigger than the factor.
-\end{remark}
-
-\begin{corollary}
+\begin{lemma}
 \label{corollary:whereIsMax}
 Given a wedge permutation $\sigma$, 
-if $\factor(i)$ is an ascent (respectively descent) factor 
-then topmost (resp. bottommost) element of $\ppattern[\LMEi(\factor(i+1)):]$
+if $\factor(i)$ is a RLMin (resp. RLMax) factor 
+the topmost (resp. bottommost) element of 
+$\factor(i)\ldots \factor(1)$
 is the leftmost element of $\factor(i-1)$.  
-\end{corollary}
-
-\begin{proof}[of Corollary~\ref{corollary:whereIsMax}]
+\end{lemma}
+
+\begin{proof} %[of Corollary~\ref{corollary:whereIsMax}]
 This corollary states that, given a wedge permutation 
-if the permutation starts with an ascent (respectively descent) elements then the topmost (resp.
-bottommost) element of this permutation is the first descent (resp.
-ascent) element (see Figure \ref{fig:where to find the max}).
-This is easy to see from Corollary  \ref{corollary:max is ascent}.
-The ascent elements are below the descent element, thus the topmost element must be 
-the first descent element, which is the leftmost element of $\factor(i-1)$.
+if the permutation starts with a RLMin (resp.
+RLMax) element then the topmost (resp.
+bottommost) element of this permutation is the first RLMax (resp.
+RLMin) element (see Figure \ref{fig:where to find the max}).
+This is easy to see from the shape of a wedge permutation.
+Formally, the RLMin elements are below the RLMax element, thus the topmost element must be 
+the first RLMax element, which is the leftmost element of $\factor(i-1)$.
 \qed
@@
 
+	\draw (4,10) -- (5,9);
 	\draw (6,2) -- (7,3);
@@
 
-	\draw[fill=gray] (7,7) circle (2mm) node[above] {factor(i-1)};
-	\draw[fill=black] (6,2) circle (0mm) node[below] {factor(i)};;
+	\draw[fill=gray] (7,7) circle (2mm) node[above] {$\factor(i-1)$};
+	\draw[fill=black] (6,2) circle (0mm) node[below] {$\factor(i)$};
+		\draw[fill=black] (4,10) circle (0mm) node[above] {$\factor(i+1)$};
 
@@
 
-We define the set
+%We define the set
 $\SET{\ppattern}{\ptext}{i}{j}$ 
-as the set of every subsequence $s$ of $\ptext[j:]$ that starts at $\ptext[j]$ and
-that is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$.
+as the set of all subsequences $s$ of $\ptext[j:]$ that start at $\ptext[j]$ and
+that are  occurrences of $\factor(i)\ldots \factor(1)$.
+%This set control the rectangles (not minimal) of the occurrences:
+%each rectangle
+%assume that $\factor(i)$ is a RLMax (resp. RLMin) factor, 
+%then $\pi[j]$ is the top left (resp. bottom left) 
+%of the rectangle of the occurrence. 
+%Also, note that we can always assume that the right edge
+%of the rectangle is on the rightmost element of $\pi$,
+%as we can always expend a rectangle of a occurrence, 
+%without loosing elements of the occurrence.
+%We are left with the choose of the top edge,
+%this is what the next lemma is for.
 
@@
 \label{lemma:ts}
-Let $\ppattern$ be a permutation, 
-$\factor(i)$ be an ascent (respectively descent) factor,
-$s$ be a subsequence of $\pi$ such that $s \in \SET{\ppattern}{\ptext}{i}{j}$ and
-that minimizes (resp. maximizes) the matching of the leftmost element of $\factor(i-1)$.
-For all subsequences 
-$s' \in \SET{\ppattern}{\ptext}{i}{j}$ and for all subsequences $t$ of $\ptext$, such that $t=t's'$, 
-if $t$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ such that the leftmost element of $\factor(i)$ is matched to $\ptext[j]$ then the subsequence $t's$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ such that the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
+Let $\ppattern$ be a wedge permutation and
+$\factor(i)$ be an RLMin (resp. RLMax) factor $\sigma$.
+Let $\pi$ be a permutation and $s$ a subsequence of $\pi$ such that
+$s \in \SET{\ppattern}{\ptext}{i}{j}$ and
+$s$ minimizes (resp. maximizes) the matching of the leftmost element of $\factor(i-1)$.
+Let $s'$ be a subsequence of $\pi$ such that
+$s \in \SET{\ppattern}{\ptext}{i}{j}$
+and let $t=t's'$ be a subsequence of $\pi$ that extends $s'$ on the right.
+Assume $t$ is an occurrence of $\factor(i+1)\ldots \factor(1)$ such that the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
+Then the subsequence $t's$ is also an occurrence of $\factor(i+1)\ldots \factor(1)$ such that the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
 \end{lemma}
 
-This lemma states that given any occurrence of $\factor(i+1)$ $\factor(i)$ $\ldots$ $\factor(1)$,
-where $\factor(i)$ is an ascent (resp. descent) factor,
+Informally, this lemma states that we can replace
+the rectangle of an occurrence in $\SET{\ppattern}{\ptext}{i}{j}$
+by another rectangle of an occurrence in $\SET{\ppattern}{\ptext}{i}{j}$
+such that the second rectangle shares the same edges as the first one,
+except for the top edge which is lower. 
+Especially the second rectangle can be chosen as the one with
+the lowest top edge in all the rectangles sharing the right, bottom 
+and left edges.
+More formally, given any occurrence of $\factor(i+1)$ $\factor(i)$ $\ldots$ $\factor(1)$,
+where $\factor(i)$ is a RLMin (resp. RLMax) factor,
 we can replace the part of the occurrence where $\factor(i)$ $\ldots$ $\factor(1)$ occurs, by any occurrence
@@
 
-\begin{proof}[of Lemma~\ref{lemma:ts}]
-Let us consider the case where $\factor(i)$ is an ascent factor.
+\begin{proof} %[of Lemma~\ref{lemma:ts}]
+Let us consider the case where $\factor(i)$ is a RLMin factor.
 By definition $s$ is an occurrence of $\ppattern[\LMEi(\factor(i)):]$.
-To prove that $t's$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ we need to prove that the elements of t' are above the elements of $s$.
-If $t's'$ is an occurrence of $\ppattern[\LMEi(\factor(i+1)):]$ then the elements of $t'$ are above the elements of $s'$.
-Moreover the topmost element of $s$ is below (or equal to) the topmost element of $s'$ thus the elements of $s$ are below the elements of $t$.
-We use a similar argument if $\factor(i)$ is a descent factor.
+First of all, remark that $t'$ is an occurrence of $\factor(i+1)$.
+So to prove that $t's$ is an occurrence of $\factor(i+1)\ldots \factor(1)$ we need to prove that the elements of t' are above the elements of $s$. 
+Since $t's'$ is an occurrence of $\factor(i+1)\ldots \factor(1)$ it follows that the elements of $t'$ are above the elements of $s'$.
+Moreover the topmost element of $s$ is below (or equal to) the topmost element of $s'$ thus the elements of $s$ are below the elements of $t'$.
+We use a symmetric argument if $\factor(i)$ is a RLMax factor.
 \qed
@@
 Let $\ppattern$ be a permutation, 
-$\factor(i)$ be an ascent (respectively descent) factor
+$\factor(i)$ be a RLMin (resp. RLMax) factor
 and 
@@
 that minimizes (resp. maximizes) the matching of the leftmost element of $\factor(i-1)$.
-These following statements are equivalent :
+The following statements are equivalent:
 \begin{itemize}
@@
 	 of $\ppattern$ in $\ptext$ where the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
-	\item There exists an occurrence $t$ of $\sigma[:\LMEi(\factor(i))-1]$ in $\ptext[:j-1]$  such that $ts$ is an occurrence of $\ppattern$ in $\ptext$ with the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
+	\item There exists an occurrence $t$ of $\factor(\ell)\ldots \factor(i+1)$ in $\ptext[:j-1]$  such that $ts$ is an occurrence of $\ppattern$ in $\ptext$ with the leftmost element of $\factor(i)$ is matched to $\ptext[j]$.
 \end{itemize}
@@
 
-\begin{proof}[of Corollary~\ref{corollary:we can chose a matching}]
-This corollary takes a step further from the previous one, as it states that if there is no occurrence using any occurrence that maximises (resp.
-minimises) the leftmost element of $\factor(i-1)$ then there does not exist any occurrence at all.
-The backward direction is trivial and the forward direction is applying the Lemma~\ref{lemma:ts}.
+\begin{proof} %[of Corollary~\ref{corollary:we can chose a matching}]
+This corollary takes a step further from the previous one, as it states that if there is no occurrence of $\ppattern$ in $\ptext$ where the leftmost element of $\factor(i)$ is matched to $\ptext[j]$ and such that
+the leftmost element of $\factor(i-1)$ is minimized (resp. maximized)
+then there does not exist any occurrence at all. The backward direction is trivial and the forward direction follows the Lemma~\ref{lemma:ts}. 
 \qed
@@
 
-This corollary is central to the algorithm because it allows to test only the occurrence that  maximises (resp. minimises) the leftmost element of $\factor(i-1)$.
+%This corollary is central to the algorithm because it allows to test only the occurrence that  minimizes (resp. maximizes) the leftmost element of $\factor(i-1)$.
 
@@
 \label{Proposition:sigma avoids 213 and 231}
-Let $\sigma$ be a wedge permutation and $\pi \in S_n$.
+Let $\sigma$ be a wedge permutation of size $k$ 
+and $\pi$ a permutation of size $n$.
 One can decide in $O(max(kn^2,n^2\log(\log(n)))$ time
-and $O(kn^2)$ space if $\pi$ has an occurrence $\sigma$.
+and $O(n^3)$ space if $\pi$ contains an occurrence $\sigma$.
 \end{proposition}
@@
 \begin{proof}
-
-We first introduce a set of values needed to our proof.
-Let $LIS_{\ptext}(i,j,bound)$ (resp. $LDS_{\ptext}(i,j,bound)$) be the longest increasing 
-(resp. decreasing) sequence in $\ptext[i:j]$ starting at $i$,
-with every element of this sequence being
-smaller (resp. bigger) than $bound$.
+The algorithm follows the previous one,
+but instead of return true or false,
+assuming that $\factor(i)$ is a RLMin (resp. RLMax) factor
+the algorithm return the value of the 
+top (resp. bottom) edge.
+So that once we compute the problem for $R_2$
+we can use this value has the top (resp. bottom) edge
+for the rectangle $R_1$.
+
+We first introduce a set of values needed in the problems.
+Let $LIS_{\ptext}(j,j',bound)$ (resp. $LDS_{\ptext}(j,j',bound)$) be the longest increasing 
+(resp. decreasing) subsequence in $\ptext[j:j']$ starting at $\pi[j]$,
+with every element of this subsequence being
+smaller (resp. larger) than $bound$.
 $LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in 
 $O(n^2\log(\log(n)))$ time (see \cite{Bespamyatnikh00enumeratinglongest}).
-As stated before, those values allow us to find an occurrence of a factor.
-
-Given a factor $i$ of $\sigma$ and a position j of $\pi$,
-we want the optimal value of the matching of $\LMEi(\factor(i-1))$
-in any occurrence of  $\sigma[\LMEi(\factor(i)):]$
-in $\pi[j:]$ starting at $\pi[j]$ (see Figure \ref{fig: algo 1 fig}),
-which we denote as:
-
-$$
-\LM{\ppattern}{\ptext}{i}{j} =
+$LIS_{\ptext}(j,j',bound)$ 
+(resp. $LDS_{\ptext}(j,j',bound)$) 
+allow us to decide 
+the existence of an occurrence of any LRMin (resp. LRMax) factor
+in the rectangle $((j,\pi[j]),(j',bound))$ (resp. $((j,bound),(j',\pi[j])$).
+
+Given a RLMin (resp. RLMax) factor $\factor(i)$  of $\sigma$ and a position $j$ in $\pi$,
+we want the value of the top (resp. bottom) edge
+of any rectangle with left bottom (resp. with left top) corner   $(j,\pi[j])$  containing an occurrence of  $\factor(i) \ldots \factor(1)$ starting at $\pi[j]$
+and which minimizes (resp. maximizes) its top (resp. bottom) edge
+or a value which indicate that no occurrence exists in this rectangle. More formally:
+\begin{itemize}
+\item If $\factor(i)$ is RLMin factor.
+
+$$
+\PM^\pi_\sigma(i,j) =
+$$
+$$
 \begin{cases}
 
-	\text{The minimal value of the matching } 
-		& \text{If $\factor(i)$ is} \\
-	\text{ of $\LMEi(\factor(i-1))$ } 
-		& \text{an ascent factor} \\	
-	\text{ in any occurrence of  $\sigma[\LMEi(\factor(i)):]$ } & \\
-	\text{ in $\pi[j:]$ strarting at $\pi[j]$} & \\
-	\text{Or $\infty$ if no occurrence exists} & \text{} \\
-
-	&\\
-
-	\text{The maximal value of the matching } 
-		& \text{If $\factor(i)$ is} \\
-	\text{ of $\LMEi(\factor(i-1))$ } 
-		& \text{an descent factor} \\	
-	\text{ in any occurrence of  $\sigma[\LMEi(\factor(i)):]$ } & \\
-	\text{ in $\pi[j:]$ strarting at $\pi[j]$} & \\
-	\text{Or $0$ if no occurrence exists} & \text{} \\
-
+	\text{The top edge of any rectangle with left bottom corner   $(j,\pi[j])$} \\
+	\text{ with right edge  $n$ containing an occurrence of  } \\	
+	\text{ $\factor(i) \ldots \factor(1)$ starting at $\pi[j]$ which minimize the top edge}  \\
+	\text{ } \\
+	\text{Or $\infty$ if no occurrence exists} \text{} \\ 
 \end{cases}		
@@
 
-\begin{figure}[t] 
-	\centering	
-	\begin{tikzpicture}[scale=.3]
-
-	\draw[pattern=north east lines] (2,3) rectangle (5.5,5);
-	\draw[pattern=grid] (6,10) rectangle (12,5);
-
-	\draw[dotted,-] (0,10) -- (13,10) node[right] {$\LM{\ppattern}{\ptext}{i}{j}$};
-
-	\draw[dotted,-] (0,5) -- (13,5) node[right] {$\LM{\ppattern}{\ptext}{i-1}{j'+1}$};
-
-	\draw[dotted,-] (2,12) -- (2,0) node[below] {$j$};
-	\draw[dotted,-] (5.5,12) -- (5.5,0) node[below] {$j'$};
-	\draw[dotted,-] (6,12) -- (6,-2) node[below] {$j'+1$};
-
-	%	\draw (6.2,2.2) -- (6.5,10);
-	%	\path (6.2,10) node[above] {$x$};
-
-	\end{tikzpicture}
-
-	\caption{
-		When looking for an occurrence of $\sigma[\LMEi(\factor(i)):]$ (represented by the dashed and gridded rectangle) starting at $\pi[j:]$, (1) the dashed rectangle is an occurrence of $\factor(i)$ if and only if
-		it contains an increasing subsequence of size equal or bigger than $|\factor(i)|$.
-		(2) the dashed and gridded rectangles have to be "compatible": their x-coordinates and y-coordinates have to be disjoint and the dashed rectangle has to be on the left and below the gridded rectangle.
-		$\AF{\ppattern}{\ptext}{i}{j}$ is the set of y-coordinates of every top edge of the gridded rectangle which is compatible.
-$\LM{\ppattern}{\ptext}{i}{j}$ is the minimal element of $\AF{\ppattern}{\ptext}{i}{j}$ if the set is not empty.}
-	\label{fig: algo 1 fig}	
-\end{figure}
-
-There exists an occurrence of $\ppattern$ in $\ptext$ if and only if
-there exists a $1 \leq i \leq n$ such that $LM(n_{factors},i)$ $\neq$ $0$ and $LM(n_{factors},i)\neq \infty$
-with $n_{factors}$ the number of factor in $\ppattern$.
+\item If $\factor(i)$ is RLMax factor.
+$$
+\PM^\pi_\sigma(i,j) =
+$$
+$$
+\begin{cases}
+
+	\text{The bottom edge of any rectangle with left top corner   $(j,\pi[j])$} \\
+	\text{ with right edge  $n$ containing an occurrence of  } \\	
+	\text{ $\factor(i) \ldots \factor(1)$ starting at $\pi[j]$ which 
+	maximize its bottom edge}  \\
+	\text{ } \\
+	\text{Or $0$ if no occurrence exists} \text{} \\ 
+\end{cases}		
+$$
+
+\end{itemize}
+
+By definition, there exists an occurrence of $\ppattern$ in $\ptext$ if and only if
+there exists a $1 \leq j \leq n$ such that 
+$\PM^\pi_\sigma(\ell,j)$ $\neq$ $0$ and $\PM^\pi_\sigma(1,\ell,j) \neq \infty$
+with $\ell$ the number of factors in $\ppattern$.
+
 We show how to compute recursively those values.
-
-\noindent\textbf{BASE :}
-\begin{align*}
-\LM{\ppattern}{\ptext}{1}{j} 
-&=
-\begin{cases}
-		\min_{j<j'}\{\infty\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\factor(1)$ is}  \\
-		\text{ $|\factor(1)| \leq LIS(j,j',\ptext[j']+1)  $}\}
-			&\text{ an ascent factor} \\
-		&\\
-		\max_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
-			& \text{If $\factor(1)$ is}  \\
-		\text{ $|\factor(1)| \leq LDS(j,j',\ptext[j']-1) $}\}
-			&\text{ a descent factor}\\
-\end{cases}
-\\
-\intertext{
-In the base case,
-one is looking for an occurrence of the first factor.
-}
-\\
-\intertext{\textbf{STEP :}}
-\LM{\ppattern}{\ptext}{i}{j} 
-&=
-\begin{cases}
-	\min \{\infty\} \cup  \AF{\ppattern}{\ptext}{i}{j} &
-	\text{If $\factor(i)$ is an ascent factor}\\
-	\max \{0\} \cup  \DF{\ppattern}{\ptext}{i}{j} &
-	\text{If $\factor(i)$ is a descent factor}\\
-\end{cases}
-\end{align*}
-where $\AF{\ppattern}{\ptext}{i}{j}$ and $\DF{\ppattern}{\ptext}{i}{j}$ are the sets 
-of elements matching the leftmost element of $\factor(i-1)$ in an occurrence of $\sigma[\LMEi(\factor(i)):]$ starting at $\ptext[j:]$.
-$\LM{\ppattern}{\ptext}{i}{j}$  has a solution
-if and only if
-$\ptext[j:j']$ contains an occurrence of $\factor(i)$ "compatibles" with an occurrence in $\ptext[j'+1:]$ of $\sigma[\LMEi(\factor(i-1)):]$.
+\begin{itemize}
+\item If the permutation is reduced to a RLMin (resp. RLMax) factor
+then one has to decide the top (resp. lower ) edge of
+a rectangle that
+contains an increasing or a decreasing factor
+with the same size of larger than the 
+size of the unique factor starting at $\pi[j]$.
+This case happens when $i=1$:
+
+\begin{itemize}
+\item If $\factor(i)$ is RLMin factor.
+$$
+\PM^\pi_\sigma(1,j) = \min \text{\{$\pi[j']$ $ |$ if $ |factor(1)| \leq LIS_{\ptext}(j,j',\pi[j'])$\}}_{j'\geq j} \cup \{\infty\}
+$$
+
+\item If $\factor(i)$ is RLMax factor.
+$$
+\PM^\pi_\sigma(1,j) = \min \text{\{$\pi[j']$ $ |$ if $ |factor(1)| \leq LDS_{\ptext}(j,j',\pi[j'])$\}}_{j'\geq j} \cup \{0\}
+$$
+\end{itemize}
+
+\item Otherwise, if $\factor(i)$ is a RLMin (resp. RLMax) factor,
+ we split the rectangle into two rectangles $R_1$ and
+$R_2$ such that $R_1$ is left below $R_2$,
+$R_1$ contains an occurrence of $\factor(i)$ starting at
+$j$
+and $R_2$ contains an occurrence of $\factor(i-1) \ldots factor(1)$
+starting at $j'>j$. 
+As said before, we only need to test the pair of rectangles
+where the rectangle $R_2$ has for left edge $j'$
+and has the highest bottom (resp. lowest top) edge.
+So for $R_2$ we want 
+a rectangle starting at $j'$
+which contains an occurrence of $\factor(i-1) \ldots factor(i')$
+starting at $j'$
+with maximize the bottom (resp. minimize the top) edge.
+Moreover we also want to know the value of the bottom (resp. top) edge to use it as a bound to $R_1$ so that
+that $R_1$ is below $R_2$,
+in other words we want $\PM^\pi_\sigma(i-1,j')$.
+As before $R_1$ has to be biggest possible and
+to ensure that $R_1$ is left below (resp. above) $R_2$,
+$R_1$ must have for top right corner $(j'-1, \PM^\pi_\sigma(i-1,j')-1 )$ 
+(resp. bottom right corner $(j'-1, \PM^\pi_\sigma(i-1,j')+1 )$). 
+Finally in all the "correct" pairs of rectangles,
+we need the value of the top (resp. bottom) edge of a rectangle minimizing the top edge (resp. maximizing the bottom edge)
+containing the pair of rectangles. Note that the top (resp. bottom) edge has for value $\pi[j']$
+(the matching of  $\LMEi(\factor(i-1))$). Formally:
+
+\item If $\factor(i)$ is RLMin factor:\\
+$$
+\PM^\pi_\sigma(i,j) = 
+$$
+$
+\min \{\infty\} \cup \{ \pi[j'] \mid b=\PM^\pi_\sigma(i-1,j') \text{ is not $\infty$ and }  
+ |factor(i)| \leq LIS_{\ptext}(j,j'-1,b-1) \}_{j' < j}
+$
+
+\item If $\factor(i)$ is RLMax factor:\\
+$$
+\PM^\pi_\sigma(i,j) = 
+$$
+$
+\min \{\infty\} \cup \{ \pi[j'] \mid b=\PM^\pi_\sigma(i-1,j') \text{ is not $\infty$ and }  
+|factor(i)| \leq LDS_{\ptext}(j,j'-1,b+1) \}_{j' < j}
+$
+
+\end{itemize}
+
+%Informally, when deciding whether an occurrence of 
+%$\factor[i]\ldots \factor[1]$ starting at $j$ exists,
+%assuming that $\factor(i)$ is a LRMin factor:
+%We can decide whether or not the rectangle $R_1$ which has for bottom left corner
+%$(j,\pi[j])$ and for top right corner $(j',bound)$ 
+%contains an occurrence 
+%of $\factor[i]$, thanks to $LIS_{\ptext}(j,j',bound+1)$.
+%Next we need to find an occurrence of $\factor[i-1]\ldots \factor[1]$ which is contained in a rectangle $R_2$ such that $R_2$ is right above $R_1$.
+%A naive solution is to try every pair of rectangles
+%resulting in a $O(n^6)$ computational time for each case.
+%Indeed only the bottom left corner of $R_1$ is fixed ($(j,\pi[j])$).
+%We show how to choose $R_1$ and $R_2$ in a smart way.
+%\begin{itemize}
+%\item The only condition requires is that $R_2$ is right above $R_1$.
+%To ensure that $R_2$ is on the right of $R_1$, we fix the left edge of 
+%$R_2$ to $j'+1$. As said before, the right edge is the rightmost possible. Corollary~\ref{corollary:we can chose a matching} ensures that
+%we only need to consider the rectangle $R_2$ with the topmost bottom edge to decide whether an occurrence exist.
+Moreover the value of the topmost bottom edge possible is $\LM{\ppattern}{\ptext}{i-1}{j'}$.
+%So $R_2$ has for bottom edge $\LM{\ppattern}{\ptext}{i-1}{j'}$. 
+%\item For the top right corner of $R_1$ ($(j',bound)$), 
+%there is no smart way to choose $j'$, we need to iterate over
+%every $j<j'$ possible. To ensure that $R_1$ is below $R_2$,
+%we fix the top edge of $R_1$ to $\LM{\ppattern}{\ptext}{i-1}{j'}-1$.
+%\end{itemize}
+%Finally, to solve our problem,
+%for every pair of rectangle which contains an occurrence of $\factor[i]\ldots \factor[1]$,
+%we must find the pair, that once merged has the lowest top edge.
+%The merged rectangle shares the same top edge
+%as $R_2$. So we want the pair of rectangle such that
+%$R_2$ has the lowest top edge.
+%The case where $\factor(i)$ is a LRMax factor can be dealt with symmetry.
+%More formally:
+%
+%
+%
+%\noindent\textbf{BASE:}
+%\begin{align*}
+%\LM{\ppattern}{\ptext}{1}{j} 
+%&=
+%\begin{cases}
+%		\min_{j<j'}\{\infty\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
+%			& \text{if $\factor(1)$ is}  \\
+%		\text{ $|\factor(1)| \leq LIS(j,j',\ptext[j']+1)  $}\}
+%			&\text{ a RLMin factor} \\
+%		&\\
+%		\max_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } 
+%			& \text{if $\factor(1)$ is}  \\
+%		\text{ $|\factor(1)| \leq LDS(j,j',\ptext[j']-1) $}\}
+%			&\text{ a RLMax factor}\\
+%\end{cases}
+%\\
+%\intertext{
+%In the base case,
+%one is looking for an occurrence of the first factor.
+%}
+%\\
+%\intertext{\textbf{STEP:}}
+%\LM{\ppattern}{\ptext}{i}{j} 
+%&=
+%\begin{cases}
+%	\min \{\infty\} \cup  \AF{\ppattern}{\ptext}{i}{j} &
+%	\text{if $\factor(i)$ is a RLMin factor}\\
+%	\max \{0\} \cup  \DF{\ppattern}{\ptext}{i}{j} &
+%	\text{if $\factor(i)$ is a RLMax factor}\\
+%\end{cases}
+%\end{align*}
+%where $\AF{\ppattern}{\ptext}{i}{j}$ and $\DF{\ppattern}{\ptext}{i}{j}$ are 
+%the sets 
+%of elements matching the leftmost element of $\factor(i-1)$ in an occurrence of $\sigma[\LMEi(\factor(i)):]$ starting at $\ptext[j:]$.
+%$\AF{\ppattern}{\ptext}{i}{j}$ (resp. $\DF{\ppattern}{\ptext}{i}{j}$)
+%can be understand as the set of all top edges (resp. bottom edges)
+%of the merged rectangles.
+%$\LM{\ppattern}{\ptext}{i}{j}$  has a solution
+%if and only if
+%$\ptext[j:j']$ contains an occurrence of $\factor(i)$ "compatible" with an occurrence in $\ptext[j'+1:]$ of $\sigma[\LMEi(\factor(i-1)):]$.
 It is enough to ensure that every element of the occurrence of $\factor(i)$ is below (resp.
 above) the elements of the occurrence of $\sigma[\LMEi(\factor(i-1)):]$.
-
 Thus we can compute $\AF{\ppattern}{\ptext}{i}{j}$ and $\DF{\ppattern}{\ptext}{i}{j}$ as follows:
-\begin{align*}
-\AF{\ppattern}{\ptext}{i}{j}
-&=
-\text{$\{\ptext[j'+1] \;|\; j<j'<n$ and $\LM{\ppattern}{\ptext}{i-1}{j'+1} \neq 0$ and} 
-\\
-&\qquad 
-\text{$|\factor(i)| \leq LIS_{\ptext}(j,j',\LM{\ppattern}{\ptext}{i-1}{j'+1})\}$} 
-\\
-\DF{\ppattern}{\ptext}{i}{j}
-&=
-\text{$\{\ptext[j'+1] \;|\; j<j'<n$ and $\LM{\ppattern}{\ptext}{i-1}{j'+1} \neq \infty$ and}
-\\
-&\qquad
-\text{$|\factor(i)| \leq LDS_{\ptext}(j,j',\LM{\ppattern}{\ptext}{i-1}{j'+1})\}$}
-\end{align*}
-
-The number of factors is bound by $k$.
-Every instance of $LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(n^2\log(\log(n))$.
+%
+%\begin{align*}
+%\AF{\ppattern}{\ptext}{i}{j}
+%&=
+%\text{$\{\ptext[j'+1] \;|\; j<j'<n$ and $\LM{\ppattern}{\ptext}{i-1}{j'+1} \neq 0$ and} 
+%\\
+%&\qquad 
+%\text{$|\factor(i)| \leq LIS_{\ptext}(j,j',\LM{\ppattern}{\ptext}{i-1}{j'+1})\}$} 
+%\\
+%\DF{\ppattern}{\ptext}{i}{j}
+%&=
+%\text{$\{\ptext[j'+1] \;|\; j<j'<n$ and $\LM{\ppattern}{\ptext}{i-1}{j'+1} \neq \infty$ and}
+%\\
+%&\qquad
+%\text{$|\factor(i)| \leq LDS_{\ptext}(j,j',\LM{\ppattern}{\ptext}{i-1}{j'+1})\}$}
+%\end{align*}
+
+The number of factors is bounded by $k$.
+Every instance of $LIS_{\ptext}$ and $LDS_{\ptext}$ can be computed in $O(n^2\log(\log(n))$ (see \cite{Bespamyatnikh00enumeratinglongest})
+and takes $O(n^3)$ space.
 There are $n$ base cases that can be computed in $O(n)$ time, thus computing every base case
@@
 Thus computing all the values takes $O(max(kn^2,n^2\log(\log(n)))$ time.
-Every value takes $O(1)$ space, thus the whole problem takes $O(kn^2)$ space.
+Every value takes $O(1)$ space, thus the problem takes $O(kn^2)$ space
+but $LIS_{\ptext}$ and $LDS_{\ptext}$ takes $O(n^3)$ space.
 \qed
@@
 Recall that a bivincular pattern generalises a permutation pattern by
-being able to force elements to be consecutive in value or/and in position.
-Hence,  bivincular pattern adds more restrictions on what the occurrence must look like.
-As a consequence it is easier to avoid a bivincular permutation pattern than
-the same permutation pattern.
+being able to force elements
+in an occurrence
+to be consecutive in value or/and in position.
+%Hence,  bivincular pattern adds more restrictions on what the occurrence must look like.
+%As a consequence it is easier to avoid a bivincular permutation pattern than
+%the same permutation pattern.
 Intuitively we cannot use the previous algorithm, as the restrictions on position and value are not managed.
-As in a wedge permutation, we can describe the structural property of a  bivincular wedge permutation pattern.
+
+Given a bivincular permutation pattern $\widetilde{\sigma}$, 
+we let $\widetilde{\sigma}[i:]$ refers to
+the bivincular permutation pattern 
+which has for bottom line the bottom line of $\widetilde{\sigma}$
+where we remove the elements before $i$
+and has for top line the elements of $\sigma[i:]$
+where $m$ and $m+1$ are overlined if and only if
+$m$ and $m+1$ are in $\sigma[i:]$,
+and $m$ and $m+1$ are overlined in $\widetilde{\sigma}$.
+For example given $\widetilde{\sigma} = \BV{12\overline{34}\urcorner}{\llcorner 21\underline{43}}$,
+$\sigma = 2143$ and 
+$\widetilde{\sigma}[2:] = \BV{2\overline{34}\urcorner}{1\underline{43}}$.
+
+We describe other structures properties of wedge permutations
+needed to solve the problem.
+
+\begin{lemma}
+\label{lemma:after}
+Let $\sigma$ be a wedge permutation. 
+\begin{itemize}
+\item If $\sigma[i]$ is a RLMin element and is not the rightmost element, then $\sigma[i]+1$ is to the right of $\sigma[i]$. 
+\item If $\sigma[i]$ is a RLMax element and is not the rightmost element, then $\sigma[i]-1$ is to the right of $\sigma[i]$. 
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+For the first point,
+by contradiction, $\sigma[i]+1$ would serve as a `$2$', $\sigma[i]$ would serve as a `$1$' and $\sigma[i+1]$ would serve as a `$3$' in 
+an occurrence of $213$.
+For the second point,
+by contradiction, $\sigma[i]-1$ would serve as a `$2$', $\sigma[i]$ would serve as a `$3$' and $\sigma[i+1]$ would serve as a `$1$' in 
+an occurrence of $231$.
+\qed
+\end{proof}
 
@@
 \label{lemma:ascentDescentAscent}
-Given $\ppattern$ a bivincular wedge permutation pattern,
-if $\overline{m(m+1)}$ such that $\sigma[i]=m$ and $\sigma[j]=m+1$,
-if $\sigma[i]$ is an ascent (resp. decent) element and if $\sigma[i]+1$ is an ascent 
-(resp. decent) element then :  
+Let $\sigma$ be a wedge permutation.
 \begin{itemize}
-	\item $i<j$ (resp. $j>i$)
-	\item For every $\ell$, $i<\ell<j$ (resp. $j>\ell>i$), $\sigma[\ell]$ is a descent (resp. ascent) element.    
+\item If $m$ and $m+1$ are both RLMin elements
+then any element between $m$ and $m+1$ (if any)
+is a RLMax element.
+\item If $m$ and $m-1$ are both RLmax elements
+then any element between $m$ and $m-1$ (if any)
+is a RLMin element.
 \end{itemize}
+
 \end{lemma}
 
-This lemma states that if two ascent (resp. descent) elements
-need to be matched to consecutive elements in value then every element between those two elements (if any) is a descent (resp. ascent) element.
-
-\begin{proof}[of Lemma~\ref{lemma:ascentDescentAscent}]
-The first statement is explained by the fact that ascent elements are increasing,
-as $\sigma[i]<\sigma[j]$ then
-$\sigma[i]$ is at the left of $\sigma[j]$ thus $i<j$. 
-Suppose that there exists $\ell$, $i<\ell<j$,
-such that $\ppattern[\ell]$ is ascent. Ascent elements are increasing  so $\sigma[i]<\sigma[\ell]<\sigma[j]$ which is in contradiction with $\sigma[j]=\sigma[i]+1$.
-We use a similar argument if $\sigma[i]$ is a descent element.
+\begin{proof} %[of Lemma~\ref{lemma:ascentDescentAscent}]
+For the first point, by contradiction,
+let $\sigma[\alpha]=m$ and $\sigma[\beta]=m+1$
+and suppose that there exists $\alpha < \gamma < \beta$,
+such that $\sigma[\gamma]$ is a RLMin element.
+We know that RLMin are strictly increasing so
+$\sigma[\alpha] <  \sigma[\gamma] < \sigma[\beta]$,
+which contradict the fact that $\sigma[\beta]=\sigma[\alpha]+1$.
 \qed
@@
 \label{Proposition:bivincular pattern}
-Let $\sigma$ be a bivincular wedge permutation pattern of length $k$
-and $\pi$ an $n$-sized permutation.
+Let $\widetilde{\sigma}$ be a bivincular wedge permutation pattern of size $k$
+and $\pi$ a permutation of size $n$.
 One can decide in $O(kn^4)$ time
-and $O(kn^3)$ space if $\pi$ has an occurrence $\sigma$.
+and $O(kn^3)$ space if $\pi$ contains an occurrence $\widetilde{\sigma}$.
 \end{proposition}
@@
 
-\begin{figure}[t] 
-	\centering	
-	\begin{tikzpicture}[scale=.3]
-	\draw[pattern=north east lines] (0,12) rectangle (1,11);
-	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
-
-	\draw[pattern=north east lines] (2,0) rectangle (3,1);
-	\draw[dotted,-] (0,1.5) -- (14,1.5) node[right] {$\lb$};
-
-	\draw[fill=black] (3,1) circle (1mm) ;
-
-	\draw[dotted,-] (3.5,12) -- (3.5,-1);
-
-	% le reste du match
-	\draw[pattern=grid] (5,8) rectangle (12,4);
-	\draw (5,4) -- (7.7,7);
-
-	%point du bot
-	\draw[fill=black] (5,4) circle (1mm) node[above] {$\pi[\ell]$} ;
-
-	\draw[thick,<->] (5,3.9) -- (5,1.5) ;	
-	\draw (5,2.7) node[right] {$\overline{(\sigma[i]-1)\sigma[i]}$};
-
-	\draw[thick,<->] (4.9,4) -- (3.5,4)  node[left] {$\underline{\sigma[i-1]\sigma[i]}$};
-
-	% point du top
-	\draw[fill=black] (8,8) circle (1mm) ;
-	\draw[thick,<->] (8,8.1) -- (8,10.5) ;	
-	\draw (8,9) node[right] {$\overline{\sigma[i'](\sigma[i']+1)}$};
-
-	\end{tikzpicture}		
-	\begin{tikzpicture}[scale=.3]
-	\draw[pattern=north east lines] (0,12) rectangle (1,11);
-	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
-
-	\draw[pattern=north east lines] (2,0) rectangle (5,4);
-	\draw[dotted,-] (0,4.5) -- (14,4.5) node[right] {$\lb=\pi[\ell]+1$};
-
-	%\draw[fill=black] (3,1) circle (1mm) node[left] {$\pi[j]$};
-
-	\draw[dotted,-] (5.5,12) -- (5.5,-1);
-
-	% le reste du match
-	%\draw[dashed,red] (5,8) rectangle (12,4);
-	\draw[pattern=grid] (7,6) rectangle (12,8);
-	\draw (7,6) -- (7.7,7);
-
-	\draw[fill=black] (5,4) circle (1mm) ;
-
-	%point du bot
-	\draw[fill=black] (7,6) circle (1mm) node[above] {$\pi[\ell']$};
-
-	\draw[thick,<->] (7,5.9) -- (7,4.5) ;	
-	\draw (7,5.3) node[right] {$\overline{\sigma[i]\sigma[i+1]}$};
-
-	\draw[thick,<->] (5.5,6)   node[left] {$\underline{\sigma[i]\sigma[i+1]}$} -- (6.9,6) ;
-
-	% point du top
-	\draw[fill=black] (8,8) circle (1mm) ;
-	\draw[thick,<->] (8,8.1) -- (8,10.5) ;	
-	\draw (8,9) node[right] {$\overline{\sigma[i'](\sigma[i']+1)}$};
-
-	\end{tikzpicture}
-
-\caption{When solving $\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}$, with $\sigma[i]$ an ascent element, 
-the recursive calls of $\PM{*}{*}{*}{*}{*}{*}$ will have the same $\ub$ value,
-and the $\lb$ will be equal to the matching of $\pi[i]$ plus one. %Note that there is only ascent element before $\sigma[i']$
-}	
-\label{fig:ub dont change}
-\end{figure}
-
+%\begin{figure}[t] 
+%	\centering	
+%	\begin{tikzpicture}[scale=.3]
+%	\draw[pattern=north east lines] (0,12) rectangle (1,11);
+%	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
+%
+%	\draw[pattern=north east lines] (2,0) rectangle (3,1);
+%	\draw[dotted,-] (0,1.5) -- (14,1.5) node[right] {$\lb$};
+%	
+%	\draw[fill=black] (3,1) circle (1mm) ;
+%	
+%	\draw[dotted,-] (3.5,12) -- (3.5,-1);
+%	
+%	% le reste du match
+%	\draw[pattern=grid] (5,8) rectangle (12,4);
+%	\draw (5,4) -- (7.7,7);
+%	
+%	%point du bot
+%	\draw[fill=black] (5,4) circle (1mm) node[above] {$\pi[\ell]$} ;
+%	
+%	\draw[thick,<->] (5,3.9) -- (5,1.5) ;	
+%	\draw (5,2.7) node[right] {$\overline{(\sigma[i]-1)\sigma[i]}$};
+%	
+%	\draw[thick,<->] (4.9,4) -- (3.5,4)  node[left] {$\underline{\sigma[i-1]\sigma[i]}$};	
+%	
+%	% point du top
+%	\draw[fill=black] (8,8) circle (1mm) ;
+%	\draw[thick,<->] (8,8.1) -- (8,10.5) ;	
+%	\draw (8,9) node[right] {$\overline{\sigma[i'](\sigma[i']+1)}$};
+%		
+%
+%	\end{tikzpicture}		
+%	\begin{tikzpicture}[scale=.3]
+%	\draw[pattern=north east lines] (0,12) rectangle (1,11);
+%	\draw[dotted,-] (0,10.5) -- (14,10.5) node[right] {$\ub$};
+%	
+%	\draw[pattern=north east lines] (2,0) rectangle (5,4);
+%	\draw[dotted,-] (0,4.5) -- (14,4.5) node[right] {$\lb=\pi[\ell]+1$};
+%	
+%	%\draw[fill=black] (3,1) circle (1mm) node[left] {$\pi[j]$};
+%	
+%	\draw[dotted,-] (5.5,12) -- (5.5,-1);
+%	
+%	% le reste du match
+%	%\draw[dashed,red] (5,8) rectangle (12,4);
+%	\draw[pattern=grid] (7,6) rectangle (12,8);
+%	\draw (7,6) -- (7.7,7);
+%	
+%	
+%	\draw[fill=black] (5,4) circle (1mm) ;
+%	
+%	%point du bot
+%	\draw[fill=black] (7,6) circle (1mm) node[above] {$\pi[\ell']$};
+%	
+%
+%	\draw[thick,<->] (7,5.9) -- (7,4.5) ;	
+%	\draw (7,5.3) node[right] {$\overline{\sigma[i]\sigma[i+1]}$};
+%	
+%	\draw[thick,<->] (5.5,6)   node[left] {$\underline{\sigma[i]\sigma[i+1]}$} -- (6.9,6) ;	
+%	
+%	% point du top
+%	\draw[fill=black] (8,8) circle (1mm) ;
+%	\draw[thick,<->] (8,8.1) -- (8,10.5) ;	
+%	\draw (8,9) node[right] {$\overline{\sigma[i'](\sigma[i']+1)}$};
+%	
+%
+%	\end{tikzpicture}	
+%	
+%\caption{When solving $\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}$, with $\sigma[i]$ a RLMin element, 
+%the recursive calls of $\PM{*}{*}{*}{*}{*}{*}$ will have the same $\ub$ value,
+%and the $\lb$ will be equal to the matching of $\pi[i]$ plus one. %Note that there is only ascent element before $\sigma[i']$
+%}	
+%\label{fig:ub dont change}
+%\end{figure}
+
+Consider the following problem:
 Given a lower bound $\lb$, a upper bound $\ub$, a position i of $\sigma$
 and a position $j$ of $\pi$, we want to know if
-there exists an occurrence of $\sigma[i:]$ in $\ptext[j:]$
+there exists an occurrence of $\widetilde{\sigma}[i:]$ in $\ptext[j:]$
 with every element of the occurrence is in $[\lb,\ub]$
-and starting at $\pi[j]$,
-which we denote as:
-
-$$
-\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}=
+and starting at $\pi[j]$.
+In other words given the rectangle with bottom left edge
+$(j,\lb)$ and with top right edge $(n,\ub)$
+contains an occurrence of $\widetilde{\sigma}[i:]$
+starting at $\pi[j]$,
+More formally:
+
+$$
+\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
+$$
+$$
 \begin{cases}
-	true 	& \text{If $\ptext[j:]$ has an occurrance of $\sigma[i:]$ }\\
-			& \text{with every element of the occurrence is in $[\lb,\ub]$}\\
+	true 	& \text{if $\ptext[j:]$ has an occurrence of the bivincular pattern $\widetilde{\sigma}[i:]$ }\\
+			& \text{with every element of the occurrence in $[\lb,\ub]$}\\
 			& \text{and starting at $\pi[j]$}\\
-	false 	& otherwise\\
+			& \text{and if $\overline{\sigma[j](\sigma[j]+1)}$
+			 or $\sigma[j]^\urcorner$ appear in $\widetilde{\sigma}$ then $\pi[j]=\ub$} \\
+			& \text{and if $\overline{(\sigma[j]-1)\sigma[j]}$
+			 or $^\ulcorner{\pi[j]}$ appear in $\widetilde{\sigma}$ then $\sigma[j]=\lb$} \\			 
+	false 	& \text{otherwise}\\
 \end{cases}
 $$
-
-We now show how to compute recursively those values (see Figure \ref{fig:ub dont change}).
+Clearly if $_\llcorner{\sigma[1]}$ does not appear in $\widetilde{\sigma}$
+then $\pi$ contains an occurrence of $\widetilde{\sigma}$ 
+if and only if $\bigcup_{0<j} \PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{j}$ is true.
+If $_\llcorner{\sigma[1]}$ appear in $\sigma$ then 
+$\pi$ contains an occurrence of 
+the bivincular wedge permutation pattern $\sigma$ 
+if and only if $\PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{1}$.
+
+We show how to compute recursively those values.
+Informally, to find an occurrence of $\widetilde{\sigma}[i:]$ in $\pi[j:]$,
+given that $\sigma[i]$ is a RLMin element,
+we need to find a rectangle $R$ in $\pi$ 
+such that $R$ contains an occurrence of $\widetilde{\sigma}[i+1:]$
+and $R$ is right above $\pi[j]$.
+Moreover
+\begin{itemize}
+\item If $\underline{\sigma[i]\sigma[i+1]}$ then
+we require that $\pi[j]$ and $R$ are next to each other horizontally
+and that the occurrence in $R$ starts at the left edge of $R$.
+In other words $R$ has for left edge $\pi[j]+1$.
+\item If $\overline{\sigma[i](\sigma[i]+1)}$ then
+we require that $\pi[j]$ and $R$ are next to each other vertically
+and that the minimal (resp. maximal) element in the occurrence
+is on the bottom (resp. top) edge of $R$.
+In other words $R$ has for bottom edge $\sigma[i]+1$.
+\end{itemize}
+Note that the parameters $\lb$, $\ub$ and $j$ corresponding
+to the occurrence of $\widetilde{\sigma}[i+1:]$ are respectively,
+the bottom edge, the top edge and the left edge of the rectangle $R$.
+The case where $\sigma[i]$ is a RLMax element can be dealt with symmetry.
+More formally:
 
@@
 $$
-\PM{\sigma}{\ptext}{\lb}{\ub}{k}{j}=
+\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{k}{j}=
 \begin{cases}
 	true 	& \text{if $\ptext[j] \in [\lb,\ub ]$}\\
-			& \text{and if ${\ppattern[k]}_\lrcorner$ then $j=n$}\\
-			& \text{and if ${\ppattern[k]}^\urcorner$ then $\ptext[j]=\ub=n$}\\
-			& \text{and if  $^\ulcorner{\ppattern[k]}$ then $\ptext[j]=\lb=1$ } \\
-			& \text{and if  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then $\ptext[j]=\lb$ }  \\
-			& \text{and if  $\overline{(\ppattern[k]\ppattern[k]+1)}$ then $\ptext[j]=\ub$}  \\
+			& \text{and if ${\ppattern[k]}_\lrcorner$ appears in $\widetilde{\sigma}$ then $j=n$}\\
+			& \text{and if $_\llcorner{\sigma[k]}$ appears in $\widetilde{\sigma}$ then $j=1$}\\			
+			& \text{and if ${\ppattern[k]}^\urcorner$ appears in $\widetilde{\sigma}$ then $\ptext[j]=\ub=n$}\\
+			& \text{and if  $^\ulcorner{\ppattern[k]}$ appears in $\widetilde{\sigma}$ then $\ptext[j]=\lb=1$ } \\			
+			& \text{and if  $\overline{(\ppattern[k]-1)\ppattern[k]}$ appears in $\widetilde{\sigma}$ then $\ptext[j]=\lb$ }  \\
+			& \text{and if  $\overline{(\ppattern[k]\ppattern[k]+1)}$ 
+			appears in $\widetilde{\sigma}$
+			then $\ptext[j]=\ub$}  \\
 
@@
 This is true if $\ptext[j] \in [\lb,\ub]$.
-If ${\ppattern[k]}_\lrcorner$ then $\ppattern[k]$ must be matched to the rightmost element of $\pi$ thus $j$ must be $n$.
-If ${\ppattern[k]}^\urcorner$ then $\ppattern[k]$ must be matched to the topmost element which is $n$.
-If $^\ulcorner{\ppattern[k]}$ then $\ppattern[k]$ must be matched to the bottommost element which is $1$.
-If  $\overline{(\ppattern[k]-1)\ppattern[k] }$ then the matching element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the element matching $\ppattern[k]-1$ will be recorded in $\lb$ and by adding $1$ to it thus $\ppattern[k]$ must be matched to $\lb$.
-If  $\overline{(\ppattern[k]\ppattern[k]+1)}$ then the element matching $\ppattern[k]$ and $\ppattern[k]+1$ must be consecutive in value, by recursion the value of the  element matching $\ppattern[k]+1$ will be recorded in $\ub$ and by removing $1$ to it thus $\ppattern[k]$ must be matched to $\ub$.
+If ${\ppattern[k]}_\lrcorner$ appears in $\widetilde{\sigma}$ then $\ppattern[k]$ must be matched to the rightmost element of $\pi$ thus $j$ must be $n$.
+If ${\ppattern[k]}^\urcorner$ appears in $\widetilde{\sigma}$ then $\ppattern[k]$ must be matched to the topmost element which is $n$.
+If $^\ulcorner{\ppattern[k]}$ appears in $\widetilde{\sigma}$ then $\ppattern[k]$ must be matched to the bottommost element which is $1$.
+If  $\overline{(\ppattern[k]-1)\ppattern[k] }$ appears in $\widetilde{\sigma}$ then the matching element of $\ppattern[k]$ and $\ppattern[k]-1$ must be consecutive in value, by recursion the value of the element matching $\ppattern[k]-1$ will be recorded in $\lb$ and by adding $1$ to it thus $\ppattern[k]$ must be matched to $\lb$.
+If  $\overline{(\ppattern[k]\ppattern[k]+1)}$ appears in $\widetilde{\sigma}$ then the element matching $\ppattern[k]$ and $\ppattern[k]+1$ must be consecutive in value, by recursion the value of the  element matching $\ppattern[k]+1$ will be recorded in $\ub$ and by removing $1$ to it thus $\ppattern[k]$ must be matched to $\ub$.
 
@@
 
-We need to consider 3 cases for the problem $\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}$ :
+In the following, we use the notation $\bigcup$ to
+represent the disjunction.
+We consider 3 cases for the problem $\PM{ \widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}$:
 \begin{itemize}
@@
 	$$
-	\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j} = false
+	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j} = false
 	$$
@@
 	which is immediate from the definition.
-If $\ptext[j] \notin [\lb,\ub]$ then it cannot be part of an occurrence of  $\ppattern[i:]$ in $\ptext[j:]$ with every element of the occurrence in $[\lb,\ub]$.
-
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is an ascent element then :
-	$$
-	\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}=
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a RLMin element then:
+	$$
+	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
 	\begin{cases}
-		\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
+		\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
 			& \text{if $\ppattern[i]$ is not underlined } \\
 			& \text{ and $\ppattern[i]$ is not overlined} \\
-		\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
+		\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
 			& \text{if $\ppattern[i]$ is not underlined } \\
 			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
+			& \text{ appears in $\widetilde{\sigma}$}\\
 			& \text{ and $\ptext[j]=\lb$} \\
-		\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
+		\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
+			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
+			& \text{ appears in $\widetilde{\sigma}$}\\
+			& \text{ and $\ppattern[i]$ is not overlined} \\			
+		\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
 			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
 			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
+			& \text{ appear in $\widetilde{\sigma}$}\\
 			& \text{ and $\ptext[j]=\lb$} \\
-		\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
-			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
-			& \text{ and $\ppattern[i]$ is not overlined} \\
 		false & \text{otherwise}
@@
 	$$	
-	Remark that $\ppattern[i]$  can be matched to $\pi[i]$ because $\ptext[j] \in [\lb,\ub]$.
-	Thus if $\ptext[j+1:]$ has an occurrence of $\ppattern[i+1:]$  with every element of the occurrence in $[\pi[i]+1,\ub]$ then 
- 	$\ptext[j:]$ has an occurrence $\ppattern[i:]$. The last condition corresponds 
- 	to know if there exists $\ell$, $j<\ell$ such that
-	$\PM{\sigma}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}$ is true.
+	Remark that $\ppattern[i]$  can be matched to $\pi[j]$ because $\ptext[j] \in [\lb,\ub]$.
+	Thus if $\ptext[j+1:]$ has an occurrence of $\widetilde{\sigma}[i+1:]$  with every element of the occurrence in $[\pi[j]+1,\ub]$ then 
+ 	$\ptext[j:]$ has an occurrence $\widetilde{\sigma}[i:]$. 
+ 	To decide the latter condition,
+ 	it is enough to know 
+ 	 if there exists $\ell$, $j<\ell$ such that
+	$\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}$ is true.
 	The first case corresponds to an occurrence without restriction on position and on value. 
@@
 	is $lb-1$ thus we want $\ptext[j]=\lb$. 
-The fourth case asks for the matching of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in positions, thus the matching of $\ppattern[i+1]$ must be $\pi[j+1]$.
-The third case is a union of the second and fourth case.
-	Note that we do not have to consider the case $\overline{\ppattern[i](\ppattern[i]+1)}$
-	as the element $(\ppattern[i]+1)$ is on the right of $\ppattern[i]$ and thus will
-	be taken care of later on.
-
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a descent element then :
-
-	$$
-	\PM{\sigma}{\ptext}{\lb}{\ub}{i}{j}=
+	The third case asks for the matching of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in positions, thus the matching of $\ppattern[i+1]$ must be $\pi[j+1]$. 
+	The fourth case is a union of the second and third case. 
+%	Note that we do not have to consider the case where $\overline{\ppattern[i](\ppattern[i]+1)}$ appears in $\widetilde{\sigma}$
+%	as the element $(\ppattern[i]+1)$ is on the right of $\ppattern[i]$
+%	(see Lemma~\ref{lemma:after})
+%	and thus will
+%	be taken care
+%	during the calls of $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$
+%	for some $i<i'$.
+%	Identically  we do not have to consider the case 
+%	where $\sigma[i-1]\sigma[i]$ appears in $\widetilde{\sigma}$
+
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a RLMax element then:
+
+	$$
+	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
 	\begin{cases}
-			\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
+			\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
 				& \text{if $\ppattern[i]$ is not underlined } \\
 				& \text{ and $\ppattern[i]$ is not overlined} \\
-			\bigcup_{\ell>j} \PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
+			\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
 				& \text{if $\ppattern[i]$ is not underlined } \\
 				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
+				& \text{ appear in $\widetilde{\sigma}$}\\
 				& \text{ and $\ptext[j]=\ub$} \\
-			\PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
+				& \text{ appears in $\widetilde{\sigma}$}\\
+				& \text{ and $\ppattern[i]$ is not overlined} \\				
+			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
 				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
 				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
+				& \text{ appear in $\widetilde{\sigma}$}\\
 				& \text{ and $\ptext[j]=\ub$} \\
-			\PM{\sigma}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
-				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
-				& \text{ and $\ppattern[i]$ is not overlined} \\
 			false & \text{otherwise}
@@
 	The same remark as the last case holds.
-
 \end{itemize}
 
-Clearly if $\bigcup_{0<j} \PM{\sigma}{\ptext}{1}{n}{1}{j}$ is true then $\pi$ has an occurrence $\sigma$. We now discuss the position and value constraints.
+Remark that there are constraints that we do not concern given in
+$\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$.
+Especially in the case where $\sigma[i]$ is a RLMin
+the case where $\underline{\sigma[i-1]\sigma[i]}$,
+$\overline{\ppattern[i](\ppattern[i]+1)}$
+and every combination of the constraints
+appear in $\widetilde{\sigma}$
+are not in the conditions.
+$\underline{\sigma[i-1]\sigma[i]}$ is not 
+in the conditions because it is
+up to $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i-1}{*}$
+to ensure that the elements corresponding to elements at position $i-1$ and $i$ in an occurrence are next to each other in position.
+$\overline{\ppattern[i](\ppattern[i]+1)}$ is not
+in the conditions because $\sigma[i]+1$ is on the right 
+of $\sigma[i]$ (see Lemma~\ref{lemma:after})
+and thus will
+be taken care
+during the calls of $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$
+for some $i<i'$.
+In the same fashion,
+when $\sigma[i]$ is a RLMax $\underline{\sigma[i-1]\sigma[i]}$ 
+do not appear in the conditions for the exact same reason
+and $\overline{(\ppattern[i]-1)\ppattern[i]}$
+because $\sigma[i]-1$ is on the right of $\sigma[i]$.
+
+Clearly the problem return true if $\pi$ contains an 
+occurrence of $\widetilde{\sigma}$ if there is no constraint on position
+and on value.
+We now discus how the position and value constraints 
+are taken into account so that the algorithm
+returns true if and only if $\pi$ has an occurrence 
+of $\widetilde{\sigma}$.
+
 \paragraph{Position Constraint.} There are 3 types of position constraints that can be added by underlined elements.
 \begin{itemize} 
-	\item If $_\llcorner{\sigma[1]}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ on a occurrence of $\ppattern$ in $\ptext$).
-This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$ : if  $\PM{\sigma}{\ptext}{1}{n}{1}{1}$ is true.
-
-	\item If ${\ppattern[k]}_\lrcorner$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a occurrence of $\ppattern$ in $\ptext$).
+	\item If $_\llcorner{\sigma[1]}$ appears in $\widetilde{\sigma}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ in a occurrence of $\ppattern$ in $\ptext$).
+This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{1}$ is true.
+
+	\item If ${\ppattern[k]}_\lrcorner$ appears in $\widetilde{\sigma}$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a occurrence of $\ppattern$ in $\ptext$).
 This constraint is checked in the base case.
 
-	\item If $\underline{\ppattern[i]\ppattern[i+1]}$ then the positions of the element matching $\ppattern[i]$ and $\ppattern[i+1]$ must be consecutive.
+	\item If $\underline{\ppattern[i]\ppattern[i+1]}$ appears in $\widetilde{\sigma}$ then the positions of the element matching $\ppattern[i]$ and $\ppattern[i+1]$ must be consecutive.
 In other words, if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i+1]$ must be matched to $\ptext[j+1]$.
-We ensure this restriction by recursion by requiring that the matching of $\ppattern[i+1:]$ starts at position $j+1$ (see Figure $\ref{fig:ub dont change}$).
+We ensure this restriction by recursion by requiring that the matching of $\ppattern[i+1:]$ starts at position $j+1$.
 \end{itemize}
 
-\paragraph{Value Constraint.} There are 3 types of position constraints that can be added by overlined elements.
+\paragraph{Value Constraint.} There are 3 types of value constraints that can be added by overlined elements.
 \begin{itemize}
-	\item If $^\ulcorner{\sigma[i]}$ (and thus $\sigma[i]=1$) then the bottommost element of $\ppattern$ must be matched to the bottommost element of $\ptext$.
+	\item If $^\ulcorner{\sigma[i]}$ appears in $\widetilde{\sigma}$ (and thus $\sigma[i]=1$) then the bottommost element of $\ppattern$ must be matched to the bottommost element of $\ptext$.
 	\begin{itemize}
 
-		\item If $\sigma[i]$ is an ascent element, then remark that 
-		every problem 
-		$\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ is true if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion) thus it is enough to require that $\lb=1$.
-		Now remark that $\sigma[i]$ is the leftmost ascent element, indeed if not, then there exists an ascent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
-		As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are descent elements.
-		Moreover the recursive calls from a descent element do not change the lower bound
-		thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$, $\lb=1$ (see Figure $\ref{fig:ub dont change}$).
-
-		\item If $\sigma[i]$ is a descent element then $i=k$ ($\sigma[i]$ is the rightmost element). Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $1$.
-
+		\item If $\sigma[i]$ is a RLMin element, then remark that:
+		\begin{itemize}
+			\item Every problem 
+			$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion).
+			So it is enough to require that $\lb=1$.
+			\item The recursive calls for $\sigma[1]$, $\ldots$, $\sigma[i-1]$
+			do not change the lower bound as
+			$\sigma[i]$ is the leftmost RLMin element.
+Indeed if not, then there exists a RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
+			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
+			\item The first call of the problem has for parameter $\lb=1$. 
 		\end{itemize} 
-
-	\item If ${\ppattern[i]}^\urcorner$ (and thus $\sigma[i]=k$) then the topmost element of $\ppattern$ must be matched to the topmost element of $\ptext$.
+		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if 
+		$\sigma[i]$ is matched to $1$.
+
+		\item If $\sigma[i]$ is a RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element).
+Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true only if $\sigma[i]$ is matched to $1$.
+
+	\end{itemize}
+
+	\item If ${\ppattern[i]}^\urcorner$ appears in $\widetilde{\sigma}$ (and thus $\sigma[i]=k$) then the topmost element of $\ppattern$ must be matched to the topmost element of $\ptext$.
 	\begin{itemize}
 
-		\item If $\sigma[i]$ is an descent element, then remark that 
-		every recursive call \\ $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ is matched to element with value $\ub$ (by recursion) thus it is enough to require that $\ub=n_{\ptext}$.
-		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
-		As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are ascent elements.
-		Moreover the recursive calls from a ascent element do not change the upper bound
-		thus for every $\PM{\sigma}{\ptext}{*}{\ub}{i}{*}$, $\ub=n$ (see Figure $\ref{fig:ub dont change})$.
-
-		\item If $\sigma[i]$ is an ascent element then $i=k$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\sigma}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n_{\ptext}$.
-
+		\item If $\sigma[i]$ is a RLMax element, then remark that:
+		\begin{itemize}
+			\item Every problem 
+			$\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$ (by recursion).
+			So it is enough to require that $\ub=n$.
+			\item The recursive calls for $\sigma[1]$, $\ldots$, $\sigma[i-1]$
+			do not change the upper bound as
+			$\sigma[i]$ is the leftmost RLMax element.
+Indeed if not, then there exists a RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
+			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
+			\item The first call of the problem has for parameter $\ub=n$. 
 		\end{itemize} 
-
-	\item  If $\overline{\ppattern[i]\ppattern[i']}$,  (which implies that $\ppattern[i']=\ppattern[i]+1$) then if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i']$ must be matched to $\ptext[j]+1$.
+		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if 
+		$\sigma[i]$ is matched to $n$.
+
+		\item If $\sigma[i]$ is a RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element).
+Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n$.
+
+	\end{itemize}
+
+	\item  If $\overline{\ppattern[i]\ppattern[i']}$ appears in $\widetilde{\sigma}$,  (which implies that $\ppattern[i']=\ppattern[i]+1$) then if $\ppattern[i]$ is matched to $\ptext[j]$ then $\ppattern[i']$ must be matched to $\ptext[j]+1$
+	or f $\ppattern[i']$ is matched to $\ptext[j]$ then $\ppattern[i]$ must be matched to $\ptext[j]-1$.
 
@@
 
-			\item The case $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i<i'$ (remark that this case is equivalent to the case where  $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i'<i$) is not possible.
+			\item The cases $\ppattern[i]$ is a RLMax element, $\ppattern[i']$ is a RLMin element and $i<i'$ or  $\ppattern[i]$ is a RLMin element, $\ppattern[i']$ is a RLMax element and $i'<i$ are not possible.
 			Indeed $\ppattern[i]$ is the topmost element of $\ppattern[i:]$ thus $\ppattern[i] > \ppattern[i']$ which is in contradiction with 
@@
 
-			\item If $\ppattern[i]$ is an ascent element, $\ppattern[i']$ is a descent element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a descent element, $\ppattern[i']$ is an ascent element and $i'<i$), then
-			remark that every recursive call
-			$\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$ is true if $\sigma[i']$ is matched to the element with $\lb$ (by recursion) thus it is enough to require that $\lb=\ptext[j]+1$.
-			Now remark that
-			$\ppattern[i]$ is the rightmost ascent element and $\ppattern[i']$ is the rightmost element (or $\ppattern[i'] \neq \ppattern[i]+1$). 
-			As a consequence $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are descent elements.
-Moreover the recursive calls from a descent element do not change the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$
-			thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see Figure $\ref{fig:ub dont change}$).
-
-			\item If $\ppattern[i]$ is an ascent element and $\ppattern[i']$ is an ascent element then
-			first remark that every recursive call
-			$\PM{\sigma}{\ptext}{*}{\ub}{i'}{*}$ is true if $\sigma[i']$ is matched to element with value $\lb$. 
-			Now remark that
-
-			$i<i'$ and there is no  ascent element between $\ppattern[i]$ and $\ppattern[i']$ (lemma \ref{lemma:ascentDescentAscent}), 
-			As a consequence $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are descent elements.
-Moreover the recursive calls from a descent element do not change the lower bound and $\PM{\sigma}{\ptext}{\lb}{*}{i}{*}$ will put the lower bound to $\ptext[j]+1$ thus for every $\PM{\sigma}{\ptext}{\lb}{*}{i'}{*}$, $\lb=\ptext[j]+1$ (see Figure $\ref{fig:ub dont change}$).
+			\item If $\ppattern[i]$ is a RLMin element, $\ppattern[i']$ is a RLMax element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a RLMax element, $\ppattern[i']$ is a RLMin element and $i'<i$), then
+			remark that
+			\begin{itemize}
+				\item $i'=k$, indeed if $i'$ is not the right most element, there would exist an element between
+				$\sigma[i]$ and $\sigma[i']$. So every recursive call
+				$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$
+				is solved as a base case. So $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
+				\item The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. 
+				Indeed $\ppattern[i]$ is the rightmost RLMin.
+				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are RLMax elements. Moreover
+				recursive calls for a RLMax do not change the lower bound.
+				\item $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ sets
+				the $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
+			\end{itemize}
+			So $\sigma[i]$ is matched to $\ptext[j]$ and
+			$\sigma[i']$ is matched to $\ptext[j]+1$.
+
+			\item If $\ppattern[i]$ is a RLMin element and $\ppattern[i']$ is a RLMin element then
+			first remark: 
+			\begin{itemize}
+
+				\item From lemma~\ref{lemma:ascentDescentAscent}, 
+				we have that $i<i'$.
+
+				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.
+
+				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. Indeed
+				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
+
+				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
+
+			\end{itemize}
+			So $\sigma[i]$ is matched to $\ptext[j]$ and
+			$\sigma[i']$ is matched to $\ptext[j]+1$.
+
+			\item If $\ppattern[i]$ is a RLMax element and $\ppattern[i']$ is a RLMax element then
+			first remark: 
+			\begin{itemize}
+				\item From lemma~\ref{lemma:ascentDescentAscent}, 
+				we have that $i'<i$.
+
+				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.
+
+				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the upper bound. Indeed
+				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
+
+				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.
+
+			\end{itemize}
+			So $\sigma[i']$ is matched to $\ptext[j]$ and
+			$\sigma[i]$ is matched to $\ptext[j]-1$.
+
 		\end{itemize}
@@
 
-This section is focused on a problem related to the pattern matching problem, finding the longest wedge permutation occurring in permutations:
-Given a set of permutations, find a longest wedge permutation that occurs in
-each input permutations.
-This problem is known to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint that the subsequence must avoid $(213,231)$, as for a fixed number of permutations
-(in our case, we have two permutations) the number of permutation appear in the exponent of the complexity of the algorithm.
-Thus we focus on the cases where only one or two permutations are given in input.
+This section is focused on a problem related to the permutation pattern matching problem.
+Given a set of permutations, one must compute the longest permutation
+which occurs in each permutation in the set.
+This problem is known to be NP-Hard for an arbitrary size of the set even
+when all the permutations of this set are separable permutations (See~\cite{2007math......2109B}).
+We show how to compute the longest wedge permutation 
+occurring in a set.
+We do not hope that this problem is solvable in polynomial time 
+if the size of the set is not fixed. 
+Indeed the size of the set appears in the exponent 
+in the complexity of the algorithm.
+Thus we focus on the cases where only one or two permutations are given in set.
 
@@
 We start with the easiest case where we are given just one input permutation.
-We need the set of descent elements and the set of ascent elements.
-$A(\pi) = \{i | \text{$\pi[i]$ is an ascent element} \} \cup \{n\}$ and
-$D(\pi) = \{i | \text{$\pi[i]$ is a descent element} \} \cup \{n\}$.\\
+We need the set of RLMax elements and the set of RLMin elements.
+$A(\pi) = \{i | \text{$\pi[i]$ is a RLMin element} \} \cup \{n\}$ and
+$D(\pi) = \{i | \text{$\pi[i]$ is a RLMax element} \} \cup \{n\}$.\\
 
@@
 Let $\pi$ be a permutation. One can compute
-the longest $(213,231)$-avoiding subsequence that can occur in $\pi$
+the longest wedge subsequence that can occur in $\pi$
 in $O(n\log(\log(n)))$ time and in $O(n)$ space.
@@
 \begin{proof}[of Proposition~\ref{proposition:longest 2}]
-The Proposition \ref{proposition:longestIncreasingSubsequence} leads to an algorithm
-where one has to compute longest increasing and decreasing subsequence endings at every position possible. 
-Then finding the maximum sum of longest increasing and decreasing subsequence endings at the same position.
-Computing the longest increasing subsequence and the longest decreasing subsequence can be done in 
+Proposition \ref{proposition:longestIncreasingSubsequence} leads to an algorithm
+where one computes the longest increasing and decreasing subsequence ending at every  possible position 
+and then finds the maximum sum of longest increasing and decreasing subsequence ending at the same position.
+Computing the longest increasing subsequences and the longest decreasing subsequences can be done in 
 $O(n\log(\log(n)))$ time and $O(n)$ space 
 (see \cite{Bespamyatnikh00enumeratinglongest}), 
-then finding the maximal can be done in linear time.
+then finding the maximum can be done in linear time.
 \qed
@@
 \begin{proposition}
-Given two permutations $\pi_1$ and $\pi_2$,
+Given two permutations $\pi_1$ of size $n_1$ and $\pi_2$ of size $n_2$,
 one can compute 
-the longest common $(213,231)$-avoiding subsequence
-in $O(|\pi_1|^3|\pi_2|^3)$ time and space.
+the longest common wedge subsequence
+in $O(n_1^3n_2^3)$ time and space.
 \end{proposition}
@@
 \begin{center}
-= $\max$ \{$|s|$ $|$ $s$ occurs $\pi_1[i_1:]$ with every element of the occurrence in $[\lb_1,\ub_1]$ and $s$ occurs $\pi_2[i_2:]$ with every element of the occurrence in $[\lb_2,\ub_2]$ \}
+= $\max$ \{$|s|$ $|$ $s$ occurs $\pi_1[i_1:]$ with every element of the occurrence in $[\lb_1,\ub_1]$ and $s$ occurs $\pi_2[i_2:]$ with every element of the occurrence in $[\lb_2,\ub_2]$ and $s$ is a wedge subsequence
+ \}
 \end{center}
@@
 $$
-\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{|\pi_1|}{|\pi_2|} =
+\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{n_1}{n_2} =
 \begin{cases}
-	1 & \text{if $\lb_1 \leq \pi_1[j] \leq \ub_1$
+	1 & \text{if $\lb_1 \leq \pi_1[n_1] \leq \ub_1$
 	}\\
-	& \text{ and $\lb_2 \leq \pi_2[j] \leq \ub_2$}\\
-	0 & otherwise\\
+	& \text{ and $\lb_2 \leq \pi_2[n_2] \leq \ub_2$}\\
+	0 & \text{otherwise}\\
 \end{cases}
@@
 $$
-\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=max
+\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=\max
 \begin{cases}
@@
 $
-\match{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=\max
+\match{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}=
 \begin{cases}
@@
 to the solution the LCS for $\pi_1[i_1+1:]$ and $\pi_2[i_2+1:]$ which is compatible,
-meaning that if the matching element is an ascent (resp. descent) element
+meaning that if we consider the current elements
+to correspond to a RLMin (resp. RLMax) element in the longest wedge subsequence
 then we consider only the solution with elements above (below)
@@
 These relations lead to a $O(|\pi_1|^3|\pi_2|^3)$ time and $O(|\pi_1|^3|\pi_2|^3)$ space algorithm.
-Indeed there are $|\pi_1|^3|\pi_2|^3$ cases possible for the problem
+Indeed there are $|\pi_1|^3|\pi_2|^3$  possible cases for the problem
 and each case is solved in constant time.

### 2016-10-12 article.tex
revision

@@
 For the special case where only $\sigma$ avoids $213$ and $231$, we present a
-$O(max(kn^2,n^2\log(\log(n)))$-time algorithm. 
+$O(max(kn^2,n^2\log \log n)$-time algorithm.
 We extend our research to bivincular patterns that avoid $213$ and $231$ and present a $O(kn^4)$-time algorithm.
@@
 
-A permutation $\sigma$ is said to occur in another permutation $\pi$,
+A permutation $\sigma$ is said to \emph{occur} in another permutation $\pi$
+(or $\pi$ \emph{contains} $\sigma$),
 denoted $\sigma \preceq \pi$,
@@
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
-For example the permutation $123$ (resp. $321$) occurs in a second permutation if
-the second permutation has an increasing (resp. a decreasing) subsequence of size $3$.
+For example a permutation contains the permutation $123$ (resp. $321$) if
+it has an increasing (resp. a decreasing) subsequence of size $3$.
 Similarly, $213$ occurs in $6152347$, but $231$ does not occurs in $6152347$.
@@
 order as $\sigma$.
-A recent major step was taken by Marx and Guillemot
-\cite{Guillemot:Marx:SODA:2014}.
-They showed that
-the permutation pattern matching is fixed-parameter tractable (FPT) for by the size of $\sigma$.
+Guillemot and Marx \cite{Guillemot:Marx:SODA:2014} showed that the permutation pattern matching problem
+is solvable in $2^{O(k^2 \log k)}$, and hence is fixed-parameter tractable with respect to the length $k$
+of the pattern $\sigma$ (standard parameterization).
+However, Mach proved that the permutation containment problem under the
+standard parameterization does not have a polynomial size kernel (assuming $\NPclass \not\subseteq \coNPclass / \POLY$
+\cite{Mach:thesis:1992}.
 
 A few particular cases of the permutation pattern matching problem have been attacked successfully.
-The case of any increasing pattern is solvable in 
-$O(n \log \log k)$ time in the RAM model \cite{Crochemore:Porat:2010},
+The case of  increasing patterns is solvable in
+$O(n \log \log k)$-time \cite{Crochemore:Porat:2010},
 improving the previous 30-year bound of $O(n \log k)$.
@@
 polynomial-time for separable patterns \cite{Ibarra:1997,Bose:Buss:Lubiw:1998}
-(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for the longest common subsequence problem and related ones on separable permutations).
+(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for the longest common subsequence problem and
+related ones on separable permutations).
 Separable permutations are permutations that do not have an occurrence of
@@
 stack-sortable permutations, which avoid the pattern $231$.)
+The major negative result is given in \cite{DBLP:journals/corr/JelinekK16}.
+They prove that
+the permutation pattern matching problem is \NPC
+when $\sigma$ has no decreasing subsequence of length $3$ and
+$\pi$ has no decreasing subsequence of length $4$.
+This provides the first known example of the permutation pattern matching problem
+being hard when one or both of $\pi$ and $\sigma$ are restricted to a proper hereditary
+class of permutations.
 

### 2016-10-13 article.tex
revision

@@
 
-We focus in this paper on pattern matching issues for
-$(213,231)$-avoiding permutations that we call wedge permutations.
+We focus in this paper on pattern matching issues for \emph{wedge permutations}
 (\emph{i.e.}, those permutations that avoid both $213$ and $231$). 
@@
 than an element $\pi[\beta]$  by position (in the order given by the permutation),
-we say that $\pi_\alpha$ is on the left of (resp. on the right of) $\pi[\beta]$.
+we say that $\pi[\alpha]$ is on the left of (resp. on the right of) $\pi[\beta]$.
 Besides, the element with the largest position is called the rightmost element

### 2016-10-13 article.tex
revision

@@
 \DeclareMathOperator{\AV}{Av}
+
+\newcommand{\RLMin}{\text{RLMin}}
+\newcommand{\RLMax}{\text{RLMax}}
 
@@
 if and only if $\pi[j]=s[i]$.
-
 Geometrically, $\pi$ has an occurrence of $\sigma$ if there exists
-a set of points in $\pi$ that is isomorphic to the set of points of $\sigma$.
-In other words,
-if there exists a set of points in $\pi$ with the same disposition as the set of points of $\sigma$,
-regardless of the distance (see Figure \ref{example: pattern matching}).
+a set of points in $\pi$ whose relative positions are the same as those of $\sigma$
+(see Figure \ref{example: pattern matching}).
+%% In other words,
+%% if there exists a set of points in $\pi$ with the same disposition as the set of points of $\sigma$,
+%% regardless of the distance (see Figure \ref{example: pattern matching}).
 
@@
 
-A $\textit{right-to-left maximum}$ (abbreviated to RLMax) of $\pi$ is an element that does not have any element above it and to its right (see Figure $\ref{fig:left to right maxima}$).
-Formally, $\pi[i]$ is a RLMax if and only if $\pi[i]$ is topmost element of $\pi[i:]$.
-Similarly $\pi[i]$ is a $\textit{right-to-left minimum}$ (abbreviate RLMin) if and only if $\pi[i]$ is the bottommost element of $\pi[i:]$.
+A $\textit{right-to-left maximum}$ (\RLMax, for short) of $\pi$ is an element that does not have any element above it and to its right (see Figure $\ref{fig:left to right maxima}$).
+Formally, $\pi[i]$ is a \RLMax if and only if $\pi[i]$ is topmost element of $\pi[i:]$.
+Similarly $\pi[i]$ is a $\textit{right-to-left minimum}$ (\RLMin, for short) if and only if $\pi[i]$ is the bottommost element of $\pi[i:]$.
 
@@
 	\caption[Example pattern matching]{
-		The element is a RLMax if and only if the hashed area is empty.}
+		The element is a \RLMax if and only if the hashed area is empty.}
 	\label{fig:left to right maxima}
@@
 in other words the matching elements are consecutive in value.
-If two elements are underlined then we draw an vertical forbidden area.
+If two elements are underlined then we draw a vertical forbidden area.
 (See Figure \ref{example:bivincular pattern matching}).
@@
 $\pi$ is a wedge permutation of size $n$ if and only if for $1 \leq i \leq n$,
-$\pi[i]$ is a RLMax or a RLMin.
+$\pi[i]$ is a \RLMax or a \RLMin.
 \end{corollary}
 
-\begin{proof} %[of Lemma~\ref{lemma:first element is 1 or n}]
-Given a position $i$, $\pi[i:]$ is a wedge permutation,
-so it either starts with the maximal or the minimal element.
-\qed
-\end{proof}
+%% \begin{proof} %[of Lemma~\ref{lemma:first element is 1 or n}]
+%% Given a position $i$, $\pi[i:]$ is a wedge permutation,
+%% so it either starts with the maximal or the minimal element.
+%% \qed
+%% \end{proof}
 
 As a consequence, every element of a wedge permutation can be partitioned
-into three sets: the set of RLMax elements, the set of RLMin elements and the
-rightmost element which can be both a RLMax element and a RLMin element.
+into three sets: the set of \RLMax elements, the set of \RLMin elements and the
+rightmost element which can be both a \RLMax element and a \RLMin element.
 
 \begin{remark}
-The set of RLMax elements is a decreasing subsequence,
-indeed each element is left above the next RLMax element by definition
-of a RLMax element. In the same fashion,
-the set of RLMin elements is an increasing subsequence.
+The set of \RLMax elements is a decreasing subsequence,
+indeed each element is left above the next \RLMax element by definition
+of a \RLMax element. In the same fashion,
+the set of \RLMin elements is an increasing subsequence.
 See Figure~\ref{fig:shape of the permutation plus factor}.
@@
 \begin{remark}
-Every element of the set of RLMax elements is above the elements
-of the set of the RLMin elements.
+Every element of the set of \RLMax elements is above the elements
+of the set of the \RLMin elements.
 In other words, a wedge permutations
@@
 The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$
-represents whether $\pi[i]$ is a RLMax element or a RLMin element.
+represents whether $\pi[i]$ is a \RLMax element or a \RLMin element.
 We call this bijection $\bijection$.
@@
 
-To figure out whether or not an element is a RLMax element or a RLMin element,
+To figure out whether or not an element is a \RLMax element or a \RLMin element,
 one has to run the whole permutation from left to right starting
@@
 \begin{enumerate}
-\item $\pi[i]$ is a RLMin element if and only if $\pi[i]<\pi[i+1]$
-\item $\pi[i]$ is a RLMax element if and only if $\pi[i]>\pi[i+1]$ is a RLMax
+\item $\pi[i]$ is a \RLMin element if and only if $\pi[i]<\pi[i+1]$
+\item $\pi[i]$ is a \RLMax element if and only if $\pi[i]>\pi[i+1]$ is a \RLMax
 \end{enumerate}
@@
 The base case is a pattern of size $2$.
-Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = RLMin$.
+Suppose that $\sigma = 12$ and thus $\bijection(\sigma) = \RLMin$.
 Let $t = \pi_{i_1}\pi_{i_2}$, $i_1 < i_2$, be a subsequence of $\pi$
-such that $\bijection(t) = RLMin$, this reduces to saying that
+such that $\bijection(t) = \RLMin$, this reduces to saying that
 $\pi_{i_1} < \pi_{i_2}$,
@@
 We need to consider a specific decomposition of $\sigma$ into \textit{factors}:
-we split the permutation into maximal sequences of consecutive RLMin and RLMax elements, respectively called a RLMin factor and a RLMax factor.
-This corresponds to splitting the permutation between every pair of RLMin-RLMax and RLMax-RLMin elements (see Figure \ref{fig:shape of the permutation plus factor}).
+we split the permutation into maximal sequences of consecutive \RLMin and \RLMax elements, respectively called a \RLMin factor and a \RLMax factor.
+This corresponds to splitting the permutation between every pair of \RLMin-\RLMax and \RLMax-\RLMin elements (see Figure \ref{fig:shape of the permutation plus factor}).
 For the special case of a wedge permutation, this also corresponds to split the permutation into maximal sequences of elements consecutive in value.
 We label the factors from right to left.
-Note that the rightmost element can be both a RLMin or a RLMax,
+Note that the rightmost element can be both a \RLMin or a \RLMax,
 we take the convention that it is as the same type as the element before it for the factorization,
@@
 A rectangle contains
-an occurrence of a RLMin (resp. RLMax) factor if and only if
+an occurrence of a \RLMin (resp. \RLMax) factor if and only if
 the rectangle contains an increasing (resp. decreasing) subsequence
@@
 we ask for the occurrences that start at $\pi[j]$.
-As any element in the pattern is a RLMax or a RLMin,
+As any element in the pattern is a \RLMax or a \RLMin,
 the value of $\pi[j]$ can be used has a top or a bottom edge
@@
 Informally,
-given that the leftmost factor is a RLMin (resp. RLMax) factor and
+given that the leftmost factor is a \RLMin (resp. \RLMax) factor and
 given that the left top (resp. bottom left) corner of the second rectangle is fixed and
@@
 Given a wedge permutation $\sigma$,
-if $\factor(i)$ is a RLMin (resp. RLMax) factor
+if $\factor(i)$ is a \RLMin (resp. \RLMax) factor
 the topmost (resp. bottommost) element of
@@
 This corollary states that, given a wedge permutation
-if the permutation starts with a RLMin (resp.
-RLMax) element then the topmost (resp.
-bottommost) element of this permutation is the first RLMax (resp.
-RLMin) element (see Figure \ref{fig:where to find the max}).
+if the permutation starts with a \RLMin (resp.
+\RLMax) element then the topmost (resp.
+bottommost) element of this permutation is the first \RLMax (resp.
+\RLMin) element (see Figure \ref{fig:where to find the max}).
 This is easy to see from the shape of a wedge permutation.
-Formally, the RLMin elements are below the RLMax element, thus the topmost element must be
-the first RLMax element, which is the leftmost element of $\factor(i-1)$.
+Formally, the \RLMin elements are below the \RLMax element, thus the topmost element must be
+the first \RLMax element, which is the leftmost element of $\factor(i-1)$.
 \qed
@@
 Let $\ppattern$ be a wedge permutation and
-$\factor(i)$ be an RLMin (resp. RLMax) factor $\sigma$.
+$\factor(i)$ be an \RLMin (resp. \RLMax) factor $\sigma$.
 Let $\pi$ be a permutation and $s$ a subsequence of $\pi$ such that
@@
 More formally, given any occurrence of $\factor(i+1)$ $\factor(i)$ $\ldots$ $\factor(1)$,
-where $\factor(i)$ is a RLMin (resp. RLMax) factor,
+where $\factor(i)$ is a \RLMin (resp. \RLMax) factor,
 we can replace the part of the occurrence where $\factor(i)$ $\ldots$ $\factor(1)$ occurs, by any occurrence
@@
 \begin{proof} %[of Lemma~\ref{lemma:ts}]
-Let us consider the case where $\factor(i)$ is a RLMin factor.
+Let us consider the case where $\factor(i)$ is a \RLMin factor.
 By definition $s$ is an occurrence of $\ppattern[\LMEi(\factor(i)):]$.
@@
 Moreover the topmost element of $s$ is below (or equal to) the topmost element of $s'$ thus the elements of $s$ are below the elements of $t'$.
-We use a symmetric argument if $\factor(i)$ is a RLMax factor.
+We use a symmetric argument if $\factor(i)$ is a \RLMax factor.
 \qed
@@
 Let $\ppattern$ be a permutation,
-$\factor(i)$ be a RLMin (resp. RLMax) factor
+$\factor(i)$ be a \RLMin (resp. \RLMax) factor
 and
@@
 but instead of return true or false,
-assuming that $\factor(i)$ is a RLMin (resp. RLMax) factor
+assuming that $\factor(i)$ is a \RLMin (resp. \RLMax) factor
 the algorithm return the value of the
@@
 
-Given a RLMin (resp. RLMax) factor $\factor(i)$  of $\sigma$ and a position $j$ in $\pi$,
+Given a \RLMin (resp. \RLMax) factor $\factor(i)$  of $\sigma$ and a position $j$ in $\pi$,
 we want the value of the top (resp. bottom) edge
@@
 \begin{itemize}
-\item If $\factor(i)$ is RLMin factor.
+\item If $\factor(i)$ is \RLMin factor.
 
@@
 
-\item If $\factor(i)$ is RLMax factor.
+\item If $\factor(i)$ is \RLMax factor.
 $$
@@
 \begin{itemize}
-\item If the permutation is reduced to a RLMin (resp. RLMax) factor
+\item If the permutation is reduced to a \RLMin (resp. \RLMax) factor
 then one has to decide the top (resp. lower ) edge of
@@
 \begin{itemize}
-\item If $\factor(i)$ is RLMin factor.
+\item If $\factor(i)$ is \RLMin factor.
 $$
@@
 
-\item Otherwise, if $\factor(i)$ is a RLMin (resp. RLMax) factor,
+\item Otherwise, if $\factor(i)$ is a \RLMin (resp. \RLMax) factor,
  we split the rectangle into two rectangles $R_1$ and
@@
 
-\item If $\factor(i)$ is RLMin factor:\\
+\item If $\factor(i)$ is \RLMin factor:\\
 $$
@@
 
-\item If $\factor(i)$ is RLMax factor:\\
+\item If $\factor(i)$ is \RLMax factor:\\
 $$
@@
 \begin{itemize}
-\item If $\sigma[i]$ is a RLMin element and is not the rightmost element, then $\sigma[i]+1$ is to the right of $\sigma[i]$.
-\item If $\sigma[i]$ is a RLMax element and is not the rightmost element, then $\sigma[i]-1$ is to the right of $\sigma[i]$.
+\item If $\sigma[i]$ is a \RLMin element and is not the rightmost element, then $\sigma[i]+1$ is to the right of $\sigma[i]$.
+\item If $\sigma[i]$ is a \RLMax element and is not the rightmost element, then $\sigma[i]-1$ is to the right of $\sigma[i]$.
 \end{itemize}
@@
 \begin{itemize}
-\item If $m$ and $m+1$ are both RLMin elements
+\item If $m$ and $m+1$ are both \RLMin elements
 then any element between $m$ and $m+1$ (if any)
-is a RLMax element.
+is a \RLMax element.
 \item If $m$ and $m-1$ are both RLmax elements
 then any element between $m$ and $m-1$ (if any)
-is a RLMin element.
+is a \RLMin element.
 \end{itemize}
@@
 and suppose that there exists $\alpha < \gamma < \beta$,
-such that $\sigma[\gamma]$ is a RLMin element.
-We know that RLMin are strictly increasing so
+such that $\sigma[\gamma]$ is a \RLMin element.
+We know that \RLMin are strictly increasing so
 $\sigma[\alpha] <  \sigma[\gamma] < \sigma[\beta]$,
@@
 Informally, to find an occurrence of $\widetilde{\sigma}[i:]$ in $\pi[j:]$,
-given that $\sigma[i]$ is a RLMin element,
+given that $\sigma[i]$ is a \RLMin element,
 we need to find a rectangle $R$ in $\pi$
@@
 the bottom edge, the top edge and the left edge of the rectangle $R$.
-The case where $\sigma[i]$ is a RLMax element can be dealt with symmetry.
+The case where $\sigma[i]$ is a \RLMax element can be dealt with symmetry.
 More formally:
@@
 
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a RLMin element then:
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a \RLMin element then:
 	$$
@@
 
-	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a RLMax element then:
+	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a \RLMax element then:
 
@@
 $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$.
-Especially in the case where $\sigma[i]$ is a RLMin
+Especially in the case where $\sigma[i]$ is a \RLMin
 the case where $\underline{\sigma[i-1]\sigma[i]}$,
@@
 In the same fashion,
-when $\sigma[i]$ is a RLMax $\underline{\sigma[i-1]\sigma[i]}$
+when $\sigma[i]$ is a \RLMax $\underline{\sigma[i-1]\sigma[i]}$
 do not appear in the conditions for the exact same reason
@@
 
-		\item If $\sigma[i]$ is a RLMin element, then remark that:
+		\item If $\sigma[i]$ is a \RLMin element, then remark that:
 		\begin{itemize}
@@
 			do not change the lower bound as
-			$\sigma[i]$ is the leftmost RLMin element.
-Indeed if not, then there exists a RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
-			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
+			$\sigma[i]$ is the leftmost \RLMin element.
+Indeed if not, then there exists a \RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
+			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are \RLMax elements. Finally the recursive calls for \RLMax elements do not change the lower bound.
 			\item The first call of the problem has for parameter $\lb=1$.
@@
 
-		\item If $\sigma[i]$ is a RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element).
+		\item If $\sigma[i]$ is a \RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element).
 Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true only if $\sigma[i]$ is matched to $1$.
@@
 
-		\item If $\sigma[i]$ is a RLMax element, then remark that:
+		\item If $\sigma[i]$ is a \RLMax element, then remark that:
 		\begin{itemize}
@@
 			do not change the upper bound as
-			$\sigma[i]$ is the leftmost RLMax element.
-Indeed if not, then there exists a RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
-			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
+			$\sigma[i]$ is the leftmost \RLMax element.
+Indeed if not, then there exists a \RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
+			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are \RLMin elements. Finally the recursive calls for \RLMin elements do not change the upper bound.
 			\item The first call of the problem has for parameter $\ub=n$.
@@
 
-		\item If $\sigma[i]$ is a RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element).
+		\item If $\sigma[i]$ is a \RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element).
 Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n$.
@@
 
-			\item The cases $\ppattern[i]$ is a RLMax element, $\ppattern[i']$ is a RLMin element and $i<i'$ or  $\ppattern[i]$ is a RLMin element, $\ppattern[i']$ is a RLMax element and $i'<i$ are not possible.
+			\item The cases $\ppattern[i]$ is a \RLMax element, $\ppattern[i']$ is a \RLMin element and $i<i'$ or  $\ppattern[i]$ is a \RLMin element, $\ppattern[i']$ is a \RLMax element and $i'<i$ are not possible.
 			Indeed $\ppattern[i]$ is the topmost element of $\ppattern[i:]$ thus $\ppattern[i] > \ppattern[i']$ which is in contradiction with
@@
 
-			\item If $\ppattern[i]$ is a RLMin element, $\ppattern[i']$ is a RLMax element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a RLMax element, $\ppattern[i']$ is a RLMin element and $i'<i$), then
+			\item If $\ppattern[i]$ is a \RLMin element, $\ppattern[i']$ is a \RLMax element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a \RLMax element, $\ppattern[i']$ is a \RLMin element and $i'<i$), then
 			remark that
@@
 				\item The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound.
-				Indeed $\ppattern[i]$ is the rightmost RLMin.
-				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are RLMax elements. Moreover
-				recursive calls for a RLMax do not change the lower bound.
+				Indeed $\ppattern[i]$ is the rightmost \RLMin.
+				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are \RLMax elements. Moreover
+				recursive calls for a \RLMax do not change the lower bound.
 				\item $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ sets
@@
 
-			\item If $\ppattern[i]$ is a RLMin element and $\ppattern[i']$ is a RLMin element then
+			\item If $\ppattern[i]$ is a \RLMin element and $\ppattern[i']$ is a \RLMin element then
 			first remark:
@@
 				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. Indeed
-				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
+				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are \RLMax elements. Finally the recursive calls for \RLMax elements do not change the lower bound.
 
@@
 
-			\item If $\ppattern[i]$ is a RLMax element and $\ppattern[i']$ is a RLMax element then
+			\item If $\ppattern[i]$ is a \RLMax element and $\ppattern[i']$ is a \RLMax element then
 			first remark:
@@
 				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the upper bound. Indeed
-				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
+				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are \RLMin elements. Finally the recursive calls for \RLMin elements do not change the upper bound.
 
@@
 We start with the easiest case where we are given just one input permutation.
-We need the set of RLMax elements and the set of RLMin elements.
-$A(\pi) = \{i | \text{$\pi[i]$ is a RLMin element} \} \cup \{n\}$ and
-$D(\pi) = \{i | \text{$\pi[i]$ is a RLMax element} \} \cup \{n\}$.\\
+We need the set of \RLMax elements and the set of \RLMin elements.
+$A(\pi) = \{i | \text{$\pi[i]$ is a \RLMin element} \} \cup \{n\}$ and
+$D(\pi) = \{i | \text{$\pi[i]$ is a \RLMax element} \} \cup \{n\}$.\\
 
@@
 meaning that if we consider the current elements
-to correspond to a RLMin (resp. RLMax) element in the longest wedge subsequence
+to correspond to a \RLMin (resp. \RLMax) element in the longest wedge subsequence
 then we consider only the solution with elements above (below)

### 2016-10-14 article.tex
a

--- 2016-10-12 article.tex
@@
 For the special case where only $\sigma$ avoids $213$ and $231$, we present a
-$O(max(kn^2,n^2\log \log n)$-time algorithm.
+$O(max(kn^2,n^2\log(\log(n)))$-time algorithm. 
 We extend our research to bivincular patterns that avoid $213$ and $231$ and present a $O(kn^4)$-time algorithm.
@@
 
-A permutation $\sigma$ is said to \emph{occur} in another permutation $\pi$
-(or $\pi$ \emph{contains} $\sigma$),
+A permutation $\sigma$ is said to occur in another permutation $\pi$,
 denoted $\sigma \preceq \pi$,
@@
 Otherwise, $\pi$ is said to \emph{avoid} the permutation $\sigma$.
-For example a permutation contains the permutation $123$ (resp. $321$) if
-it has an increasing (resp. a decreasing) subsequence of size $3$.
+For example the permutation $123$ (resp. $321$) occurs in a second permutation if
+the second permutation has an increasing (resp. a decreasing) subsequence of size $3$.
 Similarly, $213$ occurs in $6152347$, but $231$ does not occurs in $6152347$.
@@
 order as $\sigma$.  
-Guillemot and Marx \cite{Guillemot:Marx:SODA:2014} showed that the permutation pattern matching problem
-is solvable in $2^{O(k^2 \log k)}$, and hence is fixed-parameter tractable with respect to the length $k$
-of the pattern $\sigma$ (standard parameterization).
-However, Mach proved that the permutation containment problem under the
-standard parameterization does not have a polynomial size kernel (assuming $\NPclass \not\subseteq \coNPclass / \POLY$
-\cite{Mach:thesis:1992}.
+A recent major step was taken by Marx and Guillemot
+\cite{Guillemot:Marx:SODA:2014}.
+They showed that
+the permutation pattern matching is fixed-parameter tractable (FPT) for by the size of $\sigma$.
 
 A few particular cases of the permutation pattern matching problem have been attacked successfully.
-The case of  increasing patterns is solvable in
-$O(n \log \log k)$-time \cite{Crochemore:Porat:2010},
+The case of any increasing pattern is solvable in 
+$O(n \log \log k)$ time in the RAM model \cite{Crochemore:Porat:2010},
 improving the previous 30-year bound of $O(n \log k)$.
@@
 polynomial-time for separable patterns \cite{Ibarra:1997,Bose:Buss:Lubiw:1998}
-(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for the longest common subsequence problem and
-related ones on separable permutations).
+(see also \cite{Bouvel:Rossin:Vialette:CPM:2007} for the longest common subsequence problem and related ones on separable permutations).
 Separable permutations are permutations that do not have an occurrence of
@@
 stack-sortable permutations, which avoid the pattern $231$.)
-The major negative result is given in \cite{DBLP:journals/corr/JelinekK16}.
-They prove that
-the permutation pattern matching problem is \NPC
-when $\sigma$ has no decreasing subsequence of length $3$ and
-$\pi$ has no decreasing subsequence of length $4$.
-This provides the first known example of the permutation pattern matching problem
-being hard when one or both of $\pi$ and $\sigma$ are restricted to a proper hereditary
-class of permutations.
 
@@
 	\item
-	If the bottom line of $\sigma$ contains
+	If the bottom line of $\widetilde{\sigma}$ contains
 	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
@@
 	non-underlined consecutive elements.
-	Moreover if the bottom row of $\sigma$ begins with
-	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$
+	Moreover if the bottom row of $\widetilde{\sigma}$ begins with
+	$_\llcorner{\sigma_1}$ then any occurrence of $\widetilde{\sigma}$
 	in a permutation $\pi$ must begin with the leftmost
@@
 	if the bottom row of $\sigma$ ends with
-	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$
+	${\sigma_k}_\lrcorner$ then any occurrence of $\widetilde{\sigma}$
 	in a permutation $\pi$ must end with the rightmost
@@
 	\item
-	If the top line of $\sigma$ contains
+	If the top line of $\widetilde{\sigma}$ contains
 	$\overline{i\,i+1\,\ldots\,j}$ then the elements corresponding to
@@
 	elements.
-	Moreover, if the top row of $\sigma$ begins with
+	Moreover, if the top row of $\widetilde{\sigma}$ begins with
 	$^\ulcorner{1}$ then
-	any occurrence of $\sigma$ in a permutation $\pi$ must contain
+	any occurrence of $\widetilde{\sigma}$ in a permutation $\pi$ must contain 
 	the bottommost element of $\pi$, and
 	if top row of $\sigma$ ends with $k^\urcorner$ then
-	any occurrence of $\sigma$ in a permutation $\pi$ must contain
+	any occurrence of $\widetilde{\sigma}$ in a permutation $\pi$ must contain
 	the topmost element of $\pi$.
@@
 
-As a consequence, every element of a wedge permutation can be partitioned
+As a consequence, a wedge permutation can be partitioned 
 into three sets: the set of RLMax elements, the set of RLMin elements and the 
 rightmost element which can be both a RLMax element and a RLMin element. 
+The partition gives a bijection between the set of wedge permutations of size $n$ with elements $1,\ldots,n$
+and the set of binary words of size $n-1$.
+The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$ 
+represents whether $\pi[i]$ is a RLMax element or a RLMin element.
+We call this bijection $\bijection$.
 
@@
 \begin{remark}
-Every element of the set of RLMax elements is above the elements
-of the set of the RLMin elements.
-In other words, a wedge permutations
-can be cut in half horizontally on the rightmost element such that the upper half contains a decreasing
-subsequence and the lower half contains an increasing subsequence.
+We can draw a horizontally line (passing thought the rightmost element) on a wedge permutations  such that the upper half contains only a  decreasing  
+subsequence and the lower half contains only an increasing subsequence.
 This shape the permutation as a $>$, 
@@
 
-\begin{remark}
-The partition gives a bijection between the set of wedge permutations of size $n$ where the elements are $1,\ldots,n$
-and the set of binary word of size $n-1$.
-The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$
-represents whether $\pi[i]$ is a RLMax element or a RLMin element.
-We call this bijection $\bijection$.
-\end{remark}
-
-To figure out whether or not an element is a RLMax element or a RLMin element,
+For any permutation, to figure out whether or not an element is a RLMax element or a RLMin element,
 one has to run the whole permutation from left to right starting 
-from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time.
+from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time for a wedge permutation.
 
@@
 \item $\pi[i]$ is a RLMin element if and only if $\pi[i]<\pi[i+1]$
-\item $\pi[i]$ is a RLMax element if and only if $\pi[i]>\pi[i+1]$ is a RLMax
+\item $\pi[i]$ is a RLMax element if and only if $\pi[i]>\pi[i+1]$
 \end{enumerate}
@@
 with every element of the occurrence is in $[\lb,\ub]$
-and starting at $\pi[j]$.
+and starting at $\pi[j]$,
 In other words given the rectangle with bottom left edge
@@
 $$
-\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
+\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j)=
 $$
@@
 then $\pi$ contains an occurrence of $\widetilde{\sigma}$ 
-if and only if $\bigcup_{0<j} \PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{j}$ is true.
+if and only if $\bigcup_{0<j} \PM^{\widetilde{\sigma}}_{\ptext}(1,n,1,j)$ is true.
 If $_\llcorner{\sigma[1]}$ appear in $\sigma$ then 
@@
 the bivincular wedge permutation pattern $\sigma$ 
-if and only if $\PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{1}$.
+if and only if $\PM^{\widetilde{\sigma}}_{\ptext}(1,n,1,1)$.
 
@@
 $$
-\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{k}{j}=
+\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,k,j)=
 \begin{cases}
@@
 The base case finds an occurrence for the rightmost element of the pattern.
-If the rightmost element does not have any restriction on positions and on values, then $\PM{\sigma}{\ptext}{\lb}{\ub}{k}{j}$ is true if and only if $\ppattern[k]$ is matched to $\ptext[j]$.
+If the rightmost element does not have any restriction on positions and on values, then $\PM^{\sigma}_{\ptext}{\lb}(\ub,k,j)$ is true if and only if $\ppattern[k]$ is matched to $\ptext[j]$.
 This is true if $\ptext[j] \in [\lb,\ub]$.
@@
 represent the disjunction.
-We consider 3 cases for the problem $\PM{ \widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}$:
+We consider 3 cases for the problem $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j)$:
 \begin{itemize}
@@
 	$$
-	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j} = false
+	\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j) = false
 	$$
@@
 	$$
-	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
+	\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j)=
 	\begin{cases}
-		\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
+		\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,\ell)
 			& \text{if $\ppattern[i]$ is not underlined } \\
 			& \text{ and $\ppattern[i]$ is not overlined} \\
-		\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
+		\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,\ell)
 			& \text{if $\ppattern[i]$ is not underlined } \\
@@
 			& \text{ and $\ptext[j]=\lb$} \\
-		\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
+		\PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,j+1)
 			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
@@
 			& \text{ and $\ppattern[i]$ is not overlined} \\			
-		\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
+		\PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,j+1)
 			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
@@
  	 if there exists $\ell$, $j<\ell$ such that
-	$\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}$ is true.
+	$\PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,\ell)$ is true.
 	The first case corresponds to an occurrence without restriction on position and on value. 
@@
 	$$
-	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
+	\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j)=
 	\begin{cases}
-			\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
+			\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,\ell)
 				& \text{if $\ppattern[i]$ is not underlined } \\
 				& \text{ and $\ppattern[i]$ is not overlined} \\
-			\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
+			\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,\ell)
 				& \text{if $\ppattern[i]$ is not underlined } \\
@@
 				& \text{ and $\ptext[j]=\ub$} \\
-			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+			\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,j+1)
 				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
@@
 				& \text{ and $\ppattern[i]$ is not overlined} \\				
-			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+			\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,j+1)
 				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
@@
 Remark that there are constraints that we do not concern given in
-$\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$.
+$\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$.
 Especially in the case where $\sigma[i]$ is a RLMin
@@
 in the conditions because it is
-up to $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i-1}{*}$
+up to $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i-1,*)$
 to ensure that the elements corresponding to elements at position $i-1$ and $i$ in an occurrence are next to each other in position.
@@
 be taken care
-during the calls of $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$
+during the calls of $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i',*)$
 for some $i<i'$.
@@
 	\item If $_\llcorner{\sigma[1]}$ appears in $\widetilde{\sigma}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ in a occurrence of $\ppattern$ in $\ptext$).
-This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{1}$ is true.
+This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM^{\widetilde{\sigma}}_{\ptext}(1,n,1,1)$ is true.
 
@@
 			\item Every problem 
-			$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion).
+			$\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion).
 			So it is enough to require that $\lb=1$.
@@
 		\end{itemize} 
-		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if
+		So $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ return true only if 
 		$\sigma[i]$ is matched to $1$.
@@
 		\item If $\sigma[i]$ is a RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true only if $\sigma[i]$ is matched to $1$.
+Thus every $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ is a base case and is true only if $\sigma[i]$ is matched to $1$.
 
@@
 			\item Every problem 
-			$\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$ (by recursion).
+			$\PM^{\widetilde{\sigma}}_{\ptext}(*,\ub,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\ub$ (by recursion).
 			So it is enough to require that $\ub=n$.
@@
 		\end{itemize} 
-		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if
+		So $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ return true only if 
 		$\sigma[i]$ is matched to $n$.
@@
 		\item If $\sigma[i]$ is a RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n$.
+Thus every $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ is a base case and is true if $\sigma[i]$ is matched to $n$.
 
@@
 				$\sigma[i]$ and $\sigma[i']$. So every recursive call
-				$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$
-				is solved as a base case. So $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
+				$\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$
+				is solved as a base case. So $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
 				\item The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. 
@@
 				recursive calls for a RLMax do not change the lower bound.
-				\item $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ sets
+				\item $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i,*)$ sets
 				the $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
@@
 
-				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.
+				\item  Every recursive call $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.
 
@@
 
-				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
+				\item $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
 
@@
 
-				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.
+				\item  Every recursive call $\PM^{\widetilde{\sigma}}_{\ptext}(*,\ub,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.
 
@@
 
-				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.
+				\item $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i',*)$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.
 

### 2016-10-14 article.tex

--- 2016-10-13 article.tex
@@
 
+As a consequence, a wedge permutation can be partitioned 
+into three sets: the set of RLMax elements, the set of RLMin elements and the 
+rightmost element which can be both a RLMax element and a RLMin element. 
+The partition gives a bijection between the set of wedge permutations of size $n$ with elements $1,\ldots,n$
+and the set of binary words of size $n-1$.
+The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$ 
+represents whether $\pi[i]$ is a RLMax element or a RLMin element.
+We call this bijection $\bijection$.
+
 As a consequence, every element of a wedge permutation can be partitioned
@@
 \begin{remark}
-Every element of the set of \RLMax elements is above the elements
-of the set of the \RLMin elements.
-In other words, a wedge permutations
-can be cut in half horizontally on the rightmost element such that the upper half contains a decreasing
-subsequence and the lower half contains an increasing subsequence.
+We can draw a horizontally line (passing thought the rightmost element) on a wedge permutations  such that the upper half contains only a  decreasing  
+subsequence and the lower half contains only an increasing subsequence.
 This shape the permutation as a $>$, 
@@
 
-\begin{remark}
-The partition gives a bijection between the set of wedge permutations of size $n$ where the elements are $1,\ldots,n$
-and the set of binary word of size $n-1$.
-The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$
-represents whether $\pi[i]$ is a \RLMax element or a \RLMin element.
-We call this bijection $\bijection$.
-\end{remark}
-
-To figure out whether or not an element is a \RLMax element or a \RLMin element,
+For any permutation, to figure out whether or not an element is a RLMax element or a RLMin element,
 one has to run the whole permutation from left to right starting 
-from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time.
+from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time for a wedge permutation.
 
@@
 \begin{enumerate}
-\item $\pi[i]$ is a \RLMin element if and only if $\pi[i]<\pi[i+1]$
-\item $\pi[i]$ is a \RLMax element if and only if $\pi[i]>\pi[i+1]$ is a \RLMax
+\item $\pi[i]$ is a RLMin element if and only if $\pi[i]<\pi[i+1]$
+\item $\pi[i]$ is a RLMax element if and only if $\pi[i]>\pi[i+1]$
 \end{enumerate}
@@
 				& \text{ and $\ppattern[i]$ is not overlined} \\				
-			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
+			\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,j+1)
+
 				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
@@
 Remark that there are constraints that we do not concern given in
-$\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$.
+$\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$.
 Especially in the case where $\sigma[i]$ is a \RLMin
@@
 \paragraph{Position Constraint.} There are 3 types of position constraints that can be added by underlined elements.
+
 \begin{itemize} 
 	\item If $_\llcorner{\sigma[1]}$ appears in $\widetilde{\sigma}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ in a occurrence of $\ppattern$ in $\ptext$).
-This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{1}$ is true.
-
+This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM^{\widetilde{\sigma}}_{\ptext}(1,n,1,1)$ is true.
 	\item If ${\ppattern[k]}_\lrcorner$ appears in $\widetilde{\sigma}$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a occurrence of $\ppattern$ in $\ptext$).
@@
 			do not change the lower bound as
-			$\sigma[i]$ is the leftmost \RLMin element.
-Indeed if not, then there exists a \RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
-			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are \RLMax elements. Finally the recursive calls for \RLMax elements do not change the lower bound.
+			$\sigma[i]$ is the leftmost RLMin element.
+Indeed if not, then there exists a RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
+			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
 			\item The first call of the problem has for parameter $\lb=1$. 
 		\end{itemize} 
-		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if
+		So $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ return true only if 
 		$\sigma[i]$ is matched to $1$.
 
-		\item If $\sigma[i]$ is a \RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true only if $\sigma[i]$ is matched to $1$.
+		\item If $\sigma[i]$ is a RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element).
+Thus every $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ is a base case and is true only if $\sigma[i]$ is matched to $1$.
 
@@
 			do not change the upper bound as
-			$\sigma[i]$ is the leftmost \RLMax element.
-Indeed if not, then there exists a \RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
-			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are \RLMin elements. Finally the recursive calls for \RLMin elements do not change the upper bound.
+			$\sigma[i]$ is the leftmost RLMax element.
+Indeed if not, then there exists a RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
+			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
 			\item The first call of the problem has for parameter $\ub=n$. 
 		\end{itemize} 
-		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if
+		So $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ return true only if 
 		$\sigma[i]$ is matched to $n$.
 
-		\item If $\sigma[i]$ is a \RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element).
-Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n$.
+		\item If $\sigma[i]$ is a RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element).
+Thus every $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ is a base case and is true if $\sigma[i]$ is matched to $n$.
 
@@
 				$\sigma[i]$ and $\sigma[i']$. So every recursive call
-				$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$
-				is solved as a base case. So $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
+				$\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$
+				is solved as a base case. So $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
 				\item The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. 
-				Indeed $\ppattern[i]$ is the rightmost \RLMin.
-				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are \RLMax elements. Moreover
-				recursive calls for a \RLMax do not change the lower bound.
-				\item $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ sets
+				Indeed $\ppattern[i]$ is the rightmost RLMin.
+				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are RLMax elements. Moreover
+				recursive calls for a RLMax do not change the lower bound.
+				\item $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i,*)$ sets
 				the $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
@@
 
-				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.
+				\item  Every recursive call $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.
 
 				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. Indeed
-				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are \RLMax elements. Finally the recursive calls for \RLMax elements do not change the lower bound.
-
-				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
+				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
+
+				\item $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
 
@@
 
-				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.
+				\item  Every recursive call $\PM^{\widetilde{\sigma}}_{\ptext}(*,\ub,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.
 
 				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the upper bound. Indeed
-				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are \RLMin elements. Finally the recursive calls for \RLMin elements do not change the upper bound.
-
-				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.
+				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
+
+				\item $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i',*)$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.
 

### 2016-10-14 article.tex
revision
probleme d indice

@@
 
-\newcommand{\RLMin}{\text{RLMin}}
-\newcommand{\RLMax}{\text{RLMax}}
+\newcommand{\RLMin}{\text{RLMin}\xspace}
+\newcommand{\RLMax}{\text{RLMax}\xspace}
 
@@
 The base case finds an occurrence for the rightmost element of the pattern.
-If the rightmost element does not have any restriction on positions and on values, then $\PM^{\sigma}_{\ptext}{\lb}(\ub,k,j)$ is true if and only if $\ppattern[k]$ is matched to $\ptext[j]$.
+If the rightmost element does not have any restriction on positions and on values, then $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,k,j)$ is true if and only if $\ppattern[k]$ is matched to $\ptext[j]$.
 This is true if $\ptext[j] \in [\lb,\ub]$.
